### 2015-01-22 tmm.tex
initial commit adapted from submission of tcsvt

%% tmm.tex
%% by Shengbin Meng

% Note that the a4paper option is mainly intended so that authors in
% countries using A4 can easily print to A4 and see how their papers will
% look in print - the typesetting of the document will not typically be
% affected with changes in paper size (but the bottom and side margins will).
% Use the testflow package mentioned above to verify correct handling of
% both paper sizes by the user's LaTeX system.
%
% Also note that the "draftcls" or "draftclsnofoot", not "draft", option 
% should be used if it is desired that the figures are to be displayed in
% draft mode.
%
%\documentclass[journal,draftclsnofoot,onecolumn]{IEEEtran}
\documentclass[journal]{IEEEtran}
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[journal]{../sty/IEEEtran}

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
   \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
   \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
   \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
   \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation
% can be obtained at: 
% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found at:
% http://www.ctan.org/tex-archive/info/epslatex/
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

% *** MATH PACKAGES ***
%
\usepackage[cmex10]{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics. If using
% it, be sure to load this package with the cmex10 option to ensure that
% only type 1 fonts will utilized at all point sizes. Without this option,
% it is possible that some math symbols, particularly those within
% footnotes, will be rendered in bitmap form which will result in a
% document that can not be IEEE Xplore compliant!
%
% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/

% *** ALIGNMENT PACKAGES ***
%
\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/tools/

% *** SPECIALIZED LIST PACKAGES ***
%
\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
% There is also a support site at:
% http://algorithms.berlios.de/index.html
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/url/
% Basically, \url{my_url_here}.

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

% added by shengbin
\usepackage{verbatim}
\usepackage{multirow}
\usepackage{subfig}
\usepackage{algorithm}

% paper title
% can use linebreaks \\ within to get better formatting as desired
% Do not put math or special symbols in the title.
\title{Scalable Video Streaming with PID-Based Quality Control and Optimized Bitstream Extraction}

% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%
\author{Shengbin~Meng,~Jun~Sun,~Yizhou~Duan~and~Zongming~Guo % <-this % stops a space
\thanks{S. Meng is with the Institute of Computer Science and Technology, Peking University, Beijing%
, 100080 China e-mail: shengbin@pku.edu.cn.}% <-this % stops a space
\thanks{J. Sun, Y. Duan, Z. Guo are with the Institute of Computer Science and Technology, Peking University.}% <-this % stops a space
\thanks{Manuscript received September 15, 2014}}

% note the % following the last \IEEEmembership and also \thanks - 
% these prevent an unwanted space from occurring between the last author name
% and the end of the author line. i.e., if you had this:
% 
% \author{....lastname \thanks{...} \thanks{...} }
%                     ^------------^------------^----Do not want these spaces!
%
% a space would be appended to the last name and could cause every name on that
% line to be shifted left slightly. This is one of those "LaTeX things". For
% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get
% "AB" then you have to do: "\textbf{A}\textbf{B}"
% \thanks is no different in this regard, so shield the last } of each \thanks
% that ends a line with a % and do not let a space in before the next \thanks.
% Spaces after \IEEEmembership other than the last one are OK (and needed) as
% you are supposed to have spaces between the names. For what it is worth,
% this is a minor point as most people would not even notice if the said evil
% space somehow managed to creep in.

% The paper headers
%\markboth{IEEE TRANSACTIONS ON CIRCUITS AND SYSTEMS FOR VIDEO TECHNOLOGY,~Vol.~11, No.~4, December~2013}%
%{Shengbin Meng \MakeLowercase{\textit{et al.}}: Efficient H.264/SVC Bitstream Extraction Based on a Linear Error Model}
% The only time the second header will appear is for the odd numbered pages
% after the title page when using the twoside option.
% 
% *** Note that you probably will NOT want to include the author's ***
% *** name in the headers of peer review papers.                   ***
% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
% you desire.

% If you want to put a publisher's ID mark on the page you can do it like
% this:
%\IEEEpubid{0000--0000/00\$00.00~\copyright~2012 IEEE}
% Remember, if you use this you must call \IEEEpubidadjcol in the second
% column for its text to clear the IEEEpubid mark.

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

\begin{document}

\listoffigures

\listoftables

% make the title area
\maketitle

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
In order to meet the challenge brought by bandwidth fluctuation of the user's network, modern video streaming systems tend to be scalable, i.e., of flexible bitrate and adaptive video quality. This paper gives solutions for two key problems within such a scalable video streaming system. We first propose a quality control algorithm, which allows the video streaming system to adjust its video quality along with the real bandwidth change. The algorithm is based on the Proportional-Integral-Derivative (PID) control method and can deliver best video quality with least quality fluctuation. Then for streaming systems that adopt Scalable Video Coding (SVC), we present an efficient solution for the bitstream extraction problem, which aims to select an optimal sub-stream from the whole bitstream under given bitrate constraint. This solution features a linear error model, which is utilized to estimate the distortion caused by discarding any combination of data packets, and a greedy algorithm scheme, which assigns each data packet a priority value to use for the R-D optimized extraction. Experimental results show that our quality control algorithm can drastically reduce the quality fluctuation while still keeping a high quality level, and the bitstream extraction method can achieve a significant PSNR gain compared to the extractors of JSVM, without computational complexity increment. The quality control algorithm has also been implemented in online video website www.7dlive.com and turns out to be practically effective in applications.
\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
video streaming, quality control, bitstream extraction, distortion model, Scalable Video Coding, PID.
\end{IEEEkeywords}

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\section{Introduction}
\label{sec:intro}
% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps.
% 
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
% 
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by IEEE):
% \IEEEPARstart{A}{}demo file is ....
% 
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
% 
\IEEEPARstart{V}{ideo} streaming applications are becoming more and more popular on the Internet. Examples of the most common usage scenarios include VOD (Video On Demand), live broadcasting, video-based online education, and so on. In these applications, video data is constantly delivered to different clients over various transmission channels, and the client media player can begin playing the video before the entire file has been transmitted. Among other features, video streaming makes it easy to watch video anywhere and anytime, and is an increasingly important way for people to consume video content.

One of the biggest challenge for video streaming is the variety of users' network environment. The users may use various types of network (Ethernet, Wi-Fi, Cellular, etc) and may also switch to a different one on going (e.g., from Wi-Fi to cellular network). Even in the same network, a user's available bandwidth may change from time to time, influenced by the overall traffic. During such an environment, bandwidth fluctuation is inevitable. If the video is streamed at a constant bitrate, it would be difficult or impossible for the client to keep a non-paused smooth playing. Therefore, to achieve better watching experience for users with various network environments, we should be able to adjust the video's bitrate or quality according to the bandwidth change. In other words, the video streaming system needs to be scalable.

There are two options to enable scalable video streaming. The first option is called simulcast, where several independent bitstreams are stored at the server side, and the client selects one of them according to its current bandwidth. Dynamic Adaptive Streaming over HTTP (DASH) \cite{DASH}, which is standardized by MPEG, mostly uses this option. Simulcast systems like DASH can provide some scalability and is relatively easy to deploy. However, the scalability it provides is limited to the number of streams, and the processing and storage of multiple streams significantly increase time and space cost. On the contrary, the second option, which is to adopt Scalable Video Coding (SVC) \cite{SVC}, does not have above shortcomings. Compared to simulcast, SVC provides seamless scalability and higher coding efficiency, thus is a better choice to build a scalable video streaming system. While our work in this paper can be partly adapted to the simulcast system, we will mainly focus on the second option, i.e., SVC streaming system.

The generally-known term SVC usually refers to the scalable extension of the H.264/AVC video coding standard \cite{SVCOverview}, which has provided an effective way to deal with the new challenges of modern video applications. SVC allows efficient scalability in terms of video frame rate, spatial resolution, and picture fidelity, with only one single bitstream. The SVC bitstream is composed of Network Abstract Layer Units (NALUs), which are separated into multiple layers: one base layer for basic video quality and several enhancement layers for video quality improvement. By discarding NALUs of the enhancement layers, the bitstream can be extracted as required, providing the most appropriate data rate and video service according to the client capability and network conditions.

In SVC streaming system, there are two important issues that need to be addressed. First is quality control, and the second is bitstream extraction. Quality control means controlling the video quality (as well as the bitrate) to follow the change of bandwidth. Once the bandwidth has changed, the quality control algorithm should determine a bitrate suitable for the current bandwidth. Given this bitrate, how to extract from the whole SVC stream to form a optimal sub-stream becomes the bitstream extraction problem. Optimized bitstream extraction aims to select a subset of data which represents video with best quality, or minimal distortion, under the constrain of given bitrate. It should be noted that, bitstream extraction is not only useful in scalable video streaming, but also in other SVC application scenarios where part of data needs to be obtained or kept, e.g., the archiving of surveillance video.

In this paper, we propose novel solutions for these two issues and construct an efficient scalable video streaming system. Apple Darwin Streaming Server (DSS) \cite{DSS}, which has been widely used to collect, cache, schedule and transmit multimedia contents in practice, is chosen as the basis of the system. We modified the original DSS project and added SVC support to it, for the purpose of both research and application. A new quality control algorithm based on the Proportional-Integral-Derivative (PID) control concept is proposed to replace the native one in DSS, and achieves higher average quality level with less quality fluctuation. In this algorithm, we can monitor and even predict the relationship between the network bandwidth and the current video data rate, so that quality adjustment can be made at any time and to any extent, accurately and smoothly. For the bitstream extraction problem, we propose a linear error model to directly estimate pixel value errors before MSE or PSNR is calculated. The linear error model exploits the linear feature of H.264/AVC coding process and achieves good performance in distortion estimation. Using this model, the error caused by the removal of each enhancement packet can be obtained independently. This enables us to estimate the distortion caused by discarding any combination of packets. Based on that, we design a greedy algorithm to calculate the priority of each quality enhancement packet according to its R-D impact. The priority value of packets can be stored in the bitstream and used for optimized extraction. The proposed algorithms perform well in experiments and the quality control algorithm is also used in practical streaming systems and proved quite effective.

The rest of this paper is organized as follows. In section \ref{sec:analysis}, we analyze the problems in detail and introduce some related works on them. Then in section \ref{sec:quality-control}, the proposed quality control algorithm is formulated and explained with term definitions and parameters selection. After that, we propose the solution for the bitstream extraction problem in \ref{sec:bit-extraction}. Section \ref{sec:experiment} lists the experimental results and compares our proposed solution with others. Finally, in section \ref{sec:conclusion}, we conclude this paper's work and point out its promising applications and extensions in the future.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Problem Analysis and Related Works}
\label{sec:analysis}

In this section, we analyze the two most concerned problems in SVC streaming, i.e., quality control and bitstream extraction, and introduce some existing related works on them.

\subsection{Quality Control}

For a quality control algorithm, there are three targets that should be achieved. First is to ensure the continuity of video playing. In real-time streaming system, each data packet has its own playtime, which is also regarded as the deadline of the transmission. If the packet does not arrive at client side before the deadline, the media player will be paused due to lack of data, and that should be avoided. The second is to keep a smooth video quality. Although network conditions may change rapidly, it is necessary for the streamed video to maintain a relatively stable quality level, since frequent change of video quality will lead to poor user experience. The third target is to make the video quality as good as possible. In other words, the available bandwidth should be fully utilized. Suppose we keep sending video data in a low bitrate (with low video quality as well), neither the playback pause nor any quality fluctuation will likely happen. However, a low video quality is certainly not what we want.

The state-of-art solutions to avoid video pause in client media player mainly focus on how to select and schedule the video packets. In \cite{Gao06}, K. Gao et al. proposed a priority based scheduling strategy which guarantees packets of higher importance will be transmitted earlier. Among the packets with the same priority, those having the earliest deadline will be transmitted first. A similar solution is proposed in \cite{Schierl10}, where video data is pre-buffered in several buffers of different priorities. Whenever re-buffering occurs, quality will be degraded to a lower level to meet the time and rate constraint. Although the priority based scheduling strategies perform well in maintaining a non-paused video playing, they do not take quality fluctuation into account. As a result, users may still suffer from the frequent fluctuation of video quality.

In DSS, quality control is implemented by monitoring packet delay (the difference between current time and the playing time of this packet). When a new packet is ready to be sent to streaming buffer, DSS checks the delay of it and compares this delay with some pre-set critical time thresholds to judge whether and how violently the quality change should be made. This algorithm can reduce quality fluctuation to some degree. However, it only provides conservative quality change, which makes its reaction so slow that sometimes media player may have already stopped due to lack of video data before quality drops. Furthermore, this algorithm has no knowledge of the bandwidth change so it cannot accurately adjust the video quality. Therefore, quality oscillation is inevitable in this algorithm.

\subsection{Bitstream Extraction}

SVC bitstream extraction is substantially a combinatorial optimization problem. More specifically, it is in the form of ``0-1 Knapsack Problem". Each NALU data packet can be treated as an object with certain value (its contribution to the video quality) and weight (its size). The solving process is mainly to decide whether or not a packet should be included in the final extracted sub-stream; or in the term of ``0-1 Knapsack Problem", to choose which object to pack up.

Generally, the optimal solution of a typical ``0-1 Knapsack Problem" can be found using the dynamic programming algorithm. However, this is not operational for the bitstream extraction problem, mainly due to the dependence between packets. First, the value of a packet is not obvious and certain, since a packet's contribution to video quality may depend on the other packets. Second, the subset of packets to be extracted cannot be chosen arbitrarily, since if a packet is included, all the packets it depends on must also be included. In fact, to the best of our knowledge, no method presented in the literature claims to find the optimal solution of the SVC bitstream extraction problem. All the effort is made to obtain a solution that is as good as possible.

In \cite{Amonou07}, Amonou et al. proposed a bitstream extraction framework based on the concept of \textit{Quality Layers}. This framework has been adopted by the SVC reference software, i.e., JSVM  \cite{JSVM}, and achieves better R-D performance compared with the basic extractor of JSVM. In Amonou's framework, a Quality Layer value, which reflects a packet's rate-distortion (R-D) impact, is calculated and used for R-D optimized bitstream extraction. The process of obtaining distortion impact of every packet is extremely time consuming, and the distortion estimation accuracy can also be further improved. So other distortion/error models were proposed to either reduce the computational complexity or improve the estimation accuracy. Sun \cite{Sun09} and Maani \cite{Maani09} constructed models to calculate distortion based on the drift propagation between frames. Sun's method is almost as good as JSVM for the performance, but with a much reduced complexity. Maani's model can achieve better estimation accuracy than JSVM; however, in order to get robust and accurate model parameters, more computation is needed for training.

In our previous work \cite{Zhang12}, we noticed the mismatch between quadratic calculations in distortion criteria like MSE or PSNR and the essential linear operations in the coding process, and proposed a linear error model to directly estimate pixel value errors before MSE or PSNR is calculated. The linear error model exploits the linear feature of pixel value errors and achieves good performance in distortion estimation and bitstream extraction with reference. However, this work assumes that the original sequence is available for reference, which is not always true. It needs adaption for widespread application.

The following of this paper will present solutions for the above problems, and lay a solid foundation for a practical scalable video streaming system.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{PID-based Quality Control Algorithm}
\label{sec:quality-control}

PID control \cite{PID}\cite{Astrom02} is a control loop feedback mechanism commonly used in industrial control systems. \textit{Process variable} and \textit{setpoint} are two core concepts in PID control. The process variable stands for the current status of the system. The setpoint is the target for this automatic control system to reach. The goal of PID control is to minimize the error between process variable and setpoint by adjusting system inputs. The controller output $u(t)$ is defined as follows:

\begin{equation}
\label{eq:pid-output}
u(t) = {K_p}e(t) + {K_i}\int_0^t {e(\tau )d\tau }  + {K_d}\frac{d}{{dt}}e(t) \: ,
\end{equation}
where $e(t)$ represents the error between process variable and setpoint at time $t$. $K_p$, $K_i$, and $K_d$ here are tuning parameters representing the proportional gain, integral gain and derivative gain respectively. Proportional part directly relates to the change of the process variable, and is also the main factor to adjust the process variable towards setpoint. There might be oscillations and steady-state errors in a pure proportional system, and they can be reduced or eliminated by adding the integral part. The appearance of derivative part is to predict future errors, so that the system tends to become steady early and quickly. The result of (\ref{eq:pid-output}) is used to manipulate the system input of next moment to adjust process variable towards setpoint.

As an effective and flexible control technique, PID control has been used to solve all kinds of control problems. In the area of video coding, we notice that PID is utilized to design rate control algorithms by many papers. For instance, in \cite{Wong04} a PID-based real time rate control scheme is proposed to trade-off between spatial and temporal quality and smooth the video quality between frames; in \cite{Yang10}, the authors designed an incremental rate control algorithm for H.264/SVC, in which the PID method is used to provide robust buffer control for each layer. We also notice some researchers have proposed theoretical model or middle-ware framework for QoS adaptation \cite{Li98}\cite{Li99}, with PID as the basic control concept. However, we have not found any paper that integrates PID method into the quality control of video streaming. While rate control of video coding and quality control of video streaming are two different problems, they do share some common properties, such as the buffer mechanism and the requirement for smoothness. That inspires us to design a PID-based quality control algorithm and utilize it to deliver best video quality with least quality fluctuation.

In this section, we first introduce the \textit{quality level} concept to discretization the bitrate and quality of scalable video. Then we define the process variable used in our PID-based quality control algorithm. After that, the PID-based quality control algorithm is formulated and explained in detail, followed by the brief discussion of parameter selection.

\subsection{Quality Level}
\label{subsec:quality-level}

The video bitrate or quality is a continuous value. In practical operation, it is not possible to control it at an arbitrary precision. So we propose a \textit{quality level} concept as the discrete description of the video quality. When the video quality needs to be adjusted, we simply increase or decrease the quality level. Each quality level corresponds to a certain bitrate. A Higher quality level corresponds to a higher bitrate, vice versa. The number of quality levels and how they are mapped to sub-streams with different bitrates depends on requirement or implementation. The more quality levels are defined, the more precisely the control algorithm can adjust bitrate to follow the bandwidth change.

\subsection{Process Variable Selection}
\label{subsec:variable}

In our PID-based quality control algorithm, the process variable is called \textit{actual\_check interval ratio}, which is defined as follows.

For DSS, two timelines are important. Push timeline indicates the time of pushing video data packets to streaming buffer, and play timeline indicates the time these data packet should be played, i.e., the presentation time stamp (often seen as PTS) of each packet. Their relationship is shown in Fig. \ref{fig:intervals}. The program will check the timelines periodically, and, in the default quality control algorithm of DSS, use the packet delays to decide whether quality change is needed. The two intervals shown in Fig. \ref{fig:intervals}, i.e., check interval and actual interval, are worth notice and may provide useful information. In the ideal situation, during each check interval, the server pushes an amount of data that will actually play for a period of time equal to that check interval, i.e., \textit{actual\_interval} = \textit{check\_interval}. If \textit{actual\_interval} is smaller than \textit{check\_interval}, it means that less data is pushed to the client, and the pushing is slowed down because bandwidth is relatively low at this time. On the other hand, if \textit{actual\_interval} is larger than \textit{check\_interval}, it indicates the bandwidth condition is good and data is being pushed quickly to the client. The ratio of these two intervals, i.e., \textit{actual\_check interval ratio}, is in direct proportion to the ratio of the data rate appropriate for bandwidth and the current pushing data rate.

The \textit{actual\_check interval ratio} is suitable for quality control because: 1) this ratio directly reflects the mismatch of current pushing data rate and the bandwidth, and by adjusting data rate according to it, this ratio can be used to accurately change video quality; 2) the desired value of this ratio is 1.0 by definition so we don't need to find the optimized setpoint by mathematical methods or experiments; and 3) it is easy to compute and implement in practical systems.

\begin{figure}[t]
\centering
\includegraphics[width = 0.9\linewidth]{intervals.jpg}
\caption{Push Time and Play Time \label{fig:intervals}}
\end{figure}

\subsection{Model Formulation}
\label{subsec:model}

As is introduced above, the \textit{actual\_check interval ratio} serves as the process variable in this PID-based quality control algorithm. In normal PID control, the controller output is calculated using the proportion, integral and differential of the error between the process variable and the setpoint, as shown in (\ref{eq:pid-output}). Considering that our process variable is a ratio and the corresponding setpoint is 1, we make a little modification to the general PID controller and obtain a ratio-based model. In this model, the ratio is directly used to calculate the controller output, and all subtraction operations in original PID equations have been changed to division operations to keep the correctness, as follows:

\begin{equation}
\label{eq:ut}
{u_t} = {K_p}E_p^t + {K_i}E_i^t + {K_d}E_d^t ,
\end{equation}

\begin{equation}
\label{eq:ep}
E_p^t = \frac{{actual\_interva{l_t}}}{{check\_interva{l_t}}} ,
\end{equation}

\begin{equation}
\label{eq:ei}
E_i^t = \frac{{long\_actual\_interva{l_t}}}{{long\_check\_interva{l_t}}} ,
\end{equation}

\begin{equation}
\label{eq:ed}
E_d^t = E_p^t/E_p^{t - 1} ,
\end{equation}

\begin{equation}
\label{eq:long-actual}
long\_actual\_interva{l_t} = \sum\limits_{\tau = {T_l}}^t {actual\_interva{l_\tau}} ,
\end{equation}

\begin{equation}
\label{eq:long-check}
long\_check\_interva{l_t} = \sum\limits_{\tau = {T_l}}^t {check\_interva{l_\tau}} .
\end{equation}

In (\ref{eq:ut}), $K_p$, $K_i$, and $K_d$ indicate the tuning parameters for proportional, integral and derivative parts respectively, and $E_p^t$, $E_i^t$, $E_d^t$ stand for the corresponding observed value for each part, which are defined in (\ref{eq:ep}) - (\ref{eq:long-check}); the controller output $u_t$ is utilized to calculate an appropriate data rate and further to determine which quality level we should transmit (see Algorithm \ref{algo:control} for more details).

In (\ref{eq:long-actual}) and (\ref{eq:long-check}), $T_l$ stands for the last quality change time. Theoretically, the integral part should be recorded and calculated from the system start. In practice, however, bandwidth may vary significantly during the transmission. If the integral part was recorded for too long time, it may not reflect the real network status and may slow down the reaction for better quality level. A compromise here is to choose a relatively long time, i.e., the time from last quality change till now, for the integral part calculation.

This ratio-based model is more simple and effective for the chosen process variable and setpoint. And note that, since the controller output ($u_t$) is also a ratio, it should be used as a multiplier to manipulate the system input, i.e., the pushing data rate.

The whole process of this algorithm is described in Algorithm \ref{algo:control}. Compared to other scheduling strategies, this quality control algorithm has several advantages. First, this algorithm does not just rely on current packet delay or information at fixed time point, so quality change may occur at any proper time. Second, since the model has taken prediction into account, we can actually decide whether the bandwidth will be high or low enough for the quality level to change, thus avoiding video quality fluctuation. Third, in this algorithm it's not necessary to change one quality level at a time. This enables fast quality drop when bandwidth suddenly decreases and fast quality rise when system starts, resulting in a seamless experience.

\begin{algorithm}
\caption{PID-based quality control algorithm}
\label{algo:control}
\begin{algorithmic}
    \STATE before packet sent
    \STATE check\_interval = curr\_time -- last\_check\_time
    \STATE actual\_interval = curr\_media\_time -- last\_check\_media\_time
    \STATE long\_check\_interval += check\_interval
    \STATE long\_actual\_interval += actual\_interval
    \STATE calculate $E_p^t$, $E_i^t$, $E_d^t$ according to Eq. (\ref{eq:ep}) - (\ref{eq:ed})
    \STATE output = ${K_p}E_p^t + {K_i}E_i^t + {K_d}E_d^t$
    \STATE new\_bitrate = output * curr\_bitrate
    \STATE new\_level = get\_level(new\_bitrate, bitrate\_of\_level[])
    \IF {quality level changed}
    	\STATE long\_check\_interval = 0
    	\STATE long\_actual\_interval = 0
    	\STATE curr\_bitrate = bitrate\_of\_level[new\_level]
    \ENDIF
    \STATE send packet according to new quality level
  \end{algorithmic}
\end{algorithm}

\subsection{Parameter Selection}
\label{subsec:parameter}

Ziegler--Nichols method \cite{Ziegler42} is used to tune $K_p$, $K_i$, and $K_d$ to obtain better performance of the PID control system. This method is performed by setting integral and derivative parameters to zero and then tuning $K_p$ to a value $K_u$ until output begins to oscillate with constant amplitude. Assuming the oscillation period is $T_u$, we set $K_p = 0.6K_u$, $K_i = 2K_u/T_u$, and $K_d = K_uT_u/8$. $K_p$, $K_i$, and $K_d$ are then normalized to get the final parameters. In the following experiments, parameters are chosen as $K_p = 0.22$, $K_i = 0.73$, $K_d = 0.05$ by this method. Note that, in the quality control algorithm, only the data rate and the bandwidth are considered, not the video content, so once the parameters are tuned they should apply well to different video streams.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Optimized Bitstream Extraction Based On Linear Error Model}
\label{sec:bit-extraction}

Once the quality control algorithm determines an appropriate bitrate and sets a quality level accordingly, the system will send a packet only belonging to this new quality level (as described at the end of Algorithm \ref{algo:control}). For SVC videos, that means to extract a subset of packets from the whole bitstream. How to optimally choose this subset to achieve minimum distortion under the given bitrate is the key point of bitstream extraction problem. In this section, we propose a linear error mode and a greedy-like algorithm to solve this problem.

\subsection{Linear Error Model for Quality Scalable Video}
\label{sec:model}

In H.264/AVC, the decoding process involves a linear feature described in \cite{Winken08}, neglecting any rounding, clipping, and deblocking filtering operation. According to this feature, the main steps in H.264/AVC coding -- prediction, transform and quantization -- are proximately linear operations, and the whole coding process can be expressed in a matrix format as follows:
	\begin{equation}
	\label{eq:linear}
s = {\rm\bf M}s + {\rm\bf T}c + p \: ,
	\end{equation}
It means, the reconstructed samples of a GOP (Group of Pictures), denoted by $s$, can be viewed as a linear combination of previously reconstructed samples in the GOP, the residual samples, and a static predictor. In (\ref{eq:linear}), $c$ refers to the transform coefficient values and $p$ is a static predictor; $M$ and $T$ are square matrices such that the product $M$s gives the MCP (Motion Compensated Prediction) signal and $Tc$ gives the residual values. The actual values of $M$ depend on the selected macroblock types, reference indices and motion vectors, whereas the actual values of $T$ depend on the chosen QP (Quantization Parameter) values.

We apply the above linear decoding model to the case of quality scalability of SVC and get a linear error model. According to (\ref{eq:linear}), for a bitstream just containing the base layer, we have:
	\begin{equation}
	\label{eq:base0}
s_{B} = {\rm\bf M}s_{B} + {\rm\bf T}_{B}c_{B} + p \: ,
	\end{equation}
where the subscript $B$ indicates the base layer variables. In quality scalability, the enhancement is mainly the refinement of transform coefficients, so for a bitstream containing an enhancement packet set $I_1$, the reconstruction relationship can be expressed as:
	\begin{equation}
	\label{eq:subset1}
s_{I_1} = {\rm\bf M}s_{I_1} + {\rm\bf T}_{B} c_{B} + \Big( \sum_{i \in I_1}{\rm\bf T}_i c_i \Big) + p \: ,
	\end{equation}
where $i$ refers to an enhancement packet as an element of $I_1$. $c_i$ is a vector containing coefficients within the enhancement packet $i$. ${\rm\bf T_i}$ is the transform matrix depending on the QP value of $i$. ${\rm\bf T}_i c_i$ gives the residual sample values decoded from $i$.

Similarly, for another bitstream containing an enhancement packet set $I_2$, we have
	\begin{equation}
	\label{eq:subset2}
s_{I_2} = {\rm\bf M}s_{I_2} + {\rm\bf T}_{B} c_{B} + \Big( \sum_{i \in I_2}{\rm\bf T}_i c_i \Big) + p \: .
	\end{equation}

Suppose $I_1$ is a subset of $I_2$, their reconstruction difference can be obtained by (\ref{eq:subset2}) - (\ref{eq:subset1}):
	\begin{equation}
	\label{eq:minus1}
(s_{I_2} - s_{I_1}) = {\rm\bf M}(s_{I_2} - s_{I_1}) + \Big( \sum_{i \in I_2}{\rm\bf T}_i c_i - \sum_{i \in I_1}{\rm\bf T}_i c_i \Big) \: ,
	\end{equation}
	\begin{equation}
	\label{eq:minus2}
\Rightarrow e = s_{I_2} - s_{I_1} = ({\rm\bf I - M})^{-1} \Big( \sum_{i \in I_2}{\rm\bf T}_i c_i - \sum_{i \in I_1}{\rm\bf T}_i c_i \Big) \: .
	\end{equation}

Particularly, if the difference of $I_2$ and $I_1$ is a single enhancement packet $j$, i.e. $I_2 \setminus I_1 = \{j\}$, then according to (\ref{eq:minus2}), the difference of the two reconstruction vectors can be written as
	\begin{equation}
	\label{eq:error_j}
e_j = ({\rm\bf I - M})^{-1} {\rm\bf T}_j c_j \: .
	\end{equation}

Obviously, $e_j$ is only determined by packet $j$, and has no relation with other enhancement packets. This value is called the ``error vector'' of packet $j$, which represents the pixel value error caused by discarding the packet $j$. We can obtain the error vector of each enhancement packet by subtraction between video sequences reconstructed from two enhancement packet subsets $I_1$ and $I_2$, with $I_1 \subseteq I_2$ and $I_2 \setminus I_1 =\{j\} $. Once all packets' error vectors are obtained, the distortion caused by discarding a group of packets can be estimated by adding up the error vector of each packet in the group.

The above model is called Linear Error Model (LEM). Note that in equations (\ref{eq:base0})-(\ref{eq:subset2}) the value of M and p remain the same, since in the case of quality scalability the enhancement packets are generated only by manipulating the transform coefficients, and not interfered with the motion compensation and static prediction.  This argument no longer holds for the other scalable dimensions, so the model does not simply apply for those cases. Further research and modification of this linear model for the spatial or temporal scalability would be our future work.

\subsection{Error Vector Acquisition}
 It would need too many decoding times to get the error vectors of all enhancement packets if we calculate them one at a time. In order to acquire error vectors of all enhancement packets efficiently, we separate all enhancement packets into several groups, such that in each group multiple error vectors can be obtained independently at the same time.

 \begin{figure}[h]
 \centering
 \includegraphics[width = 0.9\linewidth]{GOPStructure.jpg}
 \caption{SVC GOP structure \label{fig:GOP_Structure}}
 \end{figure}

 Consider a video bitstream with 8-frame GOPs (Group of Pictures) shown in Fig. \ref{fig:GOP_Structure}. Base layer packets are colored black, and enhancement packets with the same color are allocated in one group. In each group, the enhancement packets' error vectors can be calculated simultaneously, since the pixel errors they caused are not interfered with each other. For example, the loss of packet 8 would bring about distortion only in frame 1, 2 and 3, while packet 10 only in frame 5, 6 and 7(frame number starts from 0). So we can do subtraction for this group, for one time, to gain error vectors $e_{8}$ and $e_{10}$, for both packets 8 and 10, as well as peer packets in all other GOPs. Note that these error vectors are highly sparse ones, because the discarding of a single enhancement packet can bring distortion only to a limited number of frames. To acquire all error vectors, the number of required extraction and decoding is approximately the number of enhancement layers $(L_Q - 1)$ times the temporal layer number $L_T$. For the example in Fig. \ref{fig:GOP_Structure}, $L_Q = 3$ and $L_T = 4$, so the theoretical extraction-and-decoding number is $(3 - 1) \times 4 = 8$. However, we have to do the same manipulation for $L_Q - 1 = 2$ more times, to dissociate the distortion impact of ``key frame''\cite{H264Overview} (e.g. frame 0, 8, 16, etc.) packets. The loss of one enhancement packet in a key frame would bring distortion to two neighboring GOPs. As an instance, the loss of packet 4 would propagate drift into frame 1 to 15, which would interfere with the distortion impact of packets in frame 0 and 16 (packet 1, 2 and 19, 20). So key frame enhancement packets within the same quality layer (e.g. packet 2, 4 and 20) should be allocated in two groups -- one for key frame packets of even number GOPs (packet 2 and 20), the other for those of odd number GOPs (packet 4). So the actual number of extraction and decoding for error vector acquisition is $(L_Q - 1) \cdot (L_T + 1)$, approximately the same with JSVM reference software\cite{H264Overview}. Since computation is mainly consumed with this decoding in our bitstream extraction algorithm, the computation complexity has no obvious promotion compared with JSVM.

\subsection{Distortion Estimation And Model Verification}

Based on the linear error model described above, we can obtain error vectors of all enhancement packets. Then we can estimate the distortion caused by discarding any set of enhancement packets, by adding up the error vector of each packet in that set.

For example, consider a video sequence decoded from a sub-stream which is extracted by discarding packet set $I_x$. The error between this sequence and the original sequence can be estimated as

	\begin{equation}
	\label{eq:subset_error}
e(I_x) = e_{full} + \sum_{i \in {I_x}} e_i \: . 
	\end{equation}
Eq. (\ref{eq:subset_error}) has taken into consideration the error between the video sequence decoded from full enhancement packets and the original sequence, written as $e_{full}$.

To verify the linear error model, we conduct an experiment where some random sets of enhancement packets are removed from a video bitstream, and the distortion estimated by the linear error model are compared with the actual distortion. Experimental result of the sequence {\em Foreman} is partly shown in Fig. \ref{fig:linear_verification}. The horizontal axis stands for sample point numbers of those random selections, and the vertical axis for MSE measurement. The solid line represents the actual MSE of a randomly extracted substream, and the dot line shows the estimated MSE using our Linear Error Model. A 0.6\% maximum relative error of MSE demonstrates the accuracy of the proposed model.

\begin{figure}[h]
\centering
\includegraphics[width = 0.9\linewidth]{LinearVerification.jpg}
\caption{Result of SVC Linear Error Model verification \label{fig:linear_verification}}
\end{figure}

\subsection{Priority Assignment and Bitstream Extraction}
\label{subsec:priority}

In this subsection, we utilize the Linear Error Model to enable R-D optimized bitstream extraction. Since finding the global optimal solution of the bitstream extraction problem is impractical, our bitstream extraction algorithm uses a greedy method \cite{GreedyAlgo} to get a sub-optimal solution. Similar to the greedy solution of the ``0-1 Knapsack Problem", every time a packet is to be discarded, we choose the packet that has the minimal R-D impact. A packet's R-D impact is mathematically measured by:
	\begin{equation}
	\label{eq:rd_impact}
\Phi_{i} = \dfrac{\partial D}{\partial R} \: ,
	\end{equation}
where $\partial D$ represents the distortion change brought by discarding this packet, and $\partial R$ is the corresponding rate change. $\partial R$ is simply equivalent to the size of this packet, while $\partial D$ needs to be calculated by subtraction of distortions before and after the packet is discarded.

We simulate a process of discarding all the enhancement packets from a stream, using the above greedy strategy. During this process, the discarding order of a packet is regarded as its priority and recorded. Then the packets' priority values can be stored in the bitstream (either in the priority id field of the NALU header or in separate SEI messages) for real extraction in the future.

The detailed discarding and priority assignment process is described below:
\begin{description}
  	\item[1)] Initially, the sequence error vector, $e_{seq}$, is set to $e_{full}$.
  	\item[2)] Within the packets that can be discarded, find the packet $m$ having the least RD impact on the sequence, \textit{i.e. }
	\begin{equation}
	\label{eq:R-D_impact_m}
	\Phi_m = \min_{i \in I_{top}} \Phi_i \: ,
	\end{equation}
	where $I_{top}$ stands for the top layer packets, those currently able to be discarded. The RD impact of a packet is calculated based on (\ref{eq:rd_impact}), as follows: 
	\begin{equation}
	\label{eq:R-D_impact_i}
	\Phi_i = \dfrac{\partial D}{\partial R} = \dfrac{PSNR(e_{seq}) - PSNR(e_{seq} + e_i)}{SIZE(i)} \: ,
	\end{equation}
	where $PSNR(*)$ means to obtain PSNR from the error vector, and $SIZE(i)$ is the size of packet $i$.
  	\item[3)]The packet, $m$, is then removed from the bitstream, and its error vector is added to the sequence's error vector, \textit{i.e.}
  	\begin{equation}
  	\label{eq:error_update}
  	e_{seq} = e_{seq} + e_m \: .
  	\end{equation}
  	\item[4)]The process from 2) to 3) is repeated until all enhancement packets are discarded, and every packet is assigned a priority value according to the removing order.
\end{description}

For long video sequences, an optimization window is usually needed, and the priority assignment and bitstream extraction is conducted independently in each window. The computational complexity of this priority assignment algorithm is $O(K^2)$, with $K$ being the number of frames involved in the priority assignment process, \textit{i.e.}, the size of the optimization window. Note that this computation complexity is negligible compared with the decoding process needed in the error vector acquisition.

\subsection{The No-Reference Case}
\label{subsec:noref}
In some scenarios, the priority assignment and bitstream extraction needs to be conducted without access to the original YUV sequence. For example, if the bitstream extraction is not done at the encoding side, it's most likely that the original sequence is not available. This would make the bitstream extraction a more difficult problem, since the distortion is harder to obtain for lacking of reference signal. Comparing to the problem of SVC bitstream extraction with reference, this kind of ``no-reference bitstream extraction'' problem is actually more frequently encountered in real practice. In this subsection, we handle this no-reference problem as well and modify the proposed algorithm to meet the special characteristic caused by lacking of reference.

In the no-reference case, since we do not have access to the original sequence, we can not get the error between the video sequence decoded from full enhancement packets and the original sequence, which is $e_{full}$ used above. A straightforward idea is to set $e_{full}$ to zero, meaning we calculate distortion with respect to the fully reconstructed signal, rather than to the original sequence. However, simply doing so causes the algorithm to perform badly in experiments. We find that, since discarding some enhancement packets will not bring much significant error relative to the fully reconstructed signal, the calculated PSNR values are too large to well represent the real distortion. To address this issue, instead of calculating PSNR, we directly use MSE of all pixels as the distortion criteria in the priority assignment algorithm. This proves to be a simple and effective solution, and the extraction performance turns out to be much better.

We have presented experimental results for the case where reference original sequence is available in our previous work \cite{Zhang12}, so this paper will include only experimental results for the no-reference case in the following section.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experimental Results}
\label{sec:experiment}

To implement our proposed scalable streaming system requires the combination of the PID-based quality control algorithm and the optimized bitstream extraction method. The former determines the current bitrate to follow the bandwidth change, and the latter will ensure the sub-stream with the best possible quality is sent under that bitrate constrain. They work together to construct a system that delivers best quality of experience for the users. We have integrated the PID-based quality control algorithm into DSS. However, the integration of the proposed bitstream extraction method needs more engineering work and has not been accomplished. Therefore, in this section, we present separate experiments to demonstrate the advantage of each proposed solution.

\subsection{Experiments for Quality Control}

For simplicity and intuition, we combine the enhancement layers in the tested SVC video stream to construct quality levels (introduced in \ref{subsec:quality-level}) used in the quality control algorithm. The video stream is divided into several sub-streams, each of which is identified by the quality and temporal layer it contains, as illustrated in Table \ref{tab:sub-stream} (there are 3 layers in each scalability dimension; spatial scalability is not enabled). The quality level is defined as the sum of all sub-streams with ID equal or less than the level number. For example, quality level 3 would contain all sub-streams from 0 to 3, thus would include all temporal layers, but only the quality base layer 0. The tested stream has 9 quality levels from 0 to 8 (Table \ref{tab:sub-stream}), and a maximum bit rate of 1587 kbps at level 8.

\begin{table*}[t]
\centering
\caption{Sub-stream ID}
\label{tab:sub-stream}
\begin{tabular}{c|*{8}{p{1.2cm}<{\centering}|}{p{1.2cm}<{\centering}}}
	\hline\hline
	  Sub-stream ID   & 0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 \\ \hline
	Quality Layer ID  & 0 & 0 & 0 & 1 & 1 & 1 & 2 & 2 & 2 \\ \hline
	Temporal Layer ID & 0 & 1 & 2 & 0 & 1 & 2 & 0 & 1 & 2 \\ \hline
\end{tabular}
\end{table*}

We simulate network fluctuation by adjusting bandwidth around a certain level. We set this level from 400 to 1400 kbps to reflect different average bandwidth. All the experiments are conducted in Visual C++ 6.0 (with DSS as the software platform) and the bandwidth control is implemented by NetLimiter 3 \cite{Netlimiter}. The baseline algorithm in the comparison refers to the packet delay feedback (PDF) algorithm in the original DSS.

First of all, we conduct some preliminary improvement experiments using only proportional part or integral part. Since they are directly related to the short term error and long term error respectively, we call them Short Term Prediction (STP) and Long Term Prediction (LTP). Fig. \ref{fig:performance-all} shows the experimental results of these two control algorithms and the baseline algorithm. In the figures, the video quality is measured by the quality level defined in the beginning of this section, and quality smoothness is indicated by the variance of the quality levels along time. We can conclude that STP provides the best average quality level at the expense of high quality variance. This can be easily explained since this quality control strategy closely follows the bandwidth fluctuation. In contrast, LTP keeps a relatively low quality variance at a little cost of average video quality. Although it is not as good as STP in average quality, it still outperforms the baseline algorithm by 7.9\%.

Since STP and LTP have their own limitations, we implement the PID-based quality control algorithm, which can both reduces quality variance and improves average quality level. From the result shown in Fig. \ref{fig:performance-two}, we can conclude that when integrated with integral part and derivative part, the effect of proportional part is not as aggressive as in STP. An obvious proof can be found in Fig. \ref{fig:variance-two}, which clearly shows that the proposed PID quality control algorithm keeps a lower quality variance compared to PDF algorithm. Table \ref{tab:improvement} lists the statistical experimental results for these four quality control algorithms, in which PID-based control algorithm has shown its advantage over the others, especially in reducing the quality fluctuation. It can be seen that, compared to PDF, the PID-based quality control algorithm improves 8.6\% in video quality with 24.8\% reduction in quality fluctuation. The video quality fluctuation of the four control algorithms, when available bandwidth fluctuates around 800 kbps, is shown in Fig. \ref{fig:fluctuation}, from which we can see a more stable video quality in the proposed PID quality control algorithm.

\begin{figure*}[t]
\subfloat[Average quality level of different control algorithms]{
\includegraphics[width=0.5\textwidth]{quality-all.jpg}
\label{fig:quality-all}}
\subfloat[Variance of quality level of different control algorithms]{
\includegraphics[width=0.5\textwidth]{variance-all.jpg}
\label{fig:variance-all}}
\caption{Comparison of the long/short time prediction and the PDF algorithm in DSS}
\label{fig:performance-all}
\end{figure*}

\begin{figure*}[t]
\centering
\subfloat[Variance of quality level of PID and PDF control algorithms]{
\includegraphics[width=0.5\textwidth]{quality-two.jpg}
\label{fig:quality-two}}
\subfloat[Average quality level of PID and PDF control algorithms]{
\includegraphics[width=0.5\textwidth]{variance-two.jpg}
\label{fig:variance-two}}
\caption{Comparison of the proposed PID algorithm and the PDF algorithm in DDS}
\label{fig:performance-two}
\end{figure*}

\begin{table*}[t]
\centering
\caption{Improvement of Different Quality Control Schemes}
\label{tab:improvement}
\begin{tabular}[b]{p{4.2cm}<{\centering}|p{4.2cm}<{\centering}|p{4.2cm}<{\centering}}
\hline \hline
Quality control scheme & Average quality level & Quality variance \\ \hline
Packet delay feedback (PDF) & 0.0\% & 0.0\% \\ \hline
Short term prediction (STP) & \textbf{+13.5\%} & +38.5\% \\ \hline
Long term prediction (LTP) & +7.9\% & -17.2\% \\ \hline
PID based control scheme(PID) & +8.6\% & \textbf{-24.8\%} \\ \hline
\end{tabular}
\end{table*}

\begin{figure}[t]
\centering
\includegraphics[width = 0.9\linewidth]{fluctuation.jpg}
\caption{Video quality fluctuation with time \label{fig:fluctuation}}
\end{figure}

\subsection{Experiments for Bitstream Extraction}

We compare the performance of the proposed bitstream extraction method with that of JSVM 9.16.

In our experiments, all test bitstreams are encoded with the JSVM encoder, where the standard hierarchical B coding structure and CABAC entropy coding are used. Each bitstream contains one base layer and a quality enhancement layer, with quantization parameters QP = 33 and QP = 27, respectively. The enhancement layer is further divided into 2 MGS layers by configuring the MGS vector to separate the transform coefficients into two groups (containing 4 and 12 coefficients respectively). For each test bitstream, ten bitrate points (one with all enhancement packets, one with only the base layer packets, and 8 points between) are chosen for extraction. For each bitrate point, the extraction is conducted using the bitstream extractors in JSVM, with and without quality layer (denoted as JSVM QL and JSVM Basic, respectively), and the proposed method. The size of the optimization window in the proposed method is set to 4 GOPs, with a GOP size of 8. All of the eight SVC standard sequences with CIF resolution are considered at 30FPS and tested in our experiments.

The performance comparisons for City, Foreman, Harbour, and Soccer are shown in Fig. \ref{fig:performance}. It can be seen that the R-D curves of the proposed method are always on the top. For each sequence, the maximum and average PSNR gain through all 10 bitrate points are calculated and listed in Table \ref{tab:results}, which shows that our extraction method can achieve a significant performance gain compared with JSVM.

Among other bitstream extraction methods besides that of JSVM, the work in \cite{Maani09} achieves much better performance than JSVM QL, and even better than ours. However, the method of \cite{Maani09} needs more computation in order to train robust model parameters for different sequences, while the complexity of our method is always the same with JSVM QL.

\begin{comment}[8 mini-figures]
\begin{figure*}[t]
\begin{minipage}{0.5\linewidth}
\centering
\includegraphics[width = \linewidth]{City.jpg}
\caption{City \label{fig:City}}
\end{minipage}
\begin{minipage}{0.5\linewidth}
\centering
\includegraphics[width = \linewidth]{Foreman.jpg}
\caption{Foreman \label{fig:Foreman}}
\end{minipage}
\end{figure*}

\begin{figure*}[t]
\begin{minipage}{0.5\linewidth}
\centering
\includegraphics[width = \linewidth]{Harbour.jpg}
\caption{Harbour \label{fig:Harbour}}
\end{minipage}
\begin{minipage}{0.5\linewidth}
\centering 
\includegraphics[width = \linewidth]{Soccer.jpg} 
\caption{Soccer \label{fig:Soccer}}
\end{minipage} 
\end{figure*}

\end{comment}

\begin{figure*}[t]
\centering
\subfloat[City]{
\includegraphics[width=0.5\textwidth]{City.jpg}
\label{fig:City}}
\subfloat[Foreman]{
\includegraphics[width=0.5\textwidth]{Foreman.jpg}
\label{fig:Foreman}}
\qquad
\subfloat[Harbour]{
\includegraphics[width=0.5\textwidth]{Harbour.jpg}
\label{fig:Harbour}}
\subfloat[Soccer]{
\includegraphics[width=0.5\textwidth]{Soccer.jpg}
\label{fig:Soccer}}
\caption{Performance of three bitstream extraction methods for various CIF sequences}
\label{fig:performance}
\end{figure*}

\begin{table*}[t]
\centering
\caption{Algorithm Performance: Luma PSNR Gain Compared with JSVM}
\label{tab:results}
\begin{minipage}{0.95\linewidth}
% \renewcommand{\thefootnote}{\thempfootnote}
\centering
\begin{tabular}{c|c|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}| 
p{1.2cm}<{\centering}|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}}

%% |l|l| to left justify each column entry
%% |c|c| to center each column entry
%% use of \rule[]{}{} below opens up each row

\hline \hline
\multicolumn{2}{c|}{Sequence} &
{\em Bus} & {\em City} & {\em Crew} & {\em Football} & {\em Foreman} & {\em Harbour} & {\em Mobile} & {\em Soccer} \\ \hline

\multirow{2}{*}{JSVM QL\footnote{\label{footnote:JSVM_QL} Comparing the proposed algorithm with JSVM QL} (dB)}
& Max\footnote{\label{footnote:max} Maximum PSNR gain through all bitrate constraints} & 0.37 & 0.50 & 0.13 & 0.22 & 0.23 & 0.19 & 0.25 & 0.44 \\ \cline{2-10}
& Ave\footnote{\label{footnote:ave} Average PSNR gain through all bitrate constraints} & 0.11 & 0.11 & 0.05 & 0.12 & 0.05 & 0.05 & 0.06 & 0.13 \\ \hline

\multirow{2}{*}{JSVM no QL (dB)}
& Max & 0.50 & 0.83 & 0.32 & 0.29 & 0.50 & 0.34 & 0.61 & 0.53 \\ \cline{2-10}
& Ave & 0.18 & 0.37 & 0.20 & 0.15 & 0.22 & 0.15 & 0.25 & 0.29 \\ \hline

\end{tabular}
\end{minipage}
\end{table*}

\section{Conclusion}
\label{sec:conclusion}

In this paper, we propose a scalable video streaming system with PID-based quality control algorithm and optimized bitstream extraction. The PID-based quality control algorithm has a flexible mechanism to determine the suitable quality level so that it gives an accurate and swift response to the bandwidth change. Comparing with the original algorithm in DSS, this algorithm has reduced quality fluctuation significantly to improve audience satisfaction. The bitstream extraction method we propose includes a linear error model to estimate the distortion caused by discarding any combination of packets and a greedy algorithm to assign priority to each data packet. The packets' priority values can then be stored in the bitstream and used for R-D optimized extraction. Experimental results show that the proposed method can achieve PSNR gain of up to 0.5 compared to the JSVM QL extractor under the same bitrate constrain, also with the same computational complexity.

The PID-based quality control algorithm of this paper has already been integrated into the online scalable video streaming website www.7dlive.com and performs well in automatically adapting to the user's bandwidth fluctuation. This algorithm can also be easily used in other streaming systems, e.g., DASH systems. For the bitstream extraction method, there is future work to be done in the following two directions. First, we strive to integrate the bitstream extraction method into DSS, and combine it with the PID-based quality control to give user adaptive video streaming with best watching experience. Second, since the next generation video coding standard High Efficiency Video Coding (HEVC) \cite{HEVC} adopts the similar coding framework as its predecessor H.264/AVC, we expect to apply this paper's model and approach to the emerging HEVC standard and its scalable extension.

% Can use something like this to put references on a page
% by themselves when using endfloat and the captionsoff option.
\ifCLASSOPTIONcaptionsoff
  \newpage
\fi

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\begin{thebibliography}{1}

\bibitem{DASH}
T. Stockhammer, ``Dynamic adaptive streaming over HTTP: standards and design principles", in {\em Proceedings of the second annual ACM conference on Multimedia systems}, 2011.

\bibitem{SVC}
T.~Wiegand, G.~Sullivan, J.~Reichel, H.~Schwarz, M.~Wien, eds., ``Joint Draft ITU-T Rec. H.264|ISO/IEC 14496-10/Amd.3 Scalable Video Coding'', Joint Video Team, Doc. JVT-X201 Jul. 2007.

\bibitem{SVCOverview}
H.~Schwarz, D.~Marpe and T.~Wiegand, ``Overview of the scalable video coding extension of the H.264/AVC standard'', in {\em IEEE Trans. Circuits. Syst. Video Technol.}, vol. 17, no. 9, pp.~1103-1120, Sept. 2007.

\bibitem{DSS}
http://dss.macosforge.org/

\bibitem{Gao06}
K. Gao, J. Zhai, J. Li and C. Wang, ``Real-Time scheduling for scalable video coding streaming system'', in {\em IEEE Sarnoff Symposium}, Princeton, NJ, pp. 1-4, Mar. 2006.

\bibitem{Schierl10}
Y. Schierl, R. Sanchez, C. Globisch, Hellge, and T. Wiegand, ``Priority-based media delivery using SVC with RTP and HTTP streaming'', in {\em Multimedia Tools And Applications}, vol. 55, no.2, pp. 227-246, Sep. 2010.

\bibitem{Amonou07}
I.~Amonou, N.~Cammas, S.~Kervadec, S.~Pateux, ``Optimized Rate-distortion Extraction with Quality Layers in the Scalable Extension of H.264/AVC'' in {\em IEEE Trans. Circuits Syst. Video Technol.}, vol.~17, no.~9, pp.~1186--1193, Sep. 2007.

\bibitem{JSVM}
Text of ISO/IEC 14496-4:2001/PDAM 19 Reference Software for SVC, Joint Video Team (JVT) of ISO-IEC MPEG \& ITU-T VCEG, N9195, Sep. 2007.

\bibitem{Sun09}
J.~Sun, W.~Gao, D.~Zhao, W.~Li, ``On Rate-distortion Modeling and Extraction of H.264/SVC Fine-Granular Scalable Video'' in {\em IEEE Trans. Circuits Syst. Video Technol.}, vol.~19, no.~3, pp.~323--336, Mar. 2009.

\bibitem{Maani09}
E.~Maani, A.~K. Katsaggelos, ``Optimized Bit Extraction Using Distortion Modeling in the Scalable Extension of H.264/AVC'' in {\em IEEE Trans. Image Processing}, vol.~18, no.~9, pp.~2022--2029, Sep. 2009.

\bibitem{Zhang12}
W.~Zhang, J.~Sun, J.~Liu and Z.~Guo, ``Optimized bit extraction of SVC exploiting linear error model,'' {\em 2012 IEEE International Symposium on Circuits and Systems}, pp.~1887--1890, Seoul, Korea, May 2012.

\bibitem{PID}
http://en.wikipedia.org/wiki/PID\_controller

\bibitem{Astrom02}
K. J. Astrom, Control System Design, pp 216-219, 2002.

\bibitem{Wong04}
C.W.Wong, O.C.Au and H.K.Lam, ``PID-based real-time rate control'', in {\em IEEE International Conference on Multimedia and Expo}, 1: 221-224, 2004.

\bibitem{Yang10}
J. Yang, Y. Sun, Y. Zhou, S. Sun, ``Incremental rate control for H.264 scalable video coding'', in {\em IEEE Global Telecommunications Conference}, Miami, Florida, Dec. 2010.

\bibitem{Li98}
B. Li and K. Nahrstedt  ``A control theoretical model for quality of service adaptations'', in {\em Proceedings of Sixth International Workshop on Quality of Service}, 1998.

\bibitem{Li99}
B. Li and K. Nahrstedt, ``A control-sased middleware framework for Quality-of-Service adaptations'', in {\em IEEE J. Selected Areas in Comm.}, vol. 17, no. 9, pp. 1632-1650, Sept. 1999.

\bibitem{Ziegler42}
J. B. Ziegler and N. B. Nichols, ``Optimum settings for automatic controllers'', in {\em ASME Trans.}, pp. 759-768, 1942.

\bibitem{Winken08}
M.~Winken, H.~Schwarz, T.~Wiegand, ``Joint Rate-distortion Optimization of Transform Coefficients for Spatial Scalable Video Coding Using SVC'' in {\em Proc. International Conference on Image Processing 2008}.

\bibitem{H264Overview}
T.~Wiegand, G.~J. Sullivan, G.~Bj$\o$ntegaard, A.~Luthra, ``Overview of the H.264/AVC Video Coding Standard'', in {\em IEEE Trans. Circuits Syst. Video Technol.}, vol. 13, no. 7, pp.~560--576, Jul. 2003.

\bibitem{GreedyAlgo}
P.~E.~Black, ``Greedy Algorithm'' in {\em Dictionary of Algorithms and Data Structures} [online], U.S. National Institute of Standards and Technology, Feb. 2005.
\newblock http://www.nist.gov/dads/HTML/greedyalgo.html

\bibitem{Netlimiter}
NetLimiter: http://www.netlimiter.com/

\bibitem{HEVC}
G.~J.~Sullivan, J.-R.~Ohm, W.-J.~Han, and T.~Wiegand, ``Overview of the High Efficiency Video Coding (HEVC) standard'' in {\em IEEE Trans. Circuits Syst. Video Technol.}, vol.~22, no.~12, pp.~1648–1667, Dec. 2012.

\end{thebibliography}

% that's all folks
\end{document}

### 2015-02-04 tmm.tex
readable version for TMM

@@
 % Do not put math or special symbols in the title.
-\title{Scalable Video Streaming with PID-Based Quality Control and Optimized Bitstream Extraction}
+\title{Adaptive Video Streaming System with PID-Based Quality Control and Optimized Bitstream Extraction}
 
@@
 \begin{abstract}
-In order to meet the challenge brought by bandwidth fluctuation of the user's network, modern video streaming systems tend to be scalable, i.e., of flexible bitrate and adaptive video quality.
-This paper gives solutions for two key problems within such a scalable video streaming system.
-We first propose a quality control algorithm, which allows the video streaming system to adjust its video quality along with the real bandwidth change.
-The algorithm is based on the Proportional-Integral-Derivative (PID) control method and can deliver best video quality with least quality fluctuation.
-Then for streaming systems that adopt Scalable Video Coding (SVC), we present an efficient solution for the bitstream extraction problem, which aims to select an optimal sub-stream from the whole bitstream under given bitrate constraint.
-This solution features a linear error model, which is utilized to estimate the distortion caused by discarding any combination of data packets, and a greedy algorithm scheme, which assigns each data packet a priority value to use for the R-D optimized extraction.
-Experimental results show that our quality control algorithm can drastically reduce the quality fluctuation while still keeping a high quality level, and the bitstream extraction method can achieve a significant PSNR gain compared to the extractors of JSVM, without computational complexity increment.
-The quality control algorithm has also been implemented in online video website www.7dlive.com and turns out to be practically effective in applications.
+In order to meet the challenge brought by bandwidth fluctuation of the user's network, modern video streaming systems tend to be adaptive, i.e., able to adjust the video quality according to available bandwidth.
+This paper implements such an adaptive video streaming system which utilizes the Scalable Video Coding (SVC) technology, and gives novel solutions for two key problems within the system.
+First, a quality control algorithm is proposed for the video streaming system to adjust its video quality along with the real bandwidth change.
+The algorithm is based on the Proportional-Integral-Derivative (PID) control method and designed to deliver best video quality with least quality fluctuation.
+Second, an efficient solution is present for the bitstream extraction problem, which aims to select an optimal sub-stream from the whole SVC video bitstream under given bitrate constraint.
+The solution features a linear error model to estimate the distortion caused by discarding any combination of data packets, and a greedy algorithm scheme to assign each data packet a priority value for Rate-Distortion optimized extraction.
+Experimental results show that the PID-based quality control algorithm can drastically reduce the quality fluctuation while still keeping a high quality level, and the bitstream extraction method can achieve a significant PSNR gain compared to existing reference extractors, without computational complexity increment.
+The system is currently running at the online video website www.7dlive.com and proves to be practically effective.
 \end{abstract}
@@
 \IEEEPARstart{V}{ideo} streaming applications are becoming more and more popular on the Internet.
-Examples of the most common usage scenarios include VOD (Video On Demand), live broadcasting, video-based online education, and so on.
+Examples of the most common usage scenarios include VOD (Video On Demand), live broadcasting, video-based online education, etc.
 In these applications, video data is constantly delivered to different clients over various transmission channels, and the client media player can begin playing the video before the entire file has been transmitted.
@@
 One of the biggest challenge for video streaming is the variety of users' network environment.
-The users may use various types of network (Ethernet, Wi-Fi, Cellular, etc) and may also switch to a different one on going (e.g., from Wi-Fi to cellular network).
-Even in the same network, a user's available bandwidth may change from time to time, influenced by the overall traffic.
+A user may use different types of network (Ethernet, Wi-Fi, Cellular, etc) and may also switch from one type to another (e.g., from Wi-Fi to cellular network) on going.
+Even in the same network, the user's bandwidth may change from time to time, influenced by the overall traffic.
 During such an environment, bandwidth fluctuation is inevitable.
 If the video is streamed at a constant bitrate, it would be difficult or impossible for the client to keep a non-paused smooth playing.
-Therefore, to achieve better watching experience for users with various network environments, we should be able to adjust the video's bitrate or quality according to the bandwidth change.
-In other words, the video streaming system needs to be scalable.
-
-There are two options to enable scalable video streaming.
-The first option is called simulcast, where several independent bitstreams are stored at the server side, and the client selects one of them according to its current bandwidth.
-Dynamic Adaptive Streaming over HTTP (DASH) \cite{DASH}, which is standardized by MPEG, mostly uses this option.
-Simulcast systems like DASH can provide some scalability and is relatively easy to deploy.
-However, the scalability it provides is limited to the number of streams, and the processing and storage of multiple streams significantly increase time and space cost.
-On the contrary, the second option, which is to adopt Scalable Video Coding (SVC) \cite{SVC}, does not have above shortcomings.
-Compared to simulcast, SVC provides seamless scalability and higher coding efficiency, thus is a better choice to build a scalable video streaming system.
-While our work in this paper can be partly adapted to the simulcast system, we will mainly focus on the second option, i.e., SVC streaming system.
-
-The generally-known term SVC usually refers to the scalable extension of the H.264/AVC video coding standard \cite{SVCOverview}, which has provided an effective way to deal with the new challenges of modern video applications.
-SVC allows efficient scalability in terms of video frame rate, spatial resolution, and picture fidelity, with only one single bitstream.
-The SVC bitstream is composed of Network Abstract Layer Units (NALUs), which are separated into multiple layers: one base layer for basic video quality and several enhancement layers for video quality improvement.
-By discarding NALUs of the enhancement layers, the bitstream can be extracted as required, providing the most appropriate data rate and video service according to the client capability and network conditions.
-
-In SVC streaming system, there are two important issues that need to be addressed.
+Therefore, to achieve better watching experience for users with various network environment, the video's bitrate or quality should be able to adjust according to the bandwidth change.
+In other words, the video streaming system needs to be adaptive.
+
+There are generally two options to enable adaptive video streaming.
+The first option is called simulcast, where several independent bitstreams with different video quality are stored at the server, and the client selects one of them according to currently available bandwidth.
+Dynamic Adaptive Streaming over HTTP (DASH) \cite{DASH}, which is standardized by the Moving Picture Expert Group (MPEG), belongs to this option.
+The second option is to adopt the Scalable Video Coding (SVC) \cite{SVC} technology, which allows efficient scalability of video bitrate and quality with only one single bitstream.
+The generally-known term SVC usually refers to the scalable extension of the H.264/AVC video coding standard \cite{SVCOverview}.
+In SVC, a video bitstream is composed of Network Abstract Layer Units (NALUs), which are separated into multiple layers: one base layer for basic video quality and multiple enhancement layers for video quality improvement.
+By discarding NALUs of the enhancement layers, the bitstream can be extracted to provide the most appropriate data rate and video quality as required.
+
+The advantage of simulcast systems is that they need little modification of existing infrastructure and therefore are easy to deploy.
+Most commercial video websites, YouTube \cite{YouTube} for instance, use this option to enable quality adaptation.
+However, the adaptive range and granularity simulcast provides is strictly limited to the number of streams (YouTube videos have 5 quality levels at most: 240p, 360p, 480p, 720p and 1080p), and the processing and storage of multiple video streams significantly increase time and space cost.
+SVC streaming systems, on the contrary, do not have above shortcomings.
+An SVC video bitstream can be extracted at the granularity of one NALU (a very small partition of data), and thus can provide seamless scalability and adaptation.
+Besides, performance analysis \cite{SVCPerformance} shows that SVC also has much higher coding efficiency than simulcast, despite some computation and bitrate overhead comparing with single layer stream.
+Therefore, SVC is considered to be a better choice for adaptive video streaming systems.
+While our work in this paper can be partly used in a simulcast system, we will mainly focus on building an adaptive streaming system using SVC.
+
+To guarantee good performance of SVC streaming system, there are two important issues that need to be addressed well.
 First is quality control, and the second is bitstream extraction.
@@
 Once the bandwidth has changed, the quality control algorithm should determine a bitrate suitable for the current bandwidth.
-Given this bitrate, how to extract from the whole SVC stream to form a optimal sub-stream becomes the bitstream extraction problem.
-Optimized bitstream extraction aims to select a subset of data which represents video with best quality, or minimal distortion, under the constrain of given bitrate.
-It should be noted that, bitstream extraction is not only useful in scalable video streaming, but also in other SVC application scenarios where part of data needs to be obtained or kept, e.g., the archiving of surveillance video.
-
-In this paper, we propose novel solutions for these two issues and construct an efficient scalable video streaming system.
+Given this bitrate, how to extract data from the whole SVC stream to form an optimal sub-stream becomes the bitstream extraction problem.
+Optimized bitstream extraction aims to select a subset of NALUs (or packets) which represents video with best quality, or minimal distortion, under the constrain of the given bitrate.
+It should be noted that, bitstream extraction is not only useful in adaptive video streaming, but also in other SVC application scenarios where part of data needs to be obtained or kept, e.g., the archiving of surveillance video.
+
+In this paper, we propose novel solutions for these two issues and construct an efficient adaptive video streaming system.
 Apple Darwin Streaming Server (DSS) \cite{DSS}, which has been widely used to collect, cache, schedule and transmit multimedia contents in practice, is chosen as the basis of the system.
@@
 A new quality control algorithm based on the Proportional-Integral-Derivative (PID) control concept is proposed to replace the native one in DSS, and achieves higher average quality level with less quality fluctuation.
-In this algorithm, we can monitor and even predict the relationship between the network bandwidth and the current video data rate, so that quality adjustment can be made at any time and to any extent, accurately and smoothly.
 For the bitstream extraction problem, we propose a linear error model to directly estimate pixel value errors before MSE or PSNR is calculated.
-The linear error model exploits the linear feature of H.264/AVC coding process and achieves good performance in distortion estimation.
-Using this model, the error caused by the removal of each enhancement packet can be obtained independently.
-This enables us to estimate the distortion caused by discarding any combination of packets.
-Based on that, we design a greedy algorithm to calculate the priority of each quality enhancement packet according to its R-D impact.
-The priority value of packets can be stored in the bitstream and used for optimized extraction.
-The proposed algorithms perform well in experiments and the quality control algorithm is also used in practical streaming systems and proved quite effective.
+This model enables us to accurately estimate the distortion caused by discarding any combination of packets.
+Based on that, we design a greedy algorithm to assign priority for each quality enhancement packet according to its rate-distortion (R-D) impact.
+The priority value of each packet can be stored in the bitstream and used for optimized extraction.
+The proposed algorithms perform well in experiments and the quality control algorithm is also implemented in the practical streaming system we construct and proved quite effective.
 
@@
 
-In this section, we analyze the two most concerned problems in SVC streaming, i.e., quality control and bitstream extraction, and introduce some existing related works on them.
+In this section, we analyze the two most concerned problems in SVC adaptive streaming, i.e., quality control and bitstream extraction, and introduce some existing related works on them.
 
@@
 This framework has been adopted by the SVC reference software, i.e., JSVM  \cite{JSVM}, and achieves better R-D performance compared with the basic extractor of JSVM.
-In Amonou's framework, a Quality Layer value, which reflects a packet's rate-distortion (R-D) impact, is calculated and used for R-D optimized bitstream extraction.
+In Amonou's framework, a Quality Layer value, which reflects a packet's R-D impact, is calculated and used for R-D optimized bitstream extraction.
 The process of obtaining distortion impact of every packet is extremely time consuming, and the distortion estimation accuracy can also be further improved.
 So other distortion/error models were proposed to either reduce the computational complexity or improve the estimation accuracy.
-Sun \cite{Sun09} and Maani \cite{Maani09} constructed models to calculate distortion based on the drift propagation between frames.
-Sun's method is almost as good as JSVM for the performance, but with a much reduced complexity.
-Maani's model can achieve better estimation accuracy than JSVM; however, in order to get robust and accurate model parameters, more computation is needed for training.
+Sun et al.
+\cite{Sun09} and Maani et al.
+\cite{Maani09} constructed models to calculate distortion based on the drift propagation between frames.
+Sun et al.'s method is almost as good as JSVM in regard of performance, but has much reduced complexity.
+Maani et al.'s model can achieve better estimation accuracy than JSVM; however, since it is  a training-based model, more computation is needed to get robust model parameters.
 
@@
 The linear error model exploits the linear feature of pixel value errors and achieves good performance in distortion estimation and bitstream extraction with reference.
-However, this work assumes that the original sequence is available for reference, which is not always true.
-It needs adaption for widespread application.
-
-The following of this paper will present solutions for the above problems, and lay a solid foundation for a practical scalable video streaming system.
+However, this work assumes that the original video sequence is available for reference, which is not always true.
+Adaptation to handle the special characteristic of the no-reference case is lacking, and is included in this paper.
+
+The following of this paper will present solutions for the above problems, and lay a solid foundation for a practical adaptive video streaming system.
 
@@
 For instance, in \cite{Wong04} a PID-based real time rate control scheme is proposed to trade-off between spatial and temporal quality and smooth the video quality between frames; in \cite{Yang10}, the authors designed an incremental rate control algorithm for H.264/SVC, in which the PID method is used to provide robust buffer control for each layer.
-We also notice some researchers have proposed theoretical model or middle-ware framework for QoS adaptation \cite{Li98}\cite{Li99}, with PID as the basic control concept.
+We also notice that some researchers have proposed theoretical model or middle-ware framework for QoS adaptation \cite{Li98}\cite{Li99}, with PID as the basic control concept.
 However, we have not found any paper that integrates PID method into the quality control of video streaming.
@@
 Then we define the process variable used in our PID-based quality control algorithm.
-After that, the PID-based quality control algorithm is formulated and explained in detail, followed by the brief discussion of parameter selection.
+After that, the algorithm is formulated and explained in detail, followed by the brief discussion of parameter selection.
 
@@
 
-The video bitrate or quality is a continuous value.
+The video quality is a continuous value.
 In practical operation, it is not possible to control it at an arbitrary precision.
@@
 Each quality level corresponds to a certain bitrate.
-A Higher quality level corresponds to a higher bitrate, vice versa.
-The number of quality levels and how they are mapped to sub-streams with different bitrates depends on requirement or implementation.
+A higher quality level corresponds to a higher bitrate and vice versa.
+The number of quality levels and how they are mapped to sub-streams with different bitrates depends on actual requirement or implementation.
 The more quality levels are defined, the more precisely the control algorithm can adjust bitrate to follow the bandwidth change.
+As pointed out in section \ref{sec:intro}, simulcast streaming systems can only have limited quality levels while SVC streaming systems can define quality levels at a much finer granularity.
 
@@
 
-For DSS, two timelines are important.
+In DSS, two timelines are important.
 Push timeline indicates the time of pushing video data packets to streaming buffer, and play timeline indicates the time these data packet should be played, i.e., the presentation time stamp (often seen as PTS) of each packet.
@@
 \includegraphics[width = 0.9\linewidth]{intervals.jpg}
-\caption{Push Time and Play Time \label{fig:intervals}}
+\caption{Two timelines in Darwin Streaming Sever (DSS) \label{fig:intervals}}
 \end{figure}
@@
  \includegraphics[width = 0.9\linewidth]{GOPStructure.jpg}
- \caption{SVC GOP structure \label{fig:GOP_Structure}}
+ \caption{Group of pictures (GOP) in SVC \label{fig:GOP_Structure}}
  \end{figure}
@@
 
-In this paper, we propose a scalable video streaming system with PID-based quality control algorithm and optimized bitstream extraction.
+In this paper, we propose an adaptive video streaming system with PID-based quality control algorithm and optimized bitstream extraction.
 The PID-based quality control algorithm has a flexible mechanism to determine the suitable quality level so that it gives an accurate and swift response to the bandwidth change.
@@
 
-The PID-based quality control algorithm of this paper has already been integrated into the online scalable video streaming website www.7dlive.com and performs well in automatically adapting to the user's bandwidth fluctuation.
+The PID-based quality control algorithm of this paper has already been integrated into the online website www.7dlive.com and performs well in automatically adapting to the user's bandwidth fluctuation.
 This algorithm can also be easily used in other streaming systems, e.g., DASH systems.
@@
 
+\bibitem{YouTube}
+https://www.youtube.com/
+
+\bibitem{SVCPerformance}
+M. Wien , H. Schwarz and T. Oelbaum,  ``Performance Analysis of SVC'',  in {\em IEEE Trans. Circuits Syst. Video Technol.}, vol. 17, no. 9, pp.1194-1203. Sep. 2007.
+
 \bibitem{DSS}
@@
 Wiegand, ``Priority-based media delivery using SVC with RTP and HTTP streaming'', in {\em Multimedia Tools And Applications}, vol.
-55, no.2, pp.
+55, no.
+2, pp.
 227-246, Sep.

### 2015-02-05 tmm.tex
the version I sent to Sun

@@
 \usepackage{algorithm}
+\usepackage{balance}
 
@@
 % Do not put math or special symbols in the title.
-\title{Adaptive Video Streaming System with PID-Based Quality Control and Optimized Bitstream Extraction}
+\title{Adaptive Video Streaming with PID-Based Quality Control and Optimized Bitstream Extraction}
 
@@
 \thanks{S. Meng is with the Institute of Computer Science and Technology, Peking University, Beijing%
-, 100080 China e-mail: shengbin@pku.edu.cn.}% <-this % stops a space
+, China, 100080. E-mail: shengbin@pku.edu.cn.}% <-this % stops a space
 \thanks{J. Sun, Y. Duan, Z. Guo are with the Institute of Computer Science and Technology, Peking University.}% <-this % stops a space
-\thanks{Manuscript received September 15, 2014}}
+}%\thanks{Manuscript received September 15, 2014}}
 
@@
 
-\listoffigures
-
-\listoftables
+%\listoffigures
+
+%\listoftables
 
@@
 The generally-known term SVC usually refers to the scalable extension of the H.264/AVC video coding standard \cite{SVCOverview}.
-In SVC, a video bitstream is composed of Network Abstract Layer Units (NALUs), which are separated into multiple layers: one base layer for basic video quality and multiple enhancement layers for video quality improvement.
+In SVC, a video bitstream is composed of small data packets called Network Abstract Layer Units (NALUs).
+These NALUs are separated into multiple layers: one base layer for basic video quality and multiple enhancement layers for video quality improvement.
 By discarding NALUs of the enhancement layers, the bitstream can be extracted to provide the most appropriate data rate and video quality as required.
@@
 The advantage of simulcast systems is that they need little modification of existing infrastructure and therefore are easy to deploy.
-Most commercial video websites, YouTube \cite{YouTube} for instance, use this option to enable quality adaptation.
+Most existing video websites, YouTube \cite{YouTube} for instance, use this option to enable quality adaptation.
 However, the adaptive range and granularity simulcast provides is strictly limited to the number of streams (YouTube videos have 5 quality levels at most: 240p, 360p, 480p, 720p and 1080p), and the processing and storage of multiple video streams significantly increase time and space cost.
@@
 Then in section \ref{sec:quality-control}, the proposed quality control algorithm is formulated and explained with term definitions and parameters selection.
-After that, we propose the solution for the bitstream extraction problem in \ref{sec:bit-extraction}.
+After that, we propose the solution for the bitstream extraction problem in section \ref{sec:bit-extraction}.
 Section \ref{sec:experiment} lists the experimental results and compares our proposed solution with others.
@@
 SVC bitstream extraction is substantially a combinatorial optimization problem.
-More specifically, it is in the form of ``0-1 Knapsack Problem".
-Each NALU data packet can be treated as an object with certain value (its contribution to the video quality) and weight (its size).
-The solving process is mainly to decide whether or not a packet should be included in the final extracted sub-stream; or in the term of ``0-1 Knapsack Problem", to choose which object to pack up.
+More specifically, it is in the form of ``0-1 Knapsack Problem" \cite{Knapsack}.
+In the ``0-1 Knapsack Problem", given a set of objects, each with a weight and a value, one decides which object to include in the knapsack so that the total weight is no more than a given limit and the total value is as large as possible.
+Similarly, in bitstream extraction problem, each NALU data packet can be treated as an item with certain weight (the packet's size) and value (its contribution to the video quality).
+The solving process is mainly to decide whether or not a packet should be included in the final extracted sub-stream, or in the term of ``0-1 Knapsack Problem", to choose which object to pack up.
 
@@
 However, this work assumes that the original video sequence is available for reference, which is not always true.
-Adaptation to handle the special characteristic of the no-reference case is lacking, and is included in this paper.
-
-The following of this paper will present solutions for the above problems, and lay a solid foundation for a practical adaptive video streaming system.
+Adaptation to handle the special characteristic of the no-reference case is lacking in the previous work and included in this paper.
+
+The following of this paper will present solutions for the above problems in detail.
+We have published the related ideas in conference papers \cite{Meng14}\cite{Meng14-PID}, and in this paper we combine our previous works together and lay a solid foundation for a practical adaptive video streaming system.
 
@@
 In normal PID control, the controller output is calculated using the proportion, integral and differential of the error between the process variable and the setpoint, as shown in (\ref{eq:pid-output}).
-Considering that our process variable is a ratio and the corresponding setpoint is 1, we make a little modification to the general PID controller and obtain a ratio-based model.
+Considering that the chosen process variable is a ratio and the corresponding setpoint is 1, we make a little modification to the general PID controller and obtain a ratio-based model.
 In this model, the ratio is directly used to calculate the controller output, and all subtraction operations in original PID equations have been changed to division operations to keep the correctness, as follows:
@@
 In the following experiments, parameters are chosen as $K_p = 0.22$, $K_i = 0.73$, $K_d = 0.05$ by this method.
-Note that, in the quality control algorithm, only the data rate and the bandwidth are considered, not the video content, so once the parameters are tuned they should apply well to different video streams.
+As with other control systems, PID parameters are a result of tunning and may not suit to all use cases.
+However, it should be noted that in the video quality control algorithm, only the data rate and the bandwidth are considered, not the video content, so once the parameters are tuned they should apply well to different video streams.
 
@@
 packet 2, 4 and 20) should be allocated in two groups -- one for key frame packets of even number GOPs (packet 2 and 20), the other for those of odd number GOPs (packet 4).
-So the actual number of extraction and decoding for error vector acquisition is $(L_Q - 1) \cdot (L_T + 1)$, approximately the same with JSVM reference software\cite{H264Overview}.
-Since computation is mainly consumed with this decoding in our bitstream extraction algorithm, the computation complexity has no obvious promotion compared with JSVM.
+So the actual number of extraction and decoding for error vector acquisition is $(L_Q - 1) \cdot (L_T + 1)$, approximately the same with the Quality Layer information acquisition in JSVM \cite{Amonou07}.
+Since computation is mainly consumed with this decoding in the bitstream extraction algorithm, the computation complexity has no obvious promotion compared with JSVM.
 
@@
 
-To verify the linear error model, we conduct an experiment where some random sets of enhancement packets are removed from a video bitstream, and the distortion estimated by the linear error model are compared with the actual distortion.
+To verify the linear error model, we conduct an experiment where possible combinations of enhancement packets are removed from a video bitstream, and the distortion estimated by the linear error model are compared with the actual distortion caused by the removal.
+The video stream has 8-frame GOPs and three quality layers, the same as illustrated in Fig.
+\ref{fig:GOP_Structure}.
 Experimental result of the sequence {\em Foreman} is partly shown in Fig.
 \ref{fig:linear_verification}.
-The horizontal axis stands for sample point numbers of those random selections, and the vertical axis for MSE measurement.
+The horizontal axis stands for sample point numbers of those possible combinations, and the vertical axis for MSE measurement.
 The solid line represents the actual MSE of a randomly extracted substream, and the dot line shows the estimated MSE using our Linear Error Model.
@@
 However, the integration of the proposed bitstream extraction method needs more engineering work and has not been accomplished.
-Therefore, in this section, we present separate experiments to demonstrate the advantage of each proposed solution.
+Therefore, in this section, we only present separate experiments to demonstrate the advantage of each proposed solution.
+Readers who are interested in the practical implementation are encouraged to visit the online video website http://www.7dlive.com for more information.
 
@@
 
+\bibitem{Knapsack}
+http://en.wikipedia.org/wiki/Knapsack\_problem
+
 \bibitem{Schierl10}
@@
 
+\bibitem{Meng14}
+Shengbin Meng, Jun Sun, Yizhou Duan, Zongming Guo, ``An Efficient Method For No-Reference H.264/SVC Bitstream Extraction'', {\em IEEE International Conference on Acoustics, Speech, and Signal Processing}, Florence, Italy, May, 2014.
+
+\bibitem{Meng14-PID}
+Shengbin Meng, Jun Sun, Yilei Wang, Zongming Guo, ``A PID-based Quality Control Algorithm for SVC Video Streaming'', {\em IEEE International Conference on Communications}, Sydney, Australia, June, 2014.
+
 \bibitem{PID}
@@
 
+\balance
+
 % that's all folks

### 2015-02-06 tmm.tex
changed the abstract, before the introduction

@@
 %
-\author{Shengbin~Meng,~Jun~Sun,~Yizhou~Duan~and~Zongming~Guo % <-this % stops a space
-\thanks{S. Meng is with the Institute of Computer Science and Technology, Peking University, Beijing%
-, China, 100080. E-mail: shengbin@pku.edu.cn.}% <-this % stops a space
-\thanks{J. Sun, Y. Duan, Z. Guo are with the Institute of Computer Science and Technology, Peking University.}% <-this % stops a space
-}%\thanks{Manuscript received September 15, 2014}}
+\author{Shengbin~Meng,~Jun~Sun,~Yizhou~Duan~and~Zongming~Guo,~\em{Member,~IEEE} % <-this % stops a space
+\thanks{Manuscript received Febrary 15, 2015.}
+\thanks{The authors are with the Institute of Computer Science and Technology, Peking University, Beijing%
+, 100080, China (e-mail: shengbin@pku.edu.cn; sunjun@pku.edu.cn; duanyizhou@pku.edu.cn; guozongming@pku.edu.cn).}}
 
@@
 \begin{abstract}
-In order to meet the challenge brought by bandwidth fluctuation of the user's network, modern video streaming systems tend to be adaptive, i.e., able to adjust the video quality according to available bandwidth.
-This paper implements such an adaptive video streaming system which utilizes the Scalable Video Coding (SVC) technology, and gives novel solutions for two key problems within the system.
-First, a quality control algorithm is proposed for the video streaming system to adjust its video quality along with the real bandwidth change.
-The algorithm is based on the Proportional-Integral-Derivative (PID) control method and designed to deliver best video quality with least quality fluctuation.
-Second, an efficient solution is present for the bitstream extraction problem, which aims to select an optimal sub-stream from the whole SVC video bitstream under given bitrate constraint.
-The solution features a linear error model to estimate the distortion caused by discarding any combination of data packets, and a greedy algorithm scheme to assign each data packet a priority value for Rate-Distortion optimized extraction.
-Experimental results show that the PID-based quality control algorithm can drastically reduce the quality fluctuation while still keeping a high quality level, and the bitstream extraction method can achieve a significant PSNR gain compared to existing reference extractors, without computational complexity increment.
+This paper proposes an adaptive video streaming system that adjusts the video quality according to available bandwidth and gives the user best quality of service under various network conditions.
+Two key problems within the system are analyzed and solved with novel algorithms.
+First, we utilize the Proportional-Integral-Derivative (PID) method in video quality control to determine a suitable bitrate for transmission, so that the system can deliver highest video quality with least quality fluctuation.
+Second, to select an optimal sub-stream for transmission under given bitrate constraint, we use a linear error model to estimate the distortion caused by discarding any combination of data packets, and a greedy algorithm scheme to assign each data packet a priority value for Rate-Distortion optimized extraction.
+Experimental results show that the PID-based quality control algorithm brings 8.6\% higher video quality as well as 24.8\% lower quality fluctuation than the baseline algorithm, and the bitstream extraction method achieves a PSNR gain of up to 0.5dB compared to existing reference extractors, with no computational complexity increment.
 The system is currently running at the online video website www.7dlive.com and proves to be practically effective.
@@
 During such an environment, bandwidth fluctuation is inevitable.
-If the video is streamed at a constant bitrate, it would be difficult or impossible for the client to keep a non-paused smooth playing.
-Therefore, to achieve better watching experience for users with various network environment, the video's bitrate or quality should be able to adjust according to the bandwidth change.
+If the video is streamed at a constant bitrate, it would be difficult or impossible for the user to get best watching experience.
+To cope with the challenge, modern video streaming systems should be able to automatically adjust the video's bitrate or quality according to the bandwidth change.
 In other words, the video streaming system needs to be adaptive.
@@
 The first option is called simulcast, where several independent bitstreams with different video quality are stored at the server, and the client selects one of them according to currently available bandwidth.
-Dynamic Adaptive Streaming over HTTP (DASH) \cite{DASH}, which is standardized by the Moving Picture Expert Group (MPEG), belongs to this option.
-The second option is to adopt the Scalable Video Coding (SVC) \cite{SVC} technology, which allows efficient scalability of video bitrate and quality with only one single bitstream.
+The second option is to adopt the Scalable Video Coding (SVC) \cite{SVC} technology, which allows scalability of video bitrate and quality with only one single bitstream.
 The generally-known term SVC usually refers to the scalable extension of the H.264/AVC video coding standard \cite{SVCOverview}.
@@
 SVC streaming systems, on the contrary, do not have above shortcomings.
-An SVC video bitstream can be extracted at the granularity of one NALU (a very small partition of data), and thus can provide seamless scalability and adaptation.
+Since an SVC video bitstream can be extracted at the granularity of one NALU (a very small partition of data), it is able to provide seamless scalability and quality adaptation.
 Besides, performance analysis \cite{SVCPerformance} shows that SVC also has much higher coding efficiency than simulcast, despite some computation and bitrate overhead comparing with single layer stream.
 Therefore, SVC is considered to be a better choice for adaptive video streaming systems.
-While our work in this paper can be partly used in a simulcast system, we will mainly focus on building an adaptive streaming system using SVC.
-
-To guarantee good performance of SVC streaming system, there are two important issues that need to be addressed well.
-First is quality control, and the second is bitstream extraction.
-Quality control means controlling the video quality (as well as the bitrate) to follow the change of bandwidth.
+While the work of this paper can be partly used in a simulcast system, it will mainly focus on the adaptive streaming system using SVC.
+
+In a video streaming system using SVC, there are two key problems that need to be addressed well.
+The first is quality control, and the second is bitstream extraction.
+Quality control means controlling the video quality (or the video bitrate, from the transmission point of view) to follow the change of the bandwidth.
 Once the bandwidth has changed, the quality control algorithm should determine a bitrate suitable for the current bandwidth.
@@
 
-In this paper, we propose novel solutions for these two issues and construct an efficient adaptive video streaming system.
-Apple Darwin Streaming Server (DSS) \cite{DSS}, which has been widely used to collect, cache, schedule and transmit multimedia contents in practice, is chosen as the basis of the system.
-We modified the original DSS project and added SVC support to it, for the purpose of both research and application.
-A new quality control algorithm based on the Proportional-Integral-Derivative (PID) control concept is proposed to replace the native one in DSS, and achieves higher average quality level with less quality fluctuation.
-For the bitstream extraction problem, we propose a linear error model to directly estimate pixel value errors before MSE or PSNR is calculated.
-This model enables us to accurately estimate the distortion caused by discarding any combination of packets.
-Based on that, we design a greedy algorithm to assign priority for each quality enhancement packet according to its rate-distortion (R-D) impact.
-The priority value of each packet can be stored in the bitstream and used for optimized extraction.
-The proposed algorithms perform well in experiments and the quality control algorithm is also implemented in the practical streaming system we construct and proved quite effective.
+In this paper, an efficient adaptive video streaming system based on SVC is proposed.
+Apple Darwin Streaming Server (DSS) \cite{DSS}, which is open-sourced and has been widely used to stream multimedia contents in practice, is chosen as the basis of the system.
+The original DSS project is modified by us and SVC support is added to it, for the purpose of both research and application.
+Then novel algorithms are designed and implemented to better solve the two key problems mentioned above.
+The contributions of our work are threefold:
+\begin{itemize}
+\item A quality control algorithm based on the Proportional-Integral-Derivative (PID) control concept is proposed to replace the native one in DSS, and achieves higher average quality level with less quality fluctuation.
+\item A linear error model is proposed to accurately estimate the distortion caused by discarding any combination of packets from a SVC bitstream.
+\item A greedy-like algorithm is designed to assign priority for each packet, thus enables optimized bitstream extraction.
+\end{itemize}
 
@@
 Then in section \ref{sec:quality-control}, the proposed quality control algorithm is formulated and explained with term definitions and parameters selection.
-After that, we propose the solution for the bitstream extraction problem in section \ref{sec:bit-extraction}.
+After that, we present the solution for the bitstream extraction problem in section \ref{sec:bit-extraction}, including the linear error model and the greed-like algorithm.
 Section \ref{sec:experiment} lists the experimental results and compares our proposed solution with others.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Optimized Bitstream Extraction Based On Linear Error Model}
+\section{Optimized Bitstream Extraction Based on Linear Error Model}
 \label{sec:bit-extraction}
@@
 
-\subsection{Distortion Estimation And Model Verification}
+\subsection{Distortion Estimation and Model Verification}
 
@@
 The packets' priority values can then be stored in the bitstream and used for R-D optimized extraction.
-Experimental results show that the proposed method can achieve PSNR gain of up to 0.5 compared to the JSVM QL extractor under the same bitrate constrain, also with the same computational complexity.
+Experimental results show that the proposed method can achieve PSNR gain of up to 0.5dB compared to the JSVM QL extractor under the same bitrate constrain, also with the same computational complexity.
 

### 2015-02-06 tmm.tex
introduction with long paragraph

@@
 The first option is called simulcast, where several independent bitstreams with different video quality are stored at the server, and the client selects one of them according to currently available bandwidth.
+Simulcast systems need little modification of existing infrastructure and therefore are easy to deploy.
+Most commercial video websites, YouTube \cite{YouTube} for instance, use this option to enable quality adaptation.
+However, the adaptive range and granularity simulcast provides is strictly limited to the number of streams (YouTube videos have 5 quality levels at most: 240p, 360p, 480p, 720p and 1080p), and the processing and storage of multiple video streams significantly increase time and space cost.
 The second option is to adopt the Scalable Video Coding (SVC) \cite{SVC} technology, which allows scalability of video bitrate and quality with only one single bitstream.
@@
 By discarding NALUs of the enhancement layers, the bitstream can be extracted to provide the most appropriate data rate and video quality as required.
-
-The advantage of simulcast systems is that they need little modification of existing infrastructure and therefore are easy to deploy.
-Most existing video websites, YouTube \cite{YouTube} for instance, use this option to enable quality adaptation.
-However, the adaptive range and granularity simulcast provides is strictly limited to the number of streams (YouTube videos have 5 quality levels at most: 240p, 360p, 480p, 720p and 1080p), and the processing and storage of multiple video streams significantly increase time and space cost.
-SVC streaming systems, on the contrary, do not have above shortcomings.
-Since an SVC video bitstream can be extracted at the granularity of one NALU (a very small partition of data), it is able to provide seamless scalability and quality adaptation.
-Besides, performance analysis \cite{SVCPerformance} shows that SVC also has much higher coding efficiency than simulcast, despite some computation and bitrate overhead comparing with single layer stream.
-Therefore, SVC is considered to be a better choice for adaptive video streaming systems.
+SVC streaming systems do not have the shortcomings of simulcast because: 1) since an SVC video bitstream can be extracted at the granularity of one NALU (a very small partition of data), it is able to provide seamless scalability and quality adaptation; and 2) performance analysis \cite{SVCPerformance} shows that SVC also has much higher coding efficiency than simulcast, despite some computation and bitrate overhead comparing with single layer stream.
+Due to these advantages, we choose to adopt SVC in our adaptive video streaming system.
 While the work of this paper can be partly used in a simulcast system, it will mainly focus on the adaptive streaming system using SVC.

### 2015-02-06 tmm.tex
introduction with shorter paragraphs; the 2rd version sent to Sun

--- 2015-02-06 tmm.tex
@@
 If the video is streamed at a constant bitrate, it would be difficult or impossible for the user to get best watching experience.
-To cope with the challenge, modern video streaming systems should be able to automatically adjust the video's bitrate or quality according to the bandwidth change.
+To cope with this challenge, the video streaming system should be able to automatically adjust the video's bitrate or quality according to the bandwidth change.
 In other words, the video streaming system needs to be adaptive.
@@
 The first option is called simulcast, where several independent bitstreams with different video quality are stored at the server, and the client selects one of them according to currently available bandwidth.
+Dynamic Adaptive Streaming over HTTP (DASH) \cite{DASH}, which is standardized by the Moving Picture Expert Group (MPEG), belongs to this option.
 The second option is to adopt the Scalable Video Coding (SVC) \cite{SVC} technology, which allows scalability of video bitrate and quality with only one single bitstream.
@@
 In SVC, a video bitstream is composed of small data packets called Network Abstract Layer Units (NALUs).
-These NALUs are separated into multiple layers: one base layer for basic video quality and multiple enhancement layers for video quality improvement.
+These NALUs are separated into one base layer for basic video quality and multiple enhancement layers for video quality improvement.
 By discarding NALUs of the enhancement layers, the bitstream can be extracted to provide the most appropriate data rate and video quality as required.
@@
 The advantage of simulcast systems is that they need little modification of existing infrastructure and therefore are easy to deploy.
-Most existing video websites, YouTube \cite{YouTube} for instance, use this option to enable quality adaptation.
-However, the adaptive range and granularity simulcast provides is strictly limited to the number of streams (YouTube videos have 5 quality levels at most: 240p, 360p, 480p, 720p and 1080p), and the processing and storage of multiple video streams significantly increase time and space cost.
+Most commercial video websites, YouTube \cite{YouTube} for instance, use this option to enable quality adaptation.
+However, the adaptive range and granularity simulcast provides is limited to the number of streams (YouTube videos have 5 quality levels at most: 240p, 360p, 480p, 720p and 1080p), and the processing and storage of multiple video streams significantly increase time and space cost.
 SVC streaming systems, on the contrary, do not have above shortcomings.
@@
 Besides, performance analysis \cite{SVCPerformance} shows that SVC also has much higher coding efficiency than simulcast, despite some computation and bitrate overhead comparing with single layer stream.
-Therefore, SVC is considered to be a better choice for adaptive video streaming systems.
+Therefore, we choose to adopt SVC in our adaptive video streaming system.
 While the work of this paper can be partly used in a simulcast system, it will mainly focus on the adaptive streaming system using SVC.
 
-In a video streaming system using SVC, there are two key problems that need to be addressed well.
+In the SVC video streaming system, one scalable stream with enhancement data packets is produced according to actual requirement and stored at the server for streaming (how to configure and produce the stream is not in the scope of this paper).
+During the streaming process, there are two key problems that need to be addressed well.
 The first is quality control, and the second is bitstream extraction.

### 2015-04-05 tmm.tex
add the psnr fluctuation figure

@@
 \begin{abstract}
-This paper proposes an adaptive video streaming system that adjusts the video quality according to available bandwidth and gives the user best quality of service under various network conditions.
-Two key problems within the system are analyzed and solved with novel algorithms.
-First, we utilize the Proportional-Integral-Derivative (PID) method in video quality control to determine a suitable bitrate for transmission, so that the system can deliver highest video quality with least quality fluctuation.
-Second, to select an optimal sub-stream for transmission under given bitrate constraint, we use a linear error model to estimate the distortion caused by discarding any combination of data packets, and a greedy algorithm scheme to assign each data packet a priority value for Rate-Distortion optimized extraction.
-Experimental results show that the PID-based quality control algorithm brings 8.6\% higher video quality as well as 24.8\% lower quality fluctuation than the baseline algorithm, and the bitstream extraction method achieves a PSNR gain of up to 0.5dB compared to existing reference extractors, with no computational complexity increment.
-The system is currently running at the online video website www.7dlive.com and proves to be practically effective.
+In order to give the user best quality of service under bandwidth fluctuation, video streaming systems should be able to adjust the video quality according to available bandwidth.
+In this paper we propose novel models and algorithms to enable such an adaptive video streaming system which adopts the Scalable Video Coding (SVC) technology.
+First, we utilize the Proportional-Integral-Derivative (PID) method in quality control to determine a suitable transmission bitrate according to actual bandwidth condition.
+By considering bandwidth information of the past, the current and even the future, the PID-based quality control algorithm is able to deliver highest video quality with least quality fluctuation.
+Second, we present an efficient bitstream extraction scheme to select an optimal sub-stream from the whole SVC video bitstream under given bitrate constraint.
+A linear error model is used to accurately estimate the distortion caused by discarding any combination of data packets, and a greedy-like algorithm is designed to assign each data packet a priority value for Rate-Distortion optimized extraction.
+Experimental results show that comparing with the existing solutions, the PID-based quality control algorithm brings 8.6\% higher video quality with 24.8\% lower quality fluctuation, and the bitstream extraction method achieves a PSNR gain of up to 0.5dB with no computational complexity increment.
+The proposed algorithms are implemented in online video website www.7dlive.com and prove to be practically effective.
 \end{abstract}
@@
 \centering
-\includegraphics[width = 0.9\linewidth]{intervals.jpg}
+\includegraphics[width = 0.9\linewidth]{Intervals.jpg}
 \caption{Two timelines in Darwin Streaming Sever (DSS) \label{fig:intervals}}
@@
 \subfloat[Average quality level of different control algorithms]{
-\includegraphics[width=0.5\textwidth]{quality-all.jpg}
+\includegraphics[width=0.5\textwidth]{Quality-all.jpg}
 \label{fig:quality-all}}
 \subfloat[Variance of quality level of different control algorithms]{
-\includegraphics[width=0.5\textwidth]{variance-all.jpg}
+\includegraphics[width=0.5\textwidth]{Variance-all.jpg}
 \label{fig:variance-all}}
@@
 \subfloat[Variance of quality level of PID and PDF control algorithms]{
-\includegraphics[width=0.5\textwidth]{quality-two.jpg}
+\includegraphics[width=0.5\textwidth]{Quality-two.jpg}
 \label{fig:quality-two}}
 \subfloat[Average quality level of PID and PDF control algorithms]{
-\includegraphics[width=0.5\textwidth]{variance-two.jpg}
+\includegraphics[width=0.5\textwidth]{Variance-two.jpg}
 \label{fig:variance-two}}
@@
 \centering
-\includegraphics[width = 0.9\linewidth]{fluctuation.jpg}
+\includegraphics[width = 0.9\linewidth]{Fluctuation.jpg}
 \caption{Video quality fluctuation with time \label{fig:fluctuation}}
@@
 However, the method of \cite{Maani09} needs more computation in order to train robust model parameters for different sequences, while the complexity of our method is always the same with JSVM QL.
-
-\begin{comment}[8 mini-figures]
-\begin{figure*}[t]
-\begin{minipage}{0.5\linewidth}
-\centering
-\includegraphics[width = \linewidth]{City.jpg}
-\caption{City \label{fig:City}}
-\end{minipage}
-\begin{minipage}{0.5\linewidth}
-\centering
-\includegraphics[width = \linewidth]{Foreman.jpg}
-\caption{Foreman \label{fig:Foreman}}
-\end{minipage}
-\end{figure*}
-
-\begin{figure*}[t]
-\begin{minipage}{0.5\linewidth}
-\centering
-\includegraphics[width = \linewidth]{Harbour.jpg}
-\caption{Harbour \label{fig:Harbour}}
-\end{minipage}
-\begin{minipage}{0.5\linewidth}
-\centering 
-\includegraphics[width = \linewidth]{Soccer.jpg} 
-\caption{Soccer \label{fig:Soccer}}
-\end{minipage} 
-\end{figure*}
-
-\end{comment}
 
@@
 
+\subsection{Experiments for combined system}
+
+After combining the two algorithm together, we compared the proposed system's performance with the original DSS with JSVM Basic bitstream extraction. The result can be seen in 
+Fig. \ref{fig:fluctuation-psnr}.
+
+\begin{figure}[t]
+\centering
+\includegraphics[width = 0.9\linewidth]{Fluctuation-PSNR.jpg}
+\caption{PSNR fluctuation with time \label{fig:fluctuation-psnr}}
+\end{figure}
+
+\begin{figure*}[t]
+\centering
+\includegraphics[width = 0.9\linewidth]{Fluctuation-PSNR-wide.jpg}
+\caption{PSNR fluctuation with time \label{fig:fluctuation-psnr-wide}}
+\end{figure*}
+
 \section{Conclusion}

### 2015-04-10 tmm.tex
modify the paper for new experiments

@@
 \author{Shengbin~Meng,~Jun~Sun,~Yizhou~Duan~and~Zongming~Guo,~\em{Member,~IEEE} % <-this % stops a space
-\thanks{Manuscript received Febrary 15, 2015.}
+\thanks{Manuscript received April 10, 2015.}
 \thanks{The authors are with the Institute of Computer Science and Technology, Peking University, Beijing%
@@
 In order to give the user best quality of service under bandwidth fluctuation, video streaming systems should be able to adjust the video quality according to available bandwidth.
-In this paper we propose novel models and algorithms to enable such an adaptive video streaming system which adopts the Scalable Video Coding (SVC) technology.
-First, we utilize the Proportional-Integral-Derivative (PID) method in quality control to determine a suitable transmission bitrate according to actual bandwidth condition.
-By considering bandwidth information of the past, the current and even the future, the PID-based quality control algorithm is able to deliver highest video quality with least quality fluctuation.
-Second, we present an efficient bitstream extraction scheme to select an optimal sub-stream from the whole SVC video bitstream under given bitrate constraint.
+In this paper we propose such an adaptive video streaming system which adopts the Scalable Video Coding (SVC) technology and integrates novel models and algorithms.
+First, we utilize the Proportional-Integral-Derivative (PID) method to control the video quality adjustment according to actual bandwidth condition.
+By considering bandwidth information of the past, the current and even the future, the PID-based quality control algorithm is able to determine a suitable bitrate for transmission and deliver highest video quality with least fluctuation.
+Second, we present an efficient scheme to extract an optimal sub-stream from the whole SVC video bitstream under given bitrate constraint.
 A linear error model is used to accurately estimate the distortion caused by discarding any combination of data packets, and a greedy-like algorithm is designed to assign each data packet a priority value for Rate-Distortion optimized extraction.
-Experimental results show that comparing with the existing solutions, the PID-based quality control algorithm brings 8.6\% higher video quality with 24.8\% lower quality fluctuation, and the bitstream extraction method achieves a PSNR gain of up to 0.5dB with no computational complexity increment.
-The proposed algorithms are implemented in online video website www.7dlive.com and prove to be practically effective.
+Experimental results show that the PID-based quality control algorithm brings 8.6\% higher video quality with 24.8\% lower quality fluctuation comparing with the baseline algorithm, and the bitstream extraction method achieves a PSNR gain of up to 0.5dB with no computational complexity increment.
+Altogether, the system produces a higher and smoother PSNR curve representing the final video quality perceived by the user.
+The proposed system is also implemented in online video website www.7dlive.com and proves to be practically effective.
 \end{abstract}
@@
 Dynamic Adaptive Streaming over HTTP (DASH) \cite{DASH}, which is standardized by the Moving Picture Expert Group (MPEG), belongs to this option.
-The second option is to adopt the Scalable Video Coding (SVC) \cite{SVC} technology, which allows scalability of video bitrate and quality with only one single bitstream.
-The generally-known term SVC usually refers to the scalable extension of the H.264/AVC video coding standard \cite{SVCOverview}.
+The second option is to adopt the Scalable Video Coding (SVC) \cite{SVC} technology, an extension of the H.264/AVC video coding standard \cite{SVCOverview}, which allows scalability of video bitrate and quality with only one single bitstream.
 In SVC, a video bitstream is composed of small data packets called Network Abstract Layer Units (NALUs).
@@
 Most commercial video websites, YouTube \cite{YouTube} for instance, use this option to enable quality adaptation.
-However, the adaptive range and granularity simulcast provides is limited to the number of streams (YouTube videos have 5 quality levels at most: 240p, 360p, 480p, 720p and 1080p), and the processing and storage of multiple video streams significantly increase time and space cost.
+However, the adaptive range and granularity that simulcast provides is limited to the number of streams (YouTube videos have 5 quality levels at most: 240p, 360p, 480p, 720p and 1080p), and the processing and storage of multiple video streams significantly increase time and space cost.
 SVC streaming systems, on the contrary, do not have above shortcomings.
@@
 
-In the SVC video streaming system, one scalable stream with enhancement data packets is produced according to actual requirement and stored at the server for streaming (how to configure and produce the stream is not in the scope of this paper).
+In the SVC video streaming system, one scalable video stream with enhancement data packets is produced according to actual requirement and stored at the server for streaming (how to configure and produce the stream is not in the scope of this paper; users are referred to \cite{JSVM}).
 During the streaming process, there are two key problems that need to be addressed well.
@@
 Once the bandwidth has changed, the quality control algorithm should determine a bitrate suitable for the current bandwidth.
-Given this bitrate, how to extract data from the whole SVC stream to form an optimal sub-stream becomes the bitstream extraction problem.
+Given this bitrate, how to extract data from the whole SVC stream to form an optimal sub-stream becomes the second problem, i.e., bitstream extraction problem.
 Optimized bitstream extraction aims to select a subset of NALUs (or packets) which represents video with best quality, or minimal distortion, under the constrain of the given bitrate.
@@
 
-In this paper, an efficient adaptive video streaming system based on SVC is proposed.
+In this paper, an efficient adaptive video streaming system based on SVC is proposed with the above two problems better solved.
 Apple Darwin Streaming Server (DSS) \cite{DSS}, which is open-sourced and has been widely used to stream multimedia contents in practice, is chosen as the basis of the system.
 The original DSS project is modified by us and SVC support is added to it, for the purpose of both research and application.
-Then novel algorithms are designed and implemented to better solve the two key problems mentioned above.
+Then novel algorithms of quality control and bitstream extraction are designed and implemented to achieve significant improvement in terms of user-perceived video quality.
 The contributions of our work are threefold:
 \begin{itemize}
-\item A quality control algorithm based on the Proportional-Integral-Derivative (PID) control concept is proposed to replace the native one in DSS, and achieves higher average quality level with less quality fluctuation.
-\item A linear error model is proposed to accurately estimate the distortion caused by discarding any combination of packets from a SVC bitstream.
-\item A greedy-like algorithm is designed to assign priority for each packet, thus enables optimized bitstream extraction.
+\item A quality control algorithm based on the Proportional-Integral-Derivative (PID) control concept is designed to replace the native one in DSS, and achieves higher average video quality with less quality fluctuation.
+\item A linear error model is proposed to accurately estimate the distortion caused by discarding any combination of packets from a SVC bitstream, based on which a greedy-like bitstream extraction method is proposed and achieves PSNR gain of up to 0.5dB.
+\item The proposed novel solutions for quality control and bitstream extraction are combined together and result in a higher and smoother PSNR curve representing the final video quality perceived by the user.
 \end{itemize}
@@
 
-In this section, we analyze the two most concerned problems in SVC adaptive streaming, i.e., quality control and bitstream extraction, and introduce some existing related works on them.
+The two most concerned problems in SVC adaptive streaming, i.e., quality control and bitstream extraction, are illustrated in Fig.
+\ref{fig:problems}.
+In this section, we analyze the two problems in detail, and introduce some existing related works on them.
+
+\begin{figure}[t]
+\centering
+\includegraphics[width = 0.9\linewidth]{Problems.jpg}
+\caption{Two key problems in adaptive video streaming\label{fig:problems}}
+\end{figure}
 
@@
 As with other control systems, PID parameters are a result of tunning and may not suit to all use cases.
-However, it should be noted that in the video quality control algorithm, only the data rate and the bandwidth are considered, not the video content, so once the parameters are tuned they should apply well to different video streams.
+However, it should be noted that in the video quality control algorithm, only the data rate and the bandwidth are considered, not the video content.
+Therefore once the parameters are tuned they should apply well to different video streams.
 
@@
 
-Once the quality control algorithm determines an appropriate bitrate and sets a quality level accordingly, the system will send a packet only belonging to this new quality level (as described at the end of Algorithm \ref{algo:control}).
-For SVC videos, that means to extract a subset of packets from the whole bitstream.
+After the quality control algorithm determines an appropriate bitrate and sets a quality level accordingly, the system will only send packets belonging to this new quality level (as described at the end of Algorithm \ref{algo:control}).
+For SVC videos, it means to extract a subset of packets from the whole bitstream.
 How to optimally choose this subset to achieve minimum distortion under the given bitrate is the key point of bitstream extraction problem.
@@
 \subsection{Error Vector Acquisition}
+
  It would need too many decoding times to get the error vectors of all enhancement packets if we calculate them one at a time.
@@
 \label{subsec:noref}
+
 In some scenarios, the priority assignment and bitstream extraction needs to be conducted without access to the original YUV sequence.
@@
 
-To implement our proposed scalable streaming system requires the combination of the PID-based quality control algorithm and the optimized bitstream extraction method.
-The former determines the current bitrate to follow the bandwidth change, and the latter will ensure the sub-stream with the best possible quality is sent under that bitrate constrain.
+To implement our proposed adaptive streaming system requires the combination of the PID-based quality control algorithm and the optimized bitstream extraction method.
+The former determines the current bitrate to follow the bandwidth change, and the latter will ensure the sub-stream with the best possible quality is obtained and sent under that bitrate constrain.
 They work together to construct a system that delivers best quality of experience for the users.
-We have integrated the PID-based quality control algorithm into DSS.
-However, the integration of the proposed bitstream extraction method needs more engineering work and has not been accomplished.
-Therefore, in this section, we only present separate experiments to demonstrate the advantage of each proposed solution.
-Readers who are interested in the practical implementation are encouraged to visit the online video website http://www.7dlive.com for more information.
+Choosing DSS as the implementation basis, we have integrated the proposed algorithms into it for the purpose of both research and application.
+In this section, we first present separate experiments to demonstrate the advantage of each proposed solution, and then give the result when they are combined together.
+Readers who are interested in the practical implementation can also visit the online video website http://www.7dlive.com for more information.
 
 \subsection{Experiments for Quality Control}
+\label{subsec:exp-control}
 
@@
 For example, quality level 3 would contain all sub-streams from 0 to 3, thus would include all temporal layers, but only the quality base layer 0.
-The tested stream has 9 quality levels from 0 to 8 (Table \ref{tab:sub-stream}), and a maximum bit rate of 1587 kbps at level 8.
+The tested stream has 9 quality levels from 0 to 8 (see Table \ref{tab:sub-stream}), and a maximum bit rate of 1587 kbps at level 8.
 
@@
 
-\subsection{Experiments for combined system}
-
-After combining the two algorithm together, we compared the proposed system's performance with the original DSS with JSVM Basic bitstream extraction. The result can be seen in 
-Fig. \ref{fig:fluctuation-psnr}.
-
-\begin{figure}[t]
-\centering
-\includegraphics[width = 0.9\linewidth]{Fluctuation-PSNR.jpg}
-\caption{PSNR fluctuation with time \label{fig:fluctuation-psnr}}
-\end{figure}
+\subsection{Result of the combined system}
+
+After combining the two algorithms together, the proposed adaptive streaming system is able to deliver a higher and smoother video quality for the user.
+We compare the proposed system's performance with DSS that supports SVC but has its original quality control method and JSVM Basic bitstream extraction.
+The result for the same test stream as used in subsection \ref{subsec:exp-control} is present in Fig.
+\ref{fig:fluctuation-psnr}.
+It shows PSNR change perceived by the user when available bandwidth fluctuates around 800 kbps.
+It can be seen that, the proposed system has effectively avoided unnecessary quality drop (note the curve around time 50s and 350s) and been able to keep a relatively higher PSNR value (note the curve between time 450s and 600s).
 
@@
 \includegraphics[width = 0.9\linewidth]{Fluctuation-PSNR-wide.jpg}
-\caption{PSNR fluctuation with time \label{fig:fluctuation-psnr-wide}}
+\caption{User-perceived PSNR change with time when bandwidth fluctuates \label{fig:fluctuation-psnr}}
 \end{figure*}
@@
 Comparing with the original algorithm in DSS, this algorithm has reduced quality fluctuation significantly to improve audience satisfaction.
-The bitstream extraction method we propose includes a linear error model to estimate the distortion caused by discarding any combination of packets and a greedy algorithm to assign priority to each data packet.
+The bitstream extraction method includes a linear error model to estimate the distortion caused by discarding any combination of packets and a greedy algorithm to assign priority to each data packet.
 The packets' priority values can then be stored in the bitstream and used for R-D optimized extraction.
 Experimental results show that the proposed method can achieve PSNR gain of up to 0.5dB compared to the JSVM QL extractor under the same bitrate constrain, also with the same computational complexity.
-
-The PID-based quality control algorithm of this paper has already been integrated into the online website www.7dlive.com and performs well in automatically adapting to the user's bandwidth fluctuation.
-This algorithm can also be easily used in other streaming systems, e.g., DASH systems.
-For the bitstream extraction method, there is future work to be done in the following two directions.
-First, we strive to integrate the bitstream extraction method into DSS, and combine it with the PID-based quality control to give user adaptive video streaming with best watching experience.
-Second, since the next generation video coding standard High Efficiency Video Coding (HEVC) \cite{HEVC} adopts the similar coding framework as its predecessor H.264/AVC, we expect to apply this paper's model and approach to the emerging HEVC standard and its scalable extension.
+The SVC streaming system integrated with these two solutions performs well in automatically adapting to the user's bandwidth fluctuation, and is able to give the user a better watching experience.
+
+The PID-based quality control algorithm is only network-concerned thus should be easily integrated into other streaming systems, e.g., simulcast system like DASH.
+For the bitstream extraction, since the next generation video coding standard High Efficiency Video Coding (HEVC) \cite{HEVC} adopts the similar coding framework as its predecessor H.264/AVC, we expect to apply this paper's model and approach to the emerging HEVC standard and its scalable extension in our future work.
 
@@
 M. Wien , H. Schwarz and T. Oelbaum,  ``Performance Analysis of SVC'',  in {\em IEEE Trans. Circuits Syst. Video Technol.}, vol. 17, no. 9, pp.1194-1203. Sep. 2007.
+
+\bibitem{JSVM}
+Text of ISO/IEC 14496-4:2001/PDAM 19 Reference Software for SVC, Joint Video Team (JVT) of ISO-IEC MPEG \& ITU-T VCEG, N9195, Sep. 2007.
 
@@
 
-\bibitem{JSVM}
-Text of ISO/IEC 14496-4:2001/PDAM 19 Reference Software for SVC, Joint Video Team (JVT) of ISO-IEC MPEG \& ITU-T VCEG, N9195, Sep. 2007.
-
 \bibitem{Sun09}

### 2015-04-27 tmm.tex
section title shoule be capitalized
the version I think OK

@@
 \begin{abstract}
-In order to give the user best quality of service under bandwidth fluctuation, video streaming systems should be able to adjust the video quality according to available bandwidth.
-In this paper we propose such an adaptive video streaming system which adopts the Scalable Video Coding (SVC) technology and integrates novel models and algorithms.
-First, we utilize the Proportional-Integral-Derivative (PID) method to control the video quality adjustment according to actual bandwidth condition.
-By considering bandwidth information of the past, the current and even the future, the PID-based quality control algorithm is able to determine a suitable bitrate for transmission and deliver highest video quality with least fluctuation.
-Second, we present an efficient scheme to extract an optimal sub-stream from the whole SVC video bitstream under given bitrate constraint.
-A linear error model is used to accurately estimate the distortion caused by discarding any combination of data packets, and a greedy-like algorithm is designed to assign each data packet a priority value for Rate-Distortion optimized extraction.
-Experimental results show that the PID-based quality control algorithm brings 8.6\% higher video quality with 24.8\% lower quality fluctuation comparing with the baseline algorithm, and the bitstream extraction method achieves a PSNR gain of up to 0.5dB with no computational complexity increment.
-Altogether, the system produces a higher and smoother PSNR curve representing the final video quality perceived by the user.
+To cope with the challenge brought by bandwidth fluctuation and provide the user with best quality of service, this paper proposes an adaptive video streaming system which adopts the Scalable Video Coding (SVC) technology and integrates novel models and algorithms.
+First, the Proportional-Integral-Derivative (PID) method is utilized to control the video quality adjustment according to actual bandwidth condition.
+By considering bandwidth information of the past, the current and even the future, the PID-based quality control algorithm determines a suitable bitrate for transmission.
+Then, under the constraint of that bitrate, an efficient scheme is used to extract an optimal sub-stream from the whole SVC video bitstream.
+In this scheme, a linear error model enables accurate estimation of the distortion caused by discarding any combination of data packets, and a greedy-like algorithm is designed to assign each data packet a priority value for Rate-Distortion optimized bitstream extraction.
+Experimental results show that by combining the above algorithms, PSNR average can be increased from 40.29 to 40.62, and PSNR variance can be reduced from 0.66 to 0.28, i.e., both higher video quality and lower quality fluctuation are achieved.
 The proposed system is also implemented in online video website www.7dlive.com and proves to be practically effective.
@@
 One of the biggest challenge for video streaming is the variety of users' network environment.
-A user may use different types of network (Ethernet, Wi-Fi, Cellular, etc) and may also switch from one type to another (e.g., from Wi-Fi to cellular network) on going.
+A user may use different types of network (Ethernet, Wi-Fi, Cellular, etc.) and may also switch from one type to another (e.g., from Wi-Fi to cellular network) on going.
 Even in the same network, the user's bandwidth may change from time to time, influenced by the overall traffic.
@@
 Given this bitrate, how to extract data from the whole SVC stream to form an optimal sub-stream becomes the second problem, i.e., bitstream extraction problem.
-Optimized bitstream extraction aims to select a subset of NALUs (or packets) which represents video with best quality, or minimal distortion, under the constrain of the given bitrate.
+Optimized bitstream extraction aims to select a subset of NALUs (or packets) which represents video with best quality, or minimal distortion, under the constraint of the given bitrate.
 It should be noted that, bitstream extraction is not only useful in adaptive video streaming, but also in other SVC application scenarios where part of data needs to be obtained or kept, e.g., the archiving of surveillance video.
@@
 To implement our proposed adaptive streaming system requires the combination of the PID-based quality control algorithm and the optimized bitstream extraction method.
-The former determines the current bitrate to follow the bandwidth change, and the latter will ensure the sub-stream with the best possible quality is obtained and sent under that bitrate constrain.
+The former determines the current bitrate to follow the bandwidth change, and the latter will ensure the sub-stream with the best possible quality is obtained and sent under that bitrate constraint.
 They work together to construct a system that delivers best quality of experience for the users.
@@
 
-\subsection{Result of the combined system}
+\subsection{Result of the Combined System}
 
@@
 It can be seen that, the proposed system has effectively avoided unnecessary quality drop (note the curve around time 50s and 350s) and been able to keep a relatively higher PSNR value (note the curve between time 450s and 600s).
+The average and variance of PSNR delivered by the proposed system are 40.62 and 0.28, respectively, while the values of the baseline system are 40.29 and 0.66.
 
@@
 The packets' priority values can then be stored in the bitstream and used for R-D optimized extraction.
-Experimental results show that the proposed method can achieve PSNR gain of up to 0.5dB compared to the JSVM QL extractor under the same bitrate constrain, also with the same computational complexity.
+Experimental results show that the proposed method can achieve PSNR gain of up to 0.5dB compared to the JSVM QL extractor under the same bitrate constraint, also with the same computational complexity.
 The SVC streaming system integrated with these two solutions performs well in automatically adapting to the user's bandwidth fluctuation, and is able to give the user a better watching experience.

### 2015-05-06 tmm.tex
refined abstract

@@
 \begin{abstract}
-To cope with the challenge brought by bandwidth fluctuation and provide the user with best quality of service, this paper proposes an adaptive video streaming system which adopts the Scalable Video Coding (SVC) technology and integrates novel models and algorithms.
+To cope with the challenge brought by bandwidth fluctuation and provide the user with video of both smooth and high quality, an adaptive video streaming framework is proposed based on the Scalable Video Coding (SVC) extension of H.264/AVC.
 First, the Proportional-Integral-Derivative (PID) method is utilized to control the video quality adjustment according to actual bandwidth condition.
-By considering bandwidth information of the past, the current and even the future, the PID-based quality control algorithm determines a suitable bitrate for transmission.
+By monitoring and predicting bandwidth information of the past, the current and the future, the PID-based quality control algorithm determines a suitable bitrate for transmission.
 Then, under the constraint of that bitrate, an efficient scheme is used to extract an optimal sub-stream from the whole SVC video bitstream.
-In this scheme, a linear error model enables accurate estimation of the distortion caused by discarding any combination of data packets, and a greedy-like algorithm is designed to assign each data packet a priority value for Rate-Distortion optimized bitstream extraction.
-Experimental results show that by combining the above algorithms, PSNR average can be increased from 40.29 to 40.62, and PSNR variance can be reduced from 0.66 to 0.28, i.e., both higher video quality and lower quality fluctuation are achieved.
-The proposed system is also implemented in online video website www.7dlive.com and proves to be practically effective.
+In this scheme, a linear error model which exploits the linear feature of pixel value errors is used to accurately estimate the distortion caused by discarding any combination of data packets, and a greedy-like algorithm is designed to assign each data packet a priority value according to its Rate-Distortion (R-D) impact, thus enables R-D optimized bitstream extraction.
+Experimental results show that, comparing with the baseline software, the proposed framework integrating the above algorithms can achieve much lower video quality fluctuation, with PSNR variance reduced from 0.66 to 0.28, and at the same time deliver higher video quality, with an average PSNR gain of 0.33dB.
+The framework is deployed at online video website www.7dlive.com and proves to be practically effective.
 \end{abstract}

### 2015-05-11 tmm.tex
change the order of the two parts

@@
 % Do not put math or special symbols in the title.
-\title{Adaptive Video Streaming with PID-Based Quality Control and Optimized Bitstream Extraction}
+\title{Adaptive Video Streaming with Optimized Bitstream Extraction and PID-based Quality Control}
 
@@
 \begin{abstract}
-To cope with the challenge brought by bandwidth fluctuation and provide the user with video of both smooth and high quality, an adaptive video streaming framework is proposed based on the Scalable Video Coding (SVC) extension of H.264/AVC.
-First, the Proportional-Integral-Derivative (PID) method is utilized to control the video quality adjustment according to actual bandwidth condition.
-By monitoring and predicting bandwidth information of the past, the current and the future, the PID-based quality control algorithm determines a suitable bitrate for transmission.
-Then, under the constraint of that bitrate, an efficient scheme is used to extract an optimal sub-stream from the whole SVC video bitstream.
-In this scheme, a linear error model which exploits the linear feature of pixel value errors is used to accurately estimate the distortion caused by discarding any combination of data packets, and a greedy-like algorithm is designed to assign each data packet a priority value according to its Rate-Distortion (R-D) impact, thus enables R-D optimized bitstream extraction.
+To cope with the challenge brought by bandwidth fluctuation and provide the user with video of both smooth and high quality, an adaptive video streaming framework which can adjust video quality according to actual bandwidth condition is proposed based on the Scalable Video Coding (SVC) extension of H.264/AVC.
+First, a simple and effective linear error model is proposed and validated for quality scalability of SVC.
+The model exploits the linear feature of pixel value errors and can be used to accurately estimate the distortion caused by discarding any combination of enhancement data packets in an SVC bitstream.
+Then on the basis of that, a greedy-like algorithm is designed to assign each data packet a priority value according to its Rate-Distortion (R-D) impact, thus enables R-D optimized bitstream extraction under certain bitrate constraint.
+Finally, the Proportional-Integral-Derivative (PID) method is utilized to control the video quality adjustment and determine the suitable bitrate for transmission.
+By monitoring and predicting bandwidth information of the past, the current and the future, the PID-based quality control algorithm can significantly reduce quality fluctuation while still keeping a high quality level.
 Experimental results show that, comparing with the baseline software, the proposed framework integrating the above algorithms can achieve much lower video quality fluctuation, with PSNR variance reduced from 0.66 to 0.28, and at the same time deliver higher video quality, with an average PSNR gain of 0.33dB.
@@
 One of the biggest challenge for video streaming is the variety of users' network environment.
-A user may use different types of network (Ethernet, Wi-Fi, Cellular, etc.) and may also switch from one type to another (e.g., from Wi-Fi to cellular network) on going.
-Even in the same network, the user's bandwidth may change from time to time, influenced by the overall traffic.
-During such an environment, bandwidth fluctuation is inevitable.
+A user might use different types of network (Ethernet, Wi-Fi, Cellular, etc.) and might also switch from one type to another (e.g., from Wi-Fi to cellular network) on going.
+Even in the same network, the user's bandwidth will change from time to time, influenced by the overall traffic.
+Within such an environment, bandwidth fluctuation is inevitable.
 If the video is streamed at a constant bitrate, it would be difficult or impossible for the user to get best watching experience.
@@
 There are generally two options to enable adaptive video streaming.
-The first option is called simulcast, where several independent bitstreams with different video quality are stored at the server, and the client selects one of them according to currently available bandwidth.
+The first option is called simulcast, where several independent bitstreams each with different video quality are stored at the server, and the client selects one of them according to currently available bandwidth.
 Dynamic Adaptive Streaming over HTTP (DASH) \cite{DASH}, which is standardized by the Moving Picture Expert Group (MPEG), belongs to this option.
@@
 Besides, performance analysis \cite{SVCPerformance} shows that SVC also has much higher coding efficiency than simulcast, despite some computation and bitrate overhead comparing with single layer stream.
-Therefore, we choose to adopt SVC in our adaptive video streaming system.
-While the work of this paper can be partly used in a simulcast system, it will mainly focus on the adaptive streaming system using SVC.
-
-In the SVC video streaming system, one scalable video stream with enhancement data packets is produced according to actual requirement and stored at the server for streaming (how to configure and produce the stream is not in the scope of this paper; users are referred to \cite{JSVM}).
-During the streaming process, there are two key problems that need to be addressed well.
-The first is quality control, and the second is bitstream extraction.
-Quality control means controlling the video quality (or the video bitrate, from the transmission point of view) to follow the change of the bandwidth.
-Once the bandwidth has changed, the quality control algorithm should determine a bitrate suitable for the current bandwidth.
-Given this bitrate, how to extract data from the whole SVC stream to form an optimal sub-stream becomes the second problem, i.e., bitstream extraction problem.
-Optimized bitstream extraction aims to select a subset of NALUs (or packets) which represents video with best quality, or minimal distortion, under the constraint of the given bitrate.
-It should be noted that, bitstream extraction is not only useful in adaptive video streaming, but also in other SVC application scenarios where part of data needs to be obtained or kept, e.g., the archiving of surveillance video.
+Therefore, we choose to adopt SVC in our adaptive video streaming framework.
+While the work of this paper partly applies to the simulcast system, it will mainly focus on the context of SVC video streaming system.
+
+In the SVC adaptive video streaming system, there are two key problems that need to be addressed well.
+First, as the prerequisite of the adaption to bandwidth change, the whole bitstream needs to be extracted so that sub-streams with various bitrates can be obtained.
+This is called the bitstream extraction problem.
+Optimal bitstream extraction algorithm aims to extract a sub-stream with best video quality, or minimal distortion, under the constraint of a given bitrate.
+Second, when the bandwidth does change, it's necessary to make decisions about whether and how to adjust the bitrate or video quality.
+This problem is called quality control, which means controlling the video quality (or the video bitrate, from the transmission point of view) to follow the change of the bandwidth.
+A good quality control algorithm should determine a suitable bitrate for current bandwidth condition, and keep the video quality both smooth and at a high level.
 
 In this paper, an efficient adaptive video streaming system based on SVC is proposed with the above two problems better solved.
-Apple Darwin Streaming Server (DSS) \cite{DSS}, which is open-sourced and has been widely used to stream multimedia contents in practice, is chosen as the basis of the system.
-The original DSS project is modified by us and SVC support is added to it, for the purpose of both research and application.
-Then novel algorithms of quality control and bitstream extraction are designed and implemented to achieve significant improvement in terms of user-perceived video quality.
-The contributions of our work are threefold:
+Apple Darwin Streaming Server (DSS) \cite{DSS}, which is open-sourced and has been widely used to stream multimedia contents in practice, is chosen as the basis of the proposed system.
+The original DSS project is modified and SVC support is added to it, for the purpose of both research and application.
+Then novel algorithms for bitstream extraction and quality control are designed and implemented to achieve significant improvement in terms of user-perceived video quality.
+The contributions of our work can be summarized as follows:
 \begin{itemize}
-\item A quality control algorithm based on the Proportional-Integral-Derivative (PID) control concept is designed to replace the native one in DSS, and achieves higher average video quality with less quality fluctuation.
-\item A linear error model is proposed to accurately estimate the distortion caused by discarding any combination of packets from a SVC bitstream, based on which a greedy-like bitstream extraction method is proposed and achieves PSNR gain of up to 0.5dB.
-\item The proposed novel solutions for quality control and bitstream extraction are combined together and result in a higher and smoother PSNR curve representing the final video quality perceived by the user.
+\item First, a simple and effective linear error model (LEM) is proposed and validated, which can be used to accurately estimate the distortion caused by discarding any combination of packets from a SVC bitstream.
+\item Second, on the basis of the distortion estimation enabled by LEM, a greedy-like algorithm is designed to assign priority for each packet according to its R-D impact, thus enables optimized bitstream extraction.
+\item Finally, for the quality control problem, a novel algorithm based on the Proportional-Integral-Derivative (PID) control concept is proposed to replace the native one in DSS, and achieves much lower quality fluctuation with higher quality level.
 \end{itemize}
@@
 In section \ref{sec:analysis}, we analyze the problems in detail and introduce some related works on them.
-Then in section \ref{sec:quality-control}, the proposed quality control algorithm is formulated and explained with term definitions and parameters selection.
-After that, we present the solution for the bitstream extraction problem in section \ref{sec:bit-extraction}, including the linear error model and the greed-like algorithm.
+Then in section \ref{sec:bitstream-extraction}, the linear error model is proposed, and the solution for the bitstream extraction problem based on the model is present.
+After that, the PID-based quality control algorithm is proposed in section \ref{sec:quality-control}.
 Section \ref{sec:experiment} lists the experimental results and compares our proposed solution with others.
@@
 
-The two most concerned problems in SVC adaptive streaming, i.e., quality control and bitstream extraction, are illustrated in Fig.
-\ref{fig:problems}.
-In this section, we analyze the two problems in detail, and introduce some existing related works on them.
-
-\begin{figure}[t]
-\centering
-\includegraphics[width = 0.9\linewidth]{Problems.jpg}
-\caption{Two key problems in adaptive video streaming\label{fig:problems}}
-\end{figure}
-
-\subsection{Quality Control}
-
-For a quality control algorithm, there are three targets that should be achieved.
-First is to ensure the continuity of video playing.
-In real-time streaming system, each data packet has its own playtime, which is also regarded as the deadline of the transmission.
-If the packet does not arrive at client side before the deadline, the media player will be paused due to lack of data, and that should be avoided.
-The second is to keep a smooth video quality.
-Although network conditions may change rapidly, it is necessary for the streamed video to maintain a relatively stable quality level, since frequent change of video quality will lead to poor user experience.
-The third target is to make the video quality as good as possible.
-In other words, the available bandwidth should be fully utilized.
-Suppose we keep sending video data in a low bitrate (with low video quality as well), neither the playback pause nor any quality fluctuation will likely happen.
-However, a low video quality is certainly not what we want.
-
-The state-of-art solutions to avoid video pause in client media player mainly focus on how to select and schedule the video packets.
-In \cite{Gao06}, K.
-Gao et al.
-proposed a priority based scheduling strategy which guarantees packets of higher importance will be transmitted earlier.
-Among the packets with the same priority, those having the earliest deadline will be transmitted first.
-A similar solution is proposed in \cite{Schierl10}, where video data is pre-buffered in several buffers of different priorities.
-Whenever re-buffering occurs, quality will be degraded to a lower level to meet the time and rate constraint.
-Although the priority based scheduling strategies perform well in maintaining a non-paused video playing, they do not take quality fluctuation into account.
-As a result, users may still suffer from the frequent fluctuation of video quality.
-
-In DSS, quality control is implemented by monitoring packet delay (the difference between current time and the playing time of this packet).
-When a new packet is ready to be sent to streaming buffer, DSS checks the delay of it and compares this delay with some pre-set critical time thresholds to judge whether and how violently the quality change should be made.
-This algorithm can reduce quality fluctuation to some degree.
-However, it only provides conservative quality change, which makes its reaction so slow that sometimes media player may have already stopped due to lack of video data before quality drops.
-Furthermore, this algorithm has no knowledge of the bandwidth change so it cannot accurately adjust the video quality.
-Therefore, quality oscillation is inevitable in this algorithm.
+In this section, we analyze the two most concerned problems in SVC adaptive video streaming, i.e., bitstream extraction and quality control, and introduce some existing related works on them.
 
@@
 
-The following of this paper will present solutions for the above problems in detail.
-We have published the related ideas in conference papers \cite{Meng14}\cite{Meng14-PID}, and in this paper we combine our previous works together and lay a solid foundation for a practical adaptive video streaming system.
+\subsection{Quality Control}
+
+For a quality control algorithm, there are three targets that should be achieved.
+First is to ensure the continuity of video playing.
+In real-time streaming system, each data packet has its own playtime, which is also regarded as the deadline of the transmission.
+If the packet does not arrive at client side before the deadline, the media player will be paused due to lack of data, and that should be avoided.
+The second is to keep a smooth video quality.
+Although network conditions may change rapidly, it is necessary for the streamed video to maintain a relatively stable quality level, since frequent change of video quality will lead to poor user experience.
+The third target is to make the video quality as good as possible.
+In other words, the available bandwidth should be fully utilized.
+Suppose we keep sending video data in a low bitrate (with low video quality as well), neither the playback pause nor any quality fluctuation will likely happen.
+However, a low video quality is certainly not what we want.
+
+The state-of-art solutions to avoid video pause in client media player mainly focus on how to select and schedule the video packets.
+In \cite{Gao06}, K.
+Gao et al.
+proposed a priority based scheduling strategy which guarantees packets of higher importance will be transmitted earlier.
+Among the packets with the same priority, those having the earliest deadline will be transmitted first.
+A similar solution is proposed in \cite{Schierl10}, where video data is pre-buffered in several buffers of different priorities.
+Whenever re-buffering occurs, quality will be degraded to a lower level to meet the time and rate constraint.
+Although the priority based scheduling strategies perform well in maintaining a non-paused video playing, they do not take quality fluctuation into account.
+As a result, users may still suffer from the frequent fluctuation of video quality.
+
+In DSS, quality control is implemented by monitoring packet delay (the difference between current time and the playing time of this packet).
+When a new packet is ready to be sent to streaming buffer, DSS checks the delay of it and compares this delay with some pre-set critical time thresholds to judge whether and how violently the quality change should be made.
+This algorithm can reduce quality fluctuation to some degree.
+However, it only provides conservative quality change, which makes its reaction so slow that sometimes media player may have already stopped due to lack of video data before quality drops.
+Furthermore, this algorithm has no knowledge of the bandwidth change so it cannot accurately adjust the video quality.
+Therefore, quality oscillation is inevitable in this algorithm.
+
+The following of this paper will present our solutions for the above problems in detail.
+And we will combine our works together and lay a solid foundation for a practical adaptive video streaming system.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Optimized Bitstream Extraction Based on Linear Error Model}
+\label{sec:bitstream-extraction}
+
+Being able to adjust bitrate is the prerequisite for an adaptive video streaming system.
+For SVC videos, it means to extract a subset of packets from the whole bitstream.
+How to optimally choose this subset to achieve minimum distortion under the given bitrate is the key point of bitstream extraction problem.
+In this section, we propose a linear error mode and a greedy-like algorithm to solve this problem.
+
+\subsection{Linear Error Model for Quality Scalable Video}
+\label{sec:model}
+
+In H.264/AVC, the decoding process involves a linear feature described in \cite{Winken08}, neglecting any rounding, clipping, and deblocking filtering operation.
+According to this feature, the main steps in H.264/AVC coding -- prediction, transform and quantization -- are proximately linear operations, and the whole coding process can be expressed in a matrix format as follows:
+	\begin{equation}
+	\label{eq:linear}
+s = {\rm\bf M}s + {\rm\bf T}c + p \: ,
+	\end{equation}
+It means, the reconstructed samples of a GOP (Group of Pictures), denoted by $s$, can be viewed as a linear combination of previously reconstructed samples in the GOP, the residual samples, and a static predictor.
+In (\ref{eq:linear}), $c$ refers to the transform coefficient values and $p$ is a static predictor; $M$ and $T$ are square matrices such that the product $M$s gives the MCP (Motion Compensated Prediction) signal and $Tc$ gives the residual values.
+The actual values of $M$ depend on the selected macroblock types, reference indices and motion vectors, whereas the actual values of $T$ depend on the chosen QP (Quantization Parameter) values.
+
+We apply the above linear decoding model to the case of quality scalability of SVC and get a linear error model.
+According to (\ref{eq:linear}), for a bitstream just containing the base layer, we have:
+	\begin{equation}
+	\label{eq:base0}
+s_{B} = {\rm\bf M}s_{B} + {\rm\bf T}_{B}c_{B} + p \: ,
+	\end{equation}
+where the subscript $B$ indicates the base layer variables.
+In quality scalability, the enhancement is mainly the refinement of transform coefficients, so for a bitstream containing an enhancement packet set $I_1$, the reconstruction relationship can be expressed as:
+	\begin{equation}
+	\label{eq:subset1}
+s_{I_1} = {\rm\bf M}s_{I_1} + {\rm\bf T}_{B} c_{B} + \Big( \sum_{i \in I_1}{\rm\bf T}_i c_i \Big) + p \: ,
+	\end{equation}
+where $i$ refers to an enhancement packet as an element of $I_1$.
+$c_i$ is a vector containing coefficients within the enhancement packet $i$.
+${\rm\bf T_i}$ is the transform matrix depending on the QP value of $i$.
+${\rm\bf T}_i c_i$ gives the residual sample values decoded from $i$.
+
+Similarly, for another bitstream containing an enhancement packet set $I_2$, we have
+	\begin{equation}
+	\label{eq:subset2}
+s_{I_2} = {\rm\bf M}s_{I_2} + {\rm\bf T}_{B} c_{B} + \Big( \sum_{i \in I_2}{\rm\bf T}_i c_i \Big) + p \: .
+	\end{equation}
+
+Suppose $I_1$ is a subset of $I_2$, their reconstruction difference can be obtained by (\ref{eq:subset2}) - (\ref{eq:subset1}):
+	\begin{equation}
+	\label{eq:minus1}
+(s_{I_2} - s_{I_1}) = {\rm\bf M}(s_{I_2} - s_{I_1}) + \Big( \sum_{i \in I_2}{\rm\bf T}_i c_i - \sum_{i \in I_1}{\rm\bf T}_i c_i \Big) \: ,
+	\end{equation}
+	\begin{equation}
+	\label{eq:minus2}
+\Rightarrow e = s_{I_2} - s_{I_1} = ({\rm\bf I - M})^{-1} \Big( \sum_{i \in I_2}{\rm\bf T}_i c_i - \sum_{i \in I_1}{\rm\bf T}_i c_i \Big) \: .
+	\end{equation}
+
+Particularly, if the difference of $I_2$ and $I_1$ is a single enhancement packet $j$, i.e.
+$I_2 \setminus I_1 = \{j\}$, then according to (\ref{eq:minus2}), the difference of the two reconstruction vectors can be written as
+	\begin{equation}
+	\label{eq:error_j}
+e_j = ({\rm\bf I - M})^{-1} {\rm\bf T}_j c_j \: .
+	\end{equation}
+
+Obviously, $e_j$ is only determined by packet $j$, and has no relation with other enhancement packets.
+This value is called the ``error vector'' of packet $j$, which represents the pixel value error caused by discarding the packet $j$.
+We can obtain the error vector of each enhancement packet by subtraction between video sequences reconstructed from two enhancement packet subsets $I_1$ and $I_2$, with $I_1 \subseteq I_2$ and $I_2 \setminus I_1 =\{j\} $.
+Once all packets' error vectors are obtained, the distortion caused by discarding a group of packets can be estimated by adding up the error vector of each packet in the group.
+
+The above model is called Linear Error Model (LEM).
+Note that in equations (\ref{eq:base0})-(\ref{eq:subset2}) the value of M and p remain the same, since in the case of quality scalability the enhancement packets are generated only by manipulating the transform coefficients, and not interfered with the motion compensation and static prediction.
+This argument no longer holds for the other scalable dimensions, so the model does not simply apply for those cases.
+Further research and modification of this linear model for the spatial or temporal scalability would be our future work.
+
+\subsection{Error Vector Acquisition}
+
+ It would need too many decoding times to get the error vectors of all enhancement packets if we calculate them one at a time.
+In order to acquire error vectors of all enhancement packets efficiently, we separate all enhancement packets into several groups, such that in each group multiple error vectors can be obtained independently at the same time.
+
+ \begin{figure}[h]
+ \centering
+ \includegraphics[width = 0.9\linewidth]{GOPStructure.jpg}
+ \caption{Group of pictures (GOP) in SVC \label{fig:GOP_Structure}}
+ \end{figure}
+
+ Consider a video bitstream with 8-frame GOPs (Group of Pictures) shown in Fig.
+\ref{fig:GOP_Structure}.
+Base layer packets are colored black, and enhancement packets with the same color are allocated in one group.
+In each group, the enhancement packets' error vectors can be calculated simultaneously, since the pixel errors they caused are not interfered with each other.
+For example, the loss of packet 8 would bring about distortion only in frame 1, 2 and 3, while packet 10 only in frame 5, 6 and 7(frame number starts from 0).
+So we can do subtraction for this group, for one time, to gain error vectors $e_{8}$ and $e_{10}$, for both packets 8 and 10, as well as peer packets in all other GOPs.
+Note that these error vectors are highly sparse ones, because the discarding of a single enhancement packet can bring distortion only to a limited number of frames.
+To acquire all error vectors, the number of required extraction and decoding is approximately the number of enhancement layers $(L_Q - 1)$ times the temporal layer number $L_T$.
+For the example in Fig.
+\ref{fig:GOP_Structure}, $L_Q = 3$ and $L_T = 4$, so the theoretical extraction-and-decoding number is $(3 - 1) \times 4 = 8$.
+However, we have to do the same manipulation for $L_Q - 1 = 2$ more times, to dissociate the distortion impact of ``key frame''\cite{H264Overview} (e.g.
+frame 0, 8, 16, etc.) packets.
+The loss of one enhancement packet in a key frame would bring distortion to two neighboring GOPs.
+As an instance, the loss of packet 4 would propagate drift into frame 1 to 15, which would interfere with the distortion impact of packets in frame 0 and 16 (packet 1, 2 and 19, 20).
+So key frame enhancement packets within the same quality layer (e.g.
+packet 2, 4 and 20) should be allocated in two groups -- one for key frame packets of even number GOPs (packet 2 and 20), the other for those of odd number GOPs (packet 4).
+So the actual number of extraction and decoding for error vector acquisition is $(L_Q - 1) \cdot (L_T + 1)$, approximately the same with the Quality Layer information acquisition in JSVM \cite{Amonou07}.
+Since computation is mainly consumed with this decoding in the bitstream extraction algorithm, the computation complexity has no obvious promotion compared with JSVM.
+
+\subsection{Distortion Estimation and Model Verification}
+
+Based on the linear error model described above, we can obtain error vectors of all enhancement packets.
+Then we can estimate the distortion caused by discarding any set of enhancement packets, by adding up the error vector of each packet in that set.
+
+For example, consider a video sequence decoded from a sub-stream which is extracted by discarding packet set $I_x$. The error between this sequence and the original sequence can be estimated as
+
+	\begin{equation}
+	\label{eq:subset_error}
+e(I_x) = e_{full} + \sum_{i \in {I_x}} e_i \: .
+	\end{equation}
+Eq. (\ref{eq:subset_error}) has taken into consideration the error between the video sequence decoded from full enhancement packets and the original sequence, written as $e_{full}$.
+
+To verify the linear error model, we conduct an experiment where possible combinations of enhancement packets are removed from a video bitstream, and the distortion estimated by the linear error model are compared with the actual distortion caused by the removal.
+The video stream has 8-frame GOPs and three quality layers, the same as illustrated in Fig.
+\ref{fig:GOP_Structure}.
+Experimental result of the sequence {\em Foreman} is partly shown in Fig.
+\ref{fig:linear_verification}.
+The horizontal axis stands for sample point numbers of those possible combinations, and the vertical axis for MSE measurement.
+The solid line represents the actual MSE of a randomly extracted substream, and the dot line shows the estimated MSE using our Linear Error Model.
+A 0.6\% maximum relative error of MSE demonstrates the accuracy of the proposed model.
+
+\begin{figure}[h]
+\centering
+\includegraphics[width = 0.9\linewidth]{LinearVerification.jpg}
+\caption{Result of SVC Linear Error Model verification \label{fig:linear_verification}}
+\end{figure}
+
+\subsection{Priority Assignment and Bitstream Extraction}
+\label{subsec:priority}
+
+In this subsection, we utilize the Linear Error Model to enable R-D optimized bitstream extraction.
+Since finding the global optimal solution of the bitstream extraction problem is impractical, our bitstream extraction algorithm uses a greedy method \cite{GreedyAlgo} to get a sub-optimal solution.
+Similar to the greedy solution of the ``0-1 Knapsack Problem", every time a packet is to be discarded, we choose the packet that has the minimal R-D impact.
+A packet's R-D impact is mathematically measured by:
+	\begin{equation}
+	\label{eq:rd_impact}
+\Phi_{i} = \dfrac{\partial D}{\partial R} \: ,
+	\end{equation}
+where $\partial D$ represents the distortion change brought by discarding this packet, and $\partial R$ is the corresponding rate change.
+$\partial R$ is simply equivalent to the size of this packet, while $\partial D$ needs to be calculated by subtraction of distortions before and after the packet is discarded.
+
+We simulate a process of discarding all the enhancement packets from a stream, using the above greedy strategy.
+During this process, the discarding order of a packet is regarded as its priority and recorded.
+Then the packets' priority values can be stored in the bitstream (either in the priority id field of the NALU header or in separate SEI messages) for real extraction in the future.
+
+The detailed discarding and priority assignment process is described below:
+\begin{description}
+  	\item[1)] Initially, the sequence error vector, $e_{seq}$, is set to $e_{full}$.
+  	\item[2)] Within the packets that can be discarded, find the packet $m$ having the least RD impact on the sequence, \textit{i.e. }
+	\begin{equation}
+	\label{eq:R-D_impact_m}
+	\Phi_m = \min_{i \in I_{top}} \Phi_i \: ,
+	\end{equation}
+	where $I_{top}$ stands for the top layer packets, those currently able to be discarded. The RD impact of a packet is calculated based on (\ref{eq:rd_impact}), as follows: 
+	\begin{equation}
+	\label{eq:R-D_impact_i}
+	\Phi_i = \dfrac{\partial D}{\partial R} = \dfrac{PSNR(e_{seq}) - PSNR(e_{seq} + e_i)}{SIZE(i)} \: ,
+	\end{equation}
+	where $PSNR(*)$ means to obtain PSNR from the error vector, and $SIZE(i)$ is the size of packet $i$.
+  	\item[3)]The packet, $m$, is then removed from the bitstream, and its error vector is added to the sequence's error vector, \textit{i.e.}
+  	\begin{equation}
+  	\label{eq:error_update}
+  	e_{seq} = e_{seq} + e_m \: .
+  	\end{equation}
+  	\item[4)]The process from 2) to 3) is repeated until all enhancement packets are discarded, and every packet is assigned a priority value according to the removing order.
+\end{description}
+
+For long video sequences, an optimization window is usually needed, and the priority assignment and bitstream extraction is conducted independently in each window.
+The computational complexity of this priority assignment algorithm is $O(K^2)$, with $K$ being the number of frames involved in the priority assignment process, \textit{i.e.}, the size of the optimization window.
+Note that this computation complexity is negligible compared with the decoding process needed in the error vector acquisition.
+
+\subsection{The No-Reference Case}
+\label{subsec:noref}
+
+In some scenarios, the priority assignment and bitstream extraction needs to be conducted without access to the original YUV sequence.
+For example, if the bitstream extraction is not done at the encoding side, it's most likely that the original sequence is not available.
+This would make the bitstream extraction a more difficult problem, since the distortion is harder to obtain for lacking of reference signal.
+Comparing to the problem of SVC bitstream extraction with reference, this kind of ``no-reference bitstream extraction'' problem is actually more frequently encountered in real practice.
+In this subsection, we handle this no-reference problem as well and modify the proposed algorithm to meet the special characteristic caused by lacking of reference.
+
+In the no-reference case, since we do not have access to the original sequence, we can not get the error between the video sequence decoded from full enhancement packets and the original sequence, which is $e_{full}$ used above.
+A straightforward idea is to set $e_{full}$ to zero, meaning we calculate distortion with respect to the fully reconstructed signal, rather than to the original sequence.
+However, simply doing so causes the algorithm to perform badly in experiments.
+We find that, since discarding some enhancement packets will not bring much significant error relative to the fully reconstructed signal, the calculated PSNR values are too large to well represent the real distortion.
+To address this issue, instead of calculating PSNR, we directly use MSE of all pixels as the distortion criteria in the priority assignment algorithm.
+This proves to be a simple and effective solution, and the extraction performance turns out to be much better.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Optimized Bitstream Extraction Based on Linear Error Model}
-\label{sec:bit-extraction}
-
-After the quality control algorithm determines an appropriate bitrate and sets a quality level accordingly, the system will only send packets belonging to this new quality level (as described at the end of Algorithm \ref{algo:control}).
-For SVC videos, it means to extract a subset of packets from the whole bitstream.
-How to optimally choose this subset to achieve minimum distortion under the given bitrate is the key point of bitstream extraction problem.
-In this section, we propose a linear error mode and a greedy-like algorithm to solve this problem.
-
-\subsection{Linear Error Model for Quality Scalable Video}
-\label{sec:model}
-
-In H.264/AVC, the decoding process involves a linear feature described in \cite{Winken08}, neglecting any rounding, clipping, and deblocking filtering operation.
-According to this feature, the main steps in H.264/AVC coding -- prediction, transform and quantization -- are proximately linear operations, and the whole coding process can be expressed in a matrix format as follows:
-	\begin{equation}
-	\label{eq:linear}
-s = {\rm\bf M}s + {\rm\bf T}c + p \: ,
-	\end{equation}
-It means, the reconstructed samples of a GOP (Group of Pictures), denoted by $s$, can be viewed as a linear combination of previously reconstructed samples in the GOP, the residual samples, and a static predictor.
-In (\ref{eq:linear}), $c$ refers to the transform coefficient values and $p$ is a static predictor; $M$ and $T$ are square matrices such that the product $M$s gives the MCP (Motion Compensated Prediction) signal and $Tc$ gives the residual values.
-The actual values of $M$ depend on the selected macroblock types, reference indices and motion vectors, whereas the actual values of $T$ depend on the chosen QP (Quantization Parameter) values.
-
-We apply the above linear decoding model to the case of quality scalability of SVC and get a linear error model.
-According to (\ref{eq:linear}), for a bitstream just containing the base layer, we have:
-	\begin{equation}
-	\label{eq:base0}
-s_{B} = {\rm\bf M}s_{B} + {\rm\bf T}_{B}c_{B} + p \: ,
-	\end{equation}
-where the subscript $B$ indicates the base layer variables.
-In quality scalability, the enhancement is mainly the refinement of transform coefficients, so for a bitstream containing an enhancement packet set $I_1$, the reconstruction relationship can be expressed as:
-	\begin{equation}
-	\label{eq:subset1}
-s_{I_1} = {\rm\bf M}s_{I_1} + {\rm\bf T}_{B} c_{B} + \Big( \sum_{i \in I_1}{\rm\bf T}_i c_i \Big) + p \: ,
-	\end{equation}
-where $i$ refers to an enhancement packet as an element of $I_1$.
-$c_i$ is a vector containing coefficients within the enhancement packet $i$.
-${\rm\bf T_i}$ is the transform matrix depending on the QP value of $i$.
-${\rm\bf T}_i c_i$ gives the residual sample values decoded from $i$.
-
-Similarly, for another bitstream containing an enhancement packet set $I_2$, we have
-	\begin{equation}
-	\label{eq:subset2}
-s_{I_2} = {\rm\bf M}s_{I_2} + {\rm\bf T}_{B} c_{B} + \Big( \sum_{i \in I_2}{\rm\bf T}_i c_i \Big) + p \: .
-	\end{equation}
-
-Suppose $I_1$ is a subset of $I_2$, their reconstruction difference can be obtained by (\ref{eq:subset2}) - (\ref{eq:subset1}):
-	\begin{equation}
-	\label{eq:minus1}
-(s_{I_2} - s_{I_1}) = {\rm\bf M}(s_{I_2} - s_{I_1}) + \Big( \sum_{i \in I_2}{\rm\bf T}_i c_i - \sum_{i \in I_1}{\rm\bf T}_i c_i \Big) \: ,
-	\end{equation}
-	\begin{equation}
-	\label{eq:minus2}
-\Rightarrow e = s_{I_2} - s_{I_1} = ({\rm\bf I - M})^{-1} \Big( \sum_{i \in I_2}{\rm\bf T}_i c_i - \sum_{i \in I_1}{\rm\bf T}_i c_i \Big) \: .
-	\end{equation}
-
-Particularly, if the difference of $I_2$ and $I_1$ is a single enhancement packet $j$, i.e.
-$I_2 \setminus I_1 = \{j\}$, then according to (\ref{eq:minus2}), the difference of the two reconstruction vectors can be written as
-	\begin{equation}
-	\label{eq:error_j}
-e_j = ({\rm\bf I - M})^{-1} {\rm\bf T}_j c_j \: .
-	\end{equation}
-
-Obviously, $e_j$ is only determined by packet $j$, and has no relation with other enhancement packets.
-This value is called the ``error vector'' of packet $j$, which represents the pixel value error caused by discarding the packet $j$.
-We can obtain the error vector of each enhancement packet by subtraction between video sequences reconstructed from two enhancement packet subsets $I_1$ and $I_2$, with $I_1 \subseteq I_2$ and $I_2 \setminus I_1 =\{j\} $.
-Once all packets' error vectors are obtained, the distortion caused by discarding a group of packets can be estimated by adding up the error vector of each packet in the group.
-
-The above model is called Linear Error Model (LEM).
-Note that in equations (\ref{eq:base0})-(\ref{eq:subset2}) the value of M and p remain the same, since in the case of quality scalability the enhancement packets are generated only by manipulating the transform coefficients, and not interfered with the motion compensation and static prediction.
-This argument no longer holds for the other scalable dimensions, so the model does not simply apply for those cases.
-Further research and modification of this linear model for the spatial or temporal scalability would be our future work.
-
-\subsection{Error Vector Acquisition}
-
- It would need too many decoding times to get the error vectors of all enhancement packets if we calculate them one at a time.
-In order to acquire error vectors of all enhancement packets efficiently, we separate all enhancement packets into several groups, such that in each group multiple error vectors can be obtained independently at the same time.
-
- \begin{figure}[h]
- \centering
- \includegraphics[width = 0.9\linewidth]{GOPStructure.jpg}
- \caption{Group of pictures (GOP) in SVC \label{fig:GOP_Structure}}
- \end{figure}
-
- Consider a video bitstream with 8-frame GOPs (Group of Pictures) shown in Fig.
-\ref{fig:GOP_Structure}.
-Base layer packets are colored black, and enhancement packets with the same color are allocated in one group.
-In each group, the enhancement packets' error vectors can be calculated simultaneously, since the pixel errors they caused are not interfered with each other.
-For example, the loss of packet 8 would bring about distortion only in frame 1, 2 and 3, while packet 10 only in frame 5, 6 and 7(frame number starts from 0).
-So we can do subtraction for this group, for one time, to gain error vectors $e_{8}$ and $e_{10}$, for both packets 8 and 10, as well as peer packets in all other GOPs.
-Note that these error vectors are highly sparse ones, because the discarding of a single enhancement packet can bring distortion only to a limited number of frames.
-To acquire all error vectors, the number of required extraction and decoding is approximately the number of enhancement layers $(L_Q - 1)$ times the temporal layer number $L_T$.
-For the example in Fig.
-\ref{fig:GOP_Structure}, $L_Q = 3$ and $L_T = 4$, so the theoretical extraction-and-decoding number is $(3 - 1) \times 4 = 8$.
-However, we have to do the same manipulation for $L_Q - 1 = 2$ more times, to dissociate the distortion impact of ``key frame''\cite{H264Overview} (e.g.
-frame 0, 8, 16, etc.) packets.
-The loss of one enhancement packet in a key frame would bring distortion to two neighboring GOPs.
-As an instance, the loss of packet 4 would propagate drift into frame 1 to 15, which would interfere with the distortion impact of packets in frame 0 and 16 (packet 1, 2 and 19, 20).
-So key frame enhancement packets within the same quality layer (e.g.
-packet 2, 4 and 20) should be allocated in two groups -- one for key frame packets of even number GOPs (packet 2 and 20), the other for those of odd number GOPs (packet 4).
-So the actual number of extraction and decoding for error vector acquisition is $(L_Q - 1) \cdot (L_T + 1)$, approximately the same with the Quality Layer information acquisition in JSVM \cite{Amonou07}.
-Since computation is mainly consumed with this decoding in the bitstream extraction algorithm, the computation complexity has no obvious promotion compared with JSVM.
-
-\subsection{Distortion Estimation and Model Verification}
-
-Based on the linear error model described above, we can obtain error vectors of all enhancement packets.
-Then we can estimate the distortion caused by discarding any set of enhancement packets, by adding up the error vector of each packet in that set.
-
-For example, consider a video sequence decoded from a sub-stream which is extracted by discarding packet set $I_x$. The error between this sequence and the original sequence can be estimated as
-
-	\begin{equation}
-	\label{eq:subset_error}
-e(I_x) = e_{full} + \sum_{i \in {I_x}} e_i \: .
-	\end{equation}
-Eq. (\ref{eq:subset_error}) has taken into consideration the error between the video sequence decoded from full enhancement packets and the original sequence, written as $e_{full}$.
-
-To verify the linear error model, we conduct an experiment where possible combinations of enhancement packets are removed from a video bitstream, and the distortion estimated by the linear error model are compared with the actual distortion caused by the removal.
-The video stream has 8-frame GOPs and three quality layers, the same as illustrated in Fig.
-\ref{fig:GOP_Structure}.
-Experimental result of the sequence {\em Foreman} is partly shown in Fig.
-\ref{fig:linear_verification}.
-The horizontal axis stands for sample point numbers of those possible combinations, and the vertical axis for MSE measurement.
-The solid line represents the actual MSE of a randomly extracted substream, and the dot line shows the estimated MSE using our Linear Error Model.
-A 0.6\% maximum relative error of MSE demonstrates the accuracy of the proposed model.
-
-\begin{figure}[h]
-\centering
-\includegraphics[width = 0.9\linewidth]{LinearVerification.jpg}
-\caption{Result of SVC Linear Error Model verification \label{fig:linear_verification}}
-\end{figure}
-
-\subsection{Priority Assignment and Bitstream Extraction}
-\label{subsec:priority}
-
-In this subsection, we utilize the Linear Error Model to enable R-D optimized bitstream extraction.
-Since finding the global optimal solution of the bitstream extraction problem is impractical, our bitstream extraction algorithm uses a greedy method \cite{GreedyAlgo} to get a sub-optimal solution.
-Similar to the greedy solution of the ``0-1 Knapsack Problem", every time a packet is to be discarded, we choose the packet that has the minimal R-D impact.
-A packet's R-D impact is mathematically measured by:
-	\begin{equation}
-	\label{eq:rd_impact}
-\Phi_{i} = \dfrac{\partial D}{\partial R} \: ,
-	\end{equation}
-where $\partial D$ represents the distortion change brought by discarding this packet, and $\partial R$ is the corresponding rate change.
-$\partial R$ is simply equivalent to the size of this packet, while $\partial D$ needs to be calculated by subtraction of distortions before and after the packet is discarded.
-
-We simulate a process of discarding all the enhancement packets from a stream, using the above greedy strategy.
-During this process, the discarding order of a packet is regarded as its priority and recorded.
-Then the packets' priority values can be stored in the bitstream (either in the priority id field of the NALU header or in separate SEI messages) for real extraction in the future.
-
-The detailed discarding and priority assignment process is described below:
-\begin{description}
-  	\item[1)] Initially, the sequence error vector, $e_{seq}$, is set to $e_{full}$.
-  	\item[2)] Within the packets that can be discarded, find the packet $m$ having the least RD impact on the sequence, \textit{i.e. }
-	\begin{equation}
-	\label{eq:R-D_impact_m}
-	\Phi_m = \min_{i \in I_{top}} \Phi_i \: ,
-	\end{equation}
-	where $I_{top}$ stands for the top layer packets, those currently able to be discarded. The RD impact of a packet is calculated based on (\ref{eq:rd_impact}), as follows: 
-	\begin{equation}
-	\label{eq:R-D_impact_i}
-	\Phi_i = \dfrac{\partial D}{\partial R} = \dfrac{PSNR(e_{seq}) - PSNR(e_{seq} + e_i)}{SIZE(i)} \: ,
-	\end{equation}
-	where $PSNR(*)$ means to obtain PSNR from the error vector, and $SIZE(i)$ is the size of packet $i$.
-  	\item[3)]The packet, $m$, is then removed from the bitstream, and its error vector is added to the sequence's error vector, \textit{i.e.}
-  	\begin{equation}
-  	\label{eq:error_update}
-  	e_{seq} = e_{seq} + e_m \: .
-  	\end{equation}
-  	\item[4)]The process from 2) to 3) is repeated until all enhancement packets are discarded, and every packet is assigned a priority value according to the removing order.
-\end{description}
-
-For long video sequences, an optimization window is usually needed, and the priority assignment and bitstream extraction is conducted independently in each window.
-The computational complexity of this priority assignment algorithm is $O(K^2)$, with $K$ being the number of frames involved in the priority assignment process, \textit{i.e.}, the size of the optimization window.
-Note that this computation complexity is negligible compared with the decoding process needed in the error vector acquisition.
-
-\subsection{The No-Reference Case}
-\label{subsec:noref}
-
-In some scenarios, the priority assignment and bitstream extraction needs to be conducted without access to the original YUV sequence.
-For example, if the bitstream extraction is not done at the encoding side, it's most likely that the original sequence is not available.
-This would make the bitstream extraction a more difficult problem, since the distortion is harder to obtain for lacking of reference signal.
-Comparing to the problem of SVC bitstream extraction with reference, this kind of ``no-reference bitstream extraction'' problem is actually more frequently encountered in real practice.
-In this subsection, we handle this no-reference problem as well and modify the proposed algorithm to meet the special characteristic caused by lacking of reference.
-
-In the no-reference case, since we do not have access to the original sequence, we can not get the error between the video sequence decoded from full enhancement packets and the original sequence, which is $e_{full}$ used above.
-A straightforward idea is to set $e_{full}$ to zero, meaning we calculate distortion with respect to the fully reconstructed signal, rather than to the original sequence.
-However, simply doing so causes the algorithm to perform badly in experiments.
-We find that, since discarding some enhancement packets will not bring much significant error relative to the fully reconstructed signal, the calculated PSNR values are too large to well represent the real distortion.
-To address this issue, instead of calculating PSNR, we directly use MSE of all pixels as the distortion criteria in the priority assignment algorithm.
-This proves to be a simple and effective solution, and the extraction performance turns out to be much better.
-
-We have presented experimental results for the case where reference original sequence is available in our previous work \cite{Zhang12}, so this paper will include only experimental results for the no-reference case in the following section.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Experimental Results}
@@
 
-To implement our proposed adaptive streaming system requires the combination of the PID-based quality control algorithm and the optimized bitstream extraction method.
-The former determines the current bitrate to follow the bandwidth change, and the latter will ensure the sub-stream with the best possible quality is obtained and sent under that bitrate constraint.
+To implement our proposed adaptive streaming system requires the combination of the optimized bitstream extraction method and the PID-based quality control algorithm.
+The latter determines the current bitrate to follow the bandwidth change, and the former will ensure the sub-stream with the best possible quality is obtained and sent under that bitrate constraint.
 They work together to construct a system that delivers best quality of experience for the users.
@@
 Readers who are interested in the practical implementation can also visit the online video website http://www.7dlive.com for more information.
-
-\subsection{Experiments for Quality Control}
-\label{subsec:exp-control}
-
-For simplicity and intuition, we combine the enhancement layers in the tested SVC video stream to construct quality levels (introduced in \ref{subsec:quality-level}) used in the quality control algorithm.
-The video stream is divided into several sub-streams, each of which is identified by the quality and temporal layer it contains, as illustrated in Table \ref{tab:sub-stream} (there are 3 layers in each scalability dimension; spatial scalability is not enabled).
-The quality level is defined as the sum of all sub-streams with ID equal or less than the level number.
-For example, quality level 3 would contain all sub-streams from 0 to 3, thus would include all temporal layers, but only the quality base layer 0.
-The tested stream has 9 quality levels from 0 to 8 (see Table \ref{tab:sub-stream}), and a maximum bit rate of 1587 kbps at level 8.
-
-\begin{table*}[t]
-\centering
-\caption{Sub-stream ID}
-\label{tab:sub-stream}
-\begin{tabular}{c|*{8}{p{1.2cm}<{\centering}|}{p{1.2cm}<{\centering}}}
-	\hline\hline
-	  Sub-stream ID   & 0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 \\ \hline
-	Quality Layer ID  & 0 & 0 & 0 & 1 & 1 & 1 & 2 & 2 & 2 \\ \hline
-	Temporal Layer ID & 0 & 1 & 2 & 0 & 1 & 2 & 0 & 1 & 2 \\ \hline
-\end{tabular}
-\end{table*}
-
-We simulate network fluctuation by adjusting bandwidth around a certain level.
-We set this level from 400 to 1400 kbps to reflect different average bandwidth.
-All the experiments are conducted in Visual C++ 6.0 (with DSS as the software platform) and the bandwidth control is implemented by NetLimiter 3 \cite{Netlimiter}.
-The baseline algorithm in the comparison refers to the packet delay feedback (PDF) algorithm in the original DSS.
-
-First of all, we conduct some preliminary improvement experiments using only proportional part or integral part.
-Since they are directly related to the short term error and long term error respectively, we call them Short Term Prediction (STP) and Long Term Prediction (LTP).
-Fig.
-\ref{fig:performance-all} shows the experimental results of these two control algorithms and the baseline algorithm.
-In the figures, the video quality is measured by the quality level defined in the beginning of this section, and quality smoothness is indicated by the variance of the quality levels along time.
-We can conclude that STP provides the best average quality level at the expense of high quality variance.
-This can be easily explained since this quality control strategy closely follows the bandwidth fluctuation.
-In contrast, LTP keeps a relatively low quality variance at a little cost of average video quality.
-Although it is not as good as STP in average quality, it still outperforms the baseline algorithm by 7.9\%.
-
-Since STP and LTP have their own limitations, we implement the PID-based quality control algorithm, which can both reduces quality variance and improves average quality level.
-From the result shown in Fig.
-\ref{fig:performance-two}, we can conclude that when integrated with integral part and derivative part, the effect of proportional part is not as aggressive as in STP.
-An obvious proof can be found in Fig.
-\ref{fig:variance-two}, which clearly shows that the proposed PID quality control algorithm keeps a lower quality variance compared to PDF algorithm.
-Table \ref{tab:improvement} lists the statistical experimental results for these four quality control algorithms, in which PID-based control algorithm has shown its advantage over the others, especially in reducing the quality fluctuation.
-It can be seen that, compared to PDF, the PID-based quality control algorithm improves 8.6\% in video quality with 24.8\% reduction in quality fluctuation.
-The video quality fluctuation of the four control algorithms, when available bandwidth fluctuates around 800 kbps, is shown in Fig.
-\ref{fig:fluctuation}, from which we can see a more stable video quality in the proposed PID quality control algorithm.
-
-\begin{figure*}[t]
-\subfloat[Average quality level of different control algorithms]{
-\includegraphics[width=0.5\textwidth]{Quality-all.jpg}
-\label{fig:quality-all}}
-\subfloat[Variance of quality level of different control algorithms]{
-\includegraphics[width=0.5\textwidth]{Variance-all.jpg}
-\label{fig:variance-all}}
-\caption{Comparison of the long/short time prediction and the PDF algorithm in DSS}
-\label{fig:performance-all}
-\end{figure*}
-
-\begin{figure*}[t]
-\centering
-\subfloat[Variance of quality level of PID and PDF control algorithms]{
-\includegraphics[width=0.5\textwidth]{Quality-two.jpg}
-\label{fig:quality-two}}
-\subfloat[Average quality level of PID and PDF control algorithms]{
-\includegraphics[width=0.5\textwidth]{Variance-two.jpg}
-\label{fig:variance-two}}
-\caption{Comparison of the proposed PID algorithm and the PDF algorithm in DDS}
-\label{fig:performance-two}
-\end{figure*}
-
-\begin{table*}[t]
-\centering
-\caption{Improvement of Different Quality Control Schemes}
-\label{tab:improvement}
-\begin{tabular}[b]{p{4.2cm}<{\centering}|p{4.2cm}<{\centering}|p{4.2cm}<{\centering}}
-\hline \hline
-Quality control scheme & Average quality level & Quality variance \\ \hline
-Packet delay feedback (PDF) & 0.0\% & 0.0\% \\ \hline
-Short term prediction (STP) & \textbf{+13.5\%} & +38.5\% \\ \hline
-Long term prediction (LTP) & +7.9\% & -17.2\% \\ \hline
-PID based control scheme(PID) & +8.6\% & \textbf{-24.8\%} \\ \hline
-\end{tabular}
-\end{table*}
-
-\begin{figure}[t]
-\centering
-\includegraphics[width = 0.9\linewidth]{Fluctuation.jpg}
-\caption{Video quality fluctuation with time \label{fig:fluctuation}}
-\end{figure}
 
@@
 
+\subsection{Experiments for Quality Control}
+\label{subsec:exp-control}
+
+For simplicity and intuition, we combine the enhancement layers in the tested SVC video stream to construct quality levels (introduced in \ref{subsec:quality-level}) used in the quality control algorithm.
+The video stream is divided into several sub-streams, each of which is identified by the quality and temporal layer it contains, as illustrated in Table \ref{tab:sub-stream} (there are 3 layers in each scalability dimension; spatial scalability is not enabled).
+The quality level is defined as the sum of all sub-streams with ID equal or less than the level number.
+For example, quality level 3 would contain all sub-streams from 0 to 3, thus would include all temporal layers, but only the quality base layer 0.
+The tested stream has 9 quality levels from 0 to 8 (see Table \ref{tab:sub-stream}), and a maximum bit rate of 1587 kbps at level 8.
+
+\begin{table*}[t]
+\centering
+\caption{Sub-stream ID}
+\label{tab:sub-stream}
+\begin{tabular}{c|*{8}{p{1.2cm}<{\centering}|}{p{1.2cm}<{\centering}}}
+	\hline\hline
+	  Sub-stream ID   & 0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 \\ \hline
+	Quality Layer ID  & 0 & 0 & 0 & 1 & 1 & 1 & 2 & 2 & 2 \\ \hline
+	Temporal Layer ID & 0 & 1 & 2 & 0 & 1 & 2 & 0 & 1 & 2 \\ \hline
+\end{tabular}
+\end{table*}
+
+We simulate network fluctuation by adjusting bandwidth around a certain level.
+We set this level from 400 to 1400 kbps to reflect different average bandwidth.
+All the experiments are conducted in Visual C++ 6.0 (with DSS as the software platform) and the bandwidth control is implemented by NetLimiter 3 \cite{Netlimiter}.
+The baseline algorithm in the comparison refers to the packet delay feedback (PDF) algorithm in the original DSS.
+
+First of all, we conduct some preliminary improvement experiments using only proportional part or integral part.
+Since they are directly related to the short term error and long term error respectively, we call them Short Term Prediction (STP) and Long Term Prediction (LTP).
+Fig.
+\ref{fig:performance-all} shows the experimental results of these two control algorithms and the baseline algorithm.
+In the figures, the video quality is measured by the quality level defined in the beginning of this section, and quality smoothness is indicated by the variance of the quality levels along time.
+We can conclude that STP provides the best average quality level at the expense of high quality variance.
+This can be easily explained since this quality control strategy closely follows the bandwidth fluctuation.
+In contrast, LTP keeps a relatively low quality variance at a little cost of average video quality.
+Although it is not as good as STP in average quality, it still outperforms the baseline algorithm by 7.9\%.
+
+Since STP and LTP have their own limitations, we implement the PID-based quality control algorithm, which can both reduces quality variance and improves average quality level.
+From the result shown in Fig.
+\ref{fig:performance-two}, we can conclude that when integrated with integral part and derivative part, the effect of proportional part is not as aggressive as in STP.
+An obvious proof can be found in Fig.
+\ref{fig:variance-two}, which clearly shows that the proposed PID quality control algorithm keeps a lower quality variance compared to PDF algorithm.
+Table \ref{tab:improvement} lists the statistical experimental results for these four quality control algorithms, in which PID-based control algorithm has shown its advantage over the others, especially in reducing the quality fluctuation.
+It can be seen that, compared to PDF, the PID-based quality control algorithm improves 8.6\% in video quality with 24.8\% reduction in quality fluctuation.
+The video quality fluctuation of the four control algorithms, when available bandwidth fluctuates around 800 kbps, is shown in Fig.
+\ref{fig:fluctuation}, from which we can see a more stable video quality in the proposed PID quality control algorithm.
+
+\begin{figure*}[t]
+\subfloat[Average quality level of different control algorithms]{
+\includegraphics[width=0.5\textwidth]{Quality-all.jpg}
+\label{fig:quality-all}}
+\subfloat[Variance of quality level of different control algorithms]{
+\includegraphics[width=0.5\textwidth]{Variance-all.jpg}
+\label{fig:variance-all}}
+\caption{Comparison of the long/short time prediction and the PDF algorithm in DSS}
+\label{fig:performance-all}
+\end{figure*}
+
+\begin{figure*}[t]
+\centering
+\subfloat[Variance of quality level of PID and PDF control algorithms]{
+\includegraphics[width=0.5\textwidth]{Quality-two.jpg}
+\label{fig:quality-two}}
+\subfloat[Average quality level of PID and PDF control algorithms]{
+\includegraphics[width=0.5\textwidth]{Variance-two.jpg}
+\label{fig:variance-two}}
+\caption{Comparison of the proposed PID algorithm and the PDF algorithm in DDS}
+\label{fig:performance-two}
+\end{figure*}
+
+\begin{table*}[t]
+\centering
+\caption{Improvement of Different Quality Control Schemes}
+\label{tab:improvement}
+\begin{tabular}[b]{p{4.2cm}<{\centering}|p{4.2cm}<{\centering}|p{4.2cm}<{\centering}}
+\hline \hline
+Quality control scheme & Average quality level & Quality variance \\ \hline
+Packet delay feedback (PDF) & 0.0\% & 0.0\% \\ \hline
+Short term prediction (STP) & \textbf{+13.5\%} & +38.5\% \\ \hline
+Long term prediction (LTP) & +7.9\% & -17.2\% \\ \hline
+PID based control scheme(PID) & +8.6\% & \textbf{-24.8\%} \\ \hline
+\end{tabular}
+\end{table*}
+
+\begin{figure}[t]
+\centering
+\includegraphics[width = 0.9\linewidth]{Fluctuation.jpg}
+\caption{Video quality fluctuation with time \label{fig:fluctuation}}
+\end{figure}
+
 \subsection{Result of the Combined System}

### 2015-05-12 tmm.tex
finish changing order and reorder the refs

@@
 To cope with the challenge brought by bandwidth fluctuation and provide the user with video of both smooth and high quality, an adaptive video streaming framework which can adjust video quality according to actual bandwidth condition is proposed based on the Scalable Video Coding (SVC) extension of H.264/AVC.
-First, a simple and effective linear error model is proposed and validated for quality scalability of SVC.
+First, a simple and effective linear error model is proposed and verified for quality scalability of SVC.
 The model exploits the linear feature of pixel value errors and can be used to accurately estimate the distortion caused by discarding any combination of enhancement data packets in an SVC bitstream.
@@
 \begin{itemize}
-\item First, a simple and effective linear error model (LEM) is proposed and validated, which can be used to accurately estimate the distortion caused by discarding any combination of packets from a SVC bitstream.
+\item First, a simple and effective linear error model (LEM) is proposed and verified, which can be used to accurately estimate the distortion caused by discarding any combination of packets from a SVC bitstream.
 \item Second, on the basis of the distortion estimation enabled by LEM, a greedy-like algorithm is designed to assign priority for each packet according to its R-D impact, thus enables optimized bitstream extraction.
@@
 \end{itemize}
+
+The proposed solutions for bitstream extraction and quality control are combined together and result in a higher and smoother PSNR curve representing the final video quality perceived by the user.
 
@@
 
-In this paper, we propose an adaptive video streaming system with PID-based quality control algorithm and optimized bitstream extraction.
-The PID-based quality control algorithm has a flexible mechanism to determine the suitable quality level so that it gives an accurate and swift response to the bandwidth change.
-Comparing with the original algorithm in DSS, this algorithm has reduced quality fluctuation significantly to improve audience satisfaction.
+In this paper, we propose an adaptive video streaming system with optimized bitstream extraction and PID-based quality control.
 The bitstream extraction method includes a linear error model to estimate the distortion caused by discarding any combination of packets and a greedy algorithm to assign priority to each data packet.
@@
 Experimental results show that the proposed method can achieve PSNR gain of up to 0.5dB compared to the JSVM QL extractor under the same bitrate constraint, also with the same computational complexity.
+The PID-based quality control algorithm has a flexible mechanism to determine the suitable quality level so that it gives an accurate and swift response to the bandwidth change.
+Comparing with the original algorithm in DSS, this algorithm has reduced quality fluctuation significantly to improve audience satisfaction.
 The SVC streaming system integrated with these two solutions performs well in automatically adapting to the user's bandwidth fluctuation, and is able to give the user a better watching experience.
 
-The PID-based quality control algorithm is only network-concerned thus should be easily integrated into other streaming systems, e.g., simulcast system like DASH.
-For the bitstream extraction, since the next generation video coding standard High Efficiency Video Coding (HEVC) \cite{HEVC} adopts the similar coding framework as its predecessor H.264/AVC, we expect to apply this paper's model and approach to the emerging HEVC standard and its scalable extension in our future work.
+Since the next generation video coding standard High Efficiency Video Coding (HEVC) \cite{HEVC} adopts the similar coding framework as its predecessor H.264/AVC, we expect to apply this paper's model and approach for bitstream extraction to the emerging HEVC standard and its scalable extension in our future work.
+As for the PID-based quality control algorithm, it is only network-concerned thus should be easily integrated into other streaming systems, e.g., simulcast system like DASH.
 
@@
 
+\bibitem{DSS}
+http://dss.macosforge.org/
+
+\bibitem{Knapsack}
+http://en.wikipedia.org/wiki/Knapsack\_problem
+
+\bibitem{Amonou07}
+I.~Amonou, N.~Cammas, S.~Kervadec, S.~Pateux, ``Optimized Rate-distortion Extraction with Quality Layers in the Scalable Extension of H.264/AVC'' in {\em IEEE Trans.
+Circuits Syst.
+Video Technol.}, vol.~17, no.~9, pp.~1186--1193, Sep.
+2007.
+
 \bibitem{JSVM}
@@
 
-\bibitem{DSS}
-http://dss.macosforge.org/
+\bibitem{Sun09}
+J.~Sun, W.~Gao, D.~Zhao, W.~Li, ``On Rate-distortion Modeling and Extraction of H.264/SVC Fine-Granular Scalable Video'' in {\em IEEE Trans.
+Circuits Syst.
+Video Technol.}, vol.~19, no.~3, pp.~323--336, Mar.
+2009.
+
+\bibitem{Maani09}
+E.~Maani, A.~K.
+Katsaggelos, ``Optimized Bit Extraction Using Distortion Modeling in the Scalable Extension of H.264/AVC'' in {\em IEEE Trans.
+Image Processing}, vol.~18, no.~9, pp.~2022--2029, Sep.
+2009.
+
+\bibitem{Zhang12}
+W.~Zhang, J.~Sun, J.~Liu and Z.~Guo, ``Optimized bit extraction of SVC exploiting linear error model,'' {\em 2012 IEEE International Symposium on Circuits and Systems}, pp.~1887--1890, Seoul, Korea, May 2012.
 
@@
 K. Gao, J. Zhai, J. Li and C. Wang, ``Real-Time scheduling for scalable video coding streaming system'', in {\em IEEE Sarnoff Symposium}, Princeton, NJ, pp. 1-4, Mar. 2006.
-
-\bibitem{Knapsack}
-http://en.wikipedia.org/wiki/Knapsack\_problem
 
@@
 
-\bibitem{Amonou07}
-I.~Amonou, N.~Cammas, S.~Kervadec, S.~Pateux, ``Optimized Rate-distortion Extraction with Quality Layers in the Scalable Extension of H.264/AVC'' in {\em IEEE Trans.
-Circuits Syst.
-Video Technol.}, vol.~17, no.~9, pp.~1186--1193, Sep.
-2007.
-
-\bibitem{Sun09}
-J.~Sun, W.~Gao, D.~Zhao, W.~Li, ``On Rate-distortion Modeling and Extraction of H.264/SVC Fine-Granular Scalable Video'' in {\em IEEE Trans.
-Circuits Syst.
-Video Technol.}, vol.~19, no.~3, pp.~323--336, Mar.
-2009.
-
-\bibitem{Maani09}
-E.~Maani, A.~K.
-Katsaggelos, ``Optimized Bit Extraction Using Distortion Modeling in the Scalable Extension of H.264/AVC'' in {\em IEEE Trans.
-Image Processing}, vol.~18, no.~9, pp.~2022--2029, Sep.
-2009.
-
-\bibitem{Zhang12}
-W.~Zhang, J.~Sun, J.~Liu and Z.~Guo, ``Optimized bit extraction of SVC exploiting linear error model,'' {\em 2012 IEEE International Symposium on Circuits and Systems}, pp.~1887--1890, Seoul, Korea, May 2012.
-
-\bibitem{Meng14}
-Shengbin Meng, Jun Sun, Yizhou Duan, Zongming Guo, ``An Efficient Method For No-Reference H.264/SVC Bitstream Extraction'', {\em IEEE International Conference on Acoustics, Speech, and Signal Processing}, Florence, Italy, May, 2014.
-
-\bibitem{Meng14-PID}
-Shengbin Meng, Jun Sun, Yilei Wang, Zongming Guo, ``A PID-based Quality Control Algorithm for SVC Video Streaming'', {\em IEEE International Conference on Communications}, Sydney, Australia, June, 2014.
-
-\bibitem{PID}
-http://en.wikipedia.org/wiki/PID\_controller
-
-\bibitem{Astrom02}
-K. J. Astrom, Control System Design, pp 216-219, 2002.
-
-\bibitem{Wong04}
-C.W.Wong, O.C.Au and H.K.Lam, ``PID-based real-time rate control'', in {\em IEEE International Conference on Multimedia and Expo}, 1: 221-224, 2004.
-
-\bibitem{Yang10}
-J. Yang, Y. Sun, Y. Zhou, S. Sun, ``Incremental rate control for H.264 scalable video coding'', in {\em IEEE Global Telecommunications Conference}, Miami, Florida, Dec. 2010.
-
-\bibitem{Li98}
-B. Li and K. Nahrstedt  ``A control theoretical model for quality of service adaptations'', in {\em Proceedings of Sixth International Workshop on Quality of Service}, 1998.
-
-\bibitem{Li99}
-B. Li and K. Nahrstedt, ``A control-sased middleware framework for Quality-of-Service adaptations'', in {\em IEEE J. Selected Areas in Comm.}, vol. 17, no. 9, pp. 1632-1650, Sept. 1999.
-
-\bibitem{Ziegler42}
-J. B. Ziegler and N. B. Nichols, ``Optimum settings for automatic controllers'', in {\em ASME Trans.}, pp. 759-768, 1942.
-
 \bibitem{Winken08}
@@
 International Conference on Image Processing 2008}.
+
+%\bibitem{Meng14}
+%Shengbin Meng, Jun Sun, Yizhou Duan, Zongming Guo, ``An Efficient Method For No-Reference H.264/SVC Bitstream Extraction'', {\em IEEE International Conference on Acoustics, Speech, and Signal Processing}, Florence, Italy, May, 2014.
+
+%\bibitem{Meng14-PID}
+%Shengbin Meng, Jun Sun, Yilei Wang, Zongming Guo, ``A PID-based Quality Control Algorithm for SVC Video Streaming'', {\em IEEE International Conference on Communications}, Sydney, Australia, June, 2014.
 
@@
 
+\bibitem{PID}
+http://en.wikipedia.org/wiki/PID\_controller
+
+\bibitem{Astrom02}
+K. J. Astrom, Control System Design, pp 216-219, 2002.
+
+\bibitem{Wong04}
+C.W.Wong, O.C.Au and H.K.Lam, ``PID-based real-time rate control'', in {\em IEEE International Conference on Multimedia and Expo}, 1: 221-224, 2004.
+
+\bibitem{Yang10}
+J. Yang, Y. Sun, Y. Zhou, S. Sun, ``Incremental rate control for H.264 scalable video coding'', in {\em IEEE Global Telecommunications Conference}, Miami, Florida, Dec. 2010.
+
+\bibitem{Li98}
+B. Li and K. Nahrstedt  ``A control theoretical model for quality of service adaptations'', in {\em Proceedings of Sixth International Workshop on Quality of Service}, 1998.
+
+\bibitem{Li99}
+B. Li and K. Nahrstedt, ``A control-sased middleware framework for Quality-of-Service adaptations'', in {\em IEEE J. Selected Areas in Comm.}, vol. 17, no. 9, pp. 1632-1650, Sept. 1999.
+
+\bibitem{Ziegler42}
+J. B. Ziegler and N. B. Nichols, ``Optimum settings for automatic controllers'', in {\em ASME Trans.}, pp. 759-768, 1942.
+
 \bibitem{Netlimiter}

### 2015-05-19 tmm.tex
more problem analysis

@@
 
-In this section, we analyze the two most concerned problems in SVC adaptive video streaming, i.e., bitstream extraction and quality control, and introduce some existing related works on them.
+In this section, we analyze the two most concerned problems in SVC adaptive video streaming, i.e., bitstream extraction and quality control, and introduce some related works on them.
 
@@
 
-SVC bitstream extraction is substantially a combinatorial optimization problem.
-More specifically, it is in the form of ``0-1 Knapsack Problem" \cite{Knapsack}.
-In the ``0-1 Knapsack Problem", given a set of objects, each with a weight and a value, one decides which object to include in the knapsack so that the total weight is no more than a given limit and the total value is as large as possible.
-Similarly, in bitstream extraction problem, each NALU data packet can be treated as an item with certain weight (the packet's size) and value (its contribution to the video quality).
-The solving process is mainly to decide whether or not a packet should be included in the final extracted sub-stream, or in the term of ``0-1 Knapsack Problem", to choose which object to pack up.
-
+Bitstream extraction is the operation of choosing a subset of data packets from a whole SVC bitstream to form a sub-stream.
+Fig.
+\ref{fig:Bitstream-Extraction} illustrates the structure of an SVC stream and a possible way to extract a sub-stream from it.
+The data packets in the stream are divided into different layers.
+The temporal layer (T0$\sim$T3) reflects the reference or dependency relationship between the frames, shown by the arrows on the top pointing from the frame which is referenced to the frame which is dependent on the reference.
+The quality layer (Q0$\sim$Q2) indicates scalability of video quality within each frame.
+The dash line demonstrates the sample extraction which will keep the data packets below the line and discard all the packets above it.
+This is only one option of the many possible ways, because there are many combinations of packets to be discarded.
+Our goal, however, is to choose a way that maximums the video quality of the extracted sub-stream, under the constrain of a give bitrate.
+
+\begin{figure}[h]
+\centering
+\includegraphics[width = 0.9\linewidth]{Bitstream-Extraction.jpg}
+\caption{Bitstream extraction of SVC \label{fig:Bitstream-Extraction}}
+\end{figure}
+
+SVC bitstream extraction, as we can see, is substantially a combinatorial optimization problem. More specifically, it is in the form of ``0-1 Knapsack Problem" \cite{Knapsack}. 
 Generally, the optimal solution of a typical ``0-1 Knapsack Problem" can be found using the dynamic programming algorithm.
@@
 For example, consider a video sequence decoded from a sub-stream which is extracted by discarding packet set $I_x$. The error between this sequence and the original sequence can be estimated as
-
 \begin{equation}
@@
 p{1.2cm}<{\centering}|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}}
-
 %% |l|l| to left justify each column entry
@@
 %% use of \rule[]{}{} below opens up each row 
-
 \hline \hline
@@
 {\em Bus} & {\em City} & {\em Crew} & {\em Football} & {\em Foreman} & {\em Harbour} & {\em Mobile} & {\em Soccer} \\ \hline 
-
 \multirow{2}{*}{JSVM QL\footnote{\label{footnote:JSVM_QL} Comparing the proposed algorithm with JSVM QL} (dB)}
@@
 & Ave\footnote{\label{footnote:ave} Average PSNR gain through all bitrate constraints} & 0.11 & 0.11 & 0.05 & 0.12 & 0.05 & 0.05 & 0.06 & 0.13 \\ \hline
-
 \multirow{2}{*}{JSVM no QL (dB)}
@@
 & Ave & 0.18 & 0.37 & 0.20 & 0.15 & 0.22 & 0.15 & 0.25 & 0.29 \\ \hline
-
 \end{tabular}
@@
 
+\bibitem{Ramanathan12}
+P.~Ramanathan and N.~Jayant. ``RD optimized bitstream extraction for H. 264/SVC based video streaming'' In {\em Proceedings of IEEE International Conference on Image Processing}, pp. 2241-2244, 2012.
+
+\bibitem{Yang13}
+K.~Yang, S.~Wan, Y.~Gong, and Y.~Feng.
+``A fast algorithm of bitstream extraction using distortion prediction based on simulated annealing'' In {\em Journal of Visual Communication and Image Representation}, no.7, 752-759, 2013.
+
 \bibitem{Maani09}
@@
 \bibitem{Zhang12}
-W.~Zhang, J.~Sun, J.~Liu and Z.~Guo, ``Optimized bit extraction of SVC exploiting linear error model,'' {\em 2012 IEEE International Symposium on Circuits and Systems}, pp.~1887--1890, Seoul, Korea, May 2012.
+W.~Zhang, J.~Sun, J.~Liu and Z.~Guo, ``Optimized bit extraction of SVC exploiting linear error model,'' {\em Proceedings of IEEE International Symposium on Circuits and Systems}, pp.~1887--1890, Seoul, Korea, May 2012.
 
@@
 \bibitem{Winken08}
-M.~Winken, H.~Schwarz, T.~Wiegand, ``Joint Rate-distortion Optimization of Transform Coefficients for Spatial Scalable Video Coding Using SVC'' in {\em Proc.
-International Conference on Image Processing 2008}.
+M.~Winken, H.~Schwarz, T.~Wiegand, ``Joint Rate-distortion Optimization of Transform Coefficients for Spatial Scalable Video Coding Using SVC'' in {\em Proceedings of IEEE International Conference on Image Processing}, 2008.
 
@@
 \bibitem{Wong04}
-C.W.Wong, O.C.Au and H.K.Lam, ``PID-based real-time rate control'', in {\em IEEE International Conference on Multimedia and Expo}, 1: 221-224, 2004.
+C.W.Wong, O.C.Au and H.K.Lam, ``PID-based real-time rate control'', in {\em Proceedings of IEEE International Conference on Multimedia and Expo}, 1: 221-224, 2004.
 

### 2015-05-20 tmm.tex
add related work and refine the text

@@
 Bitstream extraction is the operation of choosing a subset of data packets from a whole SVC bitstream to form a sub-stream.
+It makes the bitrate adjustable and is the prerequisite of an adaptive streaming system.
 Fig.
@@
 The data packets in the stream are divided into different layers.
-The temporal layer (T0$\sim$T3) reflects the reference or dependency relationship between the frames, shown by the arrows on the top pointing from the frame which is referenced to the frame which is dependent on the reference.
-The quality layer (Q0$\sim$Q2) indicates scalability of video quality within each frame.
-The dash line demonstrates the sample extraction which will keep the data packets below the line and discard all the packets above it.
-This is only one option of the many possible ways, because there are many combinations of packets to be discarded.
-Our goal, however, is to choose a way that maximums the video quality of the extracted sub-stream, under the constrain of a give bitrate.
+The temporal layer (T0$\sim$T3) reflects the reference or dependency relationship between the frames, shown by the arrows on the top pointing from the referenced frame to the frame which is dependent on it.
+The quality layer (Q0$\sim$Q2) indicates scalability of video quality within each frame, and packets in the higher quality layers (i.e., Q1 and Q2) are partially discarded to implement the extraction.
+For example, the dash line demonstrates the sample extraction which will keep the data packets below the line and discard all the packets above it.
+There are many combinations of packets to be discarded, which means there are many possible ways for an extraction.
+Our goal, however, is to choose a way that maximums the video quality of the extracted sub-stream, under the constraint of a given bitrate.
 
@@
 
-SVC bitstream extraction, as we can see, is substantially a combinatorial optimization problem. More specifically, it is in the form of ``0-1 Knapsack Problem" \cite{Knapsack}. 
-Generally, the optimal solution of a typical ``0-1 Knapsack Problem" can be found using the dynamic programming algorithm.
-However, this is not operational for the bitstream extraction problem, mainly due to the dependence between packets.
-First, the value of a packet is not obvious and certain, since a packet's contribution to video quality may depend on the other packets.
-Second, the subset of packets to be extracted cannot be chosen arbitrarily, since if a packet is included, all the packets it depends on must also be included.
+As we can see, in its nature SVC bitstream extraction is a combinatorial optimization problem.
+More specifically, it is in the form of ``0-1 Knapsack Problem" \cite{Knapsack}.
+In the ``0-1 Knapsack Problem", given some objects, each with a weight and a value, one decides which object to include in the knapsack so that the total weight is no more than a given limit and the total value is as large as possible.
+Similarly, in bitstream extraction problem, each data packet can be treated as an item with certain weight (the packet's size) and value (its contribution to the video quality).
+The solving process is mainly to decide whether or not a packet should be included in the final extracted sub-stream, or in the term of ``0-1 Knapsack Problem", to choose which object to pack up.
+
+For a typical ``0-1 Knapsack Problem", the optimal solution can generally be found using the dynamic programming algorithm.
+However, this is not operational for the bitstream extraction problem, mainly due to the dependence between the stream's data packets.
+First, the subset of packets to be extracted cannot be chosen arbitrarily, since if a packet is included, all the packets it depends on must also be included.
+For example, in Fig.
+\ref{fig:Bitstream-Extraction}, we cannot include the packet in Q2 of a frame without including the packet in Q1 of the same frame.
+Second, the value of a packet is not obvious and certain, since a packet's contribution to video quality may depend on the other packets.
+Unless we discard a packet and calculate the distortion it causes for real, there is no way to exactly tell its value.
 In fact, to the best of our knowledge, no method presented in the literature claims to find the optimal solution of the SVC bitstream extraction problem.
@@
 Maani et al.'s model can achieve better estimation accuracy than JSVM; however, since it is a training-based model, more computation is needed to get robust model parameters.
+Ramanathan et al.
+\cite{Ramanathan12} proposed their concept and calculation method of the ``Quality Metadata'' to signal and use in bitstream extraction.
+Yang et al.
+\cite{Yang13} proposed a method based-on simulated annealing to solve the bitstream extraction problem.
+In both methods, the accuracy of distortion estimation is the key of the performance.
 
@@
 \subsection{Quality Control}
+
+Quality control is the second problem we will address in this paper.
+The result of a quality control algorithm determines the suitable bitrate for current transmission, which is directly related to the change of video quality perceived by the user.
+It should be noted that, the bitstream extraction is performed under constraint of that bitrate determined by quality control, and even in non-SVC streaming systems (DASH, for example), quality control is an important part that requires careful design.
 
@@
 In other words, the available bandwidth should be fully utilized.
-Suppose we keep sending video data in a low bitrate (with low video quality as well), neither the playback pause nor any quality fluctuation will likely happen.
+Suppose we keep sending video data in a low bitrate (with low video quality as well), neither the playback will pause nor any quality fluctuation will happen.
 However, a low video quality is certainly not what we want.
@@
 
-In DSS, quality control is implemented by monitoring packet delay (the difference between current time and the playing time of this packet).
-When a new packet is ready to be sent to streaming buffer, DSS checks the delay of it and compares this delay with some pre-set critical time thresholds to judge whether and how violently the quality change should be made.
+In the widely-used video streaming server DSS, quality control is implemented by monitoring packet delay (the difference between current time and the playing time of this packet).
+When a new packet is ready to be sent to streaming buffer, DSS checks the delay of it and compares this delay with some pre-set thresholds to judge whether and how violently the quality change should be made.
 This algorithm can reduce quality fluctuation to some degree.
 However, it only provides conservative quality change, which makes its reaction so slow that sometimes media player may have already stopped due to lack of video data before quality drops.
-Furthermore, this algorithm has no knowledge of the bandwidth change so it cannot accurately adjust the video quality.
-Therefore, quality oscillation is inevitable in this algorithm.
+Furthermore, this algorithm does not keep track of the bandwidth change so it cannot adjust the video quality accordingly.
+Quality oscillation might occur in this algorithm.
 
 The following of this paper will present our solutions for the above problems in detail.
-And we will combine our works together and lay a solid foundation for a practical adaptive video streaming system.
+The solutions then work together and serve as a solid foundation for a practical adaptive video streaming system.
 
@@
 
-Being able to adjust bitrate is the prerequisite for an adaptive video streaming system.
+Being able to adjust bitrate is the prerequisite of an adaptive video streaming system.
 For SVC videos, it means to extract a subset of packets from the whole bitstream.
@@
 Note that in equations (\ref{eq:base0})-(\ref{eq:subset2}) the value of M and p remain the same, since in the case of quality scalability the enhancement packets are generated only by manipulating the transform coefficients, and not interfered with the motion compensation and static prediction.
-This argument no longer holds for the other scalable dimensions, so the model does not simply apply for those cases.
-Further research and modification of this linear model for the spatial or temporal scalability would be our future work.
+This argument no longer holds for the other scalable dimensions (e.g., spatial scalability), so the model does not simply apply for those cases.
+Only quality scalable videos are used in our system, and further research for other scalable dimensions can be our future work.
 
@@
 This proves to be a simple and effective solution, and the extraction performance turns out to be much better.
+
+After each packet is assigned a priority value and optimized extraction is made possible, the video stream now can well adapt to different data rates.
+Next, we propose the quality control algorithm based on the PID control mechanism, which is responsible for determining a suitable data rate according to current bandwidth condition.
 
@@
 The latter determines the current bitrate to follow the bandwidth change, and the former will ensure the sub-stream with the best possible quality is obtained and sent under that bitrate constraint.
-They work together to construct a system that delivers best quality of experience for the users.
+They work together to deliver best quality of service for the user.
 Choosing DSS as the implementation basis, we have integrated the proposed algorithms into it for the purpose of both research and application.
-In this section, we first present separate experiments to demonstrate the advantage of each proposed solution, and then give the result when they are combined together.
-Readers who are interested in the practical implementation can also visit the online video website http://www.7dlive.com for more information.
+In this section, we first present separate experiments to show the advantage of each proposed solution, and then give the result when they are combined together.
+Readers who are interested in the practical implementation and demonstration can visit the online video website http://www.7dlive.com for more information.
 
@@
 The bitstream extraction method includes a linear error model to estimate the distortion caused by discarding any combination of packets and a greedy algorithm to assign priority to each data packet.
-The packets' priority values can then be stored in the bitstream and used for R-D optimized extraction.
+The priority values can then be stored in the bitstream and used for R-D optimized extraction.
 Experimental results show that the proposed method can achieve PSNR gain of up to 0.5dB compared to the JSVM QL extractor under the same bitrate constraint, also with the same computational complexity.
@@
 
-Since the next generation video coding standard High Efficiency Video Coding (HEVC) \cite{HEVC} adopts the similar coding framework as its predecessor H.264/AVC, we expect to apply this paper's model and approach for bitstream extraction to the emerging HEVC standard and its scalable extension in our future work.
+Since the next generation video coding standard High Efficiency Video Coding (HEVC) \cite{HEVC} adopts the similar coding framework as its predecessor H.264/AVC, we expect to apply this paper's model and approach of bitstream extraction to the emerging HEVC standard and its scalable extension.
 As for the PID-based quality control algorithm, it is only network-concerned thus should be easily integrated into other streaming systems, e.g., simulcast system like DASH.
@@
 
-\bibitem{Ramanathan12}
-P.~Ramanathan and N.~Jayant. ``RD optimized bitstream extraction for H. 264/SVC based video streaming'' In {\em Proceedings of IEEE International Conference on Image Processing}, pp. 2241-2244, 2012.
-
-\bibitem{Yang13}
-K.~Yang, S.~Wan, Y.~Gong, and Y.~Feng.
-``A fast algorithm of bitstream extraction using distortion prediction based on simulated annealing'' In {\em Journal of Visual Communication and Image Representation}, no.7, 752-759, 2013.
-
 \bibitem{Maani09}
@@
 2009.
+
+\bibitem{Ramanathan12}
+P.~Ramanathan and N.~Jayant. ``RD optimized bitstream extraction for H. 264/SVC based video streaming'' In {\em Proceedings of IEEE International Conference on Image Processing}, pp. 2241-2244, 2012.
+
+\bibitem{Yang13}
+K.~Yang, S.~Wan, Y.~Gong, and Y.~Feng.
+``A fast algorithm of bitstream extraction using distortion prediction based on simulated annealing'' In {\em Journal of Visual Communication and Image Representation}, no.7, 752-759, 2013.
 

### 2015-06-17 tmm.tex
redraw pictures

@@
 \author{Shengbin~Meng,~Jun~Sun,~Yizhou~Duan~and~Zongming~Guo,~\em{Member,~IEEE} % <-this % stops a space
-\thanks{Manuscript received April 10, 2015.}
+\thanks{Manuscript received May 20, 2015.}
 \thanks{The authors are with the Institute of Computer Science and Technology, Peking University, Beijing%
@@
 \begin{abstract}
-To cope with the challenge brought by bandwidth fluctuation and provide the user with video of both smooth and high quality, an adaptive video streaming framework which can adjust video quality according to actual bandwidth condition is proposed based on the Scalable Video Coding (SVC) extension of H.264/AVC.
+To cope with the challenge brought by bandwidth fluctuation and provide the user with best online video watching experience, an adaptive video streaming system which can adjust video quality according to actual bandwidth condition is proposed based on the Scalable Video Coding (SVC) extension of H.264/AVC.
 First, a simple and effective linear error model is proposed and verified for quality scalability of SVC.
 The model exploits the linear feature of pixel value errors and can be used to accurately estimate the distortion caused by discarding any combination of enhancement data packets in an SVC bitstream.
-Then on the basis of that, a greedy-like algorithm is designed to assign each data packet a priority value according to its Rate-Distortion (R-D) impact, thus enables R-D optimized bitstream extraction under certain bitrate constraint.
+Then on that basis, a greedy-like algorithm is designed to assign each data packet a priority value according to its Rate-Distortion (R-D) impact, thus enables R-D optimized bitstream extraction under certain bitrate constraint.
 Finally, the Proportional-Integral-Derivative (PID) method is utilized to control the video quality adjustment and determine the suitable bitrate for transmission.
 By monitoring and predicting bandwidth information of the past, the current and the future, the PID-based quality control algorithm can significantly reduce quality fluctuation while still keeping a high quality level.
-Experimental results show that, comparing with the baseline software, the proposed framework integrating the above algorithms can achieve much lower video quality fluctuation, with PSNR variance reduced from 0.66 to 0.28, and at the same time deliver higher video quality, with an average PSNR gain of 0.33dB.
-The framework is deployed at online video website www.7dlive.com and proves to be practically effective.
+Experimental results show that, comparing with the baseline software, the proposed system integrating the above algorithms can achieve much lower video quality fluctuation, with PSNR variance reduced from 0.66 to 0.28, and at the same time deliver higher video quality, with an average PSNR gain of 0.33dB.
+The system is deployed at online video website www.7dlive.com and proves to be practically effective.
 \end{abstract}
@@
 The quality layer (Q0$\sim$Q2) indicates scalability of video quality within each frame, and packets in the higher quality layers (i.e., Q1 and Q2) are partially discarded to implement the extraction.
-For example, the dash line demonstrates the sample extraction which will keep the data packets below the line and discard all the packets above it.
-There are many combinations of packets to be discarded, which means there are many possible ways for an extraction.
-Our goal, however, is to choose a way that maximums the video quality of the extracted sub-stream, under the constraint of a given bitrate.
+For example, the dash line demonstrates the extraction which will keep the data packets below the line and discard all the packets above it.
 
@@
 As we can see, in its nature SVC bitstream extraction is a combinatorial optimization problem.
-More specifically, it is in the form of ``0-1 Knapsack Problem" \cite{Knapsack}.
-In the ``0-1 Knapsack Problem", given some objects, each with a weight and a value, one decides which object to include in the knapsack so that the total weight is no more than a given limit and the total value is as large as possible.
-Similarly, in bitstream extraction problem, each data packet can be treated as an item with certain weight (the packet's size) and value (its contribution to the video quality).
+There are many combinations of packets to be discarded, and we want to choose a combination that maximums the video quality of the extracted sub-stream, under the constraint of a given bitrate.
+More specifically, this problem in the form of ``0-1 Knapsack Problem" \cite{Knapsack}.
+Each data packet can be treated as an object with certain weight (the packet's size) and value (its contribution to the video quality).
 The solving process is mainly to decide whether or not a packet should be included in the final extracted sub-stream, or in the term of ``0-1 Knapsack Problem", to choose which object to pack up.
@@
 For example, in Fig.
-\ref{fig:Bitstream-Extraction}, we cannot include the packet in Q2 of a frame without including the packet in Q1 of the same frame.
+\ref{fig:Bitstream-Extraction}, we cannot include the Q2 packet of a frame without including the Q1 packet of the same frame.
 Second, the value of a packet is not obvious and certain, since a packet's contribution to video quality may depend on the other packets.
@@
 
-To verify the linear error model, we conduct an experiment where possible combinations of enhancement packets are removed from a video bitstream, and the distortion estimated by the linear error model are compared with the actual distortion caused by the removal.
-The video stream has 8-frame GOPs and three quality layers, the same as illustrated in Fig.
+To verify the linear error model, we conduct an experiment where random combinations of enhancement packets are removed from a video bitstream, and the distortion estimated by the linear error model are compared with the actual distortion caused by the removal.
+Experimental result of the sequence {\em Foreman} is shown in Fig.
+\ref{fig:model_verification}.
+The bitstream has 8-frame GOPs and three quality layers, the same as illustrated in Fig.
 \ref{fig:GOP_Structure}.
-Experimental result of the sequence {\em Foreman} is partly shown in Fig.
-\ref{fig:linear_verification}.
-The horizontal axis stands for sample point numbers of those possible combinations, and the vertical axis for MSE measurement.
-The solid line represents the actual MSE of a randomly extracted substream, and the dot line shows the estimated MSE using our Linear Error Model.
-A 0.6\% maximum relative error of MSE demonstrates the accuracy of the proposed model.
+There are 33 frames in the sequence.
+The horizontal axis stands for frame index, and the vertical axis for MSE measurement.
+The solid line represents the actual MSE of a frame, and the dot line shows the estimated MSE using our Linear Error Model.
+It can be seen that the two lines are very close to each other, which demonstrates the accuracy of the proposed model.
+The distortion estimation error is less than 5\% in our experiments.
 
@@
 \centering
-\includegraphics[width = 0.9\linewidth]{LinearVerification.jpg}
-\caption{Result of SVC Linear Error Model verification \label{fig:linear_verification}}
+\includegraphics[width = 0.9\linewidth]{ModelVerification.png}
+\caption{Result of SVC Linear Error Model verification \label{fig:model_verification}}
 \end{figure}
@@
 \subfloat[Average quality level of different control algorithms]{
-\includegraphics[width=0.5\textwidth]{Quality-all.jpg}
+\includegraphics[width=0.5\textwidth]{Quality-all.png}
 \label{fig:quality-all}}
 \subfloat[Variance of quality level of different control algorithms]{
-\includegraphics[width=0.5\textwidth]{Variance-all.jpg}
+\includegraphics[width=0.5\textwidth]{Variance-all.png}
 \label{fig:variance-all}}
@@
 \subfloat[Variance of quality level of PID and PDF control algorithms]{
-\includegraphics[width=0.5\textwidth]{Quality-two.jpg}
+\includegraphics[width=0.5\textwidth]{Quality-two.png}
 \label{fig:quality-two}}
 \subfloat[Average quality level of PID and PDF control algorithms]{
-\includegraphics[width=0.5\textwidth]{Variance-two.jpg}
+\includegraphics[width=0.5\textwidth]{Variance-two.png}
 \label{fig:variance-two}}
@@
 \centering
-\includegraphics[width = 0.9\linewidth]{Fluctuation.jpg}
+\includegraphics[width = 0.9\linewidth]{Fluctuation.png}
 \caption{Video quality fluctuation with time \label{fig:fluctuation}}
@@
 
-\begin{figure*}[t]
+\begin{figure}[t]
 \centering
-\includegraphics[width = 0.9\linewidth]{Fluctuation-PSNR-wide.jpg}
+\includegraphics[width = 0.9\linewidth]{Fluctuation-PSNR.png}
 \caption{User-perceived PSNR change with time when bandwidth fluctuates \label{fig:fluctuation-psnr}}
-\end{figure*}
+\end{figure}
 

### 2015-06-19 tmm.tex
add data table for model verification

@@
 
-We apply the above linear decoding model to the case of quality scalability of SVC and get a linear error model.
+We apply the above linear decoding model to the case of quality scalability of SVC and get a Linear Error Model (LEM).
 According to (\ref{eq:linear}), for a bitstream just containing the base layer, we have:
@@
 
-The above model is called Linear Error Model (LEM).
 Note that in equations (\ref{eq:base0})-(\ref{eq:subset2}) the value of M and p remain the same, since in the case of quality scalability the enhancement packets are generated only by manipulating the transform coefficients, and not interfered with the motion compensation and static prediction.
-This argument no longer holds for the other scalable dimensions (e.g., spatial scalability), so the model does not simply apply for those cases.
-Only quality scalable videos are used in our system, and further research for other scalable dimensions can be our future work.
+This argument no longer holds for the other scalable dimensions (e.g., spatial scalability), so LEM does not simply apply for those cases.
+Therefor, only quality scalable videos are used in our system, and further research for other scalable dimensions can be our future work.
 
@@
 To verify the linear error model, we conduct an experiment where random combinations of enhancement packets are removed from a video bitstream, and the distortion estimated by the linear error model are compared with the actual distortion caused by the removal.
-Experimental result of the sequence {\em Foreman} is shown in Fig.
+The video stream has 33 frames, and the same GOP structure and quality layers as illustrated in Fig.
+\ref{fig:GOP_Structure}.
+One comparison result for the sequence {\em Foreman} is shown in Fig.
 \ref{fig:model_verification}.
-The bitstream has 8-frame GOPs and three quality layers, the same as illustrated in Fig.
-\ref{fig:GOP_Structure}.
-There are 33 frames in the sequence.
 The horizontal axis stands for frame index, and the vertical axis for MSE measurement.
@@
 It can be seen that the two lines are very close to each other, which demonstrates the accuracy of the proposed model.
-The distortion estimation error is less than 5\% in our experiments.
+Table \ref{tab:estimation-error} lists the distortion estimation error for different sequences and shows that the average error is only about 5\%.
 
@@
 \includegraphics[width = 0.9\linewidth]{ModelVerification.png}
-\caption{Result of SVC Linear Error Model verification \label{fig:model_verification}}
+\caption{Comparison of actual and estimated distortion for sequence {\em Foreman} \label{fig:model_verification}}
 \end{figure}
+
+\begin{table*}
+\centering
+\caption{Performance of distortion estimation using LEM}
+\label{tab:estimation-error}
+\begin{tabular}{c|*{8}{p{1.2cm}<{\centering}|}{p{1.2cm}<{\centering}}}
+	\hline\hline
+	Sequence name & {\em Bus} & {\em City} & {\em Crew} & {\em Football} & {\em Foreman} & {\em Harbour} & {\em Mobile} & {\em Soccer} & \textbf{Average} \\ \hline
+	Estimation error  & 2.83\% & 2.39\% & 10.36\% & 7.08\% & 4.95\% & 2.63\% & 5.77\% & 5.26\% & \textbf{5.16\%} \\ \hline
+\end{tabular}
+\end{table*}
 
@@
 
-In this subsection, we utilize the Linear Error Model to enable R-D optimized bitstream extraction.
+In this subsection, we utilize the linear error model to enable R-D optimized bitstream extraction.
 Since finding the global optimal solution of the bitstream extraction problem is impractical, our bitstream extraction algorithm uses a greedy method \cite{GreedyAlgo} to get a sub-optimal solution.
@@
 Comparing to the problem of SVC bitstream extraction with reference, this kind of ``no-reference bitstream extraction'' problem is actually more frequently encountered in real practice.
-In this subsection, we handle this no-reference problem as well and modify the proposed algorithm to meet the special characteristic caused by lacking of reference.
+In this subsection, we consider this no-reference problem and modify the proposed algorithm to meet the special characteristic caused by lacking of reference.
 
@@
 To address this issue, instead of calculating PSNR, we directly use MSE of all pixels as the distortion criteria in the priority assignment algorithm.
-This proves to be a simple and effective solution, and the extraction performance turns out to be much better.
+This proves to be an effective solution, and the extraction performance turns out to be much better.
 
 After each packet is assigned a priority value and optimized extraction is made possible, the video stream now can well adapt to different data rates.
-Next, we propose the quality control algorithm based on the PID control mechanism, which is responsible for determining a suitable data rate according to current bandwidth condition.
+Next, we propose the quality control algorithm based on the PID mechanism, which is responsible for determining a suitable data rate according to current bandwidth condition.
 

### 2015-07-09 tmm.tex
add more experimental results

@@
 By monitoring and predicting bandwidth information of the past, the current and the future, the PID-based quality control algorithm can significantly reduce quality fluctuation while still keeping a high quality level.
-Experimental results show that, comparing with the baseline software, the proposed system integrating the above algorithms can achieve much lower video quality fluctuation, with PSNR variance reduced from 0.66 to 0.28, and at the same time deliver higher video quality, with an average PSNR gain of 0.33dB.
+Experimental results show that, comparing with the baseline software, the proposed system integrating the above algorithms can achieve much lower video quality fluctuation, with PSNR variance reduced from 0.63 to 0.21, and at the same time deliver higher video quality, with an average PSNR gain of 0.66dB.
 The system is deployed at online video website www.7dlive.com and proves to be practically effective.
@@
 To verify the linear error model, we conduct an experiment where random combinations of enhancement packets are removed from a video bitstream, and the distortion estimated by the linear error model are compared with the actual distortion caused by the removal.
-The video stream has 33 frames, and the same GOP structure and quality layers as illustrated in Fig.
+The video stream has the same GOP structure and quality layers as illustrated in Fig.
 \ref{fig:GOP_Structure}.
-One comparison result for the sequence {\em Foreman} is shown in Fig.
+One comparison result for the sequence {\em Foreman} (only first 33 frames are used) is shown in Fig.
 \ref{fig:model_verification}.
@@
 
-\begin{figure}[t]
+\begin{figure}
 \centering
@@
 \ref{fig:fluctuation-psnr}.
-It shows PSNR change perceived by the user when available bandwidth fluctuates around 800 kbps.
-It can be seen that, the proposed system has effectively avoided unnecessary quality drop (note the curve around time 50s and 350s) and been able to keep a relatively higher PSNR value (note the curve between time 450s and 600s).
-The average and variance of PSNR delivered by the proposed system are 40.62 and 0.28, respectively, while the values of the baseline system are 40.29 and 0.66.
-
-\begin{figure}[t]
-\centering
-\includegraphics[width = 0.9\linewidth]{Fluctuation-PSNR.png}
+It shows PSNR change perceived by the user when available bandwidth fluctuates around certain values (600kbps, 800kbps, 1000kbps and 1200kbps).
+The bandwidth conditions are simulated with NetLimiter and intense fluctuations are observed.
+It can be seen that, the proposed system performs better in that it has effectively avoided unnecessary quality drop (e.g., note the curve around time 450s in Fig.
+\ref{fig:Fluctuation-PSNR1} or around 250s in Fig.
+\ref{fig:Fluctuation-PSNR3}) and been able to keep a relatively higher PSNR value (e.g., note the curve around time 400s in Fig.
+\ref{fig:Fluctuation-PSNR2} or around time 500s in Fig.
+\ref{fig:Fluctuation-PSNR4}).
+The average and variance value of PSNR is also calculated and present in Fig.
+\ref{fig:fluctuation-psnr}, which showing clearly the proposed system's advantage.
+For instance, in Fig.
+\ref{fig:Fluctuation-PSNR4} where bandwidth fluctuates around 1200kbps, the average PSNR delivered by the proposed system is 41.14dB, 0.66dB higher than that of the baseline system, and the PSNR variance is also reduced from 0.63 to 0.21, indicating a more smooth video quality change.
+
+\begin{figure*}[t]
+\centering
+\subfloat[Bandwidth fluctuates around 600kbps: PSNR average and variance in the original system are 39.63 and 0.24, while in the proposed system are 39.69 and 0.16.]{
+\includegraphics[width=0.47\textwidth]{Fluctuation-PSNR1.png}
+\label{fig:Fluctuation-PSNR1}}\hfill
+\subfloat[Bandwidth fluctuates around 800kbps: PSNR average and variance in the original system are 40.15 and 0.48, while in the proposed system are 40.62 and 0.28.]{
+\includegraphics[width=0.47\textwidth]{Fluctuation-PSNR2.png}
+\label{fig:Fluctuation-PSNR2}}
+\qquad
+\subfloat[Bandwidth fluctuates around 1000kbps: PSNR average and variance in the original system are 40.37 and 0.50, while in the proposed system are 40.74 and 0.28.]{
+\includegraphics[width=0.47\textwidth]{Fluctuation-PSNR3.png}
+\label{fig:Fluctuation-PSNR3}}\hfill
+\subfloat[Bandwidth fluctuates around 1200kbps: PSNR average and variance in the original system are 40.48 and 0.63, while in the proposed system are 41.14 and 0.21.]{
+\includegraphics[width=0.47\textwidth]{Fluctuation-PSNR4.png}
+\label{fig:Fluctuation-PSNR4}}
 \caption{User-perceived PSNR change with time when bandwidth fluctuates \label{fig:fluctuation-psnr}}
-\end{figure}
+\end{figure*}
 

### 2015-07-13 tmm.tex
before submit

@@
 \author{Shengbin~Meng,~Jun~Sun,~Yizhou~Duan~and~Zongming~Guo,~\em{Member,~IEEE} % <-this % stops a space
-\thanks{Manuscript received May 20, 2015.}
+\thanks{Manuscript received July 15, 2015.}
 \thanks{The authors are with the Institute of Computer Science and Technology, Peking University, Beijing%
@@
 In (\ref{eq:long-actual}) and (\ref{eq:long-check}), $T_l$ stands for the last quality change time.
-Theoretically, the integral part should be recorded and calculated from the system start.
+Theoretically, the integral part should be recorded and calculated since the system start.
 In practice, however, bandwidth may vary significantly during the transmission.
@@
 We set this level from 400 to 1400 kbps to reflect different average bandwidth.
-All the experiments are conducted in Visual C++ 6.0 (with DSS as the software platform) and the bandwidth control is implemented by NetLimiter 3 \cite{Netlimiter}.
+All the experiments are conducted with DSS as the software platform and the bandwidth control implemented by NetLimiter 3 \cite{Netlimiter}.
 The baseline algorithm in the comparison refers to the packet delay feedback (PDF) algorithm in the original DSS.
@@
 \centering
-\subfloat[Bandwidth fluctuates around 600kbps: PSNR average and variance in the original system are 39.63 and 0.24, while in the proposed system are 39.69 and 0.16.]{
+\subfloat[Bandwidth fluctuates around 600kbps: PSNR average and variance in the original system are 39.63 and 0.24, while in the proposed system are 39.69 (increased by 0.06) and 0.16 (reduced by 0.08).]{
 \includegraphics[width=0.47\textwidth]{Fluctuation-PSNR1.png}
 \label{fig:Fluctuation-PSNR1}}\hfill
-\subfloat[Bandwidth fluctuates around 800kbps: PSNR average and variance in the original system are 40.15 and 0.48, while in the proposed system are 40.62 and 0.28.]{
+\subfloat[Bandwidth fluctuates around 800kbps: PSNR average and variance in the original system are 40.15 and 0.48, while in the proposed system are 40.62 (increased by 0.47) and 0.28 (reduced by 0.20).]{
 \includegraphics[width=0.47\textwidth]{Fluctuation-PSNR2.png}
@@
 \qquad
-\subfloat[Bandwidth fluctuates around 1000kbps: PSNR average and variance in the original system are 40.37 and 0.50, while in the proposed system are 40.74 and 0.28.]{
+\subfloat[Bandwidth fluctuates around 1000kbps: PSNR average and variance in the original system are 40.37 and 0.50, while in the proposed system are 40.74 (increased by 0.40) and 0.28 (reduced by 0.22).]{
 \includegraphics[width=0.47\textwidth]{Fluctuation-PSNR3.png}
 \label{fig:Fluctuation-PSNR3}}\hfill
-\subfloat[Bandwidth fluctuates around 1200kbps: PSNR average and variance in the original system are 40.48 and 0.63, while in the proposed system are 41.14 and 0.21.]{
+\subfloat[Bandwidth fluctuates around 1200kbps: PSNR average and variance in the original system are 40.48 and 0.63, while in the proposed system are 41.14 (increased by 0.66) and 0.21(reduced by 0.42).]{
 \includegraphics[width=0.47\textwidth]{Fluctuation-PSNR4.png}

### 2015-07-15 tmm.tex
final edit

@@
 There are generally two options to enable adaptive video streaming.
-The first option is called simulcast, where several independent bitstreams each with different video quality are stored at the server, and the client selects one of them according to currently available bandwidth.
+The first option is called simulcast, where several independent bitstreams, each with different video quality, are stored at the server, and the client selects one of them according to currently available bandwidth.
 Dynamic Adaptive Streaming over HTTP (DASH) \cite{DASH}, which is standardized by the Moving Picture Expert Group (MPEG), belongs to this option.
@@
 Besides, performance analysis \cite{SVCPerformance} shows that SVC also has much higher coding efficiency than simulcast, despite some computation and bitrate overhead comparing with single layer stream.
-Therefore, we choose to adopt SVC in our adaptive video streaming framework.
-While the work of this paper partly applies to the simulcast system, it will mainly focus on the context of SVC video streaming system.
+Therefore, to adopt SVC in the video streaming framework is a promising option and has attracted much attention \cite{Zhu2013}\cite{Dan2013}\cite{Yang2014}.
 
@@
 Optimal bitstream extraction algorithm aims to extract a sub-stream with best video quality, or minimal distortion, under the constraint of a given bitrate.
-Second, when the bandwidth does change, it's necessary to make decisions about whether and how to adjust the bitrate or video quality.
+Second, when the bandwidth changes with time, it's necessary to make decisions about whether and how to adjust the bitrate or video quality.
 This problem is called quality control, which means controlling the video quality (or the video bitrate, from the transmission point of view) to follow the change of the bandwidth.
@@
 \begin{itemize}
-\item First, a simple and effective linear error model (LEM) is proposed and verified, which can be used to accurately estimate the distortion caused by discarding any combination of packets from a SVC bitstream.
-\item Second, on the basis of the distortion estimation enabled by LEM, a greedy-like algorithm is designed to assign priority for each packet according to its R-D impact, thus enables optimized bitstream extraction.
+\item First, a simple and effective linear error model (LEM) is proposed and verified, which can be used to accurately estimate the distortion caused by discarding any combination of data packets from an SVC bitstream.
+\item Second, on the basis of the distortion estimation enabled by LEM, a greedy-like algorithm is designed to assign priority for each data packet according to its R-D impact, thus enables optimized bitstream extraction.
 \item Finally, for the quality control problem, a novel algorithm based on the Proportional-Integral-Derivative (PID) control concept is proposed to replace the native one in DSS, and achieves much lower quality fluctuation with higher quality level.
@@
 The data packets in the stream are divided into different layers.
-The temporal layer (T0$\sim$T3) reflects the reference or dependency relationship between the frames, shown by the arrows on the top pointing from the referenced frame to the frame which is dependent on it.
-The quality layer (Q0$\sim$Q2) indicates scalability of video quality within each frame, and packets in the higher quality layers (i.e., Q1 and Q2) are partially discarded to implement the extraction.
+The temporal layer (T0$\sim$T3) reflects the reference or dependency relationship between the frames.
+The arrows on the top point from the referenced frame to the frame which is dependent on it.
+The quality layer (Q0$\sim$Q2) indicates scalability of video quality within each frame.
+Data packets in the higher quality layers (i.e., Q1 and Q2) are partially discarded to implement the extraction.
 For example, the dash line demonstrates the extraction which will keep the data packets below the line and discard all the packets above it.
@@
 \ref{fig:Bitstream-Extraction}, we cannot include the Q2 packet of a frame without including the Q1 packet of the same frame.
-Second, the value of a packet is not obvious and certain, since a packet's contribution to video quality may depend on the other packets.
+Second, the value of a packet is not obvious and certain, since a packet's contribution to video quality may depend on other packets.
 Unless we discard a packet and calculate the distortion it causes for real, there is no way to exactly tell its value.
@@
 Quality control is the second problem we will address in this paper.
-The result of a quality control algorithm determines the suitable bitrate for current transmission, which is directly related to the change of video quality perceived by the user.
-It should be noted that, the bitstream extraction is performed under constraint of that bitrate determined by quality control, and even in non-SVC streaming systems (DASH, for example), quality control is an important part that requires careful design.
+The result of a quality control algorithm gives the suitable bitrate for current transmission, which is directly related to the change of video quality perceived by the user.
+In an SVC streaming system, the bitrate determined by the quality control algorithm is used as the constraint under which bitstream extraction is performed.
+Even in non-SVC streaming systems (DASH, for example), quality control is an important part that requires careful design.
 
@@
 
-The following of this paper will present our solutions for the above problems in detail.
+The following of this paper will present our solution for each of the problems in detail.
 The solutions then work together and serve as a solid foundation for a practical adaptive video streaming system.
@@
 
-Consider a video bitstream with 8-frame GOPs (Group of Pictures) shown in Fig.
+Consider a video bitstream with 8-frame GOPs shown in Fig.
 \ref{fig:GOP_Structure}.
@@
 packet 2, 4 and 20) should be allocated in two groups -- one for key frame packets of even number GOPs (packet 2 and 20), the other for those of odd number GOPs (packet 4).
-So the actual number of extraction and decoding for error vector acquisition is $(L_Q - 1) \cdot (L_T + 1)$, approximately the same with the Quality Layer information acquisition in JSVM \cite{Amonou07}.
+Therefore, the actual number of extraction and decoding for error vector acquisition is $(L_Q - 1) \cdot (L_T + 1)$, approximately the same with the Quality Layer information acquisition in JSVM \cite{Amonou07}.
 Since computation is mainly consumed with this decoding in the bitstream extraction algorithm, the computation complexity has no obvious promotion compared with JSVM.
@@
 We set this level from 400 to 1400 kbps to reflect different average bandwidth.
-All the experiments are conducted with DSS as the software platform and the bandwidth control implemented by NetLimiter 3 \cite{Netlimiter}.
+All the experiments are conducted with DSS as the software platform, and the bandwidth simulation is implemented with NetLimiter 3 \cite{Netlimiter}.
 The baseline algorithm in the comparison refers to the packet delay feedback (PDF) algorithm in the original DSS.
 
-First of all, we conduct some preliminary improvement experiments using only proportional part or integral part.
+First of all, we conduct some preliminary improvement experiments using only proportional part or integral part of the PID model.
 Since they are directly related to the short term error and long term error respectively, we call them Short Term Prediction (STP) and Long Term Prediction (LTP).
@@
 
-Since STP and LTP have their own limitations, we implement the PID-based quality control algorithm, which can both reduces quality variance and improves average quality level.
+Since STP and LTP have their own limitations, we implement the complete PID-based quality control algorithm, which can both reduce quality variance and improve average quality level.
 From the result shown in Fig.
@@
 It can be seen that, the proposed system performs better in that it has effectively avoided unnecessary quality drop (e.g., note the curve around time 450s in Fig.
-\ref{fig:Fluctuation-PSNR1} or around 250s in Fig.
+\ref{fig:Fluctuation-PSNR1} or 250s in Fig.
 \ref{fig:Fluctuation-PSNR3}) and been able to keep a relatively higher PSNR value (e.g., note the curve around time 400s in Fig.
-\ref{fig:Fluctuation-PSNR2} or around time 500s in Fig.
+\ref{fig:Fluctuation-PSNR2} or 500s in Fig.
 \ref{fig:Fluctuation-PSNR4}).
 The average and variance value of PSNR is also calculated and present in Fig.
-\ref{fig:fluctuation-psnr}, which showing clearly the proposed system's advantage.
+\ref{fig:fluctuation-psnr}, showing clearly the proposed system's advantage.
 For instance, in Fig.
@@
 
-In this paper, we propose an adaptive video streaming system with optimized bitstream extraction and PID-based quality control.
+In this paper, an adaptive video streaming system with optimized bitstream extraction and PID-based quality control is proposed.
 The bitstream extraction method includes a linear error model to estimate the distortion caused by discarding any combination of packets and a greedy algorithm to assign priority to each data packet.
 The priority values can then be stored in the bitstream and used for R-D optimized extraction.
-Experimental results show that the proposed method can achieve PSNR gain of up to 0.5dB compared to the JSVM QL extractor under the same bitrate constraint, also with the same computational complexity.
+Experimental results show that the method can achieve PSNR gain of up to 0.5dB compared to the JSVM QL extractor under the same bitrate constraint, also with the same computational complexity.
 The PID-based quality control algorithm has a flexible mechanism to determine the suitable quality level so that it gives an accurate and swift response to the bandwidth change.
 Comparing with the original algorithm in DSS, this algorithm has reduced quality fluctuation significantly to improve audience satisfaction.
-The SVC streaming system integrated with these two solutions performs well in automatically adapting to the user's bandwidth fluctuation, and is able to give the user a better watching experience.
+The proposed SVC adaptive streaming system integrated with these two solutions performs well in automatically adapting to the user's bandwidth fluctuation, and is able to give the user a better watching experience.
 
@@
 M. Wien , H. Schwarz and T. Oelbaum,  ``Performance Analysis of SVC'',  in {\em IEEE Trans. Circuits Syst. Video Technol.}, vol. 17, no. 9, pp.1194-1203. Sep. 2007.
+
+\bibitem{Zhu2013}
+Z.
+Zhu, S.
+Li, and X.
+Chen, ``Design QoS-aware multi-path provisioning strategies for efficient cloud-assisted SVC video streaming to heterogeneous clients'', in {\em IEEE Transactions on Multimedia}, vol.
+15, no.
+4, pp.758-768, 2013.
+
+\bibitem{Dan2013}
+G.
+Dan, O.
+Hadar, R.
+Ohayon, and N.
+Amram, ``Live video streaming with adaptive pre-processing by using scalable video coding'', in {\em Proceedings of IEEE International Conference on Consumer Electronics (ICCE)}, pp.588-589, 2013.
+
+\bibitem{Yang2014}
+E.
+Yang, Y.
+Ran, S.
+Chen, and J.
+Yang, ``A multicast architecture of SVC streaming over OpenFlow networks'', in {\em Proceedings of IEEE Global Communications Conference (GLOBECOM)}, pp.1323-1328, 2014.
 

### 2015-07-15 tmm.tex
modify authors information

@@
 \thanks{The authors are with the Institute of Computer Science and Technology, Peking University, Beijing%
-, 100080, China (e-mail: shengbin@pku.edu.cn; sunjun@pku.edu.cn; duanyizhou@pku.edu.cn; guozongming@pku.edu.cn).}}
+, 100080, China (Email: shengbin@pku.edu.cn, sunjun@pku.edu.cn, duanyizhou@pku.edu.cn, guozongming@pku.edu.cn; Phone: +86 1082529615; Fax: +86 1082529207).}}
 

### 2015-07-16 tmm.tex
edit a word

--- 2015-07-13 tmm.tex
@@
 \author{Shengbin~Meng,~Jun~Sun,~Yizhou~Duan~and~Zongming~Guo,~\em{Member,~IEEE} % <-this % stops a space
-\thanks{Manuscript received July 15, 2015.}
+\thanks{Manuscript received May 20, 2015.}
 \thanks{The authors are with the Institute of Computer Science and Technology, Peking University, Beijing%
@@
 We set this level from 400 to 1400 kbps to reflect different average bandwidth.
-All the experiments are conducted with DSS as the software platform and the bandwidth control implemented by NetLimiter 3 \cite{Netlimiter}.
+All the experiments are conducted in Visual C++ 6.0 (with DSS as the software platform) and the bandwidth control is implemented by NetLimiter 3 \cite{Netlimiter}.
 The baseline algorithm in the comparison refers to the packet delay feedback (PDF) algorithm in the original DSS.
@@
 \centering
-\subfloat[Bandwidth fluctuates around 600kbps: PSNR average and variance in the original system are 39.63 and 0.24, while in the proposed system are 39.69 (increased by 0.06) and 0.16 (reduced by 0.08).]{
+\subfloat[Bandwidth fluctuates around 600kbps: PSNR average and variance in the original system are 39.63 and 0.24, while in the proposed system are 39.69 and 0.16.]{
 \includegraphics[width=0.47\textwidth]{Fluctuation-PSNR1.png}
 \label{fig:Fluctuation-PSNR1}}\hfill
-\subfloat[Bandwidth fluctuates around 800kbps: PSNR average and variance in the original system are 40.15 and 0.48, while in the proposed system are 40.62 (increased by 0.47) and 0.28 (reduced by 0.20).]{
+\subfloat[Bandwidth fluctuates around 800kbps: PSNR average and variance in the original system are 40.15 and 0.48, while in the proposed system are 40.62 and 0.28.]{
 \includegraphics[width=0.47\textwidth]{Fluctuation-PSNR2.png}
@@
 \qquad
-\subfloat[Bandwidth fluctuates around 1000kbps: PSNR average and variance in the original system are 40.37 and 0.50, while in the proposed system are 40.74 (increased by 0.40) and 0.28 (reduced by 0.22).]{
+\subfloat[Bandwidth fluctuates around 1000kbps: PSNR average and variance in the original system are 40.37 and 0.50, while in the proposed system are 40.74 and 0.28.]{
 \includegraphics[width=0.47\textwidth]{Fluctuation-PSNR3.png}
 \label{fig:Fluctuation-PSNR3}}\hfill
-\subfloat[Bandwidth fluctuates around 1200kbps: PSNR average and variance in the original system are 40.48 and 0.63, while in the proposed system are 41.14 (increased by 0.66) and 0.21(reduced by 0.42).]{
+\subfloat[Bandwidth fluctuates around 1200kbps: PSNR average and variance in the original system are 40.48 and 0.63, while in the proposed system are 41.14 and 0.21.]{
 \includegraphics[width=0.47\textwidth]{Fluctuation-PSNR4.png}

### 2015-07-16 tmm.tex
add the corresponding author note

--- 2015-07-15 tmm.tex
@@
 \thanks{The authors are with the Institute of Computer Science and Technology, Peking University, Beijing%
-, 100080, China (e-mail: shengbin@pku.edu.cn; sunjun@pku.edu.cn; duanyizhou@pku.edu.cn; guozongming@pku.edu.cn).}}
+, 100080, China (Email: shengbin@pku.edu.cn, sunjun@pku.edu.cn, duanyizhou@pku.edu.cn, guozongming@pku.edu.cn; Phone: +86 1082529615; Fax: +86 1082529207). Jun Sun is the corresponding author.}}
 
@@
 In (\ref{eq:long-actual}) and (\ref{eq:long-check}), $T_l$ stands for the last quality change time.
-Theoretically, the integral part should be recorded and calculated since the system start.
+Theoretically, the integral part should be recorded and calculated since the system starts.
 In practice, however, bandwidth may vary significantly during the transmission.

### 2015-07-25 tmm.tex
rewrite the author line
add more citations to TMM papers

@@
 %
-\author{Shengbin~Meng,~Jun~Sun,~Yizhou~Duan~and~Zongming~Guo,~\em{Member,~IEEE} % <-this % stops a space
+\author{Shengbin~Meng, Jun~Sun, {\em Member, IEEE}, Yizhou~Duan and Zongming~Guo, {\em Member, IEEE} % <-this % stops a space
 \thanks{Manuscript received July 15, 2015.}
@@
 \IEEEPARstart{V}{ideo} streaming applications are becoming more and more popular on the Internet.
-Examples of the most common usage scenarios include VOD (Video On Demand), live broadcasting, video-based online education, etc.
+Examples of the most common usage scenarios include online video-on-demand (VoD), live broadcasting, video chat, video-based online education, etc.
 In these applications, video data is constantly delivered to different clients over various transmission channels, and the client media player can begin playing the video before the entire file has been transmitted.
-Among other features, video streaming makes it easy to watch video anywhere and anytime, and is an increasingly important way for people to consume video content.
-
-One of the biggest challenge for video streaming is the variety of users' network environment.
+Among other features, video streaming makes it easy to watch video anywhere and anytime, which represents the concept of Ubiquitous Multimedia Access (UMA), a very common topic within the multimedia community during the past few years \cite{Gualdi08}.
+And due to its convenience, video streaming has also attracted a large number of users and become an increasingly important way for people to consume video content \cite{Chen13}.
+
+Although efforts on the new software defined networking (SDN) are made to facilitate efficient video streaming \cite{Egilmez13}, currently traditional best-effort networks still dominate, and the variety of users' network environment remains to be one of the biggest challenges for video streaming.
 A user might use different types of network (Ethernet, Wi-Fi, Cellular, etc.) and might also switch from one type to another (e.g., from Wi-Fi to cellular network) on going.
@@
 
-The advantage of simulcast systems is that they need little modification of existing infrastructure and therefore are easy to deploy.
+The advantage of simulcast systems like DASH is that they need little modification of existing infrastructure (servers, proxies, caches, firewall compatibility, etc.) and therefore are easy to deploy \cite{Bouten14}.
 Most commercial video websites, YouTube \cite{YouTube} for instance, use this option to enable quality adaptation.
@@
 Besides, performance analysis \cite{SVCPerformance} shows that SVC also has much higher coding efficiency than simulcast, despite some computation and bitrate overhead comparing with single layer stream.
-Therefore, to adopt SVC in the video streaming framework is a promising option and has attracted much attention \cite{Zhu2013}\cite{Dan2013}\cite{Yang2014}.
-
-In the SVC adaptive video streaming system, there are two key problems that need to be addressed well.
+Therefore, to adopt SVC in the video streaming framework is a promising option and has attracted much attention in the study \cite{Chuah12}-\cite{Cicalò14}.
+
+While these studies mostly focus on Quality of Service (QoS) optimization and resource allocation for specific networks, there are two key problems in the SVC adaptive video streaming system that need to be primarily addressed.
 First, as the prerequisite of the adaption to bandwidth change, the whole bitstream needs to be extracted so that sub-streams with various bitrates can be obtained.
@@
 
-In (\ref{eq:ut}), $K_p$, $K_i$, and $K_d$ indicate the tuning parameters for proportional, integral and derivative parts respectively, and $E_p^t$, $E_i^t$, $E_d^t$ stand for the corresponding observed value for each part, which are defined in (\ref{eq:ep}) - (\ref{eq:long-check}); the controller output $u_t$ is utilized to calculate an appropriate data rate and further to determine which quality level we should transmit (see Algorithm \ref{algo:control} for more details).
+In (\ref{eq:ut}), $K_p$, $K_i$, and $K_d$ indicate the tuning parameters for proportional, integral and derivative parts respectively, and $E_p^t$, $E_i^t$, $E_d^t$ stand for the corresponding observed value for each part, which are defined in (\ref{eq:ep})-(\ref{eq:long-check}); the controller output $u_t$ is utilized to calculate an appropriate data rate and further to determine which quality level we should transmit (see Algorithm \ref{algo:control} for more details).
 
@@
 
+\bibitem{Gualdi08}
+G. Gualdi, A. Prati, and R. Cucchiara, ``Video Streaming for Mobile Video Surveillance'', in {\em IEEE Transactions on Multimedia}, vol. 10, no. 6, pp.1142-1154, 2008.
+
+\bibitem{Chen13}
+Y.
+Chen, B.
+Zhang, Y.
+Liu, and W.
+Zhu, ``Measurement and Modeling of Video Watching Time in a Large-Scale Internet Video-on-Demand System'', in {\em IEEE Transactions on Multimedia}, vol.
+15, no.
+8, pp.2087-2098, 2013.
+
+\bibitem{Egilmez13}
+H.
+E.
+Egilmez, S.
+Civanlar, and A.
+M.
+Tekalp, ``An Optimization Framework for QoS-Enabled Adaptive Video Streaming Over OpenFlow Networks'', in {\em IEEE Transactions on Multimedia}, vol.
+15, no.
+3, pp.710-715, 2013.
+
 \bibitem{DASH}
@@
 \bibitem{SVCOverview}
-H.~Schwarz, D.~Marpe and T.~Wiegand, ``Overview of the scalable video coding extension of the H.264/AVC standard'', in {\em IEEE Trans.
+H.~Schwarz, D.~Marpe, and T.~Wiegand, ``Overview of the scalable video coding extension of the H.264/AVC standard'', in {\em IEEE Trans.
 Circuits.
@@
 
+\bibitem{Bouten14}
+N.
+Bouten, S.
+Latré, J.
+Famaey, W.
+V.
+Leekwijck, and F.
+D.
+Turck, ``In-Network Quality Optimization for Adaptive Video Streaming Services'', in {\em IEEE Transactions on Multimedia}, vol.
+16, no.
+8, pp.2281-2293, 2014.
+
 \bibitem{YouTube}
@@
 
-\bibitem{Zhu2013}
+\bibitem{Chuah12}
+S.
+Chuah, Z.
+Chen, and Y.
+Tan, ``Energy-Efficient Resource Allocation and Scheduling for Multicast of Scalable Video Over Wireless Networks'', in {\em IEEE Transactions on Multimedia}, vol.
+14, no.
+4, pp.1324-1336, 2012.
+
+\bibitem{Zhu13}
 Z.
@@
 
-\bibitem{Dan2013}
+\bibitem{Dan13}
 G.
@@
 
-\bibitem{Yang2014}
+\bibitem{Yang14}
 E.
@@
 Yang, ``A multicast architecture of SVC streaming over OpenFlow networks'', in {\em Proceedings of IEEE Global Communications Conference (GLOBECOM)}, pp.1323-1328, 2014.
+
+\bibitem{Cicalò14}
+S.
+Cicalò, and V.
+Tralli, ``Distortion-Fair Cross-Layer Resource Allocation for Scalable Video Transmission in OFDMA Wireless Networks'', in {\em IEEE Transactions on Multimedia}, vol.
+16, no.
+3, pp.848-863, 2014.
 
@@
 
-%\bibitem{Meng14}
-%Shengbin Meng, Jun Sun, Yizhou Duan, Zongming Guo, ``An Efficient Method For No-Reference H.264/SVC Bitstream Extraction'', {\em IEEE International Conference on Acoustics, Speech, and Signal Processing}, Florence, Italy, May, 2014.
-
-%\bibitem{Meng14-PID}
-%Shengbin Meng, Jun Sun, Yilei Wang, Zongming Guo, ``A PID-based Quality Control Algorithm for SVC Video Streaming'', {\em IEEE International Conference on Communications}, Sydney, Australia, June, 2014.
-
 \bibitem{H264Overview}
@@
 Circuits Syst.
-Video Technol.}, vol.~22, no.~12, pp.~1648–1667, Dec.
+Video Technol.}, vol.~22, no.~12, pp.~1648â1667, Dec.
 2012.

### 2015-11-12 tmm.tex
Begin to prepare reversion R1

@@
 \author{Shengbin~Meng, Jun~Sun, {\em Member, IEEE}, Yizhou~Duan and Zongming~Guo, {\em Member, IEEE} % <-this % stops a space
-\thanks{Manuscript received July 15, 2015.}
+\thanks{Manuscript received July 15, 2015; revised December 3, 2015.}
 \thanks{The authors are with the Institute of Computer Science and Technology, Peking University, Beijing%
-, 100080, China (Email: shengbin@pku.edu.cn, sunjun@pku.edu.cn, duanyizhou@pku.edu.cn, guozongming@pku.edu.cn; Phone: +86 1082529615; Fax: +86 1082529207). Jun Sun is the corresponding author.}}
+, 100080, China (Email: mengshengbin@pku.edu.cn, sunjun@pku.edu.cn, duanyizhou@pku.edu.cn, guozongming@pku.edu.cn; Phone: +86 1082529615; Fax: +86 1082529207). Jun Sun is the corresponding author.}}
 

### 2015-11-18 tmm.tex
Fix grammar errors and notation flaws

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Problem Analysis and Related Works}
+\section{Problem Analysis and Related Work}
 \label{sec:analysis}
@@
 As we can see, in its nature SVC bitstream extraction is a combinatorial optimization problem.
-There are many combinations of packets to be discarded, and we want to choose a combination that maximums the video quality of the extracted sub-stream, under the constraint of a given bitrate.
-More specifically, this problem in the form of ``0-1 Knapsack Problem" \cite{Knapsack}.
+There are many combinations of packets to be discarded, and we want to choose a combination that maximizes the video quality of the extracted sub-stream, under the constraint of a given bitrate.
+More specifically, this problem fits in the form of ``0-1 Knapsack Problem" \cite{Knapsack}.
 Each data packet can be treated as an object with certain weight (the packet's size) and value (its contribution to the video quality).
@@
 
-The state-of-art solutions to avoid video pause in client media player mainly focus on how to select and schedule the video packets.
+The state-of-the-art solutions to avoid video pause in client media player mainly focus on how to select and schedule the video packets.
 In \cite{Gao06}, K.
@@
 \label{eq:linear}
-s = {\rm\bf M}s + {\rm\bf T}c + p \: ,
+s = {\rm\bf M} \cdot s + {\rm\bf T} \cdot c + p \: ,
 \end{equation}
 It means, the reconstructed samples of a GOP (Group of Pictures), denoted by $s$, can be viewed as a linear combination of previously reconstructed samples in the GOP, the residual samples, and a static predictor.
-In (\ref{eq:linear}), $c$ refers to the transform coefficient values and $p$ is a static predictor; $M$ and $T$ are square matrices such that the product $M$s gives the MCP (Motion Compensated Prediction) signal and $Tc$ gives the residual values.
-The actual values of $M$ depend on the selected macroblock types, reference indices and motion vectors, whereas the actual values of $T$ depend on the chosen QP (Quantization Parameter) values.
+In (\ref{eq:linear}), $c$ refers to the transform coefficient values and $p$ is a static predictor; ${\rm\bf M}$ and ${\rm\bf T}$ are square matrices such that the product ${\rm\bf M} \cdot s$ gives the MCP (Motion Compensated Prediction) signal and ${\rm\bf T} \cdot c$ gives the residual values.
+The actual values of ${\rm\bf M}$ depend on the selected macroblock types, reference indices and motion vectors, whereas the actual values of ${\rm\bf T}$ depend on the chosen QP (Quantization Parameter) values.
 
@@
 \label{eq:base0}
-s_{B} = {\rm\bf M}s_{B} + {\rm\bf T}_{B}c_{B} + p \: ,
+s_{B} = {\rm\bf M} \cdot s_{B} + {\rm\bf T}_{B} \cdot c_{B} + p \: ,
 \end{equation}
@@
 \label{eq:subset1}
-s_{I_1} = {\rm\bf M}s_{I_1} + {\rm\bf T}_{B} c_{B} + \Big( \sum_{i \in I_1}{\rm\bf T}_i c_i \Big) + p \: ,
+s_{I_1} = {\rm\bf M} \cdot s_{I_1} + {\rm\bf T}_{B} \cdot c_{B} + \Big( \sum_{i \in I_1}{\rm\bf T}_i \cdot c_i \Big) + p \: ,
 \end{equation}
@@
 ${\rm\bf T_i}$ is the transform matrix depending on the QP value of $i$.
-${\rm\bf T}_i c_i$ gives the residual sample values decoded from $i$.
+${\rm\bf T}_i \cdot c_i$ gives the residual sample values decoded from $i$.
 
@@
 \label{eq:subset2}
-s_{I_2} = {\rm\bf M}s_{I_2} + {\rm\bf T}_{B} c_{B} + \Big( \sum_{i \in I_2}{\rm\bf T}_i c_i \Big) + p \: .
+s_{I_2} = {\rm\bf M} \cdot s_{I_2} + {\rm\bf T}_{B} \cdot c_{B} + \Big( \sum_{i \in I_2}{\rm\bf T}_i \cdot c_i \Big) + p \: .
 \end{equation}
@@
 \label{eq:minus1}
-(s_{I_2} - s_{I_1}) = {\rm\bf M}(s_{I_2} - s_{I_1}) + \Big( \sum_{i \in I_2}{\rm\bf T}_i c_i - \sum_{i \in I_1}{\rm\bf T}_i c_i \Big) \: ,
+(s_{I_2} - s_{I_1}) = {\rm\bf M} \cdot (s_{I_2} - s_{I_1}) + \Big( \sum_{i \in I_2}{\rm\bf T}_i \cdot c_i - \sum_{i \in I_1}{\rm\bf T}_i \cdot c_i \Big) \: ,
 \end{equation}
@@
 \label{eq:minus2}
-\Rightarrow e = s_{I_2} - s_{I_1} = ({\rm\bf I - M})^{-1} \Big( \sum_{i \in I_2}{\rm\bf T}_i c_i - \sum_{i \in I_1}{\rm\bf T}_i c_i \Big) \: .
+\Rightarrow e = s_{I_2} - s_{I_1} = ({\rm\bf I - M})^{-1} \cdot \Big( \sum_{i \in I_2}{\rm\bf T}_i \cdot c_i - \sum_{i \in I_1}{\rm\bf T}_i \cdot c_i \Big) \: .
 \end{equation}
@@
 \label{eq:error_j}
-e_j = ({\rm\bf I - M})^{-1} {\rm\bf T}_j c_j \: .
+e_j = ({\rm\bf I - M})^{-1} \cdot {\rm\bf T}_j \cdot c_j \: .
 \end{equation}
@@
 
-Note that in equations (\ref{eq:base0})-(\ref{eq:subset2}) the value of M and p remain the same, since in the case of quality scalability the enhancement packets are generated only by manipulating the transform coefficients, and not interfered with the motion compensation and static prediction.
+Note that in equations (\ref{eq:base0})-(\ref{eq:subset2}) the value of ${\rm\bf M}$ and $p$ remain the same, since in the case of quality scalability the enhancement packets are generated only by manipulating the transform coefficients, and not interfered with the motion compensation and static prediction.
 This argument no longer holds for the other scalable dimensions (e.g., spatial scalability), so LEM does not simply apply for those cases.
-Therefor, only quality scalable videos are used in our system, and further research for other scalable dimensions can be our future work.
+Therefore, only quality scalable videos are used in our system, and further research for other scalable dimensions can be our future work.
 
@@
 \ref{fig:GOP_Structure}, $L_Q = 3$ and $L_T = 4$, so the theoretical extraction-and-decoding number is $(3 - 1) \times 4 = 8$.
-However, we have to do the same manipulation for $L_Q - 1 = 2$ more times, to dissociate the distortion impact of ``key frame''\cite{H264Overview} (e.g.
+However, we have to do the same manipulation for $L_Q - 1 = 2$ more times, to dissociate the distortion impact of ``key frame'' \cite{H264Overview} (e.g.
 frame 0, 8, 16, etc.) packets.
@@
 \label{eq:pid-output}
-u(t) = {K_p}e(t) + {K_i}\int_0^t {e(\tau )d\tau }  + {K_d}\frac{d}{{dt}}e(t) \: ,
+u(t) = {K_p} \cdot e(t) + {K_i} \cdot \int_0^t {e(\tau )d\tau }  + {K_d} \cdot \frac{d}{{dt}}e(t) \: ,
 \end{equation}
@@
 \label{eq:ut}
-{u_t} = {K_p}E_p^t + {K_i}E_i^t + {K_d}E_d^t ,
+{u_t} = {K_p} \cdot E_p^t + {K_i} \cdot E_i^t + {K_d} \cdot E_d^t ,
 \end{equation}
@@
     \STATE calculate $E_p^t$, $E_i^t$, $E_d^t$ according to Eq. (\ref{eq:ep}) - (\ref{eq:ed})
-    \STATE output = ${K_p}E_p^t + {K_i}E_i^t + {K_d}E_d^t$
+    \STATE output = ${K_p} \cdot E_p^t + {K_i} \cdot E_i^t + {K_d} \cdot E_d^t$
     \STATE new\_bitrate = output * curr\_bitrate
@@
 This method is performed by setting integral and derivative parameters to zero and then tuning $K_p$ to a value $K_u$ until output begins to oscillate with constant amplitude.
-Assuming the oscillation period is $T_u$, we set $K_p = 0.6K_u$, $K_i = 2K_u/T_u$, and $K_d = K_uT_u/8$.
+Assuming the oscillation period is $T_u$, we set $K_p = 0.6K_u$, $K_i = 2K_u/T_u$, and $K_d = K_u \cdot T_u/8$.
 $K_p$, $K_i$, and $K_d$ are then normalized to get the final parameters.

### 2015-11-18 tmm.tex
Add citations

@@
 Among other features, video streaming makes it easy to watch video anywhere and anytime, which represents the concept of Ubiquitous Multimedia Access (UMA), a very common topic within the multimedia community during the past few years \cite{Gualdi08}.
-And due to its convenience, video streaming has also attracted a large number of users and become an increasingly important way for people to consume video content \cite{Chen13}.
-
-Although efforts on the new software defined networking (SDN) are made to facilitate efficient video streaming \cite{Egilmez13}, currently traditional best-effort networks still dominate, and the variety of users' network environment remains to be one of the biggest challenges for video streaming.
+Due to its convenience, video streaming also attracts a large number of users and becomes an increasingly important way for people to consume video content \cite{Chen13}.
+
+In video streaming, the network condition significantly influences the user's watching experience.
+To provide better streaming service, some researchers choose to adopt the new software defined networking (SDN) architecture \cite{Egilmez14}.
+Based on a successful SDN paradigm OpenFlow, noticeable results are achieved, e.g., a solution for improving network throughput in hybrid network \cite{Li14} and a demonstration of adaptive video manycast \cite{Xue15}.
+Although these studies offer a promising way to optimize network conditions, currently traditional best-effort networks still dominate, and the variety of users' network environment remains to be one of the biggest challenges for video streaming.
 A user might use different types of network (Ethernet, Wi-Fi, Cellular, etc.) and might also switch from one type to another (e.g., from Wi-Fi to cellular network) on going.
@@
 Besides, performance analysis \cite{SVCPerformance} shows that SVC also has much higher coding efficiency than simulcast, despite some computation and bitrate overhead comparing with single layer stream.
-Therefore, to adopt SVC in the video streaming framework is a promising option and has attracted much attention in the study \cite{Chuah12}-\cite{Cicalò14}.
+Therefore, to adopt SVC in the video streaming framework is a promising option and has attracted much attention in the study \cite{Chuah12}-\cite{Cicalo14}.
 
@@
 \bibitem{Gualdi08}
-G. Gualdi, A. Prati, and R. Cucchiara, ``Video Streaming for Mobile Video Surveillance'', in {\em IEEE Transactions on Multimedia}, vol. 10, no. 6, pp.1142-1154, 2008.
+G. Gualdi, A. Prati, and R. Cucchiara, ``Video Streaming for Mobile Video Surveillance'', in {\em IEEE Transactions on Multimedia}, vol. 10, no. 6, pp. 1142-1154, 2008.
 
@@
 15, no.
-8, pp.2087-2098, 2013.
-
-\bibitem{Egilmez13}
+8, pp.
+2087-2098, 2013.
+
+\bibitem{Egilmez14}
 H.
 E.
-Egilmez, S.
-Civanlar, and A.
+Egilmez and A.
 M.
-Tekalp, ``An Optimization Framework for QoS-Enabled Adaptive Video Streaming Over OpenFlow Networks'', in {\em IEEE Transactions on Multimedia}, vol.
-15, no.
-3, pp.710-715, 2013.
+Tekalp, ``Distributed QoS architectures for multimedia streaming over software defined networks'', in {\em IEEE Transactions on Multimedia}, vol.
+16, no.
+6, pp.
+1597-1609, 2014.
+
+\bibitem{Li14}
+S. Li et al., ``Flexible Traffic Engineering (F-TE): When OpenFlow Meets Multi-Protocol IP-Forwarding'', in {\em IEEE Communication Letters}, vol. 18, pp. 1699-1702, Oct. 2014.
+
+\bibitem{Xue15}
+N. Xue et al., ``Demonstration of OpenFlow-Controlled Network Orchestration for Adaptive SVC Video Manycast'', in {\em IEEE Transactions on Multimedia}, vol. 17, pp. 1617-1629, Sept. 2015.
 
@@
 17, no.
-9, pp.~1103-1120, Sept.
-2007.
+9, pp.
+1103-1120, 2007.
 
@@
 16, no.
-8, pp.2281-2293, 2014.
+8, pp.
+2281-2293, 2014.
 
@@
 \bibitem{SVCPerformance}
-M. Wien , H. Schwarz and T. Oelbaum,  ``Performance Analysis of SVC'',  in {\em IEEE Trans. Circuits Syst. Video Technol.}, vol. 17, no. 9, pp.1194-1203. Sep. 2007.
+M. Wien , H. Schwarz and T. Oelbaum,  ``Performance Analysis of SVC'',  in {\em IEEE Trans. Circuits Syst. Video Technol.}, vol. 17, no. 9, pp. 1194-1203, 2007.
 
@@
 14, no.
-4, pp.1324-1336, 2012.
+4, pp.
+1324-1336, 2012.
 
@@
 15, no.
-4, pp.758-768, 2013.
+4, pp.
+758-768, 2013.
 
@@
 Ohayon, and N.
-Amram, ``Live video streaming with adaptive pre-processing by using scalable video coding'', in {\em Proceedings of IEEE International Conference on Consumer Electronics (ICCE)}, pp.588-589, 2013.
+Amram, ``Live video streaming with adaptive pre-processing by using scalable video coding'', in {\em Proceedings of IEEE International Conference on Consumer Electronics (ICCE)}, pp.
+588-589, 2013.
 
@@
 Chen, and J.
-Yang, ``A multicast architecture of SVC streaming over OpenFlow networks'', in {\em Proceedings of IEEE Global Communications Conference (GLOBECOM)}, pp.1323-1328, 2014.
-
-\bibitem{Cicalò14}
+Yang, ``A multicast architecture of SVC streaming over OpenFlow networks'', in {\em Proceedings of IEEE Global Communications Conference (GLOBECOM)}, pp.
+1323-1328, 2014.
+
+\bibitem{Cicalo14}
 S.
-Cicalò, and V.
+Cicalo, and V.
 Tralli, ``Distortion-Fair Cross-Layer Resource Allocation for Scalable Video Transmission in OFDMA Wireless Networks'', in {\em IEEE Transactions on Multimedia}, vol.
 16, no.
-3, pp.848-863, 2014.
+3, pp.
+848-863, 2014.
 
@@
 Circuits Syst.
-Video Technol.}, vol.~17, no.~9, pp.~1186--1193, Sep.
-2007.
+Video Technol.}, vol.
+17, no.
+9, pp.
+1186-1193, 2007.
 
@@
 Circuits Syst.
-Video Technol.}, vol.~19, no.~3, pp.~323--336, Mar.
+Video Technol.}, vol.~19, no.~3, pp.~323-336, Mar.
 2009.
@@
 \bibitem{Maani09}
-E.~Maani, A.~K.
-Katsaggelos, ``Optimized Bit Extraction Using Distortion Modeling in the Scalable Extension of H.264/AVC'' in {\em IEEE Trans.
-Image Processing}, vol.~18, no.~9, pp.~2022--2029, Sep.
-2009.
+E.~Maani, A.~K. Katsaggelos, ``Optimized Bit Extraction Using Distortion Modeling in the Scalable Extension of H.264/AVC'' in {\em IEEE Trans. Image Processing}, vol.~18, no.~9, pp.~2022-2029, 2009.
 
@@
 K.~Yang, S.~Wan, Y.~Gong, and Y.~Feng.
-``A fast algorithm of bitstream extraction using distortion prediction based on simulated annealing'' In {\em Journal of Visual Communication and Image Representation}, no.7, 752-759, 2013.
+``A fast algorithm of bitstream extraction using distortion prediction based on simulated annealing'' In {\em Journal of Visual Communication and Image Representation}, no.7, pp.
+752-759, 2013.
 
 \bibitem{Zhang12}
-W.~Zhang, J.~Sun, J.~Liu and Z.~Guo, ``Optimized bit extraction of SVC exploiting linear error model,'' {\em Proceedings of IEEE International Symposium on Circuits and Systems}, pp.~1887--1890, Seoul, Korea, May 2012.
+W.~Zhang, J.~Sun, J.~Liu and Z.~Guo, ``Optimized bit extraction of SVC exploiting linear error model,'' {\em Proceedings of IEEE International Symposium on Circuits and Systems}, pp.~1887-1890, Seoul, Korea, May 2012.
 
@@
 Circuits Syst.
-Video Technol.}, vol.~22, no.~12, pp.~1648â1667, Dec.
+Video Technol.}, vol.~22, no.~12, pp.~1648-1667, Dec.
 2012.

### 2015-11-25 tmm.tex
Change encoding to UTF-8
Add pseudo code for bitstream extraction algorithm

@@
 \centering
-\includegraphics[width = 0.9\linewidth]{Bitstream-Extraction.jpg}
+\includegraphics[width = 1.0\linewidth]{Bitstream-Extraction.jpg}
 \caption{Bitstream extraction of SVC \label{fig:Bitstream-Extraction}}
@@
 \centering
-\includegraphics[width = 0.9\linewidth]{GOPStructure.jpg}
+\includegraphics[width = 1.0\linewidth]{GOPStructure.jpg}
 \caption{Group of pictures (GOP) in SVC \label{fig:GOP_Structure}}
@@
 \centering
-\includegraphics[width = 0.9\linewidth]{ModelVerification.png}
+\includegraphics[width = 1.0\linewidth]{ModelVerification.png}
 \caption{Comparison of actual and estimated distortion for sequence {\em Foreman} \label{fig:model_verification}}
@@
 During this process, the discarding order of a packet is regarded as its priority and recorded.
-Then the packets' priority values can be stored in the bitstream (either in the priority id field of the NALU header or in separate SEI messages) for real extraction in the future.
+Then the packets' priority values can be stored in the bitstream (either in the priority identifier field of the NALU header or in supplementary enhancement information messages) for real extraction in the future.
 
@@
 \end{equation}
-	where $I_{top}$ stands for the top layer packets, those currently able to be discarded. The RD impact of a packet is calculated based on (\ref{eq:rd_impact}), as follows: 
+where $I_{top}$ stands for the top-layer packets, those currently able to be discarded. The RD impact of a packet is calculated based on (\ref{eq:rd_impact}), as follows: 
 \begin{equation}
@@
 
-For long video sequences, an optimization window is usually needed, and the priority assignment and bitstream extraction is conducted independently in each window.
-The computational complexity of this priority assignment algorithm is $O(K^2)$, with $K$ being the number of frames involved in the priority assignment process, \textit{i.e.}, the size of the optimization window.
-Note that this computation complexity is negligible compared with the decoding process needed in the error vector acquisition.
+For long video sequences, an optimization window containing a certain number of frames is usually needed, and the priority assignment and bitstream extraction is conducted independently in each window.
+Suppose the size of the optimization window is $K$, i.e., there are $K$ frames involved in the above priority assignment process, and each frame contains $L_Q$ quality layers (one base layer and $L_Q-1$ enhancement layers).
+Then the number of top layer packets in step 2) of the process is $K$, and the total number of packets that can be discarded is $K \cdot (L_Q-1)$.
+Given that, the priority assignment process in each optimization window can be more specifically described in Algorithm \ref{algo:greedy}.
+It is easy to see that the computational complexity of this priority assignment algorithm is $O(K^2)$.
+Note that this computational complexity is negligible compared with the decoding process needed in the error vector acquisition.
+
+\begin{algorithm}
+\caption{Greedy-like bitstream extraction algorithm}
+\label{algo:greedy}
+\begin{algorithmic}
+    \STATE Set $e_{seq}$ to $e_{full}$, and set $p$ to 0.
+    \WHILE{$p < K \cdot (L_Q - 1)$}
+	    \FOR{$K$ top layer packets}
+		    \STATE Find the packet $m$ which has least RD impact
+		\ENDFOR
+		\STATE Set the priority value of packet $m$ to $p$
+		\STATE Remove $m$ from the sequence
+		\STATE Set $e_{seq}$ to $e_{seq} + e_m$, and set $p$ to $p+1$
+    \ENDWHILE
+\end{algorithmic}
+\end{algorithm}
+
+A larger optimization window means each time we have more packets to compare and determine their priorities.
+Therefore, choosing a larger $K$ will result in more optimized extraction.
+However, doing this will also increase the computational complexity as well as the memory used to store the error vectors.
+Besides, if the 6-bit priority identifier field of the NALU header is used to store the priority values, only a range of 0$\sim$63 is supported, which also limits the value of $K$.
 
@@
 Bouten, S.
-Latré, J.
+Latre, J.
 Famaey, W.

### 2015-11-28 tmm.tex
Change the colors in Fig.6 and Fig.7; also change some text

@@
 \IEEEPARstart{V}{ideo} streaming applications are becoming more and more popular on the Internet.
-Examples of the most common usage scenarios include online video-on-demand (VoD), live broadcasting, video chat, video-based online education, etc.
+Examples of the most common usage scenarios include online video-on-demand (VoD), live broadcasting, video-based online education, etc.
 In these applications, video data is constantly delivered to different clients over various transmission channels, and the client media player can begin playing the video before the entire file has been transmitted.
@@
 Although these studies offer a promising way to optimize network conditions, currently traditional best-effort networks still dominate, and the variety of users' network environment remains to be one of the biggest challenges for video streaming.
-A user might use different types of network (Ethernet, Wi-Fi, Cellular, etc.) and might also switch from one type to another (e.g., from Wi-Fi to cellular network) on going.
+A user might use different types of network (Ethernet, Wi-Fi, Cellular, etc.) and might also switch from one type to another on going (e.g., from Wi-Fi to cellular network).
 Even in the same network, the user's bandwidth will change from time to time, influenced by the overall traffic.
-Within such an environment, bandwidth fluctuation is inevitable.
-If the video is streamed at a constant bitrate, it would be difficult or impossible for the user to get best watching experience.
+Within such an environment, bandwidth fluctuation is inevitable and it would be difficult or impossible for the user to get best watching experience if the video is streamed at a constant bitrate.
 To cope with this challenge, the video streaming system should be able to automatically adjust the video's bitrate or quality according to the bandwidth change.
@@
 
-The advantage of simulcast systems like DASH is that they need little modification of existing infrastructure (servers, proxies, caches, firewall compatibility, etc.) and therefore are easy to deploy \cite{Bouten14}.
-Most commercial video websites, YouTube \cite{YouTube} for instance, use this option to enable quality adaptation.
-However, the adaptive range and granularity that simulcast provides is limited to the number of streams (YouTube videos have 5 quality levels at most: 240p, 360p, 480p, 720p and 1080p), and the processing and storage of multiple video streams significantly increase time and space cost.
-SVC streaming systems, on the contrary, do not have above shortcomings.
-Since an SVC video bitstream can be extracted at the granularity of one NALU (a very small partition of data), it is able to provide seamless scalability and quality adaptation.
-Besides, performance analysis \cite{SVCPerformance} shows that SVC also has much higher coding efficiency than simulcast, despite some computation and bitrate overhead comparing with single layer stream.
-Therefore, to adopt SVC in the video streaming framework is a promising option and has attracted much attention in the study \cite{Chuah12}-\cite{Cicalo14}.
-
-While these studies mostly focus on Quality of Service (QoS) optimization and resource allocation for specific networks, there are two key problems in the SVC adaptive video streaming system that need to be primarily addressed.
+Due to the easy deployment of simulcast systems \cite{Bouten14}, they are already used by many commercial video websites (e.g., YouTube \cite{YouTube}) to enable quality adaptation.
+However, the adaptive range and granularity that simulcast provides is limited to the number of streams (YouTube videos have 5 quality levels at most: 240p, 360p, 480p, 720p and 1080p), and the processing and storage of multiple video streams require a lot of computation time and disk space.
+In order to provide seamless quality adaptation at reasonable time and space cost, the adoption of SVC is necessary.
+An SVC video bitstream can be extracted at the granularity of one NALU (a very small partition of data), and performance analysis \cite{SVCPerformance} shows that SVC also has much higher coding efficiency than simulcast.
+Therefore, to adopt SVC in the video streaming framework is technically a better option and has attracted much attention in the study \cite{Chuah12}-\cite{Cicalo14}.
+
+There are two key problems in the SVC adaptive video streaming system that need to be primarily addressed.
 First, as the prerequisite of the adaption to bandwidth change, the whole bitstream needs to be extracted so that sub-streams with various bitrates can be obtained.
@@
 The original DSS project is modified and SVC support is added to it, for the purpose of both research and application.
-Then novel algorithms for bitstream extraction and quality control are designed and implemented to achieve significant improvement in terms of user-perceived video quality.
+Then novel algorithms for bitstream extraction and quality control are designed and implemented to enable better quality of service for the user.
 The contributions of our work can be summarized as follows:
@@
 A larger optimization window means each time we have more packets to compare and determine their priorities.
-Therefore, choosing a larger $K$ will result in more optimized extraction.
+Therefore, choosing a larger $K$ has the potential of more optimized extraction.
 However, doing this will also increase the computational complexity as well as the memory used to store the error vectors.
@@
 \centering
-\caption{Algorithm Performance: Luma PSNR Gain Compared with JSVM}
+\caption{Algorithm performance: Luma PSNR gain compared with JSVM}
 \label{tab:results}
@@
 For example, quality level 3 would contain all sub-streams from 0 to 3, thus would include all temporal layers, but only the quality base layer 0.
-The tested stream has 9 quality levels from 0 to 8 (see Table \ref{tab:sub-stream}), and a maximum bit rate of 1587 kbps at level 8.
+The tested stream has 9 quality levels from 0 to 8 (see Table \ref{tab:sub-stream}), and a maximum bitrate of 1587 kbps at level 8.
 
@@
 \label{fig:quality-all}}
-\subfloat[Variance of quality level of different control algorithms]{
+\subfloat[Quality level variance of different control algorithms]{
 \includegraphics[width=0.5\textwidth]{Variance-all.png}
@@
 \centering
-\subfloat[Variance of quality level of PID and PDF control algorithms]{
+\subfloat[Average quality level of PID and PDF control algorithms]{
 \includegraphics[width=0.5\textwidth]{Quality-two.png}
 \label{fig:quality-two}}
-\subfloat[Average quality level of PID and PDF control algorithms]{
+\subfloat[Quality level variance of PID and PDF control algorithms]{
 \includegraphics[width=0.5\textwidth]{Variance-two.png}
@@
 \centering
-\caption{Improvement of Different Quality Control Schemes}
+\caption{Improvement of different quality control algorithms}
 \label{tab:improvement}
@@
 \hline \hline
-Quality control scheme & Average quality level & Quality variance \\ \hline
+Quality control algorithm & Average quality level & Quality variance \\ \hline
 Packet delay feedback (PDF) & 0.0\% & 0.0\% \\ \hline

### 2015-11-29 tmm.tex
Add a table and change Fig.9

@@
 The performance comparisons for City, Foreman, Harbour, and Soccer are shown in Fig.
-\ref{fig:performance}.
+\ref{fig:extraction-performance}.
 It can be seen that the R-D curves of the proposed method are always on the top.
@@
 \caption{Performance of three bitstream extraction methods for various CIF sequences}
-\label{fig:performance}
+\label{fig:extraction-performance}
 \end{figure*}
@@
 \centering
-\caption{Algorithm performance: Luma PSNR gain compared with JSVM}
-\label{tab:results}
+\caption{Luma PSNR gain compared with JSVM}
+\label{tab:extraction-gain}
 \begin{minipage}{0.95\linewidth}
@@
 \multirow{2}{*}{JSVM QL\footnote{\label{footnote:JSVM_QL} Comparing the proposed algorithm with JSVM QL} (dB)}
-& Max\footnote{\label{footnote:max} Maximum PSNR gain through all bitrate constraints} & 0.37 & 0.50 & 0.13 & 0.22 & 0.23 & 0.19 & 0.25 & 0.44 \\ \cline{2-10}
-& Ave\footnote{\label{footnote:ave} Average PSNR gain through all bitrate constraints} & 0.11 & 0.11 & 0.05 & 0.12 & 0.05 & 0.05 & 0.06 & 0.13 \\ \hline
+& Max\footnote{\label{footnote:max} Maximum PSNR gain through all bitrate constraints}
+& 0.37 & 0.50 & 0.13 & 0.22 & 0.23 & 0.19 & 0.25 & 0.44 \\ \cline{2-10}
+& Ave\footnote{\label{footnote:ave} Average PSNR gain through all bitrate constraints}
+& 0.11 & 0.11 & 0.05 & 0.12 & 0.05 & 0.05 & 0.06 & 0.13 \\ \hline
 \multirow{2}{*}{JSVM no QL (dB)}
@@
 & Ave & 0.18 & 0.37 & 0.20 & 0.15 & 0.22 & 0.15 & 0.25 & 0.29 \\ \hline
+\end{tabular}
+\end{minipage}
+\end{table*}
+
+\begin{table*}[t]
+\centering
+\caption{Luma PSNR gain compared with JSVM QL for different windows sizes}
+\label{tab:extraction-gain-more}
+\begin{minipage}{0.95\linewidth}
+% \renewcommand{\thefootnote}{\thempfootnote}
+\centering
+\begin{tabular}{c|c|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}| 
+p{1.2cm}<{\centering}|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}}
+%% |l|l| to left justify each column entry
+%% |c|c| to center each column entry
+%% use of \rule[]{}{} below opens up each row
+\hline \hline
+\multicolumn{2}{c|}{Sequence} &
+{\em Bus} & {\em City} & {\em Crew} & {\em Football} & {\em Foreman} & {\em Harbour} & {\em Mobile} & {\em Soccer} \\ \hline 
+\multirow{2}{*}{PSNR gain}
+& 32 frames & 0.11 & 0.11 & 0.05 & 0.12 & 0.05 & 0.05 & 0.06 & 0.13 \\ \cline{2-10}
+& 48 frames & 0.12 & 0.23 & 0.16 & 0.13 & 0.15 & 0.13 & 0.08 & 0.21 \\ \hline
+
 \end{tabular}
@@
 \centering
-\subfloat[Bandwidth fluctuates around 600kbps: PSNR average and variance in the original system are 39.63 and 0.24, while in the proposed system are 39.69 (increased by 0.06) and 0.16 (reduced by 0.08).]{
+\subfloat[Bandwidth fluctuates around 400kbps: PSNR average and variance in the original system are 36.00 and 0.30, while in the proposed system are 36.50 (increased by 0.50) and 0.23 (reduced by 0.07).]{
 \includegraphics[width=0.47\textwidth]{Fluctuation-PSNR1.png}
 \label{fig:Fluctuation-PSNR1}}\hfill
-\subfloat[Bandwidth fluctuates around 800kbps: PSNR average and variance in the original system are 40.15 and 0.48, while in the proposed system are 40.62 (increased by 0.47) and 0.28 (reduced by 0.20).]{
+\subfloat[Bandwidth fluctuates around 600kbps: PSNR average and variance in the original system are 37.06 and 0.61, while in the proposed system are 37.32 (increased by 0.26) and 0.33 (reduced by 0.28).]{
 \includegraphics[width=0.47\textwidth]{Fluctuation-PSNR2.png}
@@
 \qquad
-\subfloat[Bandwidth fluctuates around 1000kbps: PSNR average and variance in the original system are 40.37 and 0.50, while in the proposed system are 40.74 (increased by 0.40) and 0.28 (reduced by 0.22).]{
+\subfloat[Bandwidth fluctuates around 800kbps: PSNR average and variance in the original system are 37.92 and 1.24, while in the proposed system are 38.75 (increased by 0.83) and 0.69 (reduced by 0.55).]{
 \includegraphics[width=0.47\textwidth]{Fluctuation-PSNR3.png}
 \label{fig:Fluctuation-PSNR3}}\hfill
-\subfloat[Bandwidth fluctuates around 1200kbps: PSNR average and variance in the original system are 40.48 and 0.63, while in the proposed system are 41.14 (increased by 0.66) and 0.21(reduced by 0.42).]{
+\subfloat[Bandwidth fluctuates around 1000kbps: PSNR average and variance in the original system are 38.28 and 1.30, while in the proposed system are 38.94 (increased by 0.66) and 0.71 (reduced by 0.59).]{
 \includegraphics[width=0.47\textwidth]{Fluctuation-PSNR4.png}

### 2015-11-30 tmm.tex
Add one more figure for consideration
Settle down experimental results

@@
 By monitoring and predicting bandwidth information of the past, the current and the future, the PID-based quality control algorithm can significantly reduce quality fluctuation while still keeping a high quality level.
-Experimental results show that, comparing with the baseline software, the proposed system integrating the above algorithms can achieve much lower video quality fluctuation, with PSNR variance reduced from 0.63 to 0.21, and at the same time deliver higher video quality, with an average PSNR gain of 0.66dB.
+Experimental results show that, comparing with the baseline software, the proposed system integrating the above algorithms can achieve much lower video quality fluctuation, with PSNR variance reduced from 1.24 to 0.69, and at the same time deliver higher video quality, with an average PSNR gain of 0.83dB.
 The system is deployed at online video website www.7dlive.com and proves to be practically effective.
@@
 \IEEEPARstart{V}{ideo} streaming applications are becoming more and more popular on the Internet.
-Examples of the most common usage scenarios include online video-on-demand (VoD), live broadcasting, video-based online education, etc.
+Examples of the most common usage scenarios include online Video-on-Demand (VoD), live broadcasting, video-based online education, etc.
 In these applications, video data is constantly delivered to different clients over various transmission channels, and the client media player can begin playing the video before the entire file has been transmitted.
@@
 In video streaming, the network condition significantly influences the user's watching experience.
-To provide better streaming service, some researchers choose to adopt the new software defined networking (SDN) architecture \cite{Egilmez14}.
+To provide better streaming service, some researchers choose to adopt the new Software Defined Networking (SDN) architecture \cite{Egilmez14}.
 Based on a successful SDN paradigm OpenFlow, noticeable results are achieved, e.g., a solution for improving network throughput in hybrid network \cite{Li14} and a demonstration of adaptive video manycast \cite{Xue15}.
@@
 \begin{itemize}
-\item First, a simple and effective linear error model (LEM) is proposed and verified, which can be used to accurately estimate the distortion caused by discarding any combination of data packets from an SVC bitstream.
-\item Second, on the basis of the distortion estimation enabled by LEM, a greedy-like algorithm is designed to assign priority for each data packet according to its R-D impact, thus enables optimized bitstream extraction.
+\item First, a simple and effective Linear Error Model (LEM) is proposed and verified, which can be used to accurately estimate the distortion caused by discarding any combination of data packets from an SVC bitstream.
+\item Second, on the basis of the distortion estimation enabled by LEM, a greedy-like algorithm is designed to assign priority for each data packet according to its Rate-Distortion (R-D) impact, thus enables optimized bitstream extraction.
 \item Finally, for the quality control problem, a novel algorithm based on the Proportional-Integral-Derivative (PID) control concept is proposed to replace the native one in DSS, and achieves much lower quality fluctuation with higher quality level.
@@
 The solutions then work together and serve as a solid foundation for a practical adaptive video streaming system.
+It should be noted that, in practical video streaming systems there are other issues that need to be addressed.
+One of them is occasional packet loss during transmission, which will cause decoding errors and corrupted images, resulting in degradation of video quality.
+However, in this paper we will focus on server-side adaptation and simply assume that no packet loss is occurred.
 
@@
 It can be seen that the R-D curves of the proposed method are always on the top.
-For each sequence, the maximum and average PSNR gain through all 10 bitrate points are calculated and listed in Table \ref{tab:results}, which shows that our extraction method can achieve a significant performance gain compared with JSVM.
+For each sequence, the maximum and average PSNR gain through all 10 bitrate points are calculated and listed in Table \ref{tab:extraction-gain}, which shows that our extraction method can achieve a significant performance gain compared with JSVM.
 
@@
 We compare the proposed system's performance with DSS that supports SVC but has its original quality control method and JSVM Basic bitstream extraction.
-The result for the same test stream as used in subsection \ref{subsec:exp-control} is present in Fig.
+The result for the test sequence Soccer is present in Fig.
 \ref{fig:fluctuation-psnr}.
-It shows PSNR change perceived by the user when available bandwidth fluctuates around certain values (600kbps, 800kbps, 1000kbps and 1200kbps).
+It shows the streamed video's PSNR change when available bandwidth fluctuates around certain values (400kbps, 600kbps, 800kbps and 1000kbps).
 The bandwidth conditions are simulated with NetLimiter and intense fluctuations are observed.
-It can be seen that, the proposed system performs better in that it has effectively avoided unnecessary quality drop (e.g., note the curve around time 450s in Fig.
-\ref{fig:Fluctuation-PSNR1} or 250s in Fig.
-\ref{fig:Fluctuation-PSNR3}) and been able to keep a relatively higher PSNR value (e.g., note the curve around time 400s in Fig.
-\ref{fig:Fluctuation-PSNR2} or 500s in Fig.
-\ref{fig:Fluctuation-PSNR4}).
+It can be seen that, the proposed system performs better in that it has effectively avoided unnecessary quality drop (e.g., note the curve around time 350s in Fig.
+\ref{fig:Fluctuation-PSNR3} or 150s in Fig.
+\ref{fig:Fluctuation-PSNR4}) and been able to keep a relatively higher PSNR value (e.g., note the curve around time 450s in Fig.
+\ref{fig:Fluctuation-PSNR1} or 500s in Fig.
+\ref{fig:Fluctuation-PSNR2}).
 The average and variance value of PSNR is also calculated and present in Fig.
@@
 For instance, in Fig.
-\ref{fig:Fluctuation-PSNR4} where bandwidth fluctuates around 1200kbps, the average PSNR delivered by the proposed system is 41.14dB, 0.66dB higher than that of the baseline system, and the PSNR variance is also reduced from 0.63 to 0.21, indicating a more smooth video quality change.
+\ref{fig:Fluctuation-PSNR3} where bandwidth fluctuates around 800kbps, the average PSNR delivered by the proposed system is 38.75dB, 0.83dB higher than that of the baseline system, and the PSNR variance is also reduced from 1.24 to 0.69, indicating a more smooth video quality change.
 
@@
 \label{fig:Fluctuation-PSNR4}}
-\caption{User-perceived PSNR change with time when bandwidth fluctuates \label{fig:fluctuation-psnr}}
+\caption{The streamed video's PSNR change with time when bandwidth fluctuates \label{fig:fluctuation-psnr}}
 \end{figure*}

### 2015-11-30 tmm.tex
Merge two tables into one

@@
 \usepackage{balance}
+\usepackage{makecell}
 
@@
 In our experiments, all test bitstreams are encoded with the JSVM encoder, where the standard hierarchical B coding structure and CABAC entropy coding are used.
-Each bitstream contains one base layer and a quality enhancement layer, with quantization parameters QP = 33 and QP = 27, respectively.
-The enhancement layer is further divided into 2 MGS layers by configuring the MGS vector to separate the transform coefficients into two groups (containing 4 and 12 coefficients respectively).
+Each bitstream contains one base layer and one enhancement layer, with quantization parameters QP = 33 and QP = 27, respectively.
+The enhancement layer is further divided into 2 Medium Grain Scalability (MGS) layers by configuring the MGS vector to separate the transform coefficients into two groups (containing 4 and 12 coefficients respectively).
 For each test bitstream, ten bitrate points (one with all enhancement packets, one with only the base layer packets, and 8 points between) are chosen for extraction.
-For each bitrate point, the extraction is conducted using the bitstream extractors in JSVM, with and without quality layer (denoted as JSVM QL and JSVM Basic, respectively), and the proposed method.
+For each bitrate point, the extraction is conducted using the bitstream extractors in JSVM, with and without \textit{Quality Layers} (denoted as JSVM QL and JSVM Basic, respectively), and the proposed method.
 The size of the optimization window in the proposed method is set to 4 GOPs, with a GOP size of 8.
@@
 It can be seen that the R-D curves of the proposed method are always on the top.
-For each sequence, the maximum and average PSNR gain through all 10 bitrate points are calculated and listed in Table \ref{tab:extraction-gain}, which shows that our extraction method can achieve a significant performance gain compared with JSVM.
+For each sequence, the maximum and average PSNR gain through all 10 bitrate points are calculated and listed in Table \ref{tab:extraction-gain}, which shows that our extraction method can achieve a significant performance gain compared with JSVM Basic, and also performs better than JSVM QL.
+Table \ref{tab:extraction-gain} also lists results when optimization window is 6 GOPs, i.e., 48 frames.
+It is demonstrated that a larger window size can increase performance to some degree.
+However, it should be noted that, the practical system we propose does not use optimization window exceeding 32 frames, for the reason stated in the end of Sub-section \ref{subsec:priority}.
 
@@
 \centering
-\caption{Luma PSNR gain compared with JSVM}
+\caption{Luma PSNR gain of the proposed algorith compared with JSVM}
 \label{tab:extraction-gain}
@@
 {\em Bus} & {\em City} & {\em Crew} & {\em Football} & {\em Foreman} & {\em Harbour} & {\em Mobile} & {\em Soccer} \\ \hline 
-\multirow{2}{*}{JSVM QL\footnote{\label{footnote:JSVM_QL} Comparing the proposed algorithm with JSVM QL} (dB)}
+\multirow{2}{*}{JSVM QL, $K$ = 32 \footnote{\label{footnote:JSVM_QL} Comparing the proposed algorithm with JSVM QL; the optimization window containing 32 frames}}
 & Max\footnote{\label{footnote:max} Maximum PSNR gain through all bitrate constraints}
@@
 & 0.11 & 0.11 & 0.05 & 0.12 & 0.05 & 0.05 & 0.06 & 0.13 \\ \hline
-\multirow{2}{*}{JSVM no QL (dB)}
+\multirow{2}{*}{JSVM Basic, $K$ = 32}
 & Max & 0.50 & 0.83 & 0.32 & 0.29 & 0.50 & 0.34 & 0.61 & 0.53 \\ \cline{2-10}
-& Ave & 0.18 & 0.37 & 0.20 & 0.15 & 0.22 & 0.15 & 0.25 & 0.29 \\ \hline
-\end{tabular}
-\end{minipage}
-\end{table*}
-
-\begin{table*}[t]
-\centering
-\caption{Luma PSNR gain compared with JSVM QL for different windows sizes}
-\label{tab:extraction-gain-more}
-\begin{minipage}{0.95\linewidth}
-% \renewcommand{\thefootnote}{\thempfootnote}
-\centering
-\begin{tabular}{c|c|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}| 
-p{1.2cm}<{\centering}|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}}
-%% |l|l| to left justify each column entry
-%% |c|c| to center each column entry
-%% use of \rule[]{}{} below opens up each row
-\hline \hline
-\multicolumn{2}{c|}{Sequence} &
-{\em Bus} & {\em City} & {\em Crew} & {\em Football} & {\em Foreman} & {\em Harbour} & {\em Mobile} & {\em Soccer} \\ \hline 
-\multirow{2}{*}{PSNR gain}
-& 32 frames & 0.11 & 0.11 & 0.05 & 0.12 & 0.05 & 0.05 & 0.06 & 0.13 \\ \cline{2-10}
-& 48 frames & 0.12 & 0.23 & 0.16 & 0.13 & 0.15 & 0.13 & 0.08 & 0.21 \\ \hline
-
+& Ave & 0.18 & 0.37 & 0.20 & 0.15 & 0.22 & 0.15 & 0.25 & 0.29 \\ \Xhline{2\arrayrulewidth}
+\multirow{2}{*}{JSVM QL, $K$ = 48}
+& Max & 0.36 & 0.39 & 0.27 & 0.30 & 0.30 & 0.38 & 0.21 & 0.40 \\ \cline{2-10}
+& Ave & 0.12 & 0.23 & 0.16 & 0.13 & 0.15 & 0.13 & 0.08 & 0.21 \\ \hline
+\multirow{2}{*}{JSVM Basic, $K$ = 48}
+& Max & 0.36 & 0.81 & 0.32 & 0.29 & 0.49 & 0.47 & 0.57 & 0.60 \\ \cline{2-10}
+& Ave & 0.19 & 0.40 & 0.19 & 0.17 & 0.28 & 0.22 & 0.28 & 0.42 \\ \hline
 \end{tabular}

### 2015-11-30 tmm.tex
Update the figure of GOP structure

@@
 \centering
-\includegraphics[width = 1.0\linewidth]{GOPStructure.jpg}
+\includegraphics[width = 0.9\linewidth]{GOP-Structure.png}
 \caption{Group of pictures (GOP) in SVC \label{fig:GOP_Structure}}
@@
 In each group, the enhancement packets' error vectors can be calculated simultaneously, since the pixel errors they caused are not interfered with each other.
-For example, the loss of packet 8 would bring about distortion only in frame 1, 2 and 3, while packet 10 only in frame 5, 6 and 7(frame number starts from 0).
+For example, the loss of packet 8 would bring about distortion only in frame 1, 2 and 3, while packet 10 only in frame 5, 6 and 7 (frame number starts from 0).
 So we can do subtraction for this group, for one time, to gain error vectors $e_{8}$ and $e_{10}$, for both packets 8 and 10, as well as peer packets in all other GOPs.

### 2015-11-30 tmm.tex
A version with all concerns addressed

@@
 
-The proposed solutions for bitstream extraction and quality control are combined together and result in a higher and smoother PSNR curve representing the final video quality perceived by the user.
+The proposed solutions for bitstream extraction and quality control are combined together and result in a higher and smoother PSNR curve representing the final video quality delivered to the user.
 
@@
 \subsection{Bitstream Extraction}
+\label{subsec:analysis-extraction}
 
@@
 Yang et al.
-\cite{Yang13} proposed a method based-on simulated annealing to solve the bitstream extraction problem.
+\cite{Yang13} proposed a method based-on simulated annealing to determine and assign priority values used in bitstream extraction.
 In both methods, the accuracy of distortion estimation is the key of the performance.
@@
 \subsection{Quality Control}
+\label{subsec:analysis-control}
 
 Quality control is the second problem we will address in this paper.
-The result of a quality control algorithm gives the suitable bitrate for current transmission, which is directly related to the change of video quality perceived by the user.
+The result of a quality control algorithm gives the suitable bitrate for current transmission, which is directly related to the change of video quality delieverd the user.
 In an SVC streaming system, the bitrate determined by the quality control algorithm is used as the constraint under which bitstream extraction is performed.
@@
 It should be noted that, in practical video streaming systems there are other issues that need to be addressed.
-One of them is occasional packet loss during transmission, which will cause decoding errors and corrupted images, resulting in degradation of video quality.
-However, in this paper we will focus on server-side adaptation and simply assume that no packet loss is occurred.
+One of them is occasional packet loss during transmission, which will cause decoding errors and corrupted images, resulting in an significant degradation of video quality.
+How to avoid or even recover from packet loss/error is an important research topic that is popular in both networking and multimedia community.
+However, in this paper which focuses on server-side adaptation, packet loss is not handled and we simply assume that the video stream will be successfully delivered to the client.
 
@@
 \subsection{Linear Error Model for Quality Scalable Video}
-\label{sec:model}
+\label{subsec:linear-model}
 
@@
 \end{equation}
-It means, the reconstructed samples of a GOP (Group of Pictures), denoted by $s$, can be viewed as a linear combination of previously reconstructed samples in the GOP, the residual samples, and a static predictor.
-In (\ref{eq:linear}), $c$ refers to the transform coefficient values and $p$ is a static predictor; ${\rm\bf M}$ and ${\rm\bf T}$ are square matrices such that the product ${\rm\bf M} \cdot s$ gives the MCP (Motion Compensated Prediction) signal and ${\rm\bf T} \cdot c$ gives the residual values.
-The actual values of ${\rm\bf M}$ depend on the selected macroblock types, reference indices and motion vectors, whereas the actual values of ${\rm\bf T}$ depend on the chosen QP (Quantization Parameter) values.
+It means, the reconstructed samples of a Group of Pictures (GOP), denoted by $s$, can be viewed as a linear combination of previously reconstructed samples in the GOP, the residual samples, and a static predictor.
+In (\ref{eq:linear}), $c$ refers to the transform coefficient values and $p$ is a static predictor; ${\rm\bf M}$ and ${\rm\bf T}$ are square matrices such that the product ${\rm\bf M} \cdot s$ gives the Motion Compensated Prediction (MCP) signal and ${\rm\bf T} \cdot c$ gives the residual values.
+The actual values of ${\rm\bf M}$ depend on the selected macroblock types, reference indices and motion vectors, whereas the actual values of ${\rm\bf T}$ depend on the chosen Quantization Parameter (QP) values.
 
@@
 \subsection{Error Vector Acquisition}
+\label{subsec:error-vector}
 
@@
 \centering
-\includegraphics[width = 0.9\linewidth]{GOP-Structure.png}
+\includegraphics[width = 1.0\linewidth]{GOP-Structure.png}
 \caption{Group of pictures (GOP) in SVC \label{fig:GOP_Structure}}
@@
 \subsection{Distortion Estimation and Model Verification}
+\label{subsec:distortion-estimation}
 
@@
 
-To verify the linear error model, we conduct an experiment where random combinations of enhancement packets are removed from a video bitstream, and the distortion estimated by the linear error model are compared with the actual distortion caused by the removal.
-The video stream has the same GOP structure and quality layers as illustrated in Fig.
-\ref{fig:GOP_Structure}.
-One comparison result for the sequence {\em Foreman} (only first 33 frames are used) is shown in Fig.
+Before using the linear error model, we conduct an experiment to verify it.
+All bitstreams in the experiment are encoded with the JSVM encoder, where the same GOP structure as illustrated in Fig.
+\ref{fig:GOP_Structure} and CABAC entropy coding are used.
+Each bitstream contains one base layer and one enhancement layer, with QP = 33 and QP = 27, respectively.
+The enhancement layer is further divided into 2 Medium Grain Scalability (MGS) layers by configuring the MGS vector to separate the transform coefficients into two groups (containing 4 and 12 coefficients respectively).
+Random combinations of enhancement packets are removed from a video bitstream, and the distortion estimated by the linear error model are compared with the actual distortion caused by the removal.
+One comparison result for the test sequence {\em Foreman} (only first 33 frames are used) is shown in Fig.
 \ref{fig:model_verification}.
 The horizontal axis stands for frame index, and the vertical axis for MSE measurement.
-The solid line represents the actual MSE of a frame, and the dot line shows the estimated MSE using our Linear Error Model.
-It can be seen that the two lines are very close to each other, which demonstrates the accuracy of the proposed model.
-Table \ref{tab:estimation-error} lists the distortion estimation error for different sequences and shows that the average error is only about 5\%.
-
-\begin{figure}[h]
+The solid line represents the actual distortion for the frames, and the dot line represents the distortion estimated by the proposed linear error model.
+It can be seen that the two lines are very close to each other, which demonstrates the accuracy of estimation using the proposed model.
+Estimation errors for all the eight SVC standard test sequences are listed in Table \ref{tab:estimation-error}, which shows that the average error is only about 5\%.
+
+\begin{figure}[t]
 \centering
@@
 \subsection{Priority Assignment and Bitstream Extraction}
-\label{subsec:priority}
+\label{subsec:priority-assign}
 
@@
 \subsection{The No-Reference Case}
-\label{subsec:noref}
+\label{subsec:noref-case}
 
@@
 The process variable stands for the current status of the system.
-The setpoint is the target for this automatic control system to reach.
+The setpoint is the target for this control system to reach.
 The goal of PID control is to minimize the error between process variable and setpoint by adjusting system inputs.
@@
 \subsection{Process Variable Selection}
-\label{subsec:variable}
+\label{subsec:process-variable}
 
@@
 \subsection{Model Formulation}
-\label{subsec:model}
+\label{subsec:model-formulation}
 
@@
 This ratio-based model is more simple and effective for the chosen process variable and setpoint.
-And note that, since the controller output ($u_t$) is also a ratio, it should be used as a multiplier to manipulate the system input, i.e., the pushing data rate.
-
-The whole process of this algorithm is described in Algorithm \ref{algo:control}.
+Moreover, in this model the controller output has intuitive meaning when the three parameters are normalized.
+It is easy to know that all of the three PID parts ($E_p^t$, $E_i^t$, $E_d^t$) are ratios with a value more or less than 1, and the controller output $u_t$ is a weighted average of the three ratios, with the three parameters as weights.
+Therefore the controller output is also a ratio value around 1, which reflects the relationship between the bitrate appropriate for bandwidth condition and the bitrate currently being used.
+In other words, if the output is larger than 1, then the controller has determined the bitrate should be increased accordingly, and vice versa.
+Use it as a multiplier to manipulate the bitrate currently being used, and we would be able to control the streaming system to match bandwidth condition.
+
+The whole process of the proposed algorithm is described in Algorithm \ref{algo:control}.
 Compared to other scheduling strategies, this quality control algorithm has several advantages.
-First, this algorithm does not just rely on current packet delay or information at fixed time point, so quality change may occur at any proper time.
-Second, since the model has taken prediction into account, we can actually decide whether the bandwidth will be high or low enough for the quality level to change, thus avoiding video quality fluctuation.
+First, this algorithm does not just rely on current packet delay or information at fixed time point, therefore quality change may occur at any proper time.
+Second, since the model has taken prediction into account, it is able to decide whether the bandwidth will be high or low enough for the quality level to change in the near future, thus avoiding video quality fluctuation.
 Third, in this algorithm it's not necessary to change one quality level at a time.
-This enables fast quality drop when bandwidth suddenly decreases and fast quality rise when system starts, resulting in a seamless experience.
+This enables fast quality drop to avoid a latent playback pause when bandwidth suddenly decreases, and fast quality rise to provide better video as soon as possible when system starts, resulting in a seamless watching experience where the user can enjoy the video without stopping or waiting.
 
@@
 \subsection{Parameter Selection}
-\label{subsec:parameter}
-
-Ziegler--Nichols method \cite{Ziegler42} is used to tune $K_p$, $K_i$, and $K_d$ to obtain better performance of the PID control system.
+\label{subsec:parameter-selection}
+
+As with other PID control systems in the industry, the selection of the three parameters is implementation-dependent and most of the time manual tuning with trial and error is required to achieve optimal results.
+Knowing the impacts of each parameter is useful in the practice of parameter selection.
+Generally,  the proportional part in PID controller affects the system's stability.
+If the proportional gain $K_p$ is too high, the system can become unstable.
+However, a low $K_p$ would result in long rising time that makes the system response slowly.
+In addition to eliminating steady-state error, the integral term also accelerates the movement of the process towards setpoint, which means increasing $K_i$ can reduce rising time.
+However, since the integral part accumulates errors from the past, it can cause the present value to overshoot the setpoint value, and too much $K_i$ will lead to instability as well.
+This can be compensated by the derivative part, which predicts system behaviour and has the effect of reducing the overshoot, increasing the stability, and improving the settling time (time it takes to reach setpoint after a disturbance).
+The big problem with derivative part is that it is very sensitive to noise, therefore industrial practices indicates that derivative gain $K_d$ should always stay low.
+
+For the proposed quality control algorithm, Ziegler--Nichols method \cite{Ziegler42} is used to select the parameters to obtain better performance.
 This method is performed by setting integral and derivative parameters to zero and then tuning $K_p$ to a value $K_u$ until output begins to oscillate with constant amplitude.
@@
 In the following experiments, parameters are chosen as $K_p = 0.22$, $K_i = 0.73$, $K_d = 0.05$ by this method.
-As with other control systems, PID parameters are a result of tunning and may not suit to all use cases.
-However, it should be noted that in the video quality control algorithm, only the data rate and the bandwidth are considered, not the video content.
-Therefore once the parameters are tuned they should apply well to different video streams.
+
+In this work we simply use the standard Ziegler--Nichols method which already takes above impacts into consideration and produces acceptably good results.
+Adopting more sophisticated or automated techniques to further optimize the parameters will be done in the future.
+It should also be noted that, in the video quality control algorithm only the data rate and the bandwidth are relevant, not the video content.
+Therefore once the parameters are chosen they should apply well to different video streams.
 
@@
 Choosing DSS as the implementation basis, we have integrated the proposed algorithms into it for the purpose of both research and application.
+The greedy-like algorithm present in \ref{subsec:priority-assign} is performed to determine priority values for all enhancement NALUs in an SVC bitstream.
+Then the priority values are injected into the bitstream, storing in the priority identifier field of the NALU header.
+When DSS streams this video, by checking this field it can extract a bitstream under certain bitrate determined by the PID-based quality control algorithm.
+
 In this section, we first present separate experiments to show the advantage of each proposed solution, and then give the result when they are combined together.
@@
 \subsection{Experiments for Bitstream Extraction}
+\label{subsec:exp-extraction}
 
@@
 
-In our experiments, all test bitstreams are encoded with the JSVM encoder, where the standard hierarchical B coding structure and CABAC entropy coding are used.
-Each bitstream contains one base layer and one enhancement layer, with quantization parameters QP = 33 and QP = 27, respectively.
-The enhancement layer is further divided into 2 Medium Grain Scalability (MGS) layers by configuring the MGS vector to separate the transform coefficients into two groups (containing 4 and 12 coefficients respectively).
+In our experiments, all test bitstreams are encoded as stated in sub-section \ref{subsec:distortion-estimation}.
 For each test bitstream, ten bitrate points (one with all enhancement packets, one with only the base layer packets, and 8 points between) are chosen for extraction.
 For each bitrate point, the extraction is conducted using the bitstream extractors in JSVM, with and without \textit{Quality Layers} (denoted as JSVM QL and JSVM Basic, respectively), and the proposed method.
-The size of the optimization window in the proposed method is set to 4 GOPs, with a GOP size of 8.
+The size of the optimization window in the proposed method is 32 frames, i.e., 4 GOPs with a GOP size of 8.
 All of the eight SVC standard sequences with CIF resolution are considered at 30FPS and tested in our experiments.
@@
 For each sequence, the maximum and average PSNR gain through all 10 bitrate points are calculated and listed in Table \ref{tab:extraction-gain}, which shows that our extraction method can achieve a significant performance gain compared with JSVM Basic, and also performs better than JSVM QL.
-Table \ref{tab:extraction-gain} also lists results when optimization window is 6 GOPs, i.e., 48 frames.
+Table \ref{tab:extraction-gain} also lists results when optimization window is 48 frames, i.e., 6 GOPs.
 It is demonstrated that a larger window size can increase performance to some degree.
-However, it should be noted that, the practical system we propose does not use optimization window exceeding 32 frames, for the reason stated in the end of Sub-section \ref{subsec:priority}.
+However, it should be noted that, the practical system we propose does not use optimization window exceeding 32 frames, for the reason stated in the end of sub-section \ref{subsec:priority-assign}.
 
@@
 We set this level from 400 to 1400 kbps to reflect different average bandwidth.
-All the experiments are conducted with DSS as the software platform, and the bandwidth simulation is implemented with NetLimiter 3 \cite{Netlimiter}.
+The simulation is implemented with NetLimiter 3 \cite{Netlimiter}, where the bandwidth varies randomly with certain distribution and intense fluctuations are observed.
 The baseline algorithm in the comparison refers to the packet delay feedback (PDF) algorithm in the original DSS.
@@
 \subsection{Result of the Combined System}
+\label{subsec:exp-combined}
 
@@
 It shows the streamed video's PSNR change when available bandwidth fluctuates around certain values (400kbps, 600kbps, 800kbps and 1000kbps).
-The bandwidth conditions are simulated with NetLimiter and intense fluctuations are observed.
 It can be seen that, the proposed system performs better in that it has effectively avoided unnecessary quality drop (e.g., note the curve around time 350s in Fig.
@@
 \label{fig:Fluctuation-PSNR4}}
-\caption{The streamed video's PSNR change with time when bandwidth fluctuates \label{fig:fluctuation-psnr}}
+\caption{The streamed video's PSNR change with time when bandwidth fluctuates
+\label{fig:fluctuation-psnr}}
 \end{figure*}

### 2015-12-01 tmm.tex
Polish the first two sections

@@
 In video streaming, the network condition significantly influences the user's watching experience.
-To provide better streaming service, some researchers choose to adopt the new Software Defined Networking (SDN) architecture \cite{Egilmez14}.
-Based on a successful SDN paradigm OpenFlow, noticeable results are achieved, e.g., a solution for improving network throughput in hybrid network \cite{Li14} and a demonstration of adaptive video manycast \cite{Xue15}.
-Although these studies offer a promising way to optimize network conditions, currently traditional best-effort networks still dominate, and the variety of users' network environment remains to be one of the biggest challenges for video streaming.
-A user might use different types of network (Ethernet, Wi-Fi, Cellular, etc.) and might also switch from one type to another on going (e.g., from Wi-Fi to cellular network).
-Even in the same network, the user's bandwidth will change from time to time, influenced by the overall traffic.
-Within such an environment, bandwidth fluctuation is inevitable and it would be difficult or impossible for the user to get best watching experience if the video is streamed at a constant bitrate.
+To provide better network condition, some researchers choose to adopt the new Software Defined Networking (SDN) architecture \cite{Egilmez14}.
+Based on a successful SDN paradigm named OpenFlow, noticeable results are achieved, e.g., a solution for improving network throughput in hybrid network \cite{Li14} and a demonstration
+of OpenFlow-controlled network orchestration for video manycast \cite{Xue15}.
+Although these studies have offered a promising alternative, currently traditional best-effort networks still dominate, and the variety of users' network environment remains to be one of the biggest challenges for video streaming.
+A user might use different types of network (Ethernet, Wi-Fi, Cellular, etc.) and might also switch from one type to another on going (e.g., from Wi-Fi to Cellular).
+Even in the same network, the end-to-end bandwidth will change from time to time, influenced by the overall traffic.
+Within such an environment, bandwidth fluctuation is inevitable, and it would be difficult or impossible for the user to get best watching experience if the video is streamed at a constant bitrate.
 To cope with this challenge, the video streaming system should be able to automatically adjust the video's bitrate or quality according to the bandwidth change.
@@
 Dynamic Adaptive Streaming over HTTP (DASH) \cite{DASH}, which is standardized by the Moving Picture Expert Group (MPEG), belongs to this option.
-The second option is to adopt the Scalable Video Coding (SVC) \cite{SVC} technology, an extension of the H.264/AVC video coding standard \cite{SVCOverview}, which allows scalability of video bitrate and quality with only one single bitstream.
+The second option is to adopt the Scalable Video Coding (SVC) \cite{SVC} technology, an extension of the H.264/AVC video coding standard \cite{SVCOverview}, which allows scalability of video quality and bitrate with only one single bitstream.
 In SVC, a video bitstream is composed of small data packets called Network Abstract Layer Units (NALUs).
 These NALUs are separated into one base layer for basic video quality and multiple enhancement layers for video quality improvement.
-By discarding NALUs of the enhancement layers, the bitstream can be extracted to provide the most appropriate data rate and video quality as required.
+By discarding NALUs of the enhancement layers, the bitstream can be extracted to provide the most appropriate video quality and bitrate as required.
 
@@
 However, the adaptive range and granularity that simulcast provides is limited to the number of streams (YouTube videos have 5 quality levels at most: 240p, 360p, 480p, 720p and 1080p), and the processing and storage of multiple video streams require a lot of computation time and disk space.
-In order to provide seamless quality adaptation at reasonable time and space cost, the adoption of SVC is necessary.
-An SVC video bitstream can be extracted at the granularity of one NALU (a very small partition of data), and performance analysis \cite{SVCPerformance} shows that SVC also has much higher coding efficiency than simulcast.
+In order to provide a wide range of seamless quality adaptation at reasonable time and space cost, the adoption of SVC is necessary.
+An SVC video bitstream can be extracted at the fine granularity of one NALU (a very small partition of data), and performance analysis \cite{SVCPerformance} shows that SVC clearly outperforms simulcast coding in terms of compression efficiency.
 Therefore, to adopt SVC in the video streaming framework is technically a better option and has attracted much attention in the study \cite{Chuah12}-\cite{Cicalo14}.
 
-There are two key problems in the SVC adaptive video streaming system that need to be primarily addressed.
-First, as the prerequisite of the adaption to bandwidth change, the whole bitstream needs to be extracted so that sub-streams with various bitrates can be obtained.
+While these studies mostly focus on Quality of Service (QoS) optimization and resource allocation for specific networks, there are two key problems that need to be primarily addressed when adopting SVC in adaptive video streaming.
+First, as the prerequisite of bitrate adaption, the whole bitstream needs to be extracted so that sub-streams with various bitrates can be obtained.
 This is called the bitstream extraction problem.
 Optimal bitstream extraction algorithm aims to extract a sub-stream with best video quality, or minimal distortion, under the constraint of a given bitrate.
-Second, when the bandwidth changes with time, it's necessary to make decisions about whether and how to adjust the bitrate or video quality.
-This problem is called quality control, which means controlling the video quality (or the video bitrate, from the transmission point of view) to follow the change of the bandwidth.
-A good quality control algorithm should determine a suitable bitrate for current bandwidth condition, and keep the video quality both smooth and at a high level.
+Second, when the bandwidth changes with time, it is necessary to make decisions about whether and how to adjust the video quality or bitrate.
+This problem is called quality control, which means controlling the video quality (or the bitrate, from the transmission point of view) to follow the change of the bandwidth.
+A good quality control algorithm should determine a suitable bitrate according to current network condition, and keep the video quality both smooth and at a high level.
 
@@
 \item First, a simple and effective Linear Error Model (LEM) is proposed and verified, which can be used to accurately estimate the distortion caused by discarding any combination of data packets from an SVC bitstream.
-\item Second, on the basis of the distortion estimation enabled by LEM, a greedy-like algorithm is designed to assign priority for each data packet according to its Rate-Distortion (R-D) impact, thus enables optimized bitstream extraction.
-\item Finally, for the quality control problem, a novel algorithm based on the Proportional-Integral-Derivative (PID) control concept is proposed to replace the native one in DSS, and achieves much lower quality fluctuation with higher quality level.
+\item Second, utilizing distortion estimation with LEM, a greedy-like algorithm is designed to assign priority for each data packet according to its Rate-Distortion (R-D) impact, thus enables optimized bitstream extraction.
+\item Finally, for the quality control problem, a novel algorithm based on the Proportional-Integral-Derivative (PID) controller is proposed to replace the native one in DSS, and much lower quality fluctuation is achieved.
 \end{itemize}
@@
 The rest of this paper is organized as follows.
-In section \ref{sec:analysis}, we analyze the problems in detail and introduce some related works on them.
-Then in section \ref{sec:bitstream-extraction}, the linear error model is proposed, and the solution for the bitstream extraction problem based on the model is present.
+In section \ref{sec:analysis}, we analyze the problems in detail and introduce some related work on them.
+Then in section \ref{sec:bitstream-extraction}, the linear error model and the solution for the bitstream extraction problem are present.
 After that, the PID-based quality control algorithm is proposed in section \ref{sec:quality-control}.
@@
 
-In this section, we analyze the two most concerned problems in SVC adaptive video streaming, i.e., bitstream extraction and quality control, and introduce some related works on them.
+In this section, we analyze the two most concerned problems in SVC adaptive video streaming, i.e., bitstream extraction and quality control, and introduce some related work on them.
 
@@
 Bitstream extraction is the operation of choosing a subset of data packets from a whole SVC bitstream to form a sub-stream.
-It makes the bitrate adjustable and is the prerequisite of an adaptive streaming system.
 Fig.
-\ref{fig:Bitstream-Extraction} illustrates the structure of an SVC stream and a possible way to extract a sub-stream from it.
-The data packets in the stream are divided into different layers.
+\ref{fig:Bitstream-Extraction} illustrates the structure of an SVC bitstream and a possible way to extract a sub-stream from it.
+The data packets in the bitstream are divided into different layers.
 The temporal layer (T0$\sim$T3) reflects the reference or dependency relationship between the frames.
@@
 There are many combinations of packets to be discarded, and we want to choose a combination that maximizes the video quality of the extracted sub-stream, under the constraint of a given bitrate.
-More specifically, this problem fits in the form of ``0-1 Knapsack Problem" \cite{Knapsack}.
+More specifically, this problem is in the form of ``0-1 Knapsack Problem" \cite{Knapsack}.
 Each data packet can be treated as an object with certain weight (the packet's size) and value (its contribution to the video quality).
@@
 For a typical ``0-1 Knapsack Problem", the optimal solution can generally be found using the dynamic programming algorithm.
-However, this is not operational for the bitstream extraction problem, mainly due to the dependence between the stream's data packets.
+However, this is not operational for the bitstream extraction problem, mainly due to the dependence between the data packets.
 First, the subset of packets to be extracted cannot be chosen arbitrarily, since if a packet is included, all the packets it depends on must also be included.
@@
 \ref{fig:Bitstream-Extraction}, we cannot include the Q2 packet of a frame without including the Q1 packet of the same frame.
-Second, the value of a packet is not obvious and certain, since a packet's contribution to video quality may depend on other packets.
-Unless we discard a packet and calculate the distortion it causes for real, there is no way to exactly tell its value.
+Second, the value of a packet is not obvious and certain, since a packet's contribution to video quality depends on other packets and may vary in different extractions.
+There is no way to exactly tell the video quality of an extracted sub-stream, unless we perform the extraction and calculate the distortion for real.
 In fact, to the best of our knowledge, no method presented in the literature claims to find the optimal solution of the SVC bitstream extraction problem.
@@
 Maani et al.'s model can achieve better estimation accuracy than JSVM; however, since it is a training-based model, more computation is needed to get robust model parameters.
+With relatively simple distortion estimation, Yang et al.
+\cite{Yang13} proposed a method based-on simulated annealing to determine priority values used in bitstream extraction.
 Ramanathan et al.
 \cite{Ramanathan12} proposed their concept and calculation method of the ``Quality Metadata'' to signal and use in bitstream extraction.
-Yang et al.
-\cite{Yang13} proposed a method based-on simulated annealing to determine and assign priority values used in bitstream extraction.
-In both methods, the accuracy of distortion estimation is the key of the performance.
-
-In our previous work \cite{Zhang12}, we noticed the mismatch between quadratic calculations in distortion criteria like MSE or PSNR and the essential linear operations in the coding process, and proposed a linear error model to directly estimate pixel value errors before MSE or PSNR is calculated.
-The linear error model exploits the linear feature of pixel value errors and achieves good performance in distortion estimation and bitstream extraction with reference.
+In both methods, the accuracy of distortion estimation still affects the performance a lot.
+
+In our previous work \cite{Zhang12}, we proposed a linear error model to directly estimate pixel value errors before MSE or PSNR is calculated, which achieves good performance in distortion estimation and bitstream extraction.
 However, this work assumes that the original video sequence is available for reference, which is not always true.
-Adaptation to handle the special characteristic of the no-reference case is lacking in the previous work and included in this paper.
+How to handle the special characteristic of the no-reference case is lacking in the previous work and included in this paper.
 
@@
 As for the PID-based quality control algorithm, it is only network-concerned thus should be easily integrated into other streaming systems, e.g., simulcast system like DASH.
+Another direction of future work is to carry out some subjective tests, comparing the performance of the proposed system from the perceived quality point of view.
 

### 2015-12-02 tmm.tex
Settle down related work and citations

@@
 This framework has been adopted by the SVC reference software, i.e., JSVM \cite{JSVM}, and achieves better R-D performance compared with the basic extractor of JSVM.
-In Amonou's framework, a Quality Layer value, which reflects a packet's R-D impact, is calculated and used for R-D optimized bitstream extraction.
+In Amonou's framework, a Quality Layer value, which reflects a data packet's R-D impact, is calculated and used for R-D optimized bitstream extraction.
 The process of obtaining distortion impact of every packet is extremely time consuming, and the distortion estimation accuracy can also be further improved.
@@
 Maani et al.'s model can achieve better estimation accuracy than JSVM; however, since it is a training-based model, more computation is needed to get robust model parameters.
-With relatively simple distortion estimation, Yang et al.
-\cite{Yang13} proposed a method based-on simulated annealing to determine priority values used in bitstream extraction.
 Ramanathan et al.
 \cite{Ramanathan12} proposed their concept and calculation method of the ``Quality Metadata'' to signal and use in bitstream extraction.
-In both methods, the accuracy of distortion estimation still affects the performance a lot.
-
-In our previous work \cite{Zhang12}, we proposed a linear error model to directly estimate pixel value errors before MSE or PSNR is calculated, which achieves good performance in distortion estimation and bitstream extraction.
+Yang et al.
+\cite{Yang13} proposed a method based on simulated annealing to solve the bitstream extraction problem.
+In both methods, the accuracy of distortion estimation affects the performance a lot.
+With a packet's distortion impact accurately estimated, its prioritization order during extraction can be determined.
+Then a priority value can be assigned to it and stored in the bitstream for optimized extraction in the future.
+In \cite{Lim06}, Lim et al.
+treated SVC bitstream as a tree structure and assigned extraction priority accordingly.
+In \cite{Zhu11}, Zhu et al.
+chose to assign priority values derived using the Langrange multiplier method.
+
+In our previous work \cite{Zhang12}, we proposed a linear error model for distortion estimation and priority assignment.
+Good bitstream extraction performance is achieved based on that.
 However, this work assumes that the original video sequence is available for reference, which is not always true.
@@
 \bibitem{Gualdi08}
-G. Gualdi, A. Prati, and R. Cucchiara, ``Video Streaming for Mobile Video Surveillance'', in {\em IEEE Transactions on Multimedia}, vol. 10, no. 6, pp. 1142-1154, 2008.
+G. Gualdi, A. Prati, and R. Cucchiara, ``Video Streaming for Mobile Video Surveillance'', {\em IEEE Transactions on Multimedia}, vol. 10, no. 6, pp. 1142-1154, 2008.
 
@@
 Liu, and W.
-Zhu, ``Measurement and Modeling of Video Watching Time in a Large-Scale Internet Video-on-Demand System'', in {\em IEEE Transactions on Multimedia}, vol.
+Zhu, ``Measurement and Modeling of Video Watching Time in a Large-Scale Internet Video-on-Demand System'', {\em IEEE Transactions on Multimedia}, vol.
 15, no.
@@
 \bibitem{Egilmez14}
-H.
-E.
-Egilmez and A.
-M.
-Tekalp, ``Distributed QoS architectures for multimedia streaming over software defined networks'', in {\em IEEE Transactions on Multimedia}, vol.
-16, no.
-6, pp.
-1597-1609, 2014.
+H. E. Egilmez and A. M. Tekalp, ``Distributed QoS architectures for multimedia streaming over software defined networks'', {\em IEEE Transactions on Multimedia}, vol. 16, no. 6, pp. 1597-1609, 2014.
 
 \bibitem{Li14}
-S. Li et al., ``Flexible Traffic Engineering (F-TE): When OpenFlow Meets Multi-Protocol IP-Forwarding'', in {\em IEEE Communication Letters}, vol. 18, pp. 1699-1702, Oct. 2014.
+S. Li et al., ``Flexible Traffic Engineering (F-TE): When OpenFlow Meets Multi-Protocol IP-Forwarding'', {\em IEEE Communication Letters}, vol. 18, pp. 1699-1702, Oct. 2014.
 
 \bibitem{Xue15}
-N. Xue et al., ``Demonstration of OpenFlow-Controlled Network Orchestration for Adaptive SVC Video Manycast'', in {\em IEEE Transactions on Multimedia}, vol. 17, pp. 1617-1629, Sept. 2015.
+N. Xue et al., ``Demonstration of OpenFlow-Controlled Network Orchestration for Adaptive SVC Video Manycast'', {\em IEEE Transactions on Multimedia}, vol. 17, pp. 1617-1629, Sept. 2015.
 
 \bibitem{DASH}
-T. Stockhammer, ``Dynamic adaptive streaming over HTTP: standards and design principles", in {\em Proceedings of the second annual ACM conference on Multimedia systems}, 2011.
+T. Stockhammer, ``Dynamic adaptive streaming over HTTP: standards and design principles'', {\em Proceedings of the second annual ACM conference on Multimedia systems}, 2011.
 
@@
 \bibitem{SVCOverview}
-H.~Schwarz, D.~Marpe, and T.~Wiegand, ``Overview of the scalable video coding extension of the H.264/AVC standard'', in {\em IEEE Trans.
+H.~Schwarz, D.~Marpe, and T.~Wiegand, ``Overview of the scalable video coding extension of the H.264/AVC standard'', {\em IEEE Trans.
 Circuits.
@@
 D.
-Turck, ``In-Network Quality Optimization for Adaptive Video Streaming Services'', in {\em IEEE Transactions on Multimedia}, vol.
+Turck, ``In-Network Quality Optimization for Adaptive Video Streaming Services'', {\em IEEE Transactions on Multimedia}, vol.
 16, no.
@@
 \bibitem{SVCPerformance}
-M. Wien , H. Schwarz and T. Oelbaum,  ``Performance Analysis of SVC'',  in {\em IEEE Trans. Circuits Syst. Video Technol.}, vol. 17, no. 9, pp. 1194-1203, 2007.
+M. Wien , H. Schwarz and T. Oelbaum,  ``Performance Analysis of SVC'', {\em IEEE Trans. Circuits Syst. Video Technol.}, vol. 17, no. 9, pp. 1194-1203, 2007.
 
@@
 Chen, and Y.
-Tan, ``Energy-Efficient Resource Allocation and Scheduling for Multicast of Scalable Video Over Wireless Networks'', in {\em IEEE Transactions on Multimedia}, vol.
+Tan, ``Energy-Efficient Resource Allocation and Scheduling for Multicast of Scalable Video Over Wireless Networks'', {\em IEEE Transactions on Multimedia}, vol.
 14, no.
@@
 Li, and X.
-Chen, ``Design QoS-aware multi-path provisioning strategies for efficient cloud-assisted SVC video streaming to heterogeneous clients'', in {\em IEEE Transactions on Multimedia}, vol.
+Chen, ``Design QoS-aware multi-path provisioning strategies for efficient cloud-assisted SVC video streaming to heterogeneous clients'', {\em IEEE Transactions on Multimedia}, vol.
 15, no.
@@
 Ohayon, and N.
-Amram, ``Live video streaming with adaptive pre-processing by using scalable video coding'', in {\em Proceedings of IEEE International Conference on Consumer Electronics (ICCE)}, pp.
+Amram, ``Live video streaming with adaptive pre-processing by using scalable video coding'', {\em Proceedings of IEEE International Conference on Consumer Electronics (ICCE)}, pp.
 588-589, 2013.
@@
 \bibitem{Yang14}
-E.
-Yang, Y.
-Ran, S.
-Chen, and J.
-Yang, ``A multicast architecture of SVC streaming over OpenFlow networks'', in {\em Proceedings of IEEE Global Communications Conference (GLOBECOM)}, pp.
-1323-1328, 2014.
+E. Yang, Y. Ran, S. Chen, and J. Yang, ``A multicast architecture of SVC streaming over OpenFlow networks'', {\em Proceedings of IEEE Global Communications Conference (GLOBECOM)}, pp. 1323-1328, 2014.
 
@@
 Cicalo, and V.
-Tralli, ``Distortion-Fair Cross-Layer Resource Allocation for Scalable Video Transmission in OFDMA Wireless Networks'', in {\em IEEE Transactions on Multimedia}, vol.
+Tralli, ``Distortion-Fair Cross-Layer Resource Allocation for Scalable Video Transmission in OFDMA Wireless Networks'', {\em IEEE Transactions on Multimedia}, vol.
 16, no.
@@
 \bibitem{Amonou07}
-I.~Amonou, N.~Cammas, S.~Kervadec, S.~Pateux, ``Optimized Rate-distortion Extraction with Quality Layers in the Scalable Extension of H.264/AVC'' in {\em IEEE Trans.
+I.~Amonou, N.~Cammas, S.~Kervadec, S.~Pateux, ``Optimized Rate-distortion Extraction with Quality Layers in the Scalable Extension of H.264/AVC'', {\em IEEE Trans.
 Circuits Syst.
@@
 \bibitem{Sun09}
-J.~Sun, W.~Gao, D.~Zhao, W.~Li, ``On Rate-distortion Modeling and Extraction of H.264/SVC Fine-Granular Scalable Video'' in {\em IEEE Trans.
+J.~Sun, W.~Gao, D.~Zhao, W.~Li, ``On Rate-distortion Modeling and Extraction of H.264/SVC Fine-Granular Scalable Video'', {\em IEEE Trans.
 Circuits Syst.
@@
 \bibitem{Maani09}
-E.~Maani, A.~K. Katsaggelos, ``Optimized Bit Extraction Using Distortion Modeling in the Scalable Extension of H.264/AVC'' in {\em IEEE Trans. Image Processing}, vol.~18, no.~9, pp.~2022-2029, 2009.
+E.~Maani, A.~K. Katsaggelos, ``Optimized Bit Extraction Using Distortion Modeling in the Scalable Extension of H.264/AVC'', {\em IEEE Trans. Image Processing}, vol.~18, no.~9, pp.~2022-2029, 2009.
 
 \bibitem{Ramanathan12}
-P.~Ramanathan and N.~Jayant. ``RD optimized bitstream extraction for H. 264/SVC based video streaming'' In {\em Proceedings of IEEE International Conference on Image Processing}, pp. 2241-2244, 2012.
+P.~Ramanathan and N.~Jayant. ``RD optimized bitstream extraction for H. 264/SVC based video streaming'', {\em Proceedings of IEEE International Conference on Image Processing}, pp. 2241-2244, 2012.
 
@@
 K.~Yang, S.~Wan, Y.~Gong, and Y.~Feng.
-``A fast algorithm of bitstream extraction using distortion prediction based on simulated annealing'' In {\em Journal of Visual Communication and Image Representation}, no.7, pp.
+``A fast algorithm of bitstream extraction using distortion prediction based on simulated annealing'', {\em Journal of Visual Communication and Image Representation}, no.7, pp.
 752-759, 2013.
 
+\bibitem{Lim06}
+J. Lim, M. Kin, and S. Hahm, ``An optimization-theoretic approach to optimal extraction of SVC Bitstreams'', ITU-T VCEG
+JVT-U081, October 2006.
+
+\bibitem{Zhu11}
+T. Zhu and X. Zhang, ``Frame distortion estimation and its application to extraction priority assignment for MGS of H. 264/SVC'', {\em Przegląd Elektrotechniczny}, vol. 87, no. 1, pp. 284-289, 2011.
+
 \bibitem{Zhang12}
-W.~Zhang, J.~Sun, J.~Liu and Z.~Guo, ``Optimized bit extraction of SVC exploiting linear error model,'' {\em Proceedings of IEEE International Symposium on Circuits and Systems}, pp.~1887-1890, Seoul, Korea, May 2012.
+W.~Zhang, J.~Sun, J.~Liu and Z.~Guo, ``Optimized bit extraction of SVC exploiting linear error model'', {\em Proceedings of IEEE International Symposium on Circuits and Systems}, pp.~1887-1890, Seoul, Korea, May 2012.
 
 \bibitem{Gao06}
-K. Gao, J. Zhai, J. Li and C. Wang, ``Real-Time scheduling for scalable video coding streaming system'', in {\em IEEE Sarnoff Symposium}, Princeton, NJ, pp. 1-4, Mar. 2006.
+K. Gao, J. Zhai, J. Li and C. Wang, ``Real-Time scheduling for scalable video coding streaming system'', {\em IEEE Sarnoff Symposium}, Princeton, NJ, pp. 1-4, Mar. 2006.
 
@@
 Globisch, Hellge, and T.
-Wiegand, ``Priority-based media delivery using SVC with RTP and HTTP streaming'', in {\em Multimedia Tools And Applications}, vol.
+Wiegand, ``Priority-based media delivery using SVC with RTP and HTTP streaming'', {\em Multimedia Tools And Applications}, vol.
 55, no.
@@
 \bibitem{Winken08}
-M.~Winken, H.~Schwarz, T.~Wiegand, ``Joint Rate-distortion Optimization of Transform Coefficients for Spatial Scalable Video Coding Using SVC'' in {\em Proceedings of IEEE International Conference on Image Processing}, 2008.
+M.~Winken, H.~Schwarz, T.~Wiegand, ``Joint Rate-distortion Optimization of Transform Coefficients for Spatial Scalable Video Coding Using SVC'', {\em Proceedings of IEEE International Conference on Image Processing}, 2008.
 
 \bibitem{H264Overview}
-T.~Wiegand, G.~J.
-Sullivan, G.~Bj$\o$ntegaard, A.~Luthra, ``Overview of the H.264/AVC Video Coding Standard'', in {\em IEEE Trans.
-Circuits Syst.
-Video Technol.}, vol.
-13, no.
-7, pp.~560--576, Jul.
-2003.
+T.~Wiegand, G.~J. Sullivan, G.~Bj$\o$ntegaard, A.~Luthra, ``Overview of the H.264/AVC Video Coding Standard'', {\em IEEE Trans. Circuits Syst. Video Technol.}, vol. 13, no. 7, pp.~560--576, Jul. 2003.
 
@@
 \bibitem{Wong04}
-C.W.Wong, O.C.Au and H.K.Lam, ``PID-based real-time rate control'', in {\em Proceedings of IEEE International Conference on Multimedia and Expo}, 1: 221-224, 2004.
+C.W.Wong, O.C.Au and H.K.Lam, ``PID-based real-time rate control'', {\em Proceedings of IEEE International Conference on Multimedia and Expo}, 1: 221-224, 2004.
 
 \bibitem{Yang10}
-J. Yang, Y. Sun, Y. Zhou, S. Sun, ``Incremental rate control for H.264 scalable video coding'', in {\em IEEE Global Telecommunications Conference}, Miami, Florida, Dec. 2010.
+J. Yang, Y. Sun, Y. Zhou, S. Sun, ``Incremental rate control for H.264 scalable video coding'', {\em IEEE Global Telecommunications Conference}, Miami, Florida, Dec. 2010.
 
 \bibitem{Li98}
-B. Li and K. Nahrstedt  ``A control theoretical model for quality of service adaptations'', in {\em Proceedings of Sixth International Workshop on Quality of Service}, 1998.
+B. Li and K. Nahrstedt  ``A control theoretical model for quality of service adaptations'', {\em Proceedings of Sixth International Workshop on Quality of Service}, 1998.
 
 \bibitem{Li99}
-B. Li and K. Nahrstedt, ``A control-sased middleware framework for Quality-of-Service adaptations'', in {\em IEEE J. Selected Areas in Comm.}, vol. 17, no. 9, pp. 1632-1650, Sept. 1999.
+B. Li and K. Nahrstedt, ``A control-sased middleware framework for Quality-of-Service adaptations'', {\em IEEE J. Selected Areas in Comm.}, vol. 17, no. 9, pp. 1632-1650, Sept. 1999.
 
 \bibitem{Ziegler42}
-J. B. Ziegler and N. B. Nichols, ``Optimum settings for automatic controllers'', in {\em ASME Trans.}, pp. 759-768, 1942.
+J. B. Ziegler and N. B. Nichols, ``Optimum settings for automatic controllers'', {\em ASME Trans.}, pp. 759-768, 1942.
 
@@
 \bibitem{HEVC}
-G.~J.~Sullivan, J.-R.~Ohm, W.-J.~Han, and T.~Wiegand, ``Overview of the High Efficiency Video Coding (HEVC) standard'' in {\em IEEE Trans.
+G.~J.~Sullivan, J.-R.~Ohm, W.-J.~Han, and T.~Wiegand, ``Overview of the High Efficiency Video Coding (HEVC) standard'', {\em IEEE Trans.
 Circuits Syst.

### 2015-12-02 tmm.tex
Add explanation to LEM and its verification experiment

@@
 To provide better network condition, some researchers choose to adopt the new Software Defined Networking (SDN) architecture \cite{Egilmez14}.
-Based on a successful SDN paradigm named OpenFlow, noticeable results are achieved, e.g., a solution for improving network throughput in hybrid network \cite{Li14} and a demonstration
-of OpenFlow-controlled network orchestration for video manycast \cite{Xue15}.
+Based on a successful SDN paradigm named OpenFlow, noticeable results are achieved, e.g., a solution for improving network throughput in hybrid network \cite{Li14} and a demonstration of OpenFlow-controlled network orchestration for video manycast \cite{Xue15}.
 Although these studies have offered a promising alternative, currently traditional best-effort networks still dominate, and the variety of users' network environment remains to be one of the biggest challenges for video streaming.
@@
 
-While these studies mostly focus on Quality of Service (QoS) optimization and resource allocation for specific networks, there are two key problems that need to be primarily addressed when adopting SVC in adaptive video streaming.
+While these studies mostly focus on Quality of Service (QoS) optimization and resource allocation for specific networks, there are two key problems that need to be primarily addressed in the SVC adaptive video streaming system.
 First, as the prerequisite of bitrate adaption, the whole bitstream needs to be extracted so that sub-streams with various bitrates can be obtained.
@@
 Quality control is the second problem we will address in this paper.
-The result of a quality control algorithm gives the suitable bitrate for current transmission, which is directly related to the change of video quality delieverd the user.
+The result of a quality control algorithm gives the suitable bitrate for current transmission, which is directly related to the change of the video quality delivered to the user.
 In an SVC streaming system, the bitrate determined by the quality control algorithm is used as the constraint under which bitstream extraction is performed.
@@
 
-For a quality control algorithm, there are three targets that should be achieved.
-First is to ensure the continuity of video playing.
+For a quality control algorithm, there are three targets to be achieved.
+The first is to ensure the continuity of video playing.
 In real-time streaming system, each data packet has its own playtime, which is also regarded as the deadline of the transmission.
@@
 Suppose we keep sending video data in a low bitrate (with low video quality as well), neither the playback will pause nor any quality fluctuation will happen.
-However, a low video quality is certainly not what we want.
-
-The state-of-the-art solutions to avoid video pause in client media player mainly focus on how to select and schedule the video packets.
+However, a low video quality is certainly not what the user want.
+
+The state-of-the-art solutions to avoid playback pause in client media player mainly focus on how to select and schedule the video packets.
 In \cite{Gao06}, K.
@@
 However, it only provides conservative quality change, which makes its reaction so slow that sometimes media player may have already stopped due to lack of video data before quality drops.
-Furthermore, this algorithm does not keep track of the bandwidth change so it cannot adjust the video quality accordingly.
+Furthermore, this algorithm does not keep track of the bandwidth change so it can only adjust the video quality based on current state.
 Quality oscillation might occur in this algorithm.
 
-The following of this paper will present our solution for each of the problems in detail.
+The following of this paper will present our solution for each of the problems.
 The solutions then work together and serve as a solid foundation for a practical adaptive video streaming system.
-It should be noted that, in practical video streaming systems there are other issues that need to be addressed.
+It should be noted that, in practical streaming systems there are other issues to be addressed.
 One of them is occasional packet loss during transmission, which will cause decoding errors and corrupted images, resulting in an significant degradation of video quality.
 How to avoid or even recover from packet loss/error is an important research topic that is popular in both networking and multimedia community.
-However, in this paper which focuses on server-side adaptation, packet loss is not handled and we simply assume that the video stream will be successfully delivered to the client.
+However, in this paper which focuses on server-side adaptation, packet loss is not handled and the video stream is assumed to be successfully delivered to the client.
 
@@
 
-In H.264/AVC, the decoding process involves a linear feature described in \cite{Winken08}, neglecting any rounding, clipping, and deblocking filtering operation.
-According to this feature, the main steps in H.264/AVC coding -- prediction, transform and quantization -- are proximately linear operations, and the whole coding process can be expressed in a matrix format as follows:
+In H.264/AVC, the decoding process involves a linear feature described in \cite{Winken08}.
+According to this feature, the main steps of decoding -- prediction, transform and quantization -- are proximately linear operations (neglecting any rounding, clipping, and deblocking filtering), and the whole process can be expressed in a matrix format as follows:
 \begin{equation}
@@
 \end{equation}
-It means, the reconstructed samples of a Group of Pictures (GOP), denoted by $s$, can be viewed as a linear combination of previously reconstructed samples in the GOP, the residual samples, and a static predictor.
-In (\ref{eq:linear}), $c$ refers to the transform coefficient values and $p$ is a static predictor; ${\rm\bf M}$ and ${\rm\bf T}$ are square matrices such that the product ${\rm\bf M} \cdot s$ gives the Motion Compensated Prediction (MCP) signal and ${\rm\bf T} \cdot c$ gives the residual values.
-The actual values of ${\rm\bf M}$ depend on the selected macroblock types, reference indices and motion vectors, whereas the actual values of ${\rm\bf T}$ depend on the chosen Quantization Parameter (QP) values.
-
-We apply the above linear decoding model to the case of quality scalability of SVC and get a Linear Error Model (LEM).
+It means, the reconstructed samples of a Group of Pictures (GOP), denoted by $s$, can be viewed as a linear combination of previously reconstructed samples in the GOP, the residuals, and a static predictor.
+In (\ref{eq:linear}), $c$ refers to the transform coefficients and $p$ is a static predictor; ${\rm\bf M}$ and ${\rm\bf T}$ are square matrices such that ${\rm\bf M} \cdot s$ gives the Motion Compensated Prediction (MCP) signal and ${\rm\bf T} \cdot c$ gives the residuals.
+The actual values of ${\rm\bf M}$ depend on the selected macroblock types, reference indices and motion vectors, whereas the actual values of ${\rm\bf T}$ depend on the chosen Quantization Parameter (QP).
+
+We apply the above linear decoding feature to the case of quality scalability of SVC and get a Linear Error Model (LEM).
 According to (\ref{eq:linear}), for a bitstream just containing the base layer, we have:
@@
 \end{equation}
-where $i$ refers to an enhancement packet as an element of $I_1$.
+where $i$ refers to an enhancement packet in the set $I_1$.
 $c_i$ is a vector containing coefficients within the enhancement packet $i$.
 ${\rm\bf T_i}$ is the transform matrix depending on the QP value of $i$.
-${\rm\bf T}_i \cdot c_i$ gives the residual sample values decoded from $i$.
+${\rm\bf T}_i \cdot c_i$ gives the residual values decoded from $i$.
 
@@
 Obviously, $e_j$ is only determined by packet $j$, and has no relation with other enhancement packets.
-This value is called the ``error vector'' of packet $j$, which represents the pixel value error caused by discarding the packet $j$.
+The value $e_j$ is defined as ``error vector'' of packet $j$, which represents the pixel value error caused by discarding the packet $j$.
 We can obtain the error vector of each enhancement packet by subtraction between video sequences reconstructed from two enhancement packet subsets $I_1$ and $I_2$, with $I_1 \subseteq I_2$ and $I_2 \setminus I_1 =\{j\} $.
-Once all packets' error vectors are obtained, the distortion caused by discarding a group of packets can be estimated by adding up the error vector of each packet in the group.
+Once all enhancement packets' error vectors are obtained, the distortion caused by discarding a set of enhancement packets can be estimated by adding up the error vector of each packet in the set.
+For example, if enhancement packets $k$, $l$, $n$ are removed from a bitstream, then the difference of the reconstruction before and after the removal is supposed to be $e = e_k + e_l + e_m$.
+The reason for this sum to be rational is twofold: first, unlike MSE or PSNR, error vector is simply the difference of raw pixel values, with no quadratic calculation ever involved; second, each enhancement packet adds its own refinement to the pixel values during the reconstruction, due to the linear feature of the decoding process (see the derivation above).
+The second point is conditionally true though, as noted below.
 
@@
 It would need too many decoding times to get the error vectors of all enhancement packets if we calculate them one at a time.
-In order to acquire error vectors of all enhancement packets efficiently, we separate all enhancement packets into several groups, such that in each group multiple error vectors can be obtained independently at the same time.
+In order to acquire error vectors of all enhancement packets efficiently, we separate all enhancement packets into several groups, such that in each group multiple error vectors can be obtained at the same time.
 
@@
 Base layer packets are colored black, and enhancement packets with the same color are allocated in one group.
-In each group, the enhancement packets' error vectors can be calculated simultaneously, since the pixel errors they caused are not interfered with each other.
-For example, the loss of packet 8 would bring about distortion only in frame 1, 2 and 3, while packet 10 only in frame 5, 6 and 7 (frame number starts from 0).
-So we can do subtraction for this group, for one time, to gain error vectors $e_{8}$ and $e_{10}$, for both packets 8 and 10, as well as peer packets in all other GOPs.
+In each group, the enhancement packets' error vectors can be calculated simultaneously, since the pixel errors they can cause are not interfered with each other.
+For example, the removal of packet 8 would cause pixel errors only in frame 1, 2 and 3, while packet 10 only in frame 5, 6 and 7 (frame index starts from 0).
+So we can do subtraction only once for this group, to obtain error vectors $e_{8}$ and $e_{10}$, for both packets 8 and 10, as well as peer packets in all other GOPs.
 Note that these error vectors are highly sparse ones, because the discarding of a single enhancement packet can bring distortion only to a limited number of frames.
@@
 For the example in Fig.
-\ref{fig:GOP_Structure}, $L_Q = 3$ and $L_T = 4$, so the theoretical extraction-and-decoding number is $(3 - 1) \times 4 = 8$.
+\ref{fig:GOP_Structure}, $L_Q = 3$ and $L_T = 4$, so the extraction-and-decoding number is $(3 - 1) \times 4 = 8$.
 However, we have to do the same manipulation for $L_Q - 1 = 2$ more times, to dissociate the distortion impact of ``key frame'' \cite{H264Overview} (e.g.
@@
 The loss of one enhancement packet in a key frame would bring distortion to two neighboring GOPs.
-As an instance, the loss of packet 4 would propagate drift into frame 1 to 15, which would interfere with the distortion impact of packets in frame 0 and 16 (packet 1, 2 and 19, 20).
+As an instance, the loss of packet 4 would propagate error into frame 1 to 15, which would interfere with the distortion impact of packets in frame 0 and 16 (packet 1, 2 and 19, 20).
 So key frame enhancement packets within the same quality layer (e.g.
@@
 
-Based on the linear error model described above, we can obtain error vectors of all enhancement packets.
-Then we can estimate the distortion caused by discarding any set of enhancement packets, by adding up the error vector of each packet in that set.
+Based on the LEM, we can estimate the distortion caused by discarding any set of enhancement packets, by adding up the error vector of each packet in that set.
 
@@
 
-Before using the linear error model, we conduct an experiment to verify it.
-All bitstreams in the experiment are encoded with the JSVM encoder, where the same GOP structure as illustrated in Fig.
-\ref{fig:GOP_Structure} and CABAC entropy coding are used.
+Before using the estimation based on LEM, we conduct an experiment to verify it.
+All bitstreams in the experiment are encoded with the JSVM encoder, where the GOP structure as illustrated in Fig.
+\ref{fig:GOP_Structure} and the CABAC entropy coding are used.
 Each bitstream contains one base layer and one enhancement layer, with QP = 33 and QP = 27, respectively.
 The enhancement layer is further divided into 2 Medium Grain Scalability (MGS) layers by configuring the MGS vector to separate the transform coefficients into two groups (containing 4 and 12 coefficients respectively).
-Random combinations of enhancement packets are removed from a video bitstream, and the distortion estimated by the linear error model are compared with the actual distortion caused by the removal.
+Random combinations of enhancement packets are removed from a bitstream, and the distortion estimated by the linear error model are compared with the actually calculated distortion.
+Decoding is performed by JSVM decoder, and distortion estimation or calculation is done by Matlab.
 One comparison result for the test sequence {\em Foreman} (only first 33 frames are used) is shown in Fig.
@@
 In this subsection, we utilize the linear error model to enable R-D optimized bitstream extraction.
-Since finding the global optimal solution of the bitstream extraction problem is impractical, our bitstream extraction algorithm uses a greedy method \cite{GreedyAlgo} to get a sub-optimal solution.
+A greedy-like \cite{GreedyAlgo} bitstream extraction algorithm is proposed.
 Similar to the greedy solution of the ``0-1 Knapsack Problem", every time a packet is to be discarded, we choose the packet that has the minimal R-D impact.
@@
 \begin{description}
-\item[1)] Initially, the sequence error vector, $e_{seq}$, is set to $e_{full}$.
+\item[1)] Initially, the sequence error vector, $e_{seq}$, is set to $e_{full}$, which is $e_{full}$ is defined in Eqation \).
 \item[2)] Within the packets that can be discarded, find the packet $m$ having the least RD impact on the sequence, \textit{i.e. }

### 2015-12-02 tmm.tex
Begin to improve the section of quality control

@@
 Quality control is the second problem we will address in this paper.
-The result of a quality control algorithm gives the suitable bitrate for current transmission, which is directly related to the change of the video quality delivered to the user.
+The result of a quality control algorithm gives the suitable bitrate for transmission, which is directly related to the change of the video quality delivered to the user.
 In an SVC streaming system, the bitrate determined by the quality control algorithm is used as the constraint under which bitstream extraction is performed.
@@
 In this subsection, we utilize the linear error model to enable R-D optimized bitstream extraction.
-A greedy-like \cite{GreedyAlgo} bitstream extraction algorithm is proposed.
-Similar to the greedy solution of the ``0-1 Knapsack Problem", every time a packet is to be discarded, we choose the packet that has the minimal R-D impact.
+Similar to the greedy \cite{GreedyAlgo} solution of the ``0-1 Knapsack Problem", every time a packet is to be discarded, we choose the packet that has the minimal R-D impact.
 A packet's R-D impact is mathematically measured by:
@@
 \label{eq:rd_impact}
-\Phi_{i} = \dfrac{\partial D}{\partial R} \: ,
+\Phi = \dfrac{\partial D}{\partial R} \: ,
 \end{equation}
@@
 
-The detailed discarding and priority assignment process is described below:
-\begin{description}
-\item[1)] Initially, the sequence error vector, $e_{seq}$, is set to $e_{full}$, which is $e_{full}$ is defined in Eqation \).
-\item[2)] Within the packets that can be discarded, find the packet $m$ having the least RD impact on the sequence, \textit{i.e. }
+For long video sequences, an optimization window containing a certain number of frames is usually needed, and the priority assignment and bitstream extraction is conducted independently in each window.
+Suppose the size of the optimization window is $K$, i.e., there are $K$ frames involved in the above process, and each frame contains $L_Q$ quality layers (one base layer and $L_Q-1$ enhancement layers).
+Then the total number of enhancement packets that can be discarded is $K \cdot (L_Q-1)$, and in every greedy step, there are at most $K$ packets, i.e., the packets currently at the top of every frame (see analysis in \ref{subsec:analysis-extraction}), that can be selected to discard.
+Given that, the priority assignment process in each optimization window can be described in Algorithm \ref{algo:greedy}, with some terms in it explained below.
+The initial value $e_{full}$ is the error between the video sequence decoded from full enhancement packets and the original video sequence, already introduced in (\ref{eq:subset_error}).
+$\Phi_m$ is defined as:
 \begin{equation}
@@
 \end{equation}
-where $I_{top}$ stands for the top-layer packets, those currently able to be discarded. The RD impact of a packet is calculated based on (\ref{eq:rd_impact}), as follows: 
+where $I_{top}$ stands for the top-layer packets, those currently able to be discarded, and $\Phi_i$ denotes the RD impact of packet $i$. $\Phi_i$ is calculated based on (\ref{eq:rd_impact}):
 \begin{equation}
 \label{eq:R-D_impact_i}
-\Phi_i = \dfrac{\partial D}{\partial R} = \dfrac{PSNR(e_{seq}) - PSNR(e_{seq} + e_i)}{SIZE(i)} \: ,
-\end{equation}
-where $PSNR(*)$ means to obtain PSNR from the error vector, and $SIZE(i)$ is the size of packet $i$.
-\item[3)]The packet, $m$, is then removed from the bitstream, and its error vector is added to the sequence's error vector, \textit{i.e.}
-\begin{equation}
-\label{eq:error_update}
-e_{seq} = e_{seq} + e_m \: .
-\end{equation}
-\item[4)]The process from 2) to 3) is repeated until all enhancement packets are discarded, and every packet is assigned a priority value according to the removing order.
-\end{description}
-
-For long video sequences, an optimization window containing a certain number of frames is usually needed, and the priority assignment and bitstream extraction is conducted independently in each window.
-Suppose the size of the optimization window is $K$, i.e., there are $K$ frames involved in the above priority assignment process, and each frame contains $L_Q$ quality layers (one base layer and $L_Q-1$ enhancement layers).
-Then the number of top layer packets in step 2) of the process is $K$, and the total number of packets that can be discarded is $K \cdot (L_Q-1)$.
-Given that, the priority assignment process in each optimization window can be more specifically described in Algorithm \ref{algo:greedy}.
-It is easy to see that the computational complexity of this priority assignment algorithm is $O(K^2)$.
-Note that this computational complexity is negligible compared with the decoding process needed in the error vector acquisition.
+\Phi_i = \dfrac{\partial D}{\partial R} = \dfrac{PSNR(e_{seq}) - PSNR(e_{seq} + e_i)}{SIZE(i)} \:,
+\end{equation}
+where $SIZE(i)$ is the size of packet $i$, and $PSNR(*)$ is the function to obtain PSNR from an error vector.
+To be clear, PSNR is defined via mean squared error (MSE), i.e., the average of the squares of the elements in the error vector.
 
@@
 \begin{algorithmic}
-    \STATE Set $e_{seq}$ to $e_{full}$, and set $p$ to 0.
+    \STATE Initialize $e_{seq}$ to $e_{full}$, and $p$ to 0.
     \WHILE{$p < K \cdot (L_Q - 1)$}
-	    \FOR{$K$ top layer packets}
-		    \STATE Find the packet $m$ which has least RD impact
+	    \FOR{the $K$ top layer packets}
+		    \STATE Find the packet $m$ which has least RD impact $\Phi_m$
 		\ENDFOR
@@
 		\STATE Remove $m$ from the sequence
-		\STATE Set $e_{seq}$ to $e_{seq} + e_m$, and set $p$ to $p+1$
+		\STATE Update $e_{seq}$ to $e_{seq} + e_m$, and update $p$ to $p+1$
     \ENDWHILE
@@
 
-A larger optimization window means each time we have more packets to compare and determine their priorities.
-Therefore, choosing a larger $K$ has the potential of more optimized extraction.
-However, doing this will also increase the computational complexity as well as the memory used to store the error vectors.
-Besides, if the 6-bit priority identifier field of the NALU header is used to store the priority values, only a range of 0$\sim$63 is supported, which also limits the value of $K$.
+It is easy to see that the computational complexity of this priority assignment algorithm is $O(K^2)$.
+Note that this computational complexity is negligible compared with the decoding process needed in the error vector acquisition.
+With a larger optimization window we have more packets to compare and determine their priorities, which will potentially result in more optimized extraction.
+However, doing this will also increase the computational complexity and, more noticeably, the memory used to store the error vectors.
+Besides, if the priority values are to be stored and signaled using the 6-bit priority identifier field of the NALU header \cite{Amonou07}, only a range of 0$\sim$63 is supported, which also limits the value of $K$.
 
@@
 
-In some scenarios, the priority assignment and bitstream extraction needs to be conducted without access to the original YUV sequence.
-For example, if the bitstream extraction is not done at the encoding side, it's most likely that the original sequence is not available.
+In some scenarios, the priority assignment and bitstream extraction needs to be conducted without access to the original video sequence.
 This would make the bitstream extraction a more difficult problem, since the distortion is harder to obtain for lacking of reference signal.
-Comparing to the problem of SVC bitstream extraction with reference, this kind of ``no-reference bitstream extraction'' problem is actually more frequently encountered in real practice.
-In this subsection, we consider this no-reference problem and modify the proposed algorithm to meet the special characteristic caused by lacking of reference.
-
-In the no-reference case, since we do not have access to the original sequence, we can not get the error between the video sequence decoded from full enhancement packets and the original sequence, which is $e_{full}$ used above.
-A straightforward idea is to set $e_{full}$ to zero, meaning we calculate distortion with respect to the fully reconstructed signal, rather than to the original sequence.
+The ``no-reference bitstream extraction'' problem is actually more frequently encountered in real practice, since it is common that streaming service provider only have the compressed bitstream rather than the video source.
+In this subsection, we consider this no-reference case and modify the proposed algorithm to meet the special characteristic caused by lacking of reference.
+
+Without the original video sequence, we can not get the error between the video sequence decoded from full enhancement packets and the original sequence, which is $e_{full}$ used in \ref{algo:greedy}.
+A straightforward idea is to set $e_{full}$ to zero, meaning all distortions are calculated with respect to the fully reconstructed signal, rather than to the original sequence.
 However, simply doing so causes the algorithm to perform badly in experiments.
-We find that, since discarding some enhancement packets will not bring much significant error relative to the fully reconstructed signal, the calculated PSNR values are too large to well represent the real distortion.
+It is found that, since discarding some enhancement packets will not bring much significant error, the calculated PSNR values are too large to well represent the real distortion.
 To address this issue, instead of calculating PSNR, we directly use MSE of all pixels as the distortion criteria in the priority assignment algorithm.
@@
 After each packet is assigned a priority value and optimized extraction is made possible, the video stream now can well adapt to different data rates.
-Next, we propose the quality control algorithm based on the PID mechanism, which is responsible for determining a suitable data rate according to current bandwidth condition.
+Next, we propose the quality control algorithm based on the PID mechanism, which is responsible for determining the suitable data rate for transmission according to current network condition.
 
@@
 
-PID control \cite{PID}\cite{Astrom02} is a control loop feedback mechanism commonly used in industrial control systems.
+PID controller \cite{PID}\cite{Astrom02} is a control loop feedback mechanism commonly used in industrial control systems.
 \textit{Process variable} and \textit{setpoint} are two core concepts in PID control.
@@
 The setpoint is the target for this control system to reach.
-The goal of PID control is to minimize the error between process variable and setpoint by adjusting system inputs.
+The goal of PID control is to minimize the error between process variable and setpoint by adjusting some control variable.
 The controller output $u(t)$ is defined as follows:
-
 \begin{equation}
@@
 where $e(t)$ represents the error between process variable and setpoint at time $t$.
-$K_p$, $K_i$, and $K_d$ here are tuning parameters representing the proportional gain, integral gain and derivative gain respectively.
-Proportional part directly relates to the change of the process variable, and is also the main factor to adjust the process variable towards setpoint.
-There might be oscillations and steady-state errors in a pure proportional system, and they can be reduced or eliminated by adding the integral part.
-The appearance of derivative part is to predict future errors, so that the system tends to become steady early and quickly.
-The result of (\ref{eq:pid-output}) is used to manipulate the system input of next moment to adjust process variable towards setpoint.
+$K_p$, $K_i$, and $K_d$ here are tuning parameters representing the proportional gain, integral gain and derivative gain, respectively.
+The result of (\ref{eq:pid-output}) is used for manipulating the system to make process variable change towards setpoint.
 
 As an effective and flexible control technique, PID control has been used to solve all kinds of control problems.
-In the area of video coding, we notice that PID is utilized to design rate control algorithms by many papers.
-For instance, in \cite{Wong04} a PID-based real time rate control scheme is proposed to trade-off between spatial and temporal quality and smooth the video quality between frames; in \cite{Yang10}, the authors designed an incremental rate control algorithm for H.264/SVC, in which the PID method is used to provide robust buffer control for each layer.
-We also notice that some researchers have proposed theoretical model or middle-ware framework for QoS adaptation \cite{Li98}\cite{Li99}, with PID as the basic control concept.
+In the area of video coding, we notice that PID is utilized to design rate control algorithms (rate control of video coding is mainly to adjust the encoding parameters for every frame, so that the bits are appropriately allocated to avoid buffer overflow and achieve desired bitrate) \cite{Wong04}\cite{Yang10}.
+We also notice that some researchers have proposed theoretical model or middle-ware framework for QoS adaptation \cite{Li98}\cite{Li99}, with PID as the basic control scheme.
 However, we have not found any paper that integrates PID method into the quality control of video streaming.
 While rate control of video coding and quality control of video streaming are two different problems, they do share some common properties, such as the buffer mechanism and the requirement for smoothness.
-That inspires us to design a PID-based quality control algorithm and utilize it to deliver best video quality with least quality fluctuation.
+That inspires us to design a PID-based quality control algorithm and utilize it to deliver better video quality to the user.
 

### 2015-12-02 tmm.tex
Update some figures
Reduce all figures to 90%
Unify phrase usage and add comment on the optimality of the greedy solution

@@
 \begin{abstract}
-To cope with the challenge brought by bandwidth fluctuation and provide the user with best online video watching experience, an adaptive video streaming system which can adjust video quality according to actual bandwidth condition is proposed based on the Scalable Video Coding (SVC) extension of H.264/AVC.
+To cope with the challenge brought by bandwidth fluctuation and provide the user with best online video watching experience, an adaptive video streaming system which can adjust video quality according to actual network condition is proposed based on the Scalable Video Coding (SVC) extension of H.264/AVC.
 First, a simple and effective linear error model is proposed and verified for quality scalability of SVC.
@@
 Based on a successful SDN paradigm named OpenFlow, noticeable results are achieved, e.g., a solution for improving network throughput in hybrid network \cite{Li14} and a demonstration of OpenFlow-controlled network orchestration for video manycast \cite{Xue15}.
-Although these studies have offered a promising alternative, currently traditional best-effort networks still dominate, and the variety of users' network environment remains to be one of the biggest challenges for video streaming.
+Although these studies have offered a promising alternative, currently traditional best-effort networks still dominate, and the variety of users' network condition remains to be one of the biggest challenges for video streaming.
 A user might use different types of network (Ethernet, Wi-Fi, Cellular, etc.) and might also switch from one type to another on going (e.g., from Wi-Fi to Cellular).
@@
 Within such an environment, bandwidth fluctuation is inevitable, and it would be difficult or impossible for the user to get best watching experience if the video is streamed at a constant bitrate.
-To cope with this challenge, the video streaming system should be able to automatically adjust the video's bitrate or quality according to the bandwidth change.
+To cope with this challenge, the video streaming system should be able to automatically adjust the video's bitrate or quality according to the network condition.
 In other words, the video streaming system needs to be adaptive.
@@
 \centering
-\includegraphics[width = 1.0\linewidth]{Bitstream-Extraction.jpg}
+\includegraphics[width = 0.9\linewidth]{Bitstream-Extraction.jpg}
 \caption{Bitstream extraction of SVC \label{fig:Bitstream-Extraction}}
@@
 
-Particularly, if the difference of $I_2$ and $I_1$ is a single enhancement packet $j$, i.e.
-$I_2 \setminus I_1 = \{j\}$, then according to (\ref{eq:minus2}), the difference of the two reconstruction vectors can be written as
+Particularly, if the difference of $I_2$ and $I_1$ is a single enhancement packet $j$, i.e., $I_2 \setminus I_1 = \{j\}$, then according to (\ref{eq:minus2}), the difference of the two reconstruction vectors can be written as
 \begin{equation}
@@
 \centering
-\includegraphics[width = 1.0\linewidth]{GOP-Structure.png}
+\includegraphics[width = 0.9\linewidth]{GOP-Structure.png}
 \caption{Group of pictures (GOP) in SVC \label{fig:GOP_Structure}}
@@
 \centering
-\includegraphics[width = 1.0\linewidth]{ModelVerification.png}
+\includegraphics[width = 0.9\linewidth]{ModelVerification.png}
 \caption{Comparison of actual and estimated distortion for sequence {\em Foreman} \label{fig:model_verification}}
@@
 In this subsection, we utilize the linear error model to enable R-D optimized bitstream extraction.
-Similar to the greedy \cite{GreedyAlgo} solution of the ``0-1 Knapsack Problem", every time a packet is to be discarded, we choose the packet that has the minimal R-D impact.
+Since finding the global optimal solution of the bitstream extraction problem is impractical, our bitstream extraction algorithm uses a greedy method \cite{GreedyAlgo} to get a sub-optimal solution.
+Note that the greedy algorithm is able to find a local optimum.
+However, the gap between the local optimum and the global optimum is uncertain.
+Similar to the greedy solution of the ``0-1 Knapsack Problem", every time a packet is to be discarded, we choose the packet that has the minimal R-D impact.
 A packet's R-D impact is mathematically measured by:
@@
 Given that, the priority assignment process in each optimization window can be described in Algorithm \ref{algo:greedy}, with some terms in it explained below.
-The initial value $e_{full}$ is the error between the video sequence decoded from full enhancement packets and the original video sequence, already introduced in (\ref{eq:subset_error}).
+The initial value $e_{full}$ is the error between the video sequence decoded from full enhancement packets and the original video sequence, as already introduced in (\ref{eq:subset_error}).
 $\Phi_m$ is defined as:
@@
 \begin{algorithm}
-\caption{Greedy-like bitstream extraction algorithm}
+\caption{Greedy-like priority assignment algorithm}
 \label{algo:greedy}
 \begin{algorithmic}
-    \STATE Initialize $e_{seq}$ to $e_{full}$, and $p$ to 0.
-    \WHILE{$p < K \cdot (L_Q - 1)$}
-	    \FOR{the $K$ top layer packets}
-		    \STATE Find the packet $m$ which has least RD impact $\Phi_m$
+    \STATE Initialize $e_{seq}$ to $e_{full}$, and $q$ to 0.
+    \WHILE{$q < K \cdot (L_Q - 1)$}
+	    \FOR{the (at most) $K$ top layer packets}
+		    \STATE Find the packet $m$ which has the least RD impact $\Phi_m$
 		\ENDFOR
-		\STATE Set the priority value of packet $m$ to $p$
+		\STATE Set the priority value of packet $m$ to $q$
 		\STATE Remove $m$ from the sequence
-		\STATE Update $e_{seq}$ to $e_{seq} + e_m$, and update $p$ to $p+1$
+		\STATE Update $e_{seq}$ to $e_{seq} + e_m$, and update $q$ to $q+1$
     \ENDWHILE
@@
 It is easy to see that the computational complexity of this priority assignment algorithm is $O(K^2)$.
-Note that this computational complexity is negligible compared with the decoding process needed in the error vector acquisition.
-With a larger optimization window we have more packets to compare and determine their priorities, which will potentially result in more optimized extraction.
-However, doing this will also increase the computational complexity and, more noticeably, the memory used to store the error vectors.
-Besides, if the priority values are to be stored and signaled using the 6-bit priority identifier field of the NALU header \cite{Amonou07}, only a range of 0$\sim$63 is supported, which also limits the value of $K$.
+Note that, however, the computation in the priority assignment process is actually very insignificant compared with the decoding process needed in the error vector acquisition.
+A larger optimization window means we have more packets to compare and determine their priorities, which will potentially result in more optimized extraction.
+However, doing this will also increase the computational complexity and, more noticeably, increase the memory used to store the error vectors.
+Besides, if the priority values are to be stored and signalled using the 6-bit priority identifier field of the NALU header \cite{Amonou07}, only a range of 0$\sim$63 is supported, which also limits the value of $K$.
 
@@
 
-After each packet is assigned a priority value and optimized extraction is made possible, the video stream now can well adapt to different data rates.
-Next, we propose the quality control algorithm based on the PID mechanism, which is responsible for determining the suitable data rate for transmission according to current network condition.
+After each packet is assigned a priority value and optimized extraction is made possible, the video stream now can well adapt to different bitrates.
+Next, we propose the quality control algorithm based on the PID mechanism, which is responsible for determining the suitable bitrate for transmission according to current network condition.
 
@@
 
-The video quality is a continuous value.
-In practical operation, it is not possible to control it at an arbitrary precision.
-So we propose a \textit{quality level} concept as the discrete description of the video quality.
+The video quality is a continuous value, and it is impractical to control it at an arbitrary precision.
+Therefore we propose a \textit{quality level} concept as the discrete description of the video quality.
 When the video quality needs to be adjusted, we simply increase or decrease the quality level.
@@
 If \textit{actual\_interval} is smaller than \textit{check\_interval}, it means that less data is pushed to the client, and the pushing is slowed down because bandwidth is relatively low at this time.
-On the other hand, if \textit{actual\_interval} is larger than \textit{check\_interval}, it indicates the bandwidth condition is good and data is being pushed quickly to the client.
-The ratio of these two intervals, i.e., \textit{actual\_check interval ratio}, is in direct proportion to the ratio of the data rate appropriate for bandwidth and the current pushing data rate.
-
-The \textit{actual\_check interval ratio} is suitable for quality control because: 1) this ratio directly reflects the mismatch of current pushing data rate and the bandwidth, and by adjusting data rate according to it, this ratio can be used to accurately change video quality; 2) the desired value of this ratio is 1.0 by definition so we don't need to find the optimized setpoint by mathematical methods or experiments; and 3) it is easy to compute and implement in practical systems.
+On the other hand, if \textit{actual\_interval} is larger than \textit{check\_interval}, it indicates the network condition is good and data is being pushed quickly to the client.
+The ratio of these two intervals, i.e., \textit{actual\_check interval ratio}, is in direct proportion to the ratio of the bitrate suitable for the network condition and the bitrate currently being used.
+
+The \textit{actual\_check interval ratio} is suitable to use in quality control because: 1) this ratio directly reflects the mismatch of current pushing bitrate and the bandwidth, and by adjusting bitrate according to it, this ratio can be used to accurately change video quality; 2) the desired value of this ratio is 1.0 by definition so we don't need to find the optimized setpoint by mathematical methods or experiments; and 3) it is easy to compute and implement in practical systems.
 
@@
 \centering
-\includegraphics[width = 0.9\linewidth]{Intervals.jpg}
+\includegraphics[width = 0.9\linewidth]{Intervals.png}
 \caption{Two timelines in Darwin Streaming Sever (DSS) \label{fig:intervals}}
@@
 Considering that the chosen process variable is a ratio and the corresponding setpoint is 1, we make a little modification to the general PID controller and obtain a ratio-based model.
-In this model, the ratio is directly used to calculate the controller output, and all subtraction operations in original PID equations have been changed to division operations to keep the correctness, as follows:
+In this model, the ratio is directly used to calculate the controller output, and all subtraction operations in original PID equations have been properly changed to division operations to keep the correctness, as follows:
 
@@
 
-In (\ref{eq:ut}), $K_p$, $K_i$, and $K_d$ indicate the tuning parameters for proportional, integral and derivative parts respectively, and $E_p^t$, $E_i^t$, $E_d^t$ stand for the corresponding observed value for each part, which are defined in (\ref{eq:ep})-(\ref{eq:long-check}); the controller output $u_t$ is utilized to calculate an appropriate data rate and further to determine which quality level we should transmit (see Algorithm \ref{algo:control} for more details).
+In (\ref{eq:ut}), $K_p$, $K_i$, and $K_d$ indicate the tuning parameters for proportional, integral and derivative parts respectively, and $E_p^t$, $E_i^t$, $E_d^t$ stand for the corresponding observed value for each part, which are defined in (\ref{eq:ep})-(\ref{eq:long-check}); the controller output $u_t$ is utilized to calculate a suitable bitrate for transmission and further to determine which quality level should be selected (see Algorithm \ref{algo:control} for more details).
 
@@
 Theoretically, the integral part should be recorded and calculated since the system starts.
-In practice, however, bandwidth may vary significantly during the transmission.
-If the integral part was recorded for too long time, it may not reflect the real network status and may slow down the reaction for better quality level.
+In practice, however, bandwidth may change significantly during the transmission.
+If the integral part is recorded for too long time, it may fail to reflect the current network condition and thus slow down the reaction for better quality level.
 A compromise here is to choose a relatively long time, i.e., the time from last quality change till now, for the integral part calculation.
@@
 Moreover, in this model the controller output has intuitive meaning when the three parameters are normalized.
-It is easy to know that all of the three PID parts ($E_p^t$, $E_i^t$, $E_d^t$) are ratios with a value more or less than 1, and the controller output $u_t$ is a weighted average of the three ratios, with the three parameters as weights.
-Therefore the controller output is also a ratio value around 1, which reflects the relationship between the bitrate appropriate for bandwidth condition and the bitrate currently being used.
+It is easy to know that all of the three PID parts ($E_p^t$, $E_i^t$, $E_d^t$) are ratios with a value more or less than 1, and the controller output $u_t$ can be seen as a weighted average of the three ratios, with the three parameters as weights.
+Therefore the controller output is also a ratio value around 1, which reflects the relationship between the bitrate suitable for the network condition and the bitrate currently being used.
 In other words, if the output is larger than 1, then the controller has determined the bitrate should be increased accordingly, and vice versa.
-Use it as a multiplier to manipulate the bitrate currently being used, and we would be able to control the streaming system to match bandwidth condition.
+Use it as a multiplier to manipulate the bitrate currently being used, and we would be able to control the streaming system to match the network condition.
 
@@
 Compared to other scheduling strategies, this quality control algorithm has several advantages.
-First, this algorithm does not just rely on current packet delay or information at fixed time point, therefore quality change may occur at any proper time.
-Second, since the model has taken prediction into account, it is able to decide whether the bandwidth will be high or low enough for the quality level to change in the near future, thus avoiding video quality fluctuation.
-Third, in this algorithm it's not necessary to change one quality level at a time.
+First, this algorithm does not just rely on current packet delay or information at a fixed time point, therefore quality change may occur at any proper time.
+Second, since the model has taken prediction into account, it is able to decide whether the bandwidth will be high or low enough for the quality level to change in the near future, thus to avoid unnecessary quality change.
+Third, in this algorithm it's not obliged to change one quality level at a time.
 This enables fast quality drop to avoid a latent playback pause when bandwidth suddenly decreases, and fast quality rise to provide better video as soon as possible when system starts, resulting in a seamless watching experience where the user can enjoy the video without stopping or waiting.
@@
 Adopting more sophisticated or automated techniques to further optimize the parameters will be done in the future.
-It should also be noted that, in the video quality control algorithm only the data rate and the bandwidth are relevant, not the video content.
+It should also be noted that, in the video quality control algorithm only the bitrate and the bandwidth are relevant, not the video content.
 Therefore once the parameters are chosen they should apply well to different video streams.
@@
 \subfloat[City]{
-\includegraphics[width=0.5\textwidth]{City.jpg}
+\includegraphics[width=0.45\textwidth]{City.jpg}
 \label{fig:City}}
 \subfloat[Foreman]{
-\includegraphics[width=0.5\textwidth]{Foreman.jpg}
+\includegraphics[width=0.45\textwidth]{Foreman.jpg}
 \label{fig:Foreman}}
@@
 \subfloat[Harbour]{
-\includegraphics[width=0.5\textwidth]{Harbour.jpg}
+\includegraphics[width=0.45\textwidth]{Harbour.jpg}
 \label{fig:Harbour}}
 \subfloat[Soccer]{
-\includegraphics[width=0.5\textwidth]{Soccer.jpg}
+\includegraphics[width=0.45\textwidth]{Soccer.jpg}
 \label{fig:Soccer}}
@@
 
-We simulate network fluctuation by adjusting bandwidth around a certain level.
+We simulate bandwidth fluctuation by adjusting bandwidth around a certain level.
 We set this level from 400 to 1400 kbps to reflect different average bandwidth.
@@
 \begin{figure*}[t]
+\centering
 \subfloat[Average quality level of different control algorithms]{
-\includegraphics[width=0.5\textwidth]{Quality-all.png}
+\includegraphics[width=0.45\textwidth]{Quality-all.png}
 \label{fig:quality-all}}
 \subfloat[Quality level variance of different control algorithms]{
-\includegraphics[width=0.5\textwidth]{Variance-all.png}
+\includegraphics[width=0.45\textwidth]{Variance-all.png}
 \label{fig:variance-all}}
@@
 \subfloat[Average quality level of PID and PDF control algorithms]{
-\includegraphics[width=0.5\textwidth]{Quality-two.png}
+\includegraphics[width=0.45\textwidth]{Quality-two.png}
 \label{fig:quality-two}}
 \subfloat[Quality level variance of PID and PDF control algorithms]{
-\includegraphics[width=0.5\textwidth]{Variance-two.png}
+\includegraphics[width=0.45\textwidth]{Variance-two.png}
 \label{fig:variance-two}}
@@
 \subfloat[Bandwidth fluctuates around 400kbps: PSNR average and variance in the original system are 36.00 and 0.30, while in the proposed system are 36.50 (increased by 0.50) and 0.23 (reduced by 0.07).]{
-\includegraphics[width=0.47\textwidth]{Fluctuation-PSNR1.png}
+\includegraphics[width=0.45\textwidth]{Fluctuation-PSNR1.png}
 \label{fig:Fluctuation-PSNR1}}\hfill
 \subfloat[Bandwidth fluctuates around 600kbps: PSNR average and variance in the original system are 37.06 and 0.61, while in the proposed system are 37.32 (increased by 0.26) and 0.33 (reduced by 0.28).]{
-\includegraphics[width=0.47\textwidth]{Fluctuation-PSNR2.png}
+\includegraphics[width=0.45\textwidth]{Fluctuation-PSNR2.png}
 \label{fig:Fluctuation-PSNR2}}
@@
 \subfloat[Bandwidth fluctuates around 800kbps: PSNR average and variance in the original system are 37.92 and 1.24, while in the proposed system are 38.75 (increased by 0.83) and 0.69 (reduced by 0.55).]{
-\includegraphics[width=0.47\textwidth]{Fluctuation-PSNR3.png}
+\includegraphics[width=0.45\textwidth]{Fluctuation-PSNR3.png}
 \label{fig:Fluctuation-PSNR3}}\hfill
 \subfloat[Bandwidth fluctuates around 1000kbps: PSNR average and variance in the original system are 38.28 and 1.30, while in the proposed system are 38.94 (increased by 0.66) and 0.71 (reduced by 0.59).]{
-\includegraphics[width=0.47\textwidth]{Fluctuation-PSNR4.png}
+\includegraphics[width=0.45\textwidth]{Fluctuation-PSNR4.png}
 \label{fig:Fluctuation-PSNR4}}

### 2015-12-02 tmm.tex
Edit the part of PID parameter selection

@@
 As with other PID control systems in the industry, the selection of the three parameters is implementation-dependent and most of the time manual tuning with trial and error is required to achieve optimal results.
-Knowing the impacts of each parameter is useful in the practice of parameter selection.
+Each parameter has impacts on different aspects of the system, and knowing them is useful in the practice of parameter selection.
 Generally,  the proportional part in PID controller affects the system's stability.
@@
 However, a low $K_p$ would result in long rising time that makes the system response slowly.
-In addition to eliminating steady-state error, the integral term also accelerates the movement of the process towards setpoint, which means increasing $K_i$ can reduce rising time.
+In addition to eliminating steady-state error, the integral term also accelerates the movement of the process towards setpoint, which means increasing $K_i$ can reduce the rising time.
 However, since the integral part accumulates errors from the past, it can cause the present value to overshoot the setpoint value, and too much $K_i$ will lead to instability as well.
-This can be compensated by the derivative part, which predicts system behaviour and has the effect of reducing the overshoot, increasing the stability, and improving the settling time (time it takes to reach setpoint after a disturbance).
-The big problem with derivative part is that it is very sensitive to noise, therefore industrial practices indicates that derivative gain $K_d$ should always stay low.
-
-For the proposed quality control algorithm, Ziegler--Nichols method \cite{Ziegler42} is used to select the parameters to obtain better performance.
+These can all be compensated by the derivative part, which predicts system behaviour and has the effect of reducing the overshoot, increasing the stability, and improving the settling time (time it takes to reach setpoint after a disturbance).
+The big problem with derivative part is that it is very sensitive to noise, therefore industrial practices indicates that derivative gain $K_d$ should usually stay low.
+
+For the proposed quality control algorithm, Ziegler--Nichols method \cite{Ziegler42} is used to select the parameters for better performance.
 This method is performed by setting integral and derivative parameters to zero and then tuning $K_p$ to a value $K_u$ until output begins to oscillate with constant amplitude.
@@
 In the following experiments, parameters are chosen as $K_p = 0.22$, $K_i = 0.73$, $K_d = 0.05$ by this method.
-
-In this work we simply use the standard Ziegler--Nichols method which already takes above impacts into consideration and produces acceptably good results.
-Adopting more sophisticated or automated techniques to further optimize the parameters will be done in the future.
-It should also be noted that, in the video quality control algorithm only the bitrate and the bandwidth are relevant, not the video content.
+With these parameters, the PID-controlled streaming system is stable and quickly begins to follow the bandwidth change, as shown by the experimental results in next section.
+
+We choose to use the standard Ziegler--Nichols method because it already takes each parameter's impacts into consideration and produces acceptably good results.
+Adopting more sophisticated or automated techniques to further optimize the parameter selection and controller performance will be our future work.
+Note that, in the video quality control algorithm only the bitrate and the bandwidth are relevant, not the video content.
 Therefore once the parameters are chosen they should apply well to different video streams.

### 2015-12-03 tmm.tex
The submittable version

@@
 \begin{abstract}
-To cope with the challenge brought by bandwidth fluctuation and provide the user with best online video watching experience, an adaptive video streaming system which can adjust video quality according to actual network condition is proposed based on the Scalable Video Coding (SVC) extension of H.264/AVC.
+To cope with the challenge brought by bandwidth fluctuation and improve the experience of watching videos online, an adaptive video streaming system which can adjust video quality according to actual network condition is proposed based on the Scalable Video Coding (SVC) extension of H.264/AVC.
 First, a simple and effective linear error model is proposed and verified for quality scalability of SVC.
 The model exploits the linear feature of pixel value errors and can be used to accurately estimate the distortion caused by discarding any combination of enhancement data packets in an SVC bitstream.
-Then on that basis, a greedy-like algorithm is designed to assign each data packet a priority value according to its Rate-Distortion (R-D) impact, thus enables R-D optimized bitstream extraction under certain bitrate constraint.
+On that basis, a greedy-like algorithm is designed to assign each data packet a priority value according to its Rate-Distortion (R-D) impact, thus enables R-D optimized bitstream extraction under certain bitrate constraint.
 Finally, the Proportional-Integral-Derivative (PID) method is utilized to control the video quality adjustment and determine the suitable bitrate for transmission.
-By monitoring and predicting bandwidth information of the past, the current and the future, the PID-based quality control algorithm can significantly reduce quality fluctuation while still keeping a high quality level.
-Experimental results show that, comparing with the baseline software, the proposed system integrating the above algorithms can achieve much lower video quality fluctuation, with PSNR variance reduced from 1.24 to 0.69, and at the same time deliver higher video quality, with an average PSNR gain of 0.83dB.
+By monitoring and predicting bandwidth information of the past, the current and the future, the PID-based quality control algorithm is able to reduce quality fluctuation while still keeping a high quality level.
+Experimental results show that, comparing with the baseline software, the proposed system integrating the above algorithms can achieve much lower video quality fluctuation, with PSNR variance reduced from 1.24 to 0.69, and at the same time deliver higher video quality, with the PSNR average increased by 0.83 dB.
 The system is deployed at online video website www.7dlive.com and proves to be practically effective.
@@
 \IEEEPARstart{V}{ideo} streaming applications are becoming more and more popular on the Internet.
-Examples of the most common usage scenarios include online Video-on-Demand (VoD), live broadcasting, video-based online education, etc.
-In these applications, video data is constantly delivered to different clients over various transmission channels, and the client media player can begin playing the video before the entire file has been transmitted.
+Examples of the most common usage scenarios include Video-on-Demand (VoD), live broadcasting, video-based online education, etc.
+In these applications, video data is constantly delivered to different clients over various transmission channels, and the client media player can begin to play the video before the entire file has been transmitted.
 Among other features, video streaming makes it easy to watch video anywhere and anytime, which represents the concept of Ubiquitous Multimedia Access (UMA), a very common topic within the multimedia community during the past few years \cite{Gualdi08}.
@@
 To provide better network condition, some researchers choose to adopt the new Software Defined Networking (SDN) architecture \cite{Egilmez14}.
-Based on a successful SDN paradigm named OpenFlow, noticeable results are achieved, e.g., a solution for improving network throughput in hybrid network \cite{Li14} and a demonstration of OpenFlow-controlled network orchestration for video manycast \cite{Xue15}.
-Although these studies have offered a promising alternative, currently traditional best-effort networks still dominate, and the variety of users' network condition remains to be one of the biggest challenges for video streaming.
+Based on a successful SDN paradigm named OpenFlow, noticeable results are achieved.
+For instance, a solution for improving network throughput in hybrid network is proposed in \cite{Li14} and a demonstration of OpenFlow-controlled network orchestration for video manycast is present in \cite{Xue15}.
+Although these studies have offered a promising way to optimize network condition, currently traditional best-effort networks still dominate, and the variety of users' network environment remains to be one of the biggest challenges for video streaming.
 A user might use different types of network (Ethernet, Wi-Fi, Cellular, etc.) and might also switch from one type to another on going (e.g., from Wi-Fi to Cellular).
 Even in the same network, the end-to-end bandwidth will change from time to time, influenced by the overall traffic.
-Within such an environment, bandwidth fluctuation is inevitable, and it would be difficult or impossible for the user to get best watching experience if the video is streamed at a constant bitrate.
-To cope with this challenge, the video streaming system should be able to automatically adjust the video's bitrate or quality according to the network condition.
+Within such an environment, bandwidth fluctuation is inevitable, and it would be difficult or impossible for the user to get best watching experience if the video is streamed at a fixed bitrate.
+To cope with this challenge, the video streaming system should be able to adjust the video's bitrate or quality according to the network condition.
 In other words, the video streaming system needs to be adaptive.
@@
 In order to provide a wide range of seamless quality adaptation at reasonable time and space cost, the adoption of SVC is necessary.
-An SVC video bitstream can be extracted at the fine granularity of one NALU (a very small partition of data), and performance analysis \cite{SVCPerformance} shows that SVC clearly outperforms simulcast coding in terms of compression efficiency.
-Therefore, to adopt SVC in the video streaming framework is technically a better option and has attracted much attention in the study \cite{Chuah12}-\cite{Cicalo14}.
+An SVC video bitstream can be extracted at the fine granularity of one NALU (a very small partition of data), and performance analysis \cite{SVCPerformance} shows that SVC also has much higher coding efficiency than simulcast where the same content is encoded multiple times.
+Therefore, to adopt SVC in the video streaming framework is technically a better option and has attracted much attention in the academia \cite{Chuah12}-\cite{Cicalo14}.
 
@@
 The solutions then work together and serve as a solid foundation for a practical adaptive video streaming system.
-It should be noted that, in practical streaming systems there are other issues to be addressed.
-One of them is occasional packet loss during transmission, which will cause decoding errors and corrupted images, resulting in an significant degradation of video quality.
+It should be noted that, in practical streaming systems another much concerned issue is the occasional packet loss during transmission, which will cause decoding errors and corrupted images, resulting in an significant degradation of video quality.
 How to avoid or even recover from packet loss/error is an important research topic that is popular in both networking and multimedia community.
@@
 Once all enhancement packets' error vectors are obtained, the distortion caused by discarding a set of enhancement packets can be estimated by adding up the error vector of each packet in the set.
-For example, if enhancement packets $k$, $l$, $n$ are removed from a bitstream, then the difference of the reconstruction before and after the removal is supposed to be $e = e_k + e_l + e_m$.
-The reason for this sum to be rational is twofold: first, unlike MSE or PSNR, error vector is simply the difference of raw pixel values, with no quadratic calculation ever involved; second, each enhancement packet adds its own refinement to the pixel values during the reconstruction, due to the linear feature of the decoding process (see the derivation above).
-The second point is conditionally true though, as noted below.
-
-Note that in equations (\ref{eq:base0})-(\ref{eq:subset2}) the value of ${\rm\bf M}$ and $p$ remain the same, since in the case of quality scalability the enhancement packets are generated only by manipulating the transform coefficients, and not interfered with the motion compensation and static prediction.
-This argument no longer holds for the other scalable dimensions (e.g., spatial scalability), so LEM does not simply apply for those cases.
+For example, if enhancement packets $x$, $y$, $z$ are removed from a bitstream, then the difference of the reconstruction before and after the removal is supposed to be $e = e_x + e_y + e_z$.
+The reason for this sum to be rational is twofold: first, unlike MSE or PSNR, error vector is simply the difference of raw pixel values, with no quadratic calculation ever involved; second, each enhancement packet linearly adds its own refinement to the pixel values during the reconstruction, due to the linear feature of the decoding process (see the derivation above).
+It is conditional for the second point to be true though, as noted below.
+
+Note that in equations (\ref{eq:base0})-(\ref{eq:subset2}), the reason why the values of ${\rm\bf M}$ and $p$ remain the same is that, in the case of quality scalability the enhancement packets are generated only by manipulating the transform coefficients, and not interfered with the motion compensation and static prediction.
+This argument no longer holds for the other scalable dimensions (e.g., spatial scalability, where the video resolution is changed), so LEM does not simply apply for those cases.
 Therefore, only quality scalable videos are used in our system, and further research for other scalable dimensions can be our future work.
@@
 Therefore, the actual number of extraction and decoding for error vector acquisition is $(L_Q - 1) \cdot (L_T + 1)$, approximately the same with the Quality Layer information acquisition in JSVM \cite{Amonou07}.
-Since computation is mainly consumed with this decoding in the bitstream extraction algorithm, the computation complexity has no obvious promotion compared with JSVM.
 
@@
 
-Before using the estimation based on LEM, we conduct an experiment to verify it.
-All bitstreams in the experiment are encoded with the JSVM encoder, where the GOP structure as illustrated in Fig.
-\ref{fig:GOP_Structure} and the CABAC entropy coding are used.
+Before using the estimation based on LEM, we conduct an experiment to verify its accuracy.
+Bitstreams in the experiment are encoded using the JSVM encoder, with the GOP structure illustrated in Fig.
+\ref{fig:GOP_Structure} and the CABAC entropy coding.
 Each bitstream contains one base layer and one enhancement layer, with QP = 33 and QP = 27, respectively.
 The enhancement layer is further divided into 2 Medium Grain Scalability (MGS) layers by configuring the MGS vector to separate the transform coefficients into two groups (containing 4 and 12 coefficients respectively).
-Random combinations of enhancement packets are removed from a bitstream, and the distortion estimated by the linear error model are compared with the actually calculated distortion.
-Decoding is performed by JSVM decoder, and distortion estimation or calculation is done by Matlab.
+Random combinations of enhancement packets are removed from a bitstream, and the distortion estimated by the linear error model are compared with the distortion actually calculated after real decoding.
+Decoding is performed by JSVM decoder, while other operations are done by MATLAB.
 One comparison result for the test sequence {\em Foreman} (only first 33 frames are used) is shown in Fig.
@@
 The horizontal axis stands for frame index, and the vertical axis for MSE measurement.
-The solid line represents the actual distortion for the frames, and the dot line represents the distortion estimated by the proposed linear error model.
+The solid line represents the actual distortion of the frames, and the dot line represents the distortion estimated by the proposed linear error model.
 It can be seen that the two lines are very close to each other, which demonstrates the accuracy of estimation using the proposed model.
@@
 In this subsection, we utilize the linear error model to enable R-D optimized bitstream extraction.
-Since finding the global optimal solution of the bitstream extraction problem is impractical, our bitstream extraction algorithm uses a greedy method \cite{GreedyAlgo} to get a sub-optimal solution.
+Since finding the global optimal solution of the bitstream extraction problem is impractical, our bitstream extraction method uses a greedy algorithm \cite{GreedyAlgo} to get a sub-optimal solution.
 Note that the greedy algorithm is able to find a local optimum.
@@
 
-For long video sequences, an optimization window containing a certain number of frames is usually needed, and the priority assignment and bitstream extraction is conducted independently in each window.
-Suppose the size of the optimization window is $K$, i.e., there are $K$ frames involved in the above process, and each frame contains $L_Q$ quality layers (one base layer and $L_Q-1$ enhancement layers).
-Then the total number of enhancement packets that can be discarded is $K \cdot (L_Q-1)$, and in every greedy step, there are at most $K$ packets, i.e., the packets currently at the top of every frame (see analysis in \ref{subsec:analysis-extraction}), that can be selected to discard.
+For long video sequences, an optimization window containing a certain number of frames is needed, and the priority assignment and bitstream extraction is conducted independently in each window.
+Suppose the size of the optimization window, i.e., the number of frames involved in the above process, is $K$, and each frame contains $L_Q$ quality layers (one base layer and $L_Q-1$ enhancement layers).
+Then the total number of enhancement packets to be discarded is $K \cdot (L_Q-1)$, and in every greedy step, there are at most $K$ packets, i.e., the packets currently at the top of every frame (see analysis in \ref{subsec:analysis-extraction}), that can be selected to discard.
 Given that, the priority assignment process in each optimization window can be described in Algorithm \ref{algo:greedy}, with some terms in it explained below.
@@
 \begin{algorithmic}
-    \STATE Initialize $e_{seq}$ to $e_{full}$, and $q$ to 0.
+    \STATE Initialize $e_{seq}$ to $e_{full}$, and initialize $q$ to 0.
     \WHILE{$q < K \cdot (L_Q - 1)$}
@@
 It is easy to see that the computational complexity of this priority assignment algorithm is $O(K^2)$.
-Note that, however, the computation in the priority assignment process is actually very insignificant compared with the decoding process needed in the error vector acquisition.
-A larger optimization window means we have more packets to compare and determine their priorities, which will potentially result in more optimized extraction.
-However, doing this will also increase the computational complexity and, more noticeably, increase the memory used to store the error vectors.
+Note that, the computation in this priority assignment process is actually very insignificant compared with the decoding process needed in the error vector acquisition.
+With a larger optimization window size $K$, we would have more packets to compare and determine their priorities each time, which will potentially result in more optimized extraction.
+However, doing this will also bring more computation and, more noticeably, increase the memory used to store the error vectors.
 Besides, if the priority values are to be stored and signalled using the 6-bit priority identifier field of the NALU header \cite{Amonou07}, only a range of 0$\sim$63 is supported, which also limits the value of $K$.
@@
 This would make the bitstream extraction a more difficult problem, since the distortion is harder to obtain for lacking of reference signal.
-The ``no-reference bitstream extraction'' problem is actually more frequently encountered in real practice, since it is common that streaming service provider only have the compressed bitstream rather than the video source.
+The ``no-reference bitstream extraction'' problem is actually more frequently encountered in real practice, since it is more common for the streaming service provider to have the compressed bitstream rather than the video source.
 In this subsection, we consider this no-reference case and modify the proposed algorithm to meet the special characteristic caused by lacking of reference.
 
-Without the original video sequence, we can not get the error between the video sequence decoded from full enhancement packets and the original sequence, which is $e_{full}$ used in \ref{algo:greedy}.
+Without the original video sequence, we cannot get the error between the video sequence decoded from full enhancement packets and the original sequence, which is $e_{full}$ used in \ref{algo:greedy}.
 A straightforward idea is to set $e_{full}$ to zero, meaning all distortions are calculated with respect to the fully reconstructed signal, rather than to the original sequence.
@@
 The process variable stands for the current status of the system.
-The setpoint is the target for this control system to reach.
-The goal of PID control is to minimize the error between process variable and setpoint by adjusting some control variable.
+The setpoint is the target for this system to reach.
+The goal of PID control is to minimize the error between process variable and setpoint.
 The controller output $u(t)$ is defined as follows:
@@
 As an effective and flexible control technique, PID control has been used to solve all kinds of control problems.
-In the area of video coding, we notice that PID is utilized to design rate control algorithms (rate control of video coding is mainly to adjust the encoding parameters for every frame, so that the bits are appropriately allocated to avoid buffer overflow and achieve desired bitrate) \cite{Wong04}\cite{Yang10}.
+In the area of video coding, we notice that PID is utilized to design rate control algorithms (rate control in video coding is mainly to adjust the encoding parameters for every frame, so that the bits are appropriately allocated and desired bitrate is achieved) \cite{Wong04}\cite{Yang10}.
 We also notice that some researchers have proposed theoretical model or middle-ware framework for QoS adaptation \cite{Li98}\cite{Li99}, with PID as the basic control scheme.
@@
 The two intervals shown in Fig.
-\ref{fig:intervals}, i.e., check interval and actual interval, are worth notice and may provide useful information.
+\ref{fig:intervals}, i.e., check interval and actual interval, are worth noticing and may provide useful information.
 In the ideal situation, during each check interval, the server pushes an amount of data that will actually play for a period of time equal to that check interval, i.e., \textit{actual\_interval} = \textit{check\_interval}.
@@
 Moreover, in this model the controller output has intuitive meaning when the three parameters are normalized.
-It is easy to know that all of the three PID parts ($E_p^t$, $E_i^t$, $E_d^t$) are ratios with a value more or less than 1, and the controller output $u_t$ can be seen as a weighted average of the three ratios, with the three parameters as weights.
+It is easy to know that $E_p^t$, $E_i^t$, $E_d^t$ are all ratios with a value more or less than 1, and the controller output $u_t$ can be seen as a weighted average of the three ratios, with the three parameters as weights.
 Therefore the controller output is also a ratio value around 1, which reflects the relationship between the bitrate suitable for the network condition and the bitrate currently being used.
@@
 Third, in this algorithm it's not obliged to change one quality level at a time.
-This enables fast quality drop to avoid a latent playback pause when bandwidth suddenly decreases, and fast quality rise to provide better video as soon as possible when system starts, resulting in a seamless watching experience where the user can enjoy the video without stopping or waiting.
+This enables fast quality drop to avoid a latent playback pause when bandwidth suddenly decreases, and also fast quality rise to provide better video as soon as possible when system starts, resulting in a seamless watching experience where the user can enjoy the video without stopping or waiting.
 
@@
 \begin{algorithmic}
-    \STATE before packet sent
+    \STATE before packet is sent
     \STATE check\_interval = curr\_time -- last\_check\_time
@@
 These can all be compensated by the derivative part, which predicts system behaviour and has the effect of reducing the overshoot, increasing the stability, and improving the settling time (time it takes to reach setpoint after a disturbance).
-The big problem with derivative part is that it is very sensitive to noise, therefore industrial practices indicates that derivative gain $K_d$ should usually stay low.
+The big problem with the derivative part is that it is very sensitive to noise, therefore industrial practices indicate that the derivative gain $K_d$ should usually stay low.
 
@@
 In the following experiments, parameters are chosen as $K_p = 0.22$, $K_i = 0.73$, $K_d = 0.05$ by this method.
-With these parameters, the PID-controlled streaming system is stable and quickly begins to follow the bandwidth change, as shown by the experimental results in next section.
+With these parameters, the PID-controlled streaming system is stable, and also quickly begins to follow the bandwidth change, as shown by the experimental results in next section.
 
@@
 
-To implement our proposed adaptive streaming system requires the combination of the optimized bitstream extraction method and the PID-based quality control algorithm.
+To implement our proposed adaptive streaming system requires the combination of the optimized bitstream extraction and the PID-based quality control algorithm.
 The latter determines the current bitrate to follow the bandwidth change, and the former will ensure the sub-stream with the best possible quality is obtained and sent under that bitrate constraint.
-They work together to deliver best quality of service for the user.
-Choosing DSS as the implementation basis, we have integrated the proposed algorithms into it for the purpose of both research and application.
-The greedy-like algorithm present in \ref{subsec:priority-assign} is performed to determine priority values for all enhancement NALUs in an SVC bitstream.
-Then the priority values are injected into the bitstream, storing in the priority identifier field of the NALU header.
-When DSS streams this video, by checking this field it can extract a bitstream under certain bitrate determined by the PID-based quality control algorithm.
-
-In this section, we first present separate experiments to show the advantage of each proposed solution, and then give the result when they are combined together.
+They work together to improve the user's experience of watching videos online.
+With DSS as the implementation basis, we have integrated the proposed algorithms into it for the purpose of both research and application.
+The system works as follows.
+The greedy-like algorithm present in \ref{subsec:priority-assign} is performed first to determine priority values for all enhancement NALUs in an SVC bitstream.
+Then the priority values are injected into the bitstream and stored in the priority identifier field of the NALU header.
+When DSS streams this video, it can extract an optimized sub-stream by simply checking this field and discarding the packets with lower priority values.
+The bitrate of the sub-stream to be extracted is determined by the PID-based quality control algorithm according to network condition.
+
+In this section, we first present separate experiments to show the advantage of each proposed solution, then give the result when they are combined together.
 Readers who are interested in the practical implementation and demonstration can visit the online video website http://www.7dlive.com for more information.
@@
 
-In our experiments, all test bitstreams are encoded as stated in sub-section \ref{subsec:distortion-estimation}.
-For each test bitstream, ten bitrate points (one with all enhancement packets, one with only the base layer packets, and 8 points between) are chosen for extraction.
+All test bitstreams are encoded the same way as in the verification experiment of Section III-C.
+For each test bitstream, ten bitrate points (one with all enhancement packets, one with only the base layer packets, and 8 uniformly spaced points between) are chosen for extraction.
 For each bitrate point, the extraction is conducted using the bitstream extractors in JSVM, with and without \textit{Quality Layers} (denoted as JSVM QL and JSVM Basic, respectively), and the proposed method.
-The size of the optimization window in the proposed method is 32 frames, i.e., 4 GOPs with a GOP size of 8.
+The size of the optimization window in the priority assignment process is 32 frames, i.e., 4 GOPs with a GOP size of 8.
 All of the eight SVC standard sequences with CIF resolution are considered at 30FPS and tested in our experiments.
@@
 \ref{fig:extraction-performance}.
-It can be seen that the R-D curves of the proposed method are always on the top.
+It can be seen that the R-D curves of the proposed method are always on the top (with only one exception in Foreman).
 For each sequence, the maximum and average PSNR gain through all 10 bitrate points are calculated and listed in Table \ref{tab:extraction-gain}, which shows that our extraction method can achieve a significant performance gain compared with JSVM Basic, and also performs better than JSVM QL.
-Table \ref{tab:extraction-gain} also lists results when optimization window is 48 frames, i.e., 6 GOPs.
+Table \ref{tab:extraction-gain} also contains results when the optimization window size is set to 48 frames, i.e., 6 GOPs.
 It is demonstrated that a larger window size can increase performance to some degree.
-However, it should be noted that, the practical system we propose does not use optimization window exceeding 32 frames, for the reason stated in the end of sub-section \ref{subsec:priority-assign}.
+However, it should be noted that, in practice the optimization window may not be that large, for the reason stated at the end of sub-section \ref{subsec:priority-assign}.
 
@@
 However, the method of \cite{Maani09} needs more computation in order to train robust model parameters for different sequences, while the complexity of our method is always the same with JSVM QL.
+As far as we know, without significantly increasing the complexity, it is difficult to achieve large PSNR gain.
 
@@
 
-For simplicity and intuition, we combine the enhancement layers in the tested SVC video stream to construct quality levels (introduced in \ref{subsec:quality-level}) used in the quality control algorithm.
-The video stream is divided into several sub-streams, each of which is identified by the quality and temporal layer it contains, as illustrated in Table \ref{tab:sub-stream} (there are 3 layers in each scalability dimension; spatial scalability is not enabled).
-The quality level is defined as the sum of all sub-streams with ID equal or less than the level number.
-For example, quality level 3 would contain all sub-streams from 0 to 3, thus would include all temporal layers, but only the quality base layer 0.
-The tested stream has 9 quality levels from 0 to 8 (see Table \ref{tab:sub-stream}), and a maximum bitrate of 1587 kbps at level 8.
+For simplicity and intuition, in the experiments for the quality control algorithm, we combine the scalability layers in the tested SVC video stream to construct quality levels introduced in \ref{subsec:quality-level}.
+The basic idea is to divide the video stream's data packets (NALUs) into several groups, according to the combination of scalability layers they belong to, i.e., the layer IDs in the NALU header.
+The association of the group ID with layer IDs is illustrated in Table \ref{tab:sub-stream} (the stream has 3 scalability layers in each of the quality and temporal dimension, therefore data packets are separated to 9 groups).
+The quality level is then defined as the sum of all groups with ID equal or less than the level number.
+For example, quality level 2 contains all data packets from Group 0 to 2, thus would include all temporal layers, but only the quality base layer 0; quality level 5 contains Group 0 to 5, thus would further add the data packets in quality enhancement layer 1.
+Like that, as the quality level increases, more enhancement packets are accumulated and the video quality becomes better.
+At the same time the bitrate also goes up, which is quite straight-forward, since better quality needs more data.
+The bitrate for the whole stream in test is 1587 kbps, which corresponds to the highest level 8.
+Combining the scalability layers in SVC to construct quality levels is simple and intuitive in that no extra data is required other than the layer IDs already contained in the bitstream.
 
@@
 \centering
-\caption{Sub-stream ID}
+\caption{Association of group ID with layer IDs during quality level definition}
 \label{tab:sub-stream}
@@
 	\hline\hline
-	  Sub-stream ID   & 0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 \\ \hline
+	  Group ID   & 0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 \\ \hline
 	Quality Layer ID  & 0 & 0 & 0 & 1 & 1 & 1 & 2 & 2 & 2 \\ \hline
@@
 We set this level from 400 to 1400 kbps to reflect different average bandwidth.
-The simulation is implemented with NetLimiter 3 \cite{Netlimiter}, where the bandwidth varies randomly with certain distribution and intense fluctuations are observed.
+The simulation is implemented with NetLimiter 3 \cite{Netlimiter}, where the bandwidth varies randomly and intense fluctuations are observed.
+Under the bandwidth fluctuation, the streaming system with certain quality control algorithm runs for 10 minutes, during which the selected quality levels are recorded.
+The video quality measured by average of the quality levels, and the quality smoothness indicated by the variance of the quality levels are used for performance comparison.
 The baseline algorithm in the comparison refers to the packet delay feedback (PDF) algorithm in the original DSS.
 
-First of all, we conduct some preliminary improvement experiments using only proportional part or integral part of the PID model.
-Since they are directly related to the short term error and long term error respectively, we call them Short Term Prediction (STP) and Long Term Prediction (LTP).
+First of all, we conduct some preliminary improvement experiments using only the proportional part or integral part of the PID model.
+Since the two parts are related to the current short term error and the accumulated long term error respectively, we call them Short Term Prediction (STP) and Long Term Prediction (LTP).
 Fig.
 \ref{fig:performance-all} shows the experimental results of these two control algorithms and the baseline algorithm.
-In the figures, the video quality is measured by the quality level defined in the beginning of this section, and quality smoothness is indicated by the variance of the quality levels along time.
-We can conclude that STP provides the best average quality level at the expense of high quality variance.
-This can be easily explained since this quality control strategy closely follows the bandwidth fluctuation.
+We can conclude that STP provides the highest average quality level at the expense of high quality variance.
+This can be easily explained since STP tends to closely follow the bandwidth fluctuation.
 In contrast, LTP keeps a relatively low quality variance at a little cost of average video quality.
-Although it is not as good as STP in average quality, it still outperforms the baseline algorithm by 7.9\%.
+Although it is not as good as STP in average quality, it still outperforms the baseline algorithm.
 
@@
 From the result shown in Fig.
-\ref{fig:performance-two}, we can conclude that when integrated with integral part and derivative part, the effect of proportional part is not as aggressive as in STP.
+\ref{fig:performance-two}, we can conclude that when integrated with the integral part and the derivative part, the effect of the proportional part is not as aggressive as in STP.
 An obvious proof can be found in Fig.
-\ref{fig:variance-two}, which clearly shows that the proposed PID quality control algorithm keeps a lower quality variance compared to PDF algorithm.
+\ref{fig:variance-two}, which clearly shows that the proposed PID quality control algorithm achieves a lower quality variance compared to PDF algorithm.
 Table \ref{tab:improvement} lists the statistical experimental results for these four quality control algorithms, in which PID-based control algorithm has shown its advantage over the others, especially in reducing the quality fluctuation.
@@
 \subfloat[Average quality level of different control algorithms]{
-\includegraphics[width=0.45\textwidth]{Quality-all.png}
+\includegraphics[width=0.42\textwidth]{Quality-all.png}
 \label{fig:quality-all}}
 \subfloat[Quality level variance of different control algorithms]{
-\includegraphics[width=0.45\textwidth]{Variance-all.png}
+\includegraphics[width=0.42\textwidth]{Variance-all.png}
 \label{fig:variance-all}}
@@
 \subfloat[Average quality level of PID and PDF control algorithms]{
-\includegraphics[width=0.45\textwidth]{Quality-two.png}
+\includegraphics[width=0.42\textwidth]{Quality-two.png}
 \label{fig:quality-two}}
 \subfloat[Quality level variance of PID and PDF control algorithms]{
-\includegraphics[width=0.45\textwidth]{Variance-two.png}
+\includegraphics[width=0.42\textwidth]{Variance-two.png}
 \label{fig:variance-two}}
@@
 After combining the two algorithms together, the proposed adaptive streaming system is able to deliver a higher and smoother video quality for the user.
-We compare the proposed system's performance with DSS that supports SVC but has its original quality control method and JSVM Basic bitstream extraction.
+We compare the combined system's performance with DSS that supports SVC but has its original quality control method and JSVM Basic bitstream extraction.
 The result for the test sequence Soccer is present in Fig.
@@
 \ref{fig:Fluctuation-PSNR2}).
-The average and variance value of PSNR is also calculated and present in Fig.
+The average and variance value of PSNR through the time is also calculated and present in Fig.
 \ref{fig:fluctuation-psnr}, showing clearly the proposed system's advantage.
@@
 As for the PID-based quality control algorithm, it is only network-concerned thus should be easily integrated into other streaming systems, e.g., simulcast system like DASH.
-Another direction of future work is to carry out some subjective tests, comparing the performance of the proposed system from the perceived quality point of view.
+Another direction of future work is to carry out some subjective tests, demonstrating the performance of the proposed system from the perceived quality point of view.
 

### 2015-12-03 response.txt
Add response to reviewer comments

Response to the reviewer comments of Paper MM-006412: Adaptive Video Streaming with Optimized Bitstream Extraction and PID-based Quality Control by Shengbin Meng, Jun Sun, Yizhou Duan and Zongming Guo.

We would like to thank the reviewers for their time and efforts to read our manuscript and provide valuable suggestions to improve this work. We have read the comments carefully, and tried to follow the suggestions as closely as possible. We have also proof-read and polished the paper to ensure correctness and readability as much as we can.

Reviewer: 1

In this paper, the authors considered how to achieve adaptive SVC video streaming with bitstream extraction and PID-based quality control. The idea is somewhat interesting and the proposed scheme has been correctly implemented in a software system. The logic flow of the paper is good and proposed algorithms look good. However, the manuscript still bears some flaws, which should be addressed before being accepted by TMM.

1. The authors proposed a system for bitstream extraction and PID-based quality control for adaptive SVC streaming. Basically, they consider the scheme in which the end-to-end network bandwidth can be correctly measured/estimated at the streaming source and then the source applies the proposed algorithms to send video packets adaptively according to the bandwidth estimation. This scenario is generally correct, but a few assumptions should be clarified. First of all, in the video streaming network, how to estimate or measure the end-to-end bandwidth precisely? If the measurements are not precise, how about the resulting performance degradation? Secondly, the authors somehow assumed that there would be no unexpected packet loss in the video streaming network, as long as the streaming bandwidth is chosen correctly. However, this is not true in a practical network. I would expect they provide some analysis on what will be the impact of packet loss? Even though the video packets are correctly selected to be transferred, they can be lost in the network, right? Will this cause a significant performance issue or can the effect from packet loss be compensated?

Response:

In the proposed quality control algorithm, we estimate the bandwidth change using a value called “actual_check interval ratio”, as explained in Section IV-B. The algorithm doesn’t depend on precise measurement of the bandwidth (only estimation). Some other systems may try to measure the bandwidth by sending special “meta data” or “control packets” and waiting for feedback. However, this would add complexity to the system design, and would also cause extra round trip time. Moreover, since bandwidth condition is complex and dynamic, we believe neither measurement nor estimation can be absolutely precise. That’s why a flexible and robust mechanism like PID is needed to make quality adjustment decisions based on not-so-precise estimation.

Packet loss, as you point out, is actually not handled in this work. In practical streaming systems, occasional packet loss does happen, and will cause a significant performance issue represented by decoding errors and corrupted images. How to avoid or compensate or even recover from packet loss/error is another research topic not in scope of this paper. We have added clarifications in the revision (see last paragraph of Section II).

2. Some recent progress on SDN-based video streaming should be commented in the Introduction:

[1] H. Egilmez and A. Tekalp, “Distributed QoS architectures for multimedia streaming over software defined networks,” IEEE Trans. Multimedia, vol. 16, pp. 1597–1609, Oct. 2014.

[2] S. Li et al., “Flexible Traffic Engineering (F-TE): When OpenFlow Meets Multi-Protocol IP-Forwarding,” IEEE Commun. Lett., vol. 18, pp. 1699-1702, Oct. 2014.

[3] N. Xue et al., “Demonstration of OpenFlow-Controlled Network Orchestration for Adaptive SVC Video Manycast,” IEEE Trans. Multimedia, vol. 17, pp. 1617-1629, Sept. 2015.

Response:

In the revision, we have added comments on the progress of this field and its relationship with our work (see second paragraph of Section I).

3. In Section III, the authors discussed the priority assignment and bitstream extraction algorithms for two scenarios, i.e., with and without references. However, the descriptions on the proposed algorithms are not very clear. I would suggest the authors to change the text descriptions to pseudo-codes and included proper explanations. Then, the procedure and complexity of the algorithms can be seen clearly. Meanwhile, I notice that the authors introduced an optimization window K in the algorithms. I would appreciate if the authors can elaborate on how to determine K and what is the impact of K’s value to the algorithms’ performance. Basically, K determines the complexity of the algorithms and I would expect that it affects the algorithms’ performance significantly too. Therefore, some simulation or experimental results should be added to comment on K’s impact.

On the other hand, the authors mentioned that the proposed algorithms are greedy or heuristics. They should comment on the optimality of the solutions from the proposed algorithms. Say, if we want to minimize the distortion under certain bandwidth constraint, how much can the proposed algorithm approximate to the optimal solution? We understand that finding a global optimal solution can be too time consuming, but theoretical analysis on the approximation gap should be provided to validate the performance of their proposals.

Response:

In the revision, we have changed to use pseudo-codes plus explanations to better explain the algorithm in an optimization window, and discussions about impact of K and how to determine its value are also provided (see Section III-D). It is right that K affects the complexity and performance to some degree. However, as noted in the paper, the computation in priority assignment process where K is involved is actually very insignificant compared with the decoding process needed in the error vector acquisition. We have added experimental results with a larger optimization window to comment on its impact (see Section V-A).

For some problems with good optimal substructure, a greedy algorithm may be proved to find the optimal solution. For the bitstream extraction problem we are not able to do that. The greedy algorithm is able to find a local optimum. However, the gap between the local optimum and the global optimum is uncertain. Unlike other well-defined combinatorial optimization problem, the bitstream extraction problem even cannot be theoretically analyzed, because, as stated in Section II-A, the data packets have dependency on each other and their contribution to video quality (distortion) cannot be calculated unless a real decoding is performed. That’s why we need to estimate the distortion caused by discarding a subset of packets. Think this way: if we can only *estimate* the result of extracting a sub-stream, it's impossible for us to tell whether it is the optimal one. Therefore, what we can do is to first make the estimation as accuracy as possible, then try to find a local optimum based on that estimation. In the revision, we have added a comment on the optimality of the solution (see first paragraph of Section III-D).

4. For the PID-based quality control algorithm described in Section IV, the selection of the parameters is rather arbitrary. The authors should elaborate on how to optimize the parameters and what are the impacts of them. Meanwhile, the convergence performance of the PID-based quality control should be discussed too. For example, how fast can the algorithm achieve close-loop control? Currently, the algorithm design just follows the standard PID-based control scheme. In order to highlight the contribution of this work, the authors should try to improve the theoretical depth.

Response:

As with other PID control systems in the industry, the selection of the three parameters is implementation-dependent and manual tuning is usually required to achieve optimal results. In the revision we have elaborated on the impacts of each parameter. Discussions on the performance of the controller and how to optimize it are also added (see Section IV-D).

5. The notations in the paper should be unified and correctly used. Currently, the usages are mixed and make the related descriptions very difficult to be understood. For instance, in Section III-A, the notations of matrices M and T are different in the equations and texts. Moreover, I would suggest the author to use M \cdot s instead of Ms to represent M * s. This should be applied to all the equations.

Response:

In the revision, we have changed the usage as suggested, and checked all the notations to ensure correctness as well as readability.

6. In Section V, the experimental setup is not clearly explained. The authors should clearly explain where the video is injected, where the proposed algorithms are applied, how the bandwidth fluctuations are simulated, etc.

Response:

In the revision, we have added detailed explanations about how the system works and how the experiments are set up.

7. In Section V, the results should be analyzed in a better way. For instance, in Fig. 5, we can see that the performance gain (PSNR) achieved by the proposed algorithm over the benchmarks is really marginal. I am wondering whether this is the best they can do or the performance can be further improved? Also, as the difference among the results is small, the authors should comment on the statistical accuracy of the experiments.

Response:

The performance can be further improved by increasing the optimization window. However, based on the results added in the revision, the improvement is very limited. As far as we know, without significantly increasing the complexity, it is difficult to achieve large PSNR gain. From the results in Fig.5 it can be seen that extraction for all bitrate points (with only one exception) in all the bitstreams are showing the superiority of our method, therefore the statistical accuracy of the experiments can be ensured.

8. The quality of Figs. 2, 3, 6, and 9 needs to be improved. Currently, when printed in a black-and-white version, it would be very difficult to distinguish the curves/bars/markers in them. Also, some texts in them are too small and cannot be seen clearly.

Response:

All the mentioned figures are re-drawn in the revision. Colors and curve types are adjusted to make the elements easier to be distinguished even when printed in a black-and-white version, and small texts are enlarged.

9. There are a few grammar errors in the paper and should be corrected. I would suggest the authors to proof-read their paper and polish it accordingly.

Response:

We have proof-read the paper carefully and corrected as many errors and flaws as possible.

Thank you again for the help.

Reviewer: 2

In this paper, the authors proposed an adaptive video streaming system based on Scalable Video Coding (SVC) extension of H.264/AVC to deal with bandwidth fluctuation and provide best online video watching experience at the same time. This paper is well organized and three main contributions are fully demonstrated: linear error model, a greedy-like algorithm of assigning priority value to each data packet, and the PID method on video quality control.

1. In the first part, the authors give an introduction to the background information of this paper. Video streaming is extremely hot topic. However, the authors should strengthen more on the necessity of SVC under the fact that most of the commercial video websites adopt simulcast approach.

Response:

We have revised the introduction part as suggested. The necessity of SVC is analyzed explicitly in the 4th paragraph.

2. In next section, related works are presented. The reviewer thinks the authors should provide related works of the priority value assigning since it’s also the main contribution of this paper. In Fig.1, the dash line has a little different part. And some little grammar flaws like “maximums” should also be corrected.

Response:

In the revision, related work of priority value assigning is added and the mentioned figure and grammar flaws are corrected.

3. The authors present the optimized bitstream extraction by first giving the linear error model. The reviewers think the linear error model should be explained in more details. And most importantly, some more reasoning on how and why the error model is accurate should be given. The experiment environment should be demonstrated more thorough. The font size in Fig.2 should be adjusted. Little grammar flaws like the difference of “Therefore” and “Therefor” should be avoided.

Response:

In the revision, we have added more explanations for the linear error model and for the verification experiments as well (see Section III-A and Section III-C). Fig.2 is re-drawn with larger font size and the mentioned grammar flaws are corrected.

4. In section four, a PID-based quality control algorithm is proposed. The reviewer thinks the meaning of controller output should be explained explicitly. And the difference of rate control and quality control should be strengthened. Some important aspects of PID, like stability, rising time, overshot, robustness over system parameters variation, should be discussed.

Response:

In the revision, more explanations on the meaning of the controller output are added (see Section IV-C). The introduction of rate control in video coding is only used to explain the widely usage of PID controller, and we have revised that part to avoid confusion (see the second paragraph of Section IV). The mentioned aspects of PID are discussed in Section IV-D along with the parameter selection.

5. In the experiment section, the author gives the experiments of the proposed method. A thorough comparison is given. The reviewer thinks the authors should demonstrate how the bandwidth varies, like distribution. And for the results, the authors should give more demonstration since the reviewers don’t see a large improvement through the comparisons.

Response:

In the revision, we have added detailed explanations about how the system works and how the experiments are set up (including how the bandwidth is simulated). We have also provided more results to demonstrate how the performance can be improved.

Thank you again for the help.

Reviewer: 3

1. The paper proposed an adaptive video streaming system which combines several novel algorithms for packet priority assignment and bitstream extraction, and quality-based bitrate adaptive control based on SVC. The proposed system was implemented on Apple Darwin Streaming Server (DSS) and its performance was compared with the native one in DSS. The results show that the proposed scheme achieved a better PSNR with lower quality fluctuation when compared with the baseline software.

Response:

We appreciate your time and the insightful comments in the following to help us improve this paper.

2. One strong element of the paper is that the proposed algorithm has been implemented in DSS. As stated in the paper, ‘the system is deployed at online video website www.7dlive.com and proves to be practically effective’. Unfortunately the site is not accessible, thus the reviewer is not able to comment on the practical effectiveness of the system.

Response:

The website is only a demo and is hosted in a server maintained by ourselves, which may not be that stable. We have checked again and ensured that the site is functional. Please visit the site using Internet Explorer and follow the instructions on the page located at http://7dlive.com/howtouse/index.html.

3. The paper has provided details on proposed algorithms on priority assignment and adaptive control. The paper is written and structured well in general.

Response:

Thank you for the kind words.

4. The reviewer felt that there are some exaggerated statements or lack of strong evidence regarding how significant improvement the work has been achieved in terms of user-perceived video quality.

For example, page 8, col 2, regarding performance comparison between the proposed method and JSVM, it is stated that “For each sequence, the maximum and average PSNR gain through all 10 bitrate points are calculated and listed in Table II, which shows that our extraction method can achieve a significant performance gain compared with JSVM.” However, if we look at Table II, the average PSNR gain is only about 0.05 dB for half of video clips and about 0.11 dB for the remaining half of video clips (compared with JSVM QL). Can we say that this performance gain is SIGNIFICENT? Are we able to differentiate them from perceived quality point of view?

Page 2, 1st column, “Then novel algorithms for bitstream extraction and quality control are designed and implemented to achieve significant improvement in terms of user-perceived video quality.” Same comment here. The paper/work is only based on PSNR and it is well-known that PSNR has poor match with user perceived quality. Even from PSNR point of view, how significant of the performance gain is?

Response:

For the PSNR comparison we have realized that some statements were indeed exaggerated and have changed them to appropriately reflect the actual achievement. Besides the PSNR increase, our work (more specifically, the PID-based quality control algorithm) also reduces the quality fluctuation of the video, which in another aspect improves the user’s watching experience. In the revision, we have rephrased the contribution of this work to clearly state the achievements without misleading. For example, by “user-perceived video quality” we actually intended to mean “the quality of the video delivered to the user”, still in PSNR rather than the subjective criterion. This misleading expression is avoided.

5. In Figure 5, PSNR results are in the range of 32 to 38 dB (in general, MOS score between 4 and 5), whereas in Figure 9, PSNR results are all above 38.5 (MOS score over 5). More explanations are required on why PSNR are in such differences for these experiments. In Figure 9, when PSNR results are all over 38.5, are you able to perceive the difference of quality fluctuation between the proposed system and the reference one? I would suggest some subjective tests to be carried out to prove that the proposed system is better than the reference one from the perceived quality point of view.

Response:

Larger PSNR values in Figure 9 are due to the relatively higher bitrates used in encoding. We have realized that it's not proper to encode the 352x288 video clip Foreman, which has quite simple scenes, with a bitrate of 800kbps or higher. In that case, PSNR values would indeed be too large. Instead, we have changed to use the video clip Soccer, which has more complex scenes, and some lower bitrates in the experiments for the combined system, such that PSNR values fall in a reasonable range. Please see the new results in the revised paper.

As for subjective test (obtaining MOS data), to be honest we did not have any experience on that before, and during the short time for this revision we would not be able to credibly follow this useful suggestion. In the revised paper, we have added a description of future work, which includes carrying out subjective test (see the last paragraph of Section VI).

6. Page 8, col 1, regarding adaptation approach, “in this algorithm, it is not necessary to change one quality level at a time. This enables fast quality drop when bandwidth suddenly decreases and fast quality rise when system starts, resulting in a seamless experience.” I don’t know what kinds of seamless experience the authors refer to. More explanations are required here. In general for video bitrate adaptation, sudden bit rate change will cause unpleasant user experience. That is why many adaptation algorithms choose to increase/decrease bitrate gradually, instead of a sudden change in bitrate.

Response:

If bandwidth suddenly decreases, fast quality drop may be helpful to avoid playback pause. When system starts, fast quality rise can provide high quality video as soon as possible. By seamless experience we mean that the user can enjoy the video without stopping or waiting. We think there are some special cases where a sudden change is benefiting and our algorithm has the potential to handle them. Of course, most of the time the adaptation algorithms should aim at a smooth quality, which is also one target of the proposed PID-based quality control. In the revision, we have added explanations here (see the last paragraph of Section IV-C).

7. It is not very clear how eight video quality levels are defined. Do they match to fixed video bitrates? The paper mentioned that a maximum bitrate of 1587 kbps at level 8. Is it just fixed for this particular experiment? How about video bitrate higher than the set value, or a video clip’s bitrate in different range? More explanations are required to make it clear.

Response:

As stated in Section IV-A, quality level is a concept to quantize the continuous video quality. The number of quality levels and how they are mapped to different bitrates are both implementation-dependent. Generally, the highest quality level corresponds to the highest bitrate available. In the case of SVC, that is the bitrate of the whole stream. Therefore, here “a maximum bitrate of 1587 kbps at level 8” means that the bitrate of the whole SVC video stream is 1587 kbps, which is mapped to the highest quality level 8. This is indeed only the case for this particular experiment, where the quality levels are simply constructed with the SVC enhancement layers. We have added more explanations to clarify the meaning of quality levels and how they are defined in our experiments (see the first paragraph of Section V-B).

8. In Table IV, the performance comparison between the proposed PID and baseline PDF, I would suggest add columns for average quality improvement in PSNR (dB) and quality variance of PSNR (dB), in addition to current average quality level and quality variance. It is difficult to judge the performance gain without a full understanding of the eight quality levels.

Response:

With the concept of quality levels explained more clearly in the revision, it should now be easy to understand that: a higher quality level is by definition corresponding to a higher bitrate, which without doubt will result in a higher PSNR, and vice versa. The quality control algorithm only concerns adjustment of the quality level (i.e., the adaptation of bitrate), and PSNR does not come into play until specific bitstream extraction is performed (the performance of bitstream extraction algorithm also affects the PSNR values). Therefore, we consider it’s better to present the comparison of PSNR in the following part of experiments for the combined system.

9. There are some typos/grammar errors in the paper. For example:

a. Page 1, 1st col, video streaming has also attracted a large number of users and become an increasingly … => becomes

b. Page 2, 2nd col, Problem Analysis and Related Works => Related Work

c. Page 2, 2nd col, this problem in the form of “0-1 Kanpsack Problem”. => this problem lies (or fits) in the form …

d. Page 3, 2nd col, The state-of-art solutions => The state-of-the-art solutions

Response:

All of these are fixed in the revision. We have proof-read the paper and corrected some other errors as well.

Thank you again for the help.

### 2015-12-04 tmm.tex
The submitted version

@@
 \begin{abstract}
-To cope with the challenge brought by bandwidth fluctuation and improve the experience of watching videos online, an adaptive video streaming system which can adjust video quality according to actual network condition is proposed based on the Scalable Video Coding (SVC) extension of H.264/AVC.
+To cope with the challenge brought by bandwidth fluctuation and improve the experience of watching online videos, an adaptive video streaming system which can adjust video quality according to actual network condition is proposed based on the Scalable Video Coding (SVC) extension of H.264/AVC.
 First, a simple and effective linear error model is proposed and verified for quality scalability of SVC.

### 2015-12-04 tmm.tex
Move description of how the system works to last sub-section of experiments

@@
 With DSS as the implementation basis, we have integrated the proposed algorithms into it for the purpose of both research and application.
-The system works as follows.
-The greedy-like algorithm present in \ref{subsec:priority-assign} is performed first to determine priority values for all enhancement NALUs in an SVC bitstream.
-Then the priority values are injected into the bitstream and stored in the priority identifier field of the NALU header.
-When DSS streams this video, it can extract an optimized sub-stream by simply checking this field and discarding the packets with lower priority values.
-The bitrate of the sub-stream to be extracted is determined by the PID-based quality control algorithm according to network condition.
 
@@
 It is demonstrated that a larger window size can increase performance to some degree.
-However, it should be noted that, in practice the optimization window may not be that large, for the reason stated at the end of sub-section \ref{subsec:priority-assign}.
+However, it should be noted that, in practice the optimization window may not be that large, for the reason stated at the end of Section \ref{subsec:priority-assign}.
 
@@
 After combining the two algorithms together, the proposed adaptive streaming system is able to deliver a higher and smoother video quality for the user.
+The system works as follows.
+The greedy-like algorithm present in \ref{subsec:priority-assign} is performed first to determine priority values for all enhancement NALUs in an SVC bitstream.
+Then the priority values are injected into the bitstream and stored in the priority identifier field of the NALU header.
+When DSS streams this video, it can extract an optimized sub-stream by simply checking this field and discarding the packets with lower priority values.
+The bitrate of the sub-stream to be extracted is determined by the PID-based quality control algorithm according to the network condition.
+
 We compare the combined system's performance with DSS that supports SVC but has its original quality control method and JSVM Basic bitstream extraction.
@@
 \ref{fig:fluctuation-psnr}.
-It shows the streamed video's PSNR change when available bandwidth fluctuates around certain values (400kbps, 600kbps, 800kbps and 1000kbps).
+It shows the streamed video's PSNR change when available bandwidth fluctuates around 400kbps, 600kbps, 800kbps and 1000kbps (bandwidth fluctuation is simulated the same way as in the previous experiments).
 It can be seen that, the proposed system performs better in that it has effectively avoided unnecessary quality drop (e.g., note the curve around time 350s in Fig.

### 2016-01-04 tmm.tex
Keep all expressions in the paper consistent
Remove the demo website

@@
 Experimental results show that, comparing with the baseline software, the proposed system integrating the above algorithms can achieve much lower video quality fluctuation, with PSNR variance reduced from 1.24 to 0.69, and at the same time deliver higher video quality, with the PSNR average increased by 0.83 dB.
-The system is deployed at online video website www.7dlive.com and proves to be practically effective.
 \end{abstract}
@@
 The latter determines the current bitrate to follow the bandwidth change, and the former will ensure the sub-stream with the best possible quality is obtained and sent under that bitrate constraint.
-They work together to improve the user's experience of watching videos online.
+They work together to improve the user's experience of watching online videos.
 With DSS as the implementation basis, we have integrated the proposed algorithms into it for the purpose of both research and application.
@@
 In this section, we first present separate experiments to show the advantage of each proposed solution, then give the result when they are combined together.
-Readers who are interested in the practical implementation and demonstration can visit the online video website http://www.7dlive.com for more information.
 

### 2016-01-04 tmm.tex
Fix a typo found by a reviewer
Edit a little

@@
 
-In this section, we first introduce the \textit{quality level} concept to discretization the bitrate and quality of scalable video.
+In this section, we first introduce the \textit{quality level} concept to discretize the bitrate and quality of scalable video.
 Then we define the process variable used in our PID-based quality control algorithm.
@@
 \centering
-\caption{Luma PSNR gain of the proposed algorith compared with JSVM}
+\caption{Luma PSNR gain of the proposed algorithm compared with JSVM}
 \label{tab:extraction-gain}

### 2016-01-12 tmm.tex
Add more discussion on the robustness of the controller
Change the first half part according to reply of editing service

@@
 \begin{abstract}
-To cope with the challenge brought by bandwidth fluctuation and improve the experience of watching online videos, an adaptive video streaming system which can adjust video quality according to actual network condition is proposed based on the Scalable Video Coding (SVC) extension of H.264/AVC.
+To cope with the challenges brought about by bandwidth fluctuation and improve the experience of watching online videos, an adaptive video streaming system that can adjust video quality according to actual network conditions is proposed based on the Scalable Video Coding (SVC) extension of H.264/AVC.
 First, a simple and effective linear error model is proposed and verified for quality scalability of SVC.
 The model exploits the linear feature of pixel value errors and can be used to accurately estimate the distortion caused by discarding any combination of enhancement data packets in an SVC bitstream.
-On that basis, a greedy-like algorithm is designed to assign each data packet a priority value according to its Rate-Distortion (R-D) impact, thus enables R-D optimized bitstream extraction under certain bitrate constraint.
-Finally, the Proportional-Integral-Derivative (PID) method is utilized to control the video quality adjustment and determine the suitable bitrate for transmission.
-By monitoring and predicting bandwidth information of the past, the current and the future, the PID-based quality control algorithm is able to reduce quality fluctuation while still keeping a high quality level.
-Experimental results show that, comparing with the baseline software, the proposed system integrating the above algorithms can achieve much lower video quality fluctuation, with PSNR variance reduced from 1.24 to 0.69, and at the same time deliver higher video quality, with the PSNR average increased by 0.83 dB.
+On that basis, a greedy-like algorithm is designed to assign each data packet a priority value according to its Rate-Distortion (R-D) impact, thus enabling R-D optimized bitstream extraction under certain bitrate constraints.
+Finally, the Proportional-Integral-Derivative (PID) method is utilized to control the video quality adjustment and determine a suitable bitrate for transmission.
+By monitoring and predicting past, current and future bandwidth information, the PID-based quality control algorithm is able to reduce quality fluctuation while still preserving a high quality level.
+Experimental results show that compared with the baseline software, the proposed system that integrates the above algorithms can achieve much lower video quality fluctuation, with PSNR variance reduced from 1.24 to 0.69, and at the same time deliver higher video quality, with the PSNR average increased by 0.83 dB.
 \end{abstract}
@@
 \IEEEPARstart{V}{ideo} streaming applications are becoming more and more popular on the Internet.
-Examples of the most common usage scenarios include Video-on-Demand (VoD), live broadcasting, video-based online education, etc.
-In these applications, video data is constantly delivered to different clients over various transmission channels, and the client media player can begin to play the video before the entire file has been transmitted.
-Among other features, video streaming makes it easy to watch video anywhere and anytime, which represents the concept of Ubiquitous Multimedia Access (UMA), a very common topic within the multimedia community during the past few years \cite{Gualdi08}.
-Due to its convenience, video streaming also attracts a large number of users and becomes an increasingly important way for people to consume video content \cite{Chen13}.
-
-In video streaming, the network condition significantly influences the user's watching experience.
-To provide better network condition, some researchers choose to adopt the new Software Defined Networking (SDN) architecture \cite{Egilmez14}.
+Examples of the most common usage scenarios are Video-on-Demand (VoD), live broadcasting, video-based online education, etc.
+In these applications, video data are constantly delivered to different clients over various transmission channels, and the client media player can begin to play the video before the entire file has been transmitted.
+Among other features, video streaming makes it easy to watch videos anywhere and anytime, which represents the concept of Ubiquitous Multimedia Access (UMA), a very common topic within the multimedia community \cite{Gualdi08}.
+Due to its convenience, video streaming also attracts a large number of users and has become an increasingly important way for people to consume video content \cite{Chen13}.
+
+In video streaming, the network conditions significantly influence the user's watching experience.
+To provide better network conditions, some researchers choose to adopt the new Software Defined Networking (SDN) architecture \cite{Egilmez14}.
 Based on a successful SDN paradigm named OpenFlow, noticeable results are achieved.
-For instance, a solution for improving network throughput in hybrid network is proposed in \cite{Li14} and a demonstration of OpenFlow-controlled network orchestration for video manycast is present in \cite{Xue15}.
-Although these studies have offered a promising way to optimize network condition, currently traditional best-effort networks still dominate, and the variety of users' network environment remains to be one of the biggest challenges for video streaming.
-A user might use different types of network (Ethernet, Wi-Fi, Cellular, etc.) and might also switch from one type to another on going (e.g., from Wi-Fi to Cellular).
+For instance, a solution for improving throughput in hybrid networks is proposed in \cite{Li14} and a demonstration of OpenFlow-controlled network orchestration for video manycast is presented in \cite{Xue15}.
+Although these studies have offered a promising way to optimize network conditions, traditional best-effort networks still dominate currently, and the variety of user network environments remains to be one of the biggest challenges for video streaming.
+A user may use different types of networks (Ethernet, Wi-Fi, Cellular, etc) and may also switch from one type to another on going (e.g., from Wi-Fi to Cellular).
 Even in the same network, the end-to-end bandwidth will change from time to time, influenced by the overall traffic.
@@
 
-There are generally two options to enable adaptive video streaming.
-The first option is called simulcast, where several independent bitstreams, each with different video quality, are stored at the server, and the client selects one of them according to currently available bandwidth.
+There are generally two options for enabling adaptive video streaming.
+The first option is called simulcast, where several independent bitstreams, each with different video quality, are stored at the server, and the client selects one of them according to the currently available bandwidth.
 Dynamic Adaptive Streaming over HTTP (DASH) \cite{DASH}, which is standardized by the Moving Picture Expert Group (MPEG), belongs to this option.
@@
 These NALUs are separated into one base layer for basic video quality and multiple enhancement layers for video quality improvement.
-By discarding NALUs of the enhancement layers, the bitstream can be extracted to provide the most appropriate video quality and bitrate as required.
-
-Due to the easy deployment of simulcast systems \cite{Bouten14}, they are already used by many commercial video websites (e.g., YouTube \cite{YouTube}) to enable quality adaptation.
-However, the adaptive range and granularity that simulcast provides is limited to the number of streams (YouTube videos have 5 quality levels at most: 240p, 360p, 480p, 720p and 1080p), and the processing and storage of multiple video streams require a lot of computation time and disk space.
+By discarding the NALUs of the enhancement layers, the bitstream can be extracted to provide the most appropriate video quality and bitrate as required.
+
+Due to their easy deployment \cite{Bouten14}, simulcast systems are already used by many commercial video websites (e.g., YouTube \cite{YouTube}) to enable quality adaptation.
+However, the adaptive range and granularity that simulcast provides is limited to the number of streams (YouTube videos have 5 quality levels at most: 240p, 360p, 480p, 720p and 1080p), and the processing and storage of multiple video streams require large amounts of computation time and disk space.
 In order to provide a wide range of seamless quality adaptation at reasonable time and space cost, the adoption of SVC is necessary.
-An SVC video bitstream can be extracted at the fine granularity of one NALU (a very small partition of data), and performance analysis \cite{SVCPerformance} shows that SVC also has much higher coding efficiency than simulcast where the same content is encoded multiple times.
-Therefore, to adopt SVC in the video streaming framework is technically a better option and has attracted much attention in the academia \cite{Chuah12}-\cite{Cicalo14}.
+An SVC video bitstream can be extracted at the fine granularity of one NALU (a very small partition of data), and performance analysis \cite{SVCPerformance} shows that SVC also has much higher coding efficiency than simulcast, where the same content is encoded multiple times.
+Therefore, adopting SVC in the video streaming framework is technically a better option and has attracted a lot of attention in the academia \cite{Chuah12}-\cite{Cicalo14}.
 
 While these studies mostly focus on Quality of Service (QoS) optimization and resource allocation for specific networks, there are two key problems that need to be primarily addressed in the SVC adaptive video streaming system.
-First, as the prerequisite of bitrate adaption, the whole bitstream needs to be extracted so that sub-streams with various bitrates can be obtained.
+First, as a prerequisite for bitrate adaption, the whole bitstream needs to be extracted so that sub-streams with various bitrates can be obtained.
 This is called the bitstream extraction problem.
-Optimal bitstream extraction algorithm aims to extract a sub-stream with best video quality, or minimal distortion, under the constraint of a given bitrate.
+Optimal bitstream extraction algorithm aims to extract a sub-stream with the best video quality, or minimal distortion, under the constraint of a given bitrate.
 Second, when the bandwidth changes with time, it is necessary to make decisions about whether and how to adjust the video quality or bitrate.
 This problem is called quality control, which means controlling the video quality (or the bitrate, from the transmission point of view) to follow the change of the bandwidth.
-A good quality control algorithm should determine a suitable bitrate according to current network condition, and keep the video quality both smooth and at a high level.
+A good quality control algorithm should determine a suitable bitrate according to current network conditions, and maintain the video quality to be both smooth and at a high level.
 
 In this paper, an efficient adaptive video streaming system based on SVC is proposed with the above two problems better solved.
-Apple Darwin Streaming Server (DSS) \cite{DSS}, which is open-sourced and has been widely used to stream multimedia contents in practice, is chosen as the basis of the proposed system.
-The original DSS project is modified and SVC support is added to it, for the purpose of both research and application.
-Then novel algorithms for bitstream extraction and quality control are designed and implemented to enable better quality of service for the user.
+Apple Darwin Streaming Server (DSS) \cite{DSS}, which is open-sourced and has been widely used to stream multimedia content in practice, is chosen as the basis for the proposed system.
+The original DSS project is modified and SVC support is added to it for the purpose of both research and application.
+Novel algorithms for bitstream extraction and quality control are then designed and implemented to enable better quality of service for the user.
 The contributions of our work can be summarized as follows:
@@
 \item First, a simple and effective Linear Error Model (LEM) is proposed and verified, which can be used to accurately estimate the distortion caused by discarding any combination of data packets from an SVC bitstream.
-\item Second, utilizing distortion estimation with LEM, a greedy-like algorithm is designed to assign priority for each data packet according to its Rate-Distortion (R-D) impact, thus enables optimized bitstream extraction.
+\item Second, utilizing distortion estimation with LEM, a greedy-like algorithm is designed to assign priority for each data packet according to its Rate-Distortion (R-D) impact, thus enabling optimized bitstream extraction.
 \item Finally, for the quality control problem, a novel algorithm based on the Proportional-Integral-Derivative (PID) controller is proposed to replace the native one in DSS, and much lower quality fluctuation is achieved.
@@
 In section \ref{sec:analysis}, we analyze the problems in detail and introduce some related work on them.
-Then in section \ref{sec:bitstream-extraction}, the linear error model and the solution for the bitstream extraction problem are present.
-After that, the PID-based quality control algorithm is proposed in section \ref{sec:quality-control}.
+Then in section \ref{sec:bitstream-extraction}, the linear error model and the solution for the bitstream extraction problem are presented.
+The PID-based quality control algorithm is proposed in section \ref{sec:quality-control}.
 Section \ref{sec:experiment} lists the experimental results and compares our proposed solution with others.
-Finally, in section \ref{sec:conclusion}, we conclude this paper's work and point out its promising applications and extensions in the future.
+Finally, in section \ref{sec:conclusion}, we conclude this paper and point out related future work.
 
@@
 
-In this section, we analyze the two most concerned problems in SVC adaptive video streaming, i.e., bitstream extraction and quality control, and introduce some related work on them.
+In this section, we analyze the two most important problems in SVC adaptive video streaming, i.e., bitstream extraction and quality control, and introduce some related work on them.
 
@@
 Fig.
-\ref{fig:Bitstream-Extraction} illustrates the structure of an SVC bitstream and a possible way to extract a sub-stream from it.
+\ref{fig:Bitstream-Extraction} illustrates the structure of an SVC bitstream and a possible way of extracting a sub-stream from it.
 The data packets in the bitstream are divided into different layers.
 The temporal layer (T0$\sim$T3) reflects the reference or dependency relationship between the frames.
-The arrows on the top point from the referenced frame to the frame which is dependent on it.
-The quality layer (Q0$\sim$Q2) indicates scalability of video quality within each frame.
+The arrows ot the top point from the referenced frame to the frame which is dependent on it.
+The quality layer (Q0$\sim$Q2) indicates the scalability of the video quality within each frame.
 Data packets in the higher quality layers (i.e., Q1 and Q2) are partially discarded to implement the extraction.
-For example, the dash line demonstrates the extraction which will keep the data packets below the line and discard all the packets above it.
+For example, the dashed line demonstrates the extraction which will keep the data packets below the line and discard all the packets above it.
 
@@
 There are many combinations of packets to be discarded, and we want to choose a combination that maximizes the video quality of the extracted sub-stream, under the constraint of a given bitrate.
-More specifically, this problem is in the form of ``0-1 Knapsack Problem" \cite{Knapsack}.
+More specifically, this problem is in the form of the ``0-1 Knapsack Problem" \cite{Knapsack}.
 Each data packet can be treated as an object with certain weight (the packet's size) and value (its contribution to the video quality).
-The solving process is mainly to decide whether or not a packet should be included in the final extracted sub-stream, or in the term of ``0-1 Knapsack Problem", to choose which object to pack up.
+The solving process is mainly deciding whether or not a packet should be included in the final extracted sub-stream, or, in terms of the ``0-1 Knapsack Problem", choosing which object to pack up.
 
@@
 However, this is not operational for the bitstream extraction problem, mainly due to the dependence between the data packets.
-First, the subset of packets to be extracted cannot be chosen arbitrarily, since if a packet is included, all the packets it depends on must also be included.
+First, the subset of packets to be extracted cannot be chosen arbitrarily, because if a packet is included, all the packets it depends on must also be included.
 For example, in Fig.
 \ref{fig:Bitstream-Extraction}, we cannot include the Q2 packet of a frame without including the Q1 packet of the same frame.
-Second, the value of a packet is not obvious and certain, since a packet's contribution to video quality depends on other packets and may vary in different extractions.
-There is no way to exactly tell the video quality of an extracted sub-stream, unless we perform the extraction and calculate the distortion for real.
-In fact, to the best of our knowledge, no method presented in the literature claims to find the optimal solution of the SVC bitstream extraction problem.
-All the effort is made to obtain a solution that is as good as possible.
+Second, the value of a packet is not obvious and certain, because a packet's contribution to video quality depends on other packets and may vary for different extractions.
+There is no way to exactly determine the video quality of an extracted sub-stream, unless we perform the extraction and calculate the distortion for real.
+To the best of our knowledge, no method presented in the literature claims to find the optimal solution of the SVC bitstream extraction problem.
+All the efforts are made to obtain a solution that is as good as possible.
 
@@
 proposed a bitstream extraction framework based on the concept of \textit{Quality Layers}.
-This framework has been adopted by the SVC reference software, i.e., JSVM \cite{JSVM}, and achieves better R-D performance compared with the basic extractor of JSVM.
+This framework has been adopted by the SVC reference software, i.e., JSVM \cite{JSVM}, and achieves better R-D performance compared to the basic extractor of JSVM.
 In Amonou's framework, a Quality Layer value, which reflects a data packet's R-D impact, is calculated and used for R-D optimized bitstream extraction.
-The process of obtaining distortion impact of every packet is extremely time consuming, and the distortion estimation accuracy can also be further improved.
-So other distortion/error models were proposed to either reduce the computational complexity or improve the estimation accuracy.
+The process of obtaining the distortion impact of every packet is extremely time consuming, and the distortion estimation accuracy can also be further improved.
+Therefore, other distortion/error models were proposed to either reduce the computational complexity or improve the estimation accuracy.
 Sun et al.
 \cite{Sun09} and Maani et al.
-\cite{Maani09} constructed models to calculate distortion based on the drift propagation between frames.
-Sun et al.'s method is almost as good as JSVM in regard of performance, but has much reduced complexity.
+\cite{Maani09} constructed models to calculate the distortion based on the drift propagation between frames.
+Sun et al.'s method is almost as good as JSVM in terms of performance, but has much reduced complexity.
 Maani et al.'s model can achieve better estimation accuracy than JSVM; however, since it is a training-based model, more computation is needed to get robust model parameters.
@@
 \cite{Yang13} proposed a method based on simulated annealing to solve the bitstream extraction problem.
-In both methods, the accuracy of distortion estimation affects the performance a lot.
-With a packet's distortion impact accurately estimated, its prioritization order during extraction can be determined.
-Then a priority value can be assigned to it and stored in the bitstream for optimized extraction in the future.
+In both methods, the accuracy of distortion estimation affects the performance significantly.
+With an accurate estimation of a packet's distortion impact, its prioritization order during extraction can be determined.
+A priority value can then be assigned to it and stored in the bitstream for optimized extraction in the future.
 In \cite{Lim06}, Lim et al.
-treated SVC bitstream as a tree structure and assigned extraction priority accordingly.
+treated the SVC bitstream as a tree structure and assigned extraction priority accordingly.
 In \cite{Zhu11}, Zhu et al.
@@
 
-In our previous work \cite{Zhang12}, we proposed a linear error model for distortion estimation and priority assignment.
-Good bitstream extraction performance is achieved based on that.
+In our previous work \cite{Zhang12}, we proposed a linear error model for distortion estimation and priority assignment, based on which good bitstream extraction performance is achieved.
 However, this work assumes that the original video sequence is available for reference, which is not always true.
@@
 Quality control is the second problem we will address in this paper.
-The result of a quality control algorithm gives the suitable bitrate for transmission, which is directly related to the change of the video quality delivered to the user.
+A quality control algorithm gives the suitable bitrate for transmission, which is directly related to the change of the video quality delivered to the user.
 In an SVC streaming system, the bitrate determined by the quality control algorithm is used as the constraint under which bitstream extraction is performed.
-Even in non-SVC streaming systems (DASH, for example), quality control is an important part that requires careful design.
+Even in non-SVC streaming systems (DASH, for example), quality control is an important aspect that requires careful design.
 
 For a quality control algorithm, there are three targets to be achieved.
-The first is to ensure the continuity of video playing.
-In real-time streaming system, each data packet has its own playtime, which is also regarded as the deadline of the transmission.
-If the packet does not arrive at client side before the deadline, the media player will be paused due to lack of data, and that should be avoided.
-The second is to keep a smooth video quality.
-Although network conditions may change rapidly, it is necessary for the streamed video to maintain a relatively stable quality level, since frequent change of video quality will lead to poor user experience.
+The first is ensuring the continuity of video play.
+In real-time streaming systems, each data packet has its own playtime, which is also treated as the deadline of the transmission.
+If the packet does not arrive at the client side before the deadline, the media player will be paused due to lack of data, and that should be avoided.
+The second is maintaining smooth video quality.
+Although network conditions may change rapidly, it is necessary for the streamed video to maintain a relatively stable quality level, because frequent change of video quality will lead to poor user experience.
 The third target is to make the video quality as good as possible.
 In other words, the available bandwidth should be fully utilized.
-Suppose we keep sending video data in a low bitrate (with low video quality as well), neither the playback will pause nor any quality fluctuation will happen.
-However, a low video quality is certainly not what the user want.
-
-The state-of-the-art solutions to avoid playback pause in client media player mainly focus on how to select and schedule the video packets.
+Suppose we keep sending video data at a low bitrate (with low video quality), neither will the playback pause nor will any quality fluctuation occur.
+However, a low video quality is certainly not what the user wants.
+
+The state-of-the-art solutions for avoiding playback pause in the client media player mainly focus on how to select and schedule the video packets.
 In \cite{Gao06}, K.
 Gao et al.
-proposed a priority based scheduling strategy which guarantees packets of higher importance will be transmitted earlier.
-Among the packets with the same priority, those having the earliest deadline will be transmitted first.
-A similar solution is proposed in \cite{Schierl10}, where video data is pre-buffered in several buffers of different priorities.
-Whenever re-buffering occurs, quality will be degraded to a lower level to meet the time and rate constraint.
-Although the priority based scheduling strategies perform well in maintaining a non-paused video playing, they do not take quality fluctuation into account.
+proposed a priority-based scheduling strategy, which guarantees that packets of higher importance will be transmitted earlier.
+Among the packets with the same priority, those with the earliest deadline will be transmitted first.
+A similar solution is proposed in \cite{Schierl10}, where the video data are pre-buffered in several buffers of different priorities.
+Whenever re-buffering occurs, the quality will be degraded to a lower level to meet the time and rate constraints.
+Although the priority-based scheduling strategies perform well in maintaining a non-paused video play, they do not take quality fluctuation into account.
 As a result, users may still suffer from the frequent fluctuation of video quality.
 
-In the widely-used video streaming server DSS, quality control is implemented by monitoring packet delay (the difference between current time and the playing time of this packet).
-When a new packet is ready to be sent to streaming buffer, DSS checks the delay of it and compares this delay with some pre-set thresholds to judge whether and how violently the quality change should be made.
+In the widely used video streaming server DSS, quality control is implemented by monitoring packet delay (the difference between the current time and the playing time of this packet).
+When a new packet is ready to be sent to the streaming buffer, DSS checks its delay and compares this delay with some pre-set thresholds to judge whether a quality change should be made and how extreme it should be.
 This algorithm can reduce quality fluctuation to some degree.
-However, it only provides conservative quality change, which makes its reaction so slow that sometimes media player may have already stopped due to lack of video data before quality drops.
-Furthermore, this algorithm does not keep track of the bandwidth change so it can only adjust the video quality based on current state.
+However, it only provides conservative quality changes, which makes its reaction so slow that sometimes the media player may have already stopped due to lack of video data before the quality drops.
+Furthermore, this algorithm does not keep track of the bandwidth change, and therefore, it can only adjust the video quality based on the current state.
 Quality oscillation might occur in this algorithm.
 
-The following of this paper will present our solution for each of the problems.
-The solutions then work together and serve as a solid foundation for a practical adaptive video streaming system.
-It should be noted that, in practical streaming systems another much concerned issue is the occasional packet loss during transmission, which will cause decoding errors and corrupted images, resulting in an significant degradation of video quality.
-How to avoid or even recover from packet loss/error is an important research topic that is popular in both networking and multimedia community.
-However, in this paper which focuses on server-side adaptation, packet loss is not handled and the video stream is assumed to be successfully delivered to the client.
+In the following part of this paper, we will present our solution for each of the problems.
+The solutions then work in combination and serve as a solid foundation for a practical adaptive video streaming system.
+It should be noted that in practical streaming systems, another issue of concern is the occasional packet loss during transmission, which will cause decoding errors and corrupted images, resulting in a significant degradation of video quality.
+Avoiding or even recovering from packet loss/error is an important research topic that is popular in both the networking and multimedia communities.
+However, in this paper, which focuses on server-side adaptation, packet loss is not handled, and the video stream is assumed to be successfully delivered to the client.
 
@@
 
-Being able to adjust bitrate is the prerequisite of an adaptive video streaming system.
-For SVC videos, it means to extract a subset of packets from the whole bitstream.
-How to optimally choose this subset to achieve minimum distortion under the given bitrate is the key point of bitstream extraction problem.
-In this section, we propose a linear error mode and a greedy-like algorithm to solve this problem.
+Being able to adjust the bitrate is the prerequisite of an adaptive video streaming system.
+For SVC videos, this means extracting a subset of packets from the whole bitstream.
+How to optimally choose this subset to achieve minimum distortion under the given bitrate is the key point of the bitstream extraction problem.
+In this section, we propose a linear error model and a greedy-like algorithm to solve this problem.
 
@@
 In H.264/AVC, the decoding process involves a linear feature described in \cite{Winken08}.
-According to this feature, the main steps of decoding -- prediction, transform and quantization -- are proximately linear operations (neglecting any rounding, clipping, and deblocking filtering), and the whole process can be expressed in a matrix format as follows:
+According to this feature, the main steps of decoding -- prediction, transform and quantization -- are approximately linear operations (neglecting any rounding, clipping, and deblocking filtering), and the whole process can be expressed in a matrix format as follows:
 \begin{equation}
 \label{eq:linear}
-s = {\rm\bf M} \cdot s + {\rm\bf T} \cdot c + p \: ,
+s = {\rm\bf M} \cdot s + {\rm\bf T} \cdot c + p \: .
 \end{equation}
 It means, the reconstructed samples of a Group of Pictures (GOP), denoted by $s$, can be viewed as a linear combination of previously reconstructed samples in the GOP, the residuals, and a static predictor.
-In (\ref{eq:linear}), $c$ refers to the transform coefficients and $p$ is a static predictor; ${\rm\bf M}$ and ${\rm\bf T}$ are square matrices such that ${\rm\bf M} \cdot s$ gives the Motion Compensated Prediction (MCP) signal and ${\rm\bf T} \cdot c$ gives the residuals.
+In (\ref{eq:linear}), $c$ refers to the transform coefficients, and $p$ is a static predictor; ${\rm\bf M}$ and ${\rm\bf T}$ are square matrices such that ${\rm\bf M} \cdot s$ gives the Motion Compensated Prediction (MCP) signal and ${\rm\bf T} \cdot c$ gives the residuals.
 The actual values of ${\rm\bf M}$ depend on the selected macroblock types, reference indices and motion vectors, whereas the actual values of ${\rm\bf T}$ depend on the chosen Quantization Parameter (QP).
 
-We apply the above linear decoding feature to the case of quality scalability of SVC and get a Linear Error Model (LEM).
+We apply the above linear decoding feature to the case of quality scalability of SVC and obtain a Linear Error Model (LEM).
 According to (\ref{eq:linear}), for a bitstream just containing the base layer, we have:
@@
 where the subscript $B$ indicates the base layer variables.
-In quality scalability, the enhancement is mainly the refinement of transform coefficients, so for a bitstream containing an enhancement packet set $I_1$, the reconstruction relationship can be expressed as:
+In quality scalability, the enhancement is mainly the refinement of the transform coefficients.
+For a bitstream containing an enhancement packet set $I_1$, the reconstruction relationship can be expressed as:
 \begin{equation}
@@
 \end{equation}
-where $i$ refers to an enhancement packet in the set $I_1$.
-$c_i$ is a vector containing coefficients within the enhancement packet $i$.
-${\rm\bf T_i}$ is the transform matrix depending on the QP value of $i$.
-${\rm\bf T}_i \cdot c_i$ gives the residual values decoded from $i$.
+where $i$ refers to an enhancement packet in the set $I_1$, $c_i$ is a vector containing coefficients within the enhancement packet $i$, ${\rm\bf T_i}$ is the transform matrix depending on the QP value of $i$ and ${\rm\bf T}_i \cdot c_i$ gives the residual values decoded from $i$.
 
@@
 
-Suppose $I_1$ is a subset of $I_2$, their reconstruction difference can be obtained by (\ref{eq:subset2}) - (\ref{eq:subset1}):
+If $I_1$ is a subset of $I_2$, their reconstruction difference can be obtained by (\ref{eq:subset2}) - (\ref{eq:subset1}):
 \begin{equation}
@@
 
-Particularly, if the difference of $I_2$ and $I_1$ is a single enhancement packet $j$, i.e., $I_2 \setminus I_1 = \{j\}$, then according to (\ref{eq:minus2}), the difference of the two reconstruction vectors can be written as
+In particular, if the difference between $I_2$ and $I_1$ is a single enhancement packet $j$, i.e., $I_2 \setminus I_1 = \{j\}$, then according to (\ref{eq:minus2}), the difference between the two reconstruction vectors can be written as
 \begin{equation}
@@
 
-Obviously, $e_j$ is only determined by packet $j$, and has no relation with other enhancement packets.
-The value $e_j$ is defined as ``error vector'' of packet $j$, which represents the pixel value error caused by discarding the packet $j$.
-We can obtain the error vector of each enhancement packet by subtraction between video sequences reconstructed from two enhancement packet subsets $I_1$ and $I_2$, with $I_1 \subseteq I_2$ and $I_2 \setminus I_1 =\{j\} $.
-Once all enhancement packets' error vectors are obtained, the distortion caused by discarding a set of enhancement packets can be estimated by adding up the error vector of each packet in the set.
-For example, if enhancement packets $x$, $y$, $z$ are removed from a bitstream, then the difference of the reconstruction before and after the removal is supposed to be $e = e_x + e_y + e_z$.
-The reason for this sum to be rational is twofold: first, unlike MSE or PSNR, error vector is simply the difference of raw pixel values, with no quadratic calculation ever involved; second, each enhancement packet linearly adds its own refinement to the pixel values during the reconstruction, due to the linear feature of the decoding process (see the derivation above).
+Obviously, $e_j$ is only determined by packet $j$ and has no relation to the other enhancement packets.
+The value $e_j$ is defined as the ``error vector'' of packet $j$, which represents the pixel value error caused by discarding the packet $j$.
+We can obtain the error vector of each enhancement packet by subtracting the video sequences reconstructed from two enhancement packet subsets $I_1$ and $I_2$, with $I_1 \subseteq I_2$ and $I_2 \setminus I_1 =\{j\} $.
+Once all the enhancement packet error vectors are obtained, the distortion caused by discarding a set of enhancement packets can be estimated by adding up the error vector of each packet in the set.
+For example, if enhancement packets $x$, $y$, $z$ are removed from a bitstream, then the difference between the reconstructions before and after the removal is supposed to be $e = e_x + e_y + e_z$.
+The reason that this sum is rational is twofold: first, unlike MSE or PSNR, the error vector is simply the difference of raw pixel values, with no quadratic calculation ever involved; second, each enhancement packet linearly adds its own refinement to the pixel values during the reconstruction, due to the linear feature of the decoding process (see the derivation above).
 It is conditional for the second point to be true though, as noted below.
 
-Note that in equations (\ref{eq:base0})-(\ref{eq:subset2}), the reason why the values of ${\rm\bf M}$ and $p$ remain the same is that, in the case of quality scalability the enhancement packets are generated only by manipulating the transform coefficients, and not interfered with the motion compensation and static prediction.
-This argument no longer holds for the other scalable dimensions (e.g., spatial scalability, where the video resolution is changed), so LEM does not simply apply for those cases.
-Therefore, only quality scalable videos are used in our system, and further research for other scalable dimensions can be our future work.
+Note that in equations (\ref{eq:base0})-(\ref{eq:subset2}), the values of ${\rm\bf M}$ and $p$ remain the same because in the case of quality scalability, the enhancement packets are generated only by manipulating the transform coefficients, and do not interfere with the motion compensation and static prediction.
+This argument no longer holds for the other scalable dimensions (e.g., spatial scalability, where the video resolution is changed), and consequently, LEM does not simply apply for those cases.
+Therefore, only quality-scalable videos are used in our system, and further research for other scalable dimensions can be our future work.
 
@@
 
-It would need too many decoding times to get the error vectors of all enhancement packets if we calculate them one at a time.
-In order to acquire error vectors of all enhancement packets efficiently, we separate all enhancement packets into several groups, such that in each group multiple error vectors can be obtained at the same time.
+Too many decoding times would be required if we calculate the error vectors one at a time.
+In order to acquire the error vectors of all the enhancement packets efficiently, we separate the enhancement packets into several groups, such that in each group, multiple error vectors can be obtained at the same time.
 
@@
 
-Consider a video bitstream with 8-frame GOPs shown in Fig.
+Consider a video bitstream with 8-frame GOPs, as shown in Fig.
 \ref{fig:GOP_Structure}.
-Base layer packets are colored black, and enhancement packets with the same color are allocated in one group.
-In each group, the enhancement packets' error vectors can be calculated simultaneously, since the pixel errors they can cause are not interfered with each other.
+Base layer packets are colored black, and enhancement packets with the same color are allocated into one group.
+In each group, error vectors of the enhancement packets can be calculated simultaneously, since the pixel errors they can cause do not interfere with each other.
 For example, the removal of packet 8 would cause pixel errors only in frame 1, 2 and 3, while packet 10 only in frame 5, 6 and 7 (frame index starts from 0).
-So we can do subtraction only once for this group, to obtain error vectors $e_{8}$ and $e_{10}$, for both packets 8 and 10, as well as peer packets in all other GOPs.
+Therefore, we can perform only one subtraction for this group, to obtain error vectors $e_{8}$ and $e_{10}$, for both packets 8 and 10, as well as peer packets in all other GOPs.
 Note that these error vectors are highly sparse ones, because the discarding of a single enhancement packet can bring distortion only to a limited number of frames.
-To acquire all error vectors, the number of required extraction and decoding is approximately the number of enhancement layers $(L_Q - 1)$ times the temporal layer number $L_T$.
+To acquire all error vectors, the number of required extraction and decoding is approximately the number of enhancement layers $(L_Q - 1)$ times the number of temporal layers $L_T$.
 For the example in Fig.
-\ref{fig:GOP_Structure}, $L_Q = 3$ and $L_T = 4$, so the extraction-and-decoding number is $(3 - 1) \times 4 = 8$.
-However, we have to do the same manipulation for $L_Q - 1 = 2$ more times, to dissociate the distortion impact of ``key frame'' \cite{H264Overview} (e.g.
-frame 0, 8, 16, etc.) packets.
+\ref{fig:GOP_Structure}, $L_Q = 3$ and $L_T = 4$, thus the extraction-and-decoding number would be $(3 - 1) \times 4 = 8$.
+However, we have to perform the same manipulation for $L_Q - 1 = 2$ more times, to dissociate the distortion impact of ``key frame'' \cite{H264Overview} (e.g.
+frame 0, 8, 16) packets.
 The loss of one enhancement packet in a key frame would bring distortion to two neighboring GOPs.
-As an instance, the loss of packet 4 would propagate error into frame 1 to 15, which would interfere with the distortion impact of packets in frame 0 and 16 (packet 1, 2 and 19, 20).
-So key frame enhancement packets within the same quality layer (e.g.
-packet 2, 4 and 20) should be allocated in two groups -- one for key frame packets of even number GOPs (packet 2 and 20), the other for those of odd number GOPs (packet 4).
-Therefore, the actual number of extraction and decoding for error vector acquisition is $(L_Q - 1) \cdot (L_T + 1)$, approximately the same with the Quality Layer information acquisition in JSVM \cite{Amonou07}.
+As an instance, the loss of packet 4 would propagate error into frame 1 to frame 15, which would interfere with the distortion impact of packets in frame 0 (packet 1, 2) and 16 (packet 19, 20).
+Therefore, key frame enhancement packets within the same quality layer (e.g.
+packet 2, 4 and 20) should be allocated in two groups -- one for key frame packets of even-numbered GOPs (packet 2 and 20), the other for those of odd-numbered GOPs (packet 4).
+The actual extraction-and-decoding number for error vector acquisition is $(L_Q - 1) \cdot (L_T + 1)$, approximately the same as that for the Quality Layer information acquisition in JSVM \cite{Amonou07}.
 
@@
 The enhancement layer is further divided into 2 Medium Grain Scalability (MGS) layers by configuring the MGS vector to separate the transform coefficients into two groups (containing 4 and 12 coefficients respectively).
-Random combinations of enhancement packets are removed from a bitstream, and the distortion estimated by the linear error model are compared with the distortion actually calculated after real decoding.
-Decoding is performed by JSVM decoder, while other operations are done by MATLAB.
-One comparison result for the test sequence {\em Foreman} (only first 33 frames are used) is shown in Fig.
+Random combinations of enhancement packets are removed from a bitstream, and the distortion estimated by the linear error model is compared with the distortion actually calculated after real decoding.
+Decoding is performed by the JSVM decoder, while other operations are performed with MATLAB.
+One comparison result for the test sequence {\em Foreman} (only the first 33 frames are used) is shown in Fig.
 \ref{fig:model_verification}.
-The horizontal axis stands for frame index, and the vertical axis for MSE measurement.
+The horizontal axis denotes the frame index, and the vertical axis for MSE measurement.
 The solid line represents the actual distortion of the frames, and the dot line represents the distortion estimated by the proposed linear error model.
@@
 Adopting more sophisticated or automated techniques to further optimize the parameter selection and controller performance will be our future work.
+The robustness of the controller will also be improved by adding a mechanism that dynamically adjusts the controller parameters based on environment and performance change.
 Note that, in the video quality control algorithm only the bitrate and the bandwidth are relevant, not the video content.

### 2016-01-12 tmm.tex
Change the second half part according to reply of editing service

@@
 \ref{fig:model_verification}.
-The horizontal axis denotes the frame index, and the vertical axis for MSE measurement.
-The solid line represents the actual distortion of the frames, and the dot line represents the distortion estimated by the proposed linear error model.
+The horizontal axis denotes the frame index, and the vertical axis denotes the MSE measurement.
+The solid line represents the actual distortion of the frames, and the dotted line represents the distortion estimated by the proposed linear error model.
 It can be seen that the two lines are very close to each other, which demonstrates the accuracy of estimation using the proposed model.
@@
 \includegraphics[width = 0.9\linewidth]{ModelVerification.png}
-\caption{Comparison of actual and estimated distortion for sequence {\em Foreman} \label{fig:model_verification}}
+\caption{Comparison of the actual and the estimated distortion for sequence {\em Foreman} \label{fig:model_verification}}
 \end{figure}
@@
 In this subsection, we utilize the linear error model to enable R-D optimized bitstream extraction.
-Since finding the global optimal solution of the bitstream extraction problem is impractical, our bitstream extraction method uses a greedy algorithm \cite{GreedyAlgo} to get a sub-optimal solution.
+Because finding the global optimal solution of the bitstream extraction problem is impractical, our bitstream extraction method uses a greedy algorithm \cite{GreedyAlgo} to obtain a sub-optimal solution.
 Note that the greedy algorithm is able to find a local optimum.
@@
 where $\partial D$ represents the distortion change brought by discarding this packet, and $\partial R$ is the corresponding rate change.
-$\partial R$ is simply equivalent to the size of this packet, while $\partial D$ needs to be calculated by subtraction of distortions before and after the packet is discarded.
-
-We simulate a process of discarding all the enhancement packets from a stream, using the above greedy strategy.
+$\partial R$ is simply equivalent to the size of this packet, while $\partial D$ needs to be calculated by subtracting the distortions before and after the packet is discarded.
+
+We simulate the process of discarding all the enhancement packets from a stream, using the above greedy strategy.
 During this process, the discarding order of a packet is regarded as its priority and recorded.
-Then the packets' priority values can be stored in the bitstream (either in the priority identifier field of the NALU header or in supplementary enhancement information messages) for real extraction in the future.
-
-For long video sequences, an optimization window containing a certain number of frames is needed, and the priority assignment and bitstream extraction is conducted independently in each window.
+Then, the packet priority values can be stored in the bitstream (either in the priority identifier field of the NALU header or in supplementary enhancement information messages) for real extraction in the future.
+
+For long video sequences, an optimization window containing a certain number of frames is required, and the priority assignment and bitstream extraction are conducted independently in each window.
 Suppose the size of the optimization window, i.e., the number of frames involved in the above process, is $K$, and each frame contains $L_Q$ quality layers (one base layer and $L_Q-1$ enhancement layers).
-Then the total number of enhancement packets to be discarded is $K \cdot (L_Q-1)$, and in every greedy step, there are at most $K$ packets, i.e., the packets currently at the top of every frame (see analysis in \ref{subsec:analysis-extraction}), that can be selected to discard.
+Then, the total number of enhancement packets to be discarded is $K \cdot (L_Q-1)$, and in every greedy step, there are at most $K$ packets, i.e., the packets currently at the top of every frame (see analysis in \ref{subsec:analysis-extraction}), that can be selected for discarding.
 Given that, the priority assignment process in each optimization window can be described in Algorithm \ref{algo:greedy}, with some terms in it explained below.
@@
 \end{equation}
-where $SIZE(i)$ is the size of packet $i$, and $PSNR(*)$ is the function to obtain PSNR from an error vector.
-To be clear, PSNR is defined via mean squared error (MSE), i.e., the average of the squares of the elements in the error vector.
+where $SIZE(i)$ is the size of packet $i$, and $PSNR(*)$ is the function for obtaining PSNR from an error vector.
+For clarification, PSNR is defined using the mean squared error (MSE), i.e., the average of the squares of the elements in the error vector.
 
@@
 	    \FOR{the (at most) $K$ top layer packets}
-		    \STATE Find the packet $m$ which has the least RD impact $\Phi_m$
+		    \STATE Find the packet $m$ that has the least RD impact $\Phi_m$
 		\ENDFOR
@@
 It is easy to see that the computational complexity of this priority assignment algorithm is $O(K^2)$.
-Note that, the computation in this priority assignment process is actually very insignificant compared with the decoding process needed in the error vector acquisition.
+Note that, the computation in this priority assignment process is actually very insignificant compared with the decoding process required for the error vector acquisition.
 With a larger optimization window size $K$, we would have more packets to compare and determine their priorities each time, which will potentially result in more optimized extraction.
-However, doing this will also bring more computation and, more noticeably, increase the memory used to store the error vectors.
-Besides, if the priority values are to be stored and signalled using the 6-bit priority identifier field of the NALU header \cite{Amonou07}, only a range of 0$\sim$63 is supported, which also limits the value of $K$.
+However, doing this will also require more computation and, more noticeably, increase the memory used to store the error vectors.
+Besides, if the priority values are to be stored and signaled using the 6-bit priority identifier field of the NALU header \cite{Amonou07}, only a range of 0$\sim$63 is supported, which also limits the value of $K$.
 
@@
 
-In some scenarios, the priority assignment and bitstream extraction needs to be conducted without access to the original video sequence.
-This would make the bitstream extraction a more difficult problem, since the distortion is harder to obtain for lacking of reference signal.
-The ``no-reference bitstream extraction'' problem is actually more frequently encountered in real practice, since it is more common for the streaming service provider to have the compressed bitstream rather than the video source.
-In this subsection, we consider this no-reference case and modify the proposed algorithm to meet the special characteristic caused by lacking of reference.
-
-Without the original video sequence, we cannot get the error between the video sequence decoded from full enhancement packets and the original sequence, which is $e_{full}$ used in \ref{algo:greedy}.
-A straightforward idea is to set $e_{full}$ to zero, meaning all distortions are calculated with respect to the fully reconstructed signal, rather than to the original sequence.
+In some scenarios, the priority assignment and bitstream extraction need to be conducted without access to the original video sequence.
+This would make the bitstream extraction a more difficult problem, because the distortion is harder to obtain as the reference signal is not available.
+This ``no-reference bitstream extraction'' problem is actually more frequently encountered in real practice, because it is more common for the streaming service provider to have a compressed bitstream rather than the video source.
+In this subsection, we consider this no-reference case and modify the proposed algorithm to meet the special characteristics caused by lacking of reference.
+
+Without the original video sequence, we cannot obtain the error between the video sequence decoded from full enhancement packets and the original sequence, which is $e_{full}$ used in \ref{algo:greedy}.
+A straightforward idea is setting $e_{full}$ to zero, which means that all distortions are calculated with respect to the fully reconstructed signal, rather than the original sequence.
 However, simply doing so causes the algorithm to perform badly in experiments.
-It is found that, since discarding some enhancement packets will not bring much significant error, the calculated PSNR values are too large to well represent the real distortion.
-To address this issue, instead of calculating PSNR, we directly use MSE of all pixels as the distortion criteria in the priority assignment algorithm.
-This proves to be an effective solution, and the extraction performance turns out to be much better.
-
-After each packet is assigned a priority value and optimized extraction is made possible, the video stream now can well adapt to different bitrates.
-Next, we propose the quality control algorithm based on the PID mechanism, which is responsible for determining the suitable bitrate for transmission according to current network condition.
+It is found that, as discarding some enhancement packets will not result in much significant error, the calculated PSNR values are too large to properly represent the real distortion.
+To address this issue, instead of calculating the PSNR, we directly use the MSE of all pixels as the distortion criteria in the priority assignment algorithm.
+This proves to be an effective solution, and the extraction performance turns out to be improved.
+
+After each packet is assigned a priority value and an optimized extraction is made possible, the video stream can now adapt to different bitrates well.
+Next, we propose a quality control algorithm based on the PID mechanism, which is responsible for determining the suitable bitrate for transmission according to the current network conditions.
 
@@
 
-PID controller \cite{PID}\cite{Astrom02} is a control loop feedback mechanism commonly used in industrial control systems.
+The PID controller \cite{PID}\cite{Astrom02} is a control loop feedback mechanism commonly used in industrial control systems.
 \textit{Process variable} and \textit{setpoint} are two core concepts in PID control.
@@
 The setpoint is the target for this system to reach.
-The goal of PID control is to minimize the error between process variable and setpoint.
+The goal of PID control is to minimize the error between the process variable and the setpoint.
 The controller output $u(t)$ is defined as follows:
@@
 \end{equation}
-where $e(t)$ represents the error between process variable and setpoint at time $t$.
-$K_p$, $K_i$, and $K_d$ here are tuning parameters representing the proportional gain, integral gain and derivative gain, respectively.
-The result of (\ref{eq:pid-output}) is used for manipulating the system to make process variable change towards setpoint.
-
-As an effective and flexible control technique, PID control has been used to solve all kinds of control problems.
-In the area of video coding, we notice that PID is utilized to design rate control algorithms (rate control in video coding is mainly to adjust the encoding parameters for every frame, so that the bits are appropriately allocated and desired bitrate is achieved) \cite{Wong04}\cite{Yang10}.
-We also notice that some researchers have proposed theoretical model or middle-ware framework for QoS adaptation \cite{Li98}\cite{Li99}, with PID as the basic control scheme.
-However, we have not found any paper that integrates PID method into the quality control of video streaming.
+where $e(t)$ represents the error between the process variable and the setpoint at time $t$.
+$K_p$, $K_i$, and $K_d$ here are tuning parameters that represent the proportional gain, integral gain and derivative gain, respectively.
+The result of (\ref{eq:pid-output}) is used for manipulating the system to make the process variable change towards the setpoint.
+
+As an effective and flexible control technique, PID control has been used to solve many kinds of control problems.
+In the area of video coding, we notice that PID is utilized to design rate control algorithms (rate control in video coding mainly involves adjusting the encoding parameters for every frame, so that the bits are appropriately allocated and the desired bitrate is achieved) \cite{Wong04}\cite{Yang10}.
+We also notice that some researchers have proposed a theoretical model or middle-ware framework for QoS adaptation \cite{Li98}\cite{Li99}, with PID as the basic control scheme.
+However, we have not found any paper that integrates the PID method into the quality control of video streaming.
 While rate control of video coding and quality control of video streaming are two different problems, they do share some common properties, such as the buffer mechanism and the requirement for smoothness.
-That inspires us to design a PID-based quality control algorithm and utilize it to deliver better video quality to the user.
-
-In this section, we first introduce the \textit{quality level} concept to discretize the bitrate and quality of scalable video.
+We are therefore inspired to design a PID-based quality control algorithm and utilize it to deliver better video quality to the user.
+
+In this section, we first introduce the \textit{quality level} concept to discretize the bitrate and quality of a scalable video.
 Then we define the process variable used in our PID-based quality control algorithm.
-After that, the algorithm is formulated and explained in detail, followed by the brief discussion of parameter selection.
+After that, the algorithm is formulated and explained in detail, followed by a brief discussion on parameter selection.
 
@@
 The video quality is a continuous value, and it is impractical to control it at an arbitrary precision.
-Therefore we propose a \textit{quality level} concept as the discrete description of the video quality.
-When the video quality needs to be adjusted, we simply increase or decrease the quality level.
+Therefore, we propose a \textit{quality level} concept for a discrete description of the video quality.
+When the video quality is to be adjusted, we simply increase or decrease the quality level.
 Each quality level corresponds to a certain bitrate.
-A higher quality level corresponds to a higher bitrate and vice versa.
-The number of quality levels and how they are mapped to sub-streams with different bitrates depends on actual requirement or implementation.
+A higher quality level corresponds to a higher bitrate, and vice versa.
+The number of quality levels and how they are mapped to sub-streams with different bitrates depend on the actual requirements or implementation.
 The more quality levels are defined, the more precisely the control algorithm can adjust bitrate to follow the bandwidth change.
@@
 In DSS, two timelines are important.
-Push timeline indicates the time of pushing video data packets to streaming buffer, and play timeline indicates the time these data packet should be played, i.e., the presentation time stamp (often seen as PTS) of each packet.
+Push timeline indicates the time of pushing video data packets to the streaming buffer, and play timeline indicates the time these data packet should be played, i.e., the presentation time stamp (often seen as PTS) of each packet.
 Their relationship is shown in Fig.
@@
 \ref{fig:intervals}, i.e., check interval and actual interval, are worth noticing and may provide useful information.
-In the ideal situation, during each check interval, the server pushes an amount of data that will actually play for a period of time equal to that check interval, i.e., \textit{actual\_interval} = \textit{check\_interval}.
+In the ideal situation, during each check interval, the server pushes an amount of data that will actually play for a period of time equal to the check interval, i.e., \textit{actual\_interval} = \textit{check\_interval}.
 If \textit{actual\_interval} is smaller than \textit{check\_interval}, it means that less data is pushed to the client, and the pushing is slowed down because bandwidth is relatively low at this time.
-On the other hand, if \textit{actual\_interval} is larger than \textit{check\_interval}, it indicates the network condition is good and data is being pushed quickly to the client.
-The ratio of these two intervals, i.e., \textit{actual\_check interval ratio}, is in direct proportion to the ratio of the bitrate suitable for the network condition and the bitrate currently being used.
-
-The \textit{actual\_check interval ratio} is suitable to use in quality control because: 1) this ratio directly reflects the mismatch of current pushing bitrate and the bandwidth, and by adjusting bitrate according to it, this ratio can be used to accurately change video quality; 2) the desired value of this ratio is 1.0 by definition so we don't need to find the optimized setpoint by mathematical methods or experiments; and 3) it is easy to compute and implement in practical systems.
+On the other hand, if \textit{actual\_interval} is larger than \textit{check\_interval}, it indicates that the network conditions are good and the data are being pushed quickly to the client.
+The ratio of these two intervals, i.e., \textit{actual\_check interval ratio}, is in direct proportion to the ratio of the bitrate suitable for the network conditions and the bitrate currently being used.
+
+The \textit{actual\_check interval ratio} is suitable for use in quality control because: 1) this ratio directly reflects the mismatch of the current pushing bitrate and the bandwidth, and by adjusting the bitrate according to it, this ratio can be used to accurately change the video quality; 2) the desired value of this ratio is 1.0 by definition, therefore, we do not need to determine the optimized setpoint using mathematical methods or experiments; and 3) it is easy to compute and implement in practical systems.
 
@@
 \includegraphics[width = 0.9\linewidth]{Intervals.png}
-\caption{Two timelines in Darwin Streaming Sever (DSS) \label{fig:intervals}}
+\caption{Two timelines in the Darwin Streaming Sever (DSS) \label{fig:intervals}}
 \end{figure}
@@
 Considering that the chosen process variable is a ratio and the corresponding setpoint is 1, we make a little modification to the general PID controller and obtain a ratio-based model.
-In this model, the ratio is directly used to calculate the controller output, and all subtraction operations in original PID equations have been properly changed to division operations to keep the correctness, as follows:
+In this model, the ratio is directly used to calculate the controller output, and all subtraction operations in the original PID equations have been properly changed to division operations for correctness, as follows:
 
@@
 
-In (\ref{eq:ut}), $K_p$, $K_i$, and $K_d$ indicate the tuning parameters for proportional, integral and derivative parts respectively, and $E_p^t$, $E_i^t$, $E_d^t$ stand for the corresponding observed value for each part, which are defined in (\ref{eq:ep})-(\ref{eq:long-check}); the controller output $u_t$ is utilized to calculate a suitable bitrate for transmission and further to determine which quality level should be selected (see Algorithm \ref{algo:control} for more details).
+In (\ref{eq:ut}), $K_p$, $K_i$, and $K_d$ indicate the tuning parameter for the proportional, integral and derivative part, respectively, and $E_p^t$, $E_i^t$, $E_d^t$ stand for the corresponding observed values for each part, which are defined in (\ref{eq:ep})-(\ref{eq:long-check}); the controller output $u_t$ is utilized to calculate a suitable bitrate for transmission and further to determine which quality level should be selected (see Algorithm \ref{algo:control} for more details).
 
@@
 Theoretically, the integral part should be recorded and calculated since the system starts.
-In practice, however, bandwidth may change significantly during the transmission.
-If the integral part is recorded for too long time, it may fail to reflect the current network condition and thus slow down the reaction for better quality level.
-A compromise here is to choose a relatively long time, i.e., the time from last quality change till now, for the integral part calculation.
+In practice, however, the bandwidth may change significantly during the transmission.
+If the integral part is recorded for too long time, it may fail to reflect the current network conditions and thus slow down the reaction for better quality levels.
+A compromise here is to choose a relatively long time, i.e., the time from last quality change till now, for the calculation of the integral part.
 
 This ratio-based model is more simple and effective for the chosen process variable and setpoint.
-Moreover, in this model the controller output has intuitive meaning when the three parameters are normalized.
-It is easy to know that $E_p^t$, $E_i^t$, $E_d^t$ are all ratios with a value more or less than 1, and the controller output $u_t$ can be seen as a weighted average of the three ratios, with the three parameters as weights.
-Therefore the controller output is also a ratio value around 1, which reflects the relationship between the bitrate suitable for the network condition and the bitrate currently being used.
-In other words, if the output is larger than 1, then the controller has determined the bitrate should be increased accordingly, and vice versa.
-Use it as a multiplier to manipulate the bitrate currently being used, and we would be able to control the streaming system to match the network condition.
-
-The whole process of the proposed algorithm is described in Algorithm \ref{algo:control}.
+Moreover, in this model, the controller output has intuitive meaning when the three parameters are normalized.
+It is easy to see that $E_p^t$, $E_i^t$, $E_d^t$ are all ratios with a value around 1, and the controller output $u_t$ can be seen as a weighted average of the three ratios, with the three parameters as weights.
+Therefore, the controller output is also a ratio with a value around 1, which reflects the relationship between the bitrate suitable for the network conditions and the bitrate currently being used.
+In other words, if the output is larger than 1, then the controller has determined that the bitrate should be increased accordingly, and vice versa.
+Use it as a multiplier to manipulate the bitrate currently being used, and we would be able to control the streaming system to match the network conditions.
+
+The proposed algorithm is described in Algorithm \ref{algo:control}.
 Compared to other scheduling strategies, this quality control algorithm has several advantages.
-First, this algorithm does not just rely on current packet delay or information at a fixed time point, therefore quality change may occur at any proper time.
-Second, since the model has taken prediction into account, it is able to decide whether the bandwidth will be high or low enough for the quality level to change in the near future, thus to avoid unnecessary quality change.
+First, this algorithm does not just rely on the current packet delay or the information at a fixed time point; therefore, a quality change may occur at any proper time.
+Second, because the model takes prediction into account, it is able to decide whether the bandwidth will be high or low enough for the quality level to change in the near future, so as to avoid unnecessary quality changes.
 Third, in this algorithm it's not obliged to change one quality level at a time.
-This enables fast quality drop to avoid a latent playback pause when bandwidth suddenly decreases, and also fast quality rise to provide better video as soon as possible when system starts, resulting in a seamless watching experience where the user can enjoy the video without stopping or waiting.
+This enables a fast quality drop to avoid latent playback pause when bandwidth suddenly decreases, as well as a fast quality rise to provide better video as soon as possible when system starts, resulting in a seamless watching experience, where the user can enjoy the video without stopping or waiting.
 
@@
     \ENDIF
-    \STATE send packet according to new quality level
+    \STATE send packet according to the new quality level
 \end{algorithmic}
@@
 
-As with other PID control systems in the industry, the selection of the three parameters is implementation-dependent and most of the time manual tuning with trial and error is required to achieve optimal results.
-Each parameter has impacts on different aspects of the system, and knowing them is useful in the practice of parameter selection.
-Generally, the proportional part in PID controller affects the system's stability.
+As with other PID control systems in the industry, the selection of the three parameters is implementation-dependent, and most of the time, manual tuning with trial and error is required to achieve optimal results.
+Each parameter has impacts on different aspects of the system, and knowing these impacts is useful for parameter selection.
+Generally, the proportional part in the PID controller affects the system's stability.
 If the proportional gain $K_p$ is too high, the system can become unstable.
-However, a low $K_p$ would result in long rising time that makes the system response slowly.
-In addition to eliminating steady-state error, the integral term also accelerates the movement of the process towards setpoint, which means increasing $K_i$ can reduce the rising time.
-However, since the integral part accumulates errors from the past, it can cause the present value to overshoot the setpoint value, and too much $K_i$ will lead to instability as well.
-These can all be compensated by the derivative part, which predicts system behaviour and has the effect of reducing the overshoot, increasing the stability, and improving the settling time (time it takes to reach setpoint after a disturbance).
-The big problem with the derivative part is that it is very sensitive to noise, therefore industrial practices indicate that the derivative gain $K_d$ should usually stay low.
-
-For the proposed quality control algorithm, Ziegler--Nichols method \cite{Ziegler42} is used to select the parameters for better performance.
-This method is performed by setting integral and derivative parameters to zero and then tuning $K_p$ to a value $K_u$ until output begins to oscillate with constant amplitude.
-Assuming the oscillation period is $T_u$, we set $K_p = 0.6K_u$, $K_i = 2K_u/T_u$, and $K_d = K_u \cdot T_u/8$.
-$K_p$, $K_i$, and $K_d$ are then normalized to get the final parameters.
-In the following experiments, parameters are chosen as $K_p = 0.22$, $K_i = 0.73$, $K_d = 0.05$ by this method.
-With these parameters, the PID-controlled streaming system is stable, and also quickly begins to follow the bandwidth change, as shown by the experimental results in next section.
-
-We choose to use the standard Ziegler--Nichols method because it already takes each parameter's impacts into consideration and produces acceptably good results.
+However, a low $K_p$ would result in a long rising time that makes the system response slow.
+In addition to eliminating the steady-state error, the integral term also accelerates the movement of the process value towards the setpoint, which means that increasing $K_i$ can reduce the rising time.
+However, because the integral part accumulates errors from the past, it can cause the present value to overshoot the setpoint value, and a too high $K_i$ will lead to instability as well.
+These can all be compensated by the derivative part, which predicts the system behavior and has the effect of reducing the overshoot, increasing the stability, and improving the settling time (the time taken to reach setpoint after a disturbance).
+The issue with the derivative part is that it is very sensitive to noise; therefore, industrial practices indicate that the derivative gain $K_d$ should usually stay low.
+
+For the proposed quality control algorithm, the Ziegler--Nichols method \cite{Ziegler42} is used to select the parameters for better performance.
+This method is performed by setting the integral and derivative parameters to zero and then tuning $K_p$ to the value $K_u$ until the output begins to oscillate with constant amplitude.
+Assuming that the oscillation period is $T_u$, we set $K_p = 0.6K_u$, $K_i = 2K_u/T_u$, and $K_d = K_u \cdot T_u/8$.
+$K_p$, $K_i$, and $K_d$ are then normalized to obtain the final parameters.
+In the following experiments, the parameters are chosen as $K_p = 0.22$, $K_i = 0.73$, $K_d = 0.05$ using this method.
+With these parameters, the PID-controlled streaming system is stable, and also quickly begins to follow the bandwidth change, as shown by the experimental results in the next section.
+
+We choose to use the standard Ziegler--Nichols method because it already considers each parameter's impacts and produces acceptably good results.
 Adopting more sophisticated or automated techniques to further optimize the parameter selection and controller performance will be our future work.
-The robustness of the controller will also be improved by adding a mechanism that dynamically adjusts the controller parameters based on environment and performance change.
-Note that, in the video quality control algorithm only the bitrate and the bandwidth are relevant, not the video content.
-Therefore once the parameters are chosen they should apply well to different video streams.
+The robustness of the controller can also be improved by adding a mechanism that dynamically adjusts the controller parameters based on environment and performance change.
+Note that in the video quality control algorithm, only the bitrate and the bandwidth are relevant, not the video content.
+Therefore, once the parameters are chosen, they should apply well to different video streams.
 
@@
 
-To implement our proposed adaptive streaming system requires the combination of the optimized bitstream extraction and the PID-based quality control algorithm.
-The latter determines the current bitrate to follow the bandwidth change, and the former will ensure the sub-stream with the best possible quality is obtained and sent under that bitrate constraint.
+Implementing our proposed adaptive streaming system requires the combination of the optimized bitstream extraction and the PID-based quality control algorithm.
+The latter determines the current bitrate to follow the bandwidth change, and the former will ensure that the sub-stream with the best possible quality is obtained and sent under that bitrate constraint.
 They work together to improve the user's experience of watching online videos.
-With DSS as the implementation basis, we have integrated the proposed algorithms into it for the purpose of both research and application.
-
-In this section, we first present separate experiments to show the advantage of each proposed solution, then give the result when they are combined together.
+With DSS as the implementation basis, we have integrated the proposed algorithms into it for the purpose of both research and applications.
+
+In this section, we first present separate experiments to show the advantage of each proposed solution, and then present the result when they are combined together.
 
@@
 
-All test bitstreams are encoded the same way as in the verification experiment of Section III-C.
-For each test bitstream, ten bitrate points (one with all enhancement packets, one with only the base layer packets, and 8 uniformly spaced points between) are chosen for extraction.
+All the test bitstreams are encoded the same way as in the verification experiment of Section III-C.
+For each test bitstream, ten bitrate points (one with all enhancement packets, one with only the base layer packets, and 8 uniformly spaced points in between) are chosen for extraction.
 For each bitrate point, the extraction is conducted using the bitstream extractors in JSVM, with and without \textit{Quality Layers} (denoted as JSVM QL and JSVM Basic, respectively), and the proposed method.
@@
 For each sequence, the maximum and average PSNR gain through all 10 bitrate points are calculated and listed in Table \ref{tab:extraction-gain}, which shows that our extraction method can achieve a significant performance gain compared with JSVM Basic, and also performs better than JSVM QL.
-Table \ref{tab:extraction-gain} also contains results when the optimization window size is set to 48 frames, i.e., 6 GOPs.
-It is demonstrated that a larger window size can increase performance to some degree.
-However, it should be noted that, in practice the optimization window may not be that large, for the reason stated at the end of Section \ref{subsec:priority-assign}.
-
-Among other bitstream extraction methods besides that of JSVM, the work in \cite{Maani09} achieves much better performance than JSVM QL, and even better than ours.
-However, the method of \cite{Maani09} needs more computation in order to train robust model parameters for different sequences, while the complexity of our method is always the same with JSVM QL.
-As far as we know, without significantly increasing the complexity, it is difficult to achieve large PSNR gain.
+Table \ref{tab:extraction-gain} also presents the results obtained when the optimization window size is set to 48 frames, i.e., 6 GOPs.
+It is demonstrated that a larger window size can increase the performance to some degree.
+However, it should be noted that, in our implementation of the proposed system, the optimization window is not that large, for the reason stated at the end of Section \ref{subsec:priority-assign}.
+
+Regarding other bitstream extraction methods in addition to JSVM, the work in \cite{Maani09} achieves a much better performance than JSVM QL, and even better than ours.
+However, the method of \cite{Maani09} requires more computation in order to train robust model parameters for different sequences, while the complexity of our method is always the same with JSVM QL.
+As far as we know, without significantly increasing the complexity, it is difficult to achieve a large PSNR gain.
 
@@
 
-For simplicity and intuition, in the experiments for the quality control algorithm, we combine the scalability layers in the tested SVC video stream to construct quality levels introduced in \ref{subsec:quality-level}.
+For simplicity and intuition, in the experiments for the quality control algorithm, we combine the scalability layers in the tested SVC video stream to construct the quality levels introduced in \ref{subsec:quality-level}.
 The basic idea is to divide the video stream's data packets (NALUs) into several groups, according to the combination of scalability layers they belong to, i.e., the layer IDs in the NALU header.
-The association of the group ID with layer IDs is illustrated in Table \ref{tab:sub-stream} (the stream has 3 scalability layers in each of the quality and temporal dimension, therefore data packets are separated to 9 groups).
-The quality level is then defined as the sum of all groups with ID equal or less than the level number.
-For example, quality level 2 contains all data packets from Group 0 to 2, thus would include all temporal layers, but only the quality base layer 0; quality level 5 contains Group 0 to 5, thus would further add the data packets in quality enhancement layer 1.
-Like that, as the quality level increases, more enhancement packets are accumulated and the video quality becomes better.
+The association of the group ID with layer IDs is illustrated in Table \ref{tab:sub-stream} (the stream has 3 scalability layers in each of the quality and temporal dimensions; therefore, the data packets are separated into 9 groups).
+The quality level is then defined as the sum of all groups with an ID equal to or less than the level number.
+For example, quality level 2 contains all the data packets from Group 0 to 2, thus would include all temporal layers, but only the quality base layer 0; quality level 5 contains Group 0 to 5, thus would further add the data packets in quality enhancement layer 1.
+Like that, as the quality level increases, more enhancement packets are accumulated and the video quality is improved.
 At the same time the bitrate also goes up, which is quite straight-forward, since better quality needs more data.
-The bitrate for the whole stream in test is 1587 kbps, which corresponds to the highest level 8.
-Combining the scalability layers in SVC to construct quality levels is simple and intuitive in that no extra data is required other than the layer IDs already contained in the bitstream.
+The bitrate for the whole stream in the test is 1587 kbps, which corresponds to the highest level.
+Combining the scalability layers in SVC to construct quality levels is simple in that no extra data are required other than the layer IDs already contained in the bitstream.
 
@@
 \centering
-\caption{Association of group ID with layer IDs during quality level definition}
+\caption{Association of the group ID with the layer IDs during the quality level definition}
 \label{tab:sub-stream}
@@
 
-We simulate bandwidth fluctuation by adjusting bandwidth around a certain level.
-We set this level from 400 to 1400 kbps to reflect different average bandwidth.
+We simulate the bandwidth fluctuation by adjusting the bandwidth around a certain level.
+We set this level from 400 to 1400 kbps to reflect different average bandwidth values.
 The simulation is implemented with NetLimiter 3 \cite{Netlimiter}, where the bandwidth varies randomly and intense fluctuations are observed.
-Under the bandwidth fluctuation, the streaming system with certain quality control algorithm runs for 10 minutes, during which the selected quality levels are recorded.
+Under the bandwidth fluctuation, the streaming system with a certain quality control algorithm runs for 10 minutes, during which the selected quality levels are recorded.
 The video quality measured by average of the quality levels, and the quality smoothness indicated by the variance of the quality levels are used for performance comparison.
@@
 
-First of all, we conduct some preliminary improvement experiments using only the proportional part or integral part of the PID model.
-Since the two parts are related to the current short term error and the accumulated long term error respectively, we call them Short Term Prediction (STP) and Long Term Prediction (LTP).
+We first conduct some preliminary improvement experiments using only the proportional part or integral part of the PID model.
+Because the two parts are related to the current short-term error and the accumulated long-term error, we call them Short-Term Prediction (STP) and Long-Term Prediction (LTP), respectively.
 Fig.
-\ref{fig:performance-all} shows the experimental results of these two control algorithms and the baseline algorithm.
+\ref{fig:performance-all} shows the experimental results for the two control algorithms and the baseline algorithm.
 We can conclude that STP provides the highest average quality level at the expense of high quality variance.
 This can be easily explained since STP tends to closely follow the bandwidth fluctuation.
-In contrast, LTP keeps a relatively low quality variance at a little cost of average video quality.
-Although it is not as good as STP in average quality, it still outperforms the baseline algorithm.
-
-Since STP and LTP have their own limitations, we implement the complete PID-based quality control algorithm, which can both reduce quality variance and improve average quality level.
-From the result shown in Fig.
-\ref{fig:performance-two}, we can conclude that when integrated with the integral part and the derivative part, the effect of the proportional part is not as aggressive as in STP.
+In contrast, LTP maintains a relatively low quality variance, at a little cost of average video quality.
+Although it is not as good as STP in terms of average quality, it still outperforms the baseline algorithm.
+
+Since STP and LTP have their own limitations, we implement the complete PID-based quality control algorithm, which can both reduce the quality variance and improve the average quality level.
+From the results shown in Fig.
+\ref{fig:performance-two}, we can conclude that when integrated with the integral part and the derivative part, the effect of the proportional part is not as aggressive as that in STP.
 An obvious proof can be found in Fig.
-\ref{fig:variance-two}, which clearly shows that the proposed PID quality control algorithm achieves a lower quality variance compared to PDF algorithm.
-Table \ref{tab:improvement} lists the statistical experimental results for these four quality control algorithms, in which PID-based control algorithm has shown its advantage over the others, especially in reducing the quality fluctuation.
-It can be seen that, compared to PDF, the PID-based quality control algorithm improves 8.6\% in video quality with 24.8\% reduction in quality fluctuation.
-The video quality fluctuation of the four control algorithms, when available bandwidth fluctuates around 800 kbps, is shown in Fig.
-\ref{fig:fluctuation}, from which we can see a more stable video quality in the proposed PID quality control algorithm.
+\ref{fig:variance-two}, which clearly shows that the proposed PID quality control algorithm achieves a lower quality variance compared to the PDF algorithm.
+Table \ref{tab:improvement} lists the statistical experimental results for these four quality control algorithms, in which the PID-based control algorithm has shown its advantage over the others, especially in reducing the quality fluctuation.
+It can be seen that, compared to PDF, the PID-based quality control algorithm improves 8.6\% in video quality with a 24.8\% reduction in quality fluctuation.
+The video quality fluctuation of the four control algorithms, when the bandwidth fluctuates around 800 kbps, is shown in Fig.
+\ref{fig:fluctuation}, from which we can observe a more stable video quality in the proposed PID quality control algorithm.
 
@@
 \centering
-\subfloat[Average quality level of PID and PDF control algorithms]{
+\subfloat[Average quality level of the PID and PDF control algorithms]{
 \includegraphics[width=0.42\textwidth]{Quality-two.png}
 \label{fig:quality-two}}
-\subfloat[Quality level variance of PID and PDF control algorithms]{
+\subfloat[Quality level variance of the PID and PDF control algorithms]{
 \includegraphics[width=0.42\textwidth]{Variance-two.png}
@@
 
-\subsection{Result of the Combined System}
+\subsection{Results of the Combined System}
 \label{subsec:exp-combined}
@@
 The system works as follows.
-The greedy-like algorithm present in \ref{subsec:priority-assign} is performed first to determine priority values for all enhancement NALUs in an SVC bitstream.
-Then the priority values are injected into the bitstream and stored in the priority identifier field of the NALU header.
+The greedy-like algorithm present in \ref{subsec:priority-assign} is performed first to determine the priority values for all enhancement NALUs in an SVC bitstream.
+Then, the priority values are injected into the bitstream and stored in the priority identifier field of the NALU header.
 When DSS streams this video, it can extract an optimized sub-stream by simply checking this field and discarding the packets with lower priority values.
@@
 
-We compare the combined system's performance with DSS that supports SVC but has its original quality control method and JSVM Basic bitstream extraction.
-The result for the test sequence Soccer is present in Fig.
-\ref{fig:fluctuation-psnr}.
-It shows the streamed video's PSNR change when available bandwidth fluctuates around 400kbps, 600kbps, 800kbps and 1000kbps (bandwidth fluctuation is simulated the same way as in the previous experiments).
-It can be seen that, the proposed system performs better in that it has effectively avoided unnecessary quality drop (e.g., note the curve around time 350s in Fig.
-\ref{fig:Fluctuation-PSNR3} or 150s in Fig.
-\ref{fig:Fluctuation-PSNR4}) and been able to keep a relatively higher PSNR value (e.g., note the curve around time 450s in Fig.
-\ref{fig:Fluctuation-PSNR1} or 500s in Fig.
+We compare the combined system's performance with DSS that supports SVC but uses its original quality control method and the JSVM Basic bitstream extraction.
+The result for the test sequence Soccer is presented in Fig.
+\ref{fig:fluctuation-psnr}, which shows the change of the streamed video's PSNR when the available bandwidth fluctuates around 400 kbps, 600 kbps, 800 kbps and 1000 kbps (bandwidth fluctuation is simulated the same way as in the previous experiments).
+It can be seen that, the proposed system performs better in that it has effectively avoided unnecessary quality drops (e.g., note the curve around time 350 s in Fig.
+\ref{fig:Fluctuation-PSNR3} or 150 s in Fig.
+\ref{fig:Fluctuation-PSNR4}) and is able to keep a relatively higher PSNR value (e.g., note the curve around time 450 s in Fig.
+\ref{fig:Fluctuation-PSNR1} or 500 s in Fig.
 \ref{fig:Fluctuation-PSNR2}).
-The average and variance value of PSNR through the time is also calculated and present in Fig.
+The average and variance of the PSNR through the time are also calculated and presented in Fig.
 \ref{fig:fluctuation-psnr}, showing clearly the proposed system's advantage.
 For instance, in Fig.
-\ref{fig:Fluctuation-PSNR3} where bandwidth fluctuates around 800kbps, the average PSNR delivered by the proposed system is 38.75dB, 0.83dB higher than that of the baseline system, and the PSNR variance is also reduced from 1.24 to 0.69, indicating a more smooth video quality change.
+\ref{fig:Fluctuation-PSNR3} where the bandwidth fluctuates around 800 kbps, the average PSNR delivered by the proposed system is 38.75 dB, 0.83 dB higher than that of the baseline system, and the PSNR variance is also reduced from 1.24 to 0.69, indicating a smoother video quality change.
 
@@
 \centering
-\subfloat[Bandwidth fluctuates around 400kbps: PSNR average and variance in the original system are 36.00 and 0.30, while in the proposed system are 36.50 (increased by 0.50) and 0.23 (reduced by 0.07).]{
+\subfloat[Bandwidth fluctuates around 400 kbps: the PSNR average and variance in the original system are 36.00 and 0.30, while in the proposed system are 36.50 (increased by 0.50) and 0.23 (reduced by 0.07).]{
 \includegraphics[width=0.45\textwidth]{Fluctuation-PSNR1.png}
 \label{fig:Fluctuation-PSNR1}}\hfill
-\subfloat[Bandwidth fluctuates around 600kbps: PSNR average and variance in the original system are 37.06 and 0.61, while in the proposed system are 37.32 (increased by 0.26) and 0.33 (reduced by 0.28).]{
+\subfloat[Bandwidth fluctuates around 600 kbps: the PSNR average and variance in the original system are 37.06 and 0.61, while in the proposed system are 37.32 (increased by 0.26) and 0.33 (reduced by 0.28).]{
 \includegraphics[width=0.45\textwidth]{Fluctuation-PSNR2.png}
@@
 \qquad
-\subfloat[Bandwidth fluctuates around 800kbps: PSNR average and variance in the original system are 37.92 and 1.24, while in the proposed system are 38.75 (increased by 0.83) and 0.69 (reduced by 0.55).]{
+\subfloat[Bandwidth fluctuates around 800 kbps: the PSNR average and variance in the original system are 37.92 and 1.24, while in the proposed system are 38.75 (increased by 0.83) and 0.69 (reduced by 0.55).]{
 \includegraphics[width=0.45\textwidth]{Fluctuation-PSNR3.png}
 \label{fig:Fluctuation-PSNR3}}\hfill
-\subfloat[Bandwidth fluctuates around 1000kbps: PSNR average and variance in the original system are 38.28 and 1.30, while in the proposed system are 38.94 (increased by 0.66) and 0.71 (reduced by 0.59).]{
+\subfloat[Bandwidth fluctuates around 1000 kbps: the PSNR average and variance in the original system are 38.28 and 1.30, while in the proposed system are 38.94 (increased by 0.66) and 0.71 (reduced by 0.59).]{
 \includegraphics[width=0.45\textwidth]{Fluctuation-PSNR4.png}
 \label{fig:Fluctuation-PSNR4}}
-\caption{The streamed video's PSNR change with time when bandwidth fluctuates
+\caption{Change of the streamed video's PSNR during bandwidth fluctuation
 \label{fig:fluctuation-psnr}}
@@
 The priority values can then be stored in the bitstream and used for R-D optimized extraction.
-Experimental results show that the method can achieve PSNR gain of up to 0.5dB compared to the JSVM QL extractor under the same bitrate constraint, also with the same computational complexity.
-The PID-based quality control algorithm has a flexible mechanism to determine the suitable quality level so that it gives an accurate and swift response to the bandwidth change.
-Comparing with the original algorithm in DSS, this algorithm has reduced quality fluctuation significantly to improve audience satisfaction.
-The proposed SVC adaptive streaming system integrated with these two solutions performs well in automatically adapting to the user's bandwidth fluctuation, and is able to give the user a better watching experience.
-
-Since the next generation video coding standard High Efficiency Video Coding (HEVC) \cite{HEVC} adopts the similar coding framework as its predecessor H.264/AVC, we expect to apply this paper's model and approach of bitstream extraction to the emerging HEVC standard and its scalable extension.
-As for the PID-based quality control algorithm, it is only network-concerned thus should be easily integrated into other streaming systems, e.g., simulcast system like DASH.
-Another direction of future work is to carry out some subjective tests, demonstrating the performance of the proposed system from the perceived quality point of view.
+Experimental results show that the method can achieve PSNR gain of up to 0.5 dB compared to the JSVM QL extractor under the same bitrate constraint, also with the same computational complexity.
+The PID-based quality control algorithm has a flexible mechanism to determine the suitable quality level for transmission so that it provides an accurate and swift response to the bandwidth change.
+Compared to the original algorithm in DSS, this algorithm has reduced quality fluctuation significantly to improve audience satisfaction.
+The proposed SVC adaptive streaming system integrated with these two solutions performs well in terms of automatically adapting to the user's bandwidth fluctuation, and it is able to provide the user a better watching experience.
+
+Because the next-generation video coding standard High Efficiency Video Coding (HEVC) \cite{HEVC} adopts the same coding framework as its predecessor H.264/AVC, we expect to apply this paper's model and approach of bitstream extraction to the emerging HEVC standard and its scalable extension.
+As for the PID-based quality control algorithm, it is only network-concerned and thus should be easily integrated into other streaming systems, e.g., a simulcast system such as DASH.
+Another direction for future work is to carry out some subjective tests, demonstrating the performance of the proposed system from the perceived quality point of view.
 

### 2016-01-12 tmm.tex
Add funding information and author biographies

@@
 \author{Shengbin~Meng, Jun~Sun, {\em Member, IEEE}, Yizhou~Duan and Zongming~Guo, {\em Member, IEEE} % <-this % stops a space
-\thanks{Manuscript received July 15, 2015; revised December 3, 2015.}
+\thanks{Manuscript received July 15, 2015; revised December 3, 2015 and January 12, 2016.
+This work was supported by  National Key Technology R\&D Program of China under Grant 2015AA011605 and National Natural Science Foundation of China under contract No.
+61271020.}
 \thanks{The authors are with the Institute of Computer Science and Technology, Peking University, Beijing%
-, 100080, China (Email: mengshengbin@pku.edu.cn, sunjun@pku.edu.cn, duanyizhou@pku.edu.cn, guozongming@pku.edu.cn; Phone: +86 1082529615; Fax: +86 1082529207). Jun Sun is the corresponding author.}}
+, 100080, China (email: mengshengbin@pku.edu.cn, sunjun@pku.edu.cn, duanyizhou@pku.edu.cn, guozongming@pku.edu.cn).
+Jun Sun and Zongming Guo are also with the Cooperative Medianet Innovation Center, Shanghai, China.
+Jun Sun is the corresponding author.}}
 
@@
 
-\balance
+% biography section
+% 
+% If you have an EPS/PDF photo (graphicx package needed) extra braces are
+% needed around the contents of the optional argument to biography to prevent
+% the LaTeX parser from getting confused when it sees the complicated
+% \includegraphics command within an optional argument. (You could create
+% your own custom macro containing the \includegraphics command to make things
+% simpler here.)
+
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{ShengbinMeng.jpg}}]{Shengbin Meng}
+received the B.E.
+degree in automation engineering from Tsinghua University, Beijing, China, in 2011.
+He is currently working towards the Ph.D.
+degree in computer science at the Institute of Computer Science and Technology, Peking University, Beijing, China.
+
+His current research interests include video coding, codec implementation and optimization, video streaming, and multimedia applications.
+\end{IEEEbiography}
+
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{JunSun.jpg}}]{Jun Sun}
+(M’07) received the B.S.
+degree in computer science from the University of Science and Technology Beijing, Beijing, China, in 1999, and the Ph.D.
+degree in computer science from the Institute of Computing Technology, Chinese Academy of Sciences, Beijing, China, in 2006.
+
+From 2006 to 2008, he was a Post-Doctorate with the Institute of DigitalMedia, EECS, Peking University, Beijing, China.
+He then joined the Institute of Computer Science and Technology, Peking University, Beijing, China, where he is currently an Associate Professor.
+His research interests include scalable video coding, rate-distortion analysis, video transcoding, video streaming, and video scheduling in wireless networks.
+He has published over 30 technical articles in referred journals and proceedings in the areas of video coding and analysis.
+\end{IEEEbiography}
+
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{YizhouDuan.jpg}}]{Yizhou Duan}
+received the B.S. degree and the Ph.D degree in computer science from Peking University, Beijing, China, in 2009 and 2015, respectively. He is currently working for Strongene Ltd., Beijing, China.
+
+His current research interests include video coding, codec implementation and optimization, scalable video systems, and rate-distortion analysis.
+\end{IEEEbiography}
+
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{ZongmingGuo.jpg}}]{Zongming Guo}
+(M’09) received the B.S. degree in mathematics, and the M.S. and Ph.D. degrees in computer science from Peking University, Beijing, China, in 1987, 1990, and 1994, respectively.
+
+He is currently a Professor with the Institute of Computer Science and Technology, Peking University. His current research interests include video coding, processing, and communication.
+
+Dr.
+Guo is the Executive Member of the China-Society of Motion Picture and Television Engineers.
+He was a recipient of the First Prize of the State Administration of Radio Film and Television Award in 2004, the First Prize of the Ministry of Education Science and Technology Progress Award in 2006, the Second Prize of the National Science and Technology Award in 2007, the Wang Xuan News Technology Award and the Chia Tai Teaching Award in 2008, the Government Allowance granted by the State Council in 2009, and the Distinguished Doctoral Dissertation Advisor Award of Peking University in 2012 and 2013.
+
+\end{IEEEbiography}
+
+% if you will not have a photo at all:
+%\begin{IEEEbiographynophoto}{John Doe}
+%Biography text here.
+%\end{IEEEbiographynophoto}
+
+% insert where needed to balance the two columns on the last page with
+% biographies
+%\newpage
+
+% You can push biographies down or up by placing
+% a \vfill before or after them. The appropriate
+% use of \vfill depends on what kind of text is
+% on the last page and whether or not the columns
+% are being equalized.
+
+%\vfill
+
+% Can be used to pull up biographies so that the bottom of the last one
+% is flush with the other column.
+%\enlargethispage{-5in}
 

### 2016-01-12 tmm.tex
Make the content fit into 13 pages

@@
 , 100080, China (email: mengshengbin@pku.edu.cn, sunjun@pku.edu.cn, duanyizhou@pku.edu.cn, guozongming@pku.edu.cn).
-Jun Sun and Zongming Guo are also with the Cooperative Medianet Innovation Center, Shanghai, China.
+Jun Sun and Zongming Guo are also with the Cooperative Medianet Innovation Center, Shanghai, 200240, China.
 Jun Sun is the corresponding author.}}
@@
 As an effective and flexible control technique, PID control has been used to solve many kinds of control problems.
-In the area of video coding, we notice that PID is utilized to design rate control algorithms (rate control in video coding mainly involves adjusting the encoding parameters for every frame, so that the bits are appropriately allocated and the desired bitrate is achieved) \cite{Wong04}\cite{Yang10}.
-We also notice that some researchers have proposed a theoretical model or middle-ware framework for QoS adaptation \cite{Li98}\cite{Li99}, with PID as the basic control scheme.
+In the area of video coding, we notice that PID is utilized to design rate control algorithms (rate control in video coding mainly involves adjusting the encoding parameters for every frame, so that the bits are appropriately allocated and the desired bitrate is achieved) \cite{Wong04}.
+We also notice that some researchers have proposed a theoretical model or middle-ware framework for QoS adaptation \cite{Li98} \cite{Li99}, with PID as the basic control scheme.
 However, we have not found any paper that integrates the PID method into the quality control of video streaming.
@@
 
-As is introduced above, the \textit{actual\_check interval ratio} serves as the process variable in this PID-based quality control algorithm.
 In normal PID control, the controller output is calculated using the proportion, integral and differential of the error between the process variable and the setpoint, as shown in (\ref{eq:pid-output}).
@@
 \subfloat[City]{
-\includegraphics[width=0.45\textwidth]{City.jpg}
+\includegraphics[width=0.42\textwidth]{City.jpg}
 \label{fig:City}}
 \subfloat[Foreman]{
-\includegraphics[width=0.45\textwidth]{Foreman.jpg}
+\includegraphics[width=0.42\textwidth]{Foreman.jpg}
 \label{fig:Foreman}}
@@
 \subfloat[Harbour]{
-\includegraphics[width=0.45\textwidth]{Harbour.jpg}
+\includegraphics[width=0.42\textwidth]{Harbour.jpg}
 \label{fig:Harbour}}
 \subfloat[Soccer]{
-\includegraphics[width=0.45\textwidth]{Soccer.jpg}
+\includegraphics[width=0.42\textwidth]{Soccer.jpg}
 \label{fig:Soccer}}
@@
 \subfloat[Average quality level of different control algorithms]{
-\includegraphics[width=0.42\textwidth]{Quality-all.png}
+\includegraphics[width=0.45\textwidth]{Quality-all.png}
 \label{fig:quality-all}}
 \subfloat[Quality level variance of different control algorithms]{
-\includegraphics[width=0.42\textwidth]{Variance-all.png}
+\includegraphics[width=0.45\textwidth]{Variance-all.png}
 \label{fig:variance-all}}
@@
 \subfloat[Average quality level of the PID and PDF control algorithms]{
-\includegraphics[width=0.42\textwidth]{Quality-two.png}
+\includegraphics[width=0.45\textwidth]{Quality-two.png}
 \label{fig:quality-two}}
 \subfloat[Quality level variance of the PID and PDF control algorithms]{
-\includegraphics[width=0.42\textwidth]{Variance-two.png}
+\includegraphics[width=0.45\textwidth]{Variance-two.png}
 \label{fig:variance-two}}
@@
 
-\bibitem{Yang10}
-J. Yang, Y. Sun, Y. Zhou, S. Sun, ``Incremental rate control for H.264 scalable video coding'', {\em IEEE Global Telecommunications Conference}, Miami, Florida, Dec. 2010.
-
 \bibitem{Li98}

### 2016-01-12 tmm.tex
Add note for the bandwidth range

@@
 We simulate the bandwidth fluctuation by adjusting the bandwidth around a certain level.
-We set this level from 400 to 1400 kbps to reflect different average bandwidth values.
+We set this level from 400 to 1400 kbps to reflect different average bandwidth values (note that the bandwidth may reach a value lower than 400 kbps or higher than 1400 kbps since the level values are averages instead of bounds; in other words, the covered bandwidth range is larger than [400, 1400]).
 The simulation is implemented with NetLimiter 3 \cite{Netlimiter}, where the bandwidth varies randomly and intense fluctuations are observed.
@@
 \subfloat[Average quality level of the PID and PDF control algorithms]{
-\includegraphics[width=0.45\textwidth]{Quality-two.png}
+\includegraphics[width=0.42\textwidth]{Quality-two.png}
 \label{fig:quality-two}}
 \subfloat[Quality level variance of the PID and PDF control algorithms]{
-\includegraphics[width=0.45\textwidth]{Variance-two.png}
+\includegraphics[width=0.42\textwidth]{Variance-two.png}
 \label{fig:variance-two}}

### 2016-01-12 response-r2.txt
Add response for reviewer comments of R1

Response to the reviewer comments of Paper MM-006412-R1: Adaptive Video Streaming with Optimized Bitstream Extraction and PID-based Quality Control by Shengbin Meng, Jun Sun, Yizhou Duan and Zongming Guo.

We would like to thank the reviewers for their help to make this paper better. We would also like to thank the associate editor for coordinating the review process. We have read the reviewer comments carefully, and tried to follow the suggestions as closely as possible. In this revision, we have also used a professional editing service to help refine and polish this paper regarding English usage.

Reviewer: 1

The reviewer is happy with the revised version of the paper and the authors¡¯ response to the reviewer¡¯s comments. The reviewer would recommend the paper to be accepted with minor corrections as listed below.

1. The reviewer is still not able to access the website (www.7dlive.com) which was mentioned in the abstract of the paper. The reviewer would suggest the authors double check the website¡¯s stability and accessibility. If the work¡¯s practical effectiveness (the suggested website to demo the proposed adaptive video streaming system) could not be checked or verified by others, the reviewer would suggest the authors remove this part of claim in the abstract and/or in the body of the paper.

Response:

In this revision, we have followed the suggestion and removed the claims about the website from this paper.

2. Typos, e.g. Table II, caption, the proposed algorith => algorithm

In future submission for a revised paper, it would be better if the authors can mark out the part of contents which are updated/added in response to reviewers¡¯ comments.

Response:

We have used a professional editing service to polish the language of this paper so that grammar flaws and typos (including the mentioned one) are corrected.

This revision includes many small updates about language usage as a result of the editing service, so it may be not appropriate to mark them in this response. We will follow your suggestion in future submission for a revised paper.

Thank you very much.

Reviewer: 2

The authors have successfully addressed all the comments I raised previously. I appreciate their efforts on the revision, and do not have any further comments.

Response:

Thank you very much.

Reviewer: 3

The authors have modified most of the parts mentioned in the first review. And the demonstration is satisfactory. The authors still need to discuss more on the robustness of the PID controller. Since the bandwidth fluctuation in the simulation is from 400kbps to 1400kbps, which is quite limited, the influence of large variance is not clear. The authors may need to do simulation on larger variance.

Response:

The values (400kbps, 1400kbps, etc.) in our simulation are average/mean values around which the bandwidth fluctuates, rather than the lower or upper bounds. The actual bandwidth can reach a value lower than 400kbps or higher than 1400kbps during the fluctuation. Therefore, the covered bandwidth range is actually larger than [400, 1400]. Robustness and performance of the proposed algorithm are verified in this range. More simulations/experiments can be performed to check the extreme cases in the future work. In this revision, we have added clarifications about the bandwidth fluctuation range (see second paragraph of Section V-B), and more discussion on the robustness of the PID controller (see last paragraph of Section IV-D).

Thank you very much.

### 2016-01-13 response-r2.txt
Edit response to mention the receipt

@@
 We have read the reviewer comments carefully, and tried to follow the suggestions as closely as possible.
-In this revision, we have also used a professional editing service to help refine and polish this paper regarding English usage.
+In this revision, we have also used a professional editing service to help refine and polish this paper regarding English usage (receipt from the editing service is attached).
 
@@
 
-We have used a professional editing service to polish the language of this paper so that grammar flaws and typos (including the mentioned one) are corrected.
+We have used a professional editing service to polish this paper so that grammar flaws and typos (including the mentioned one) are corrected.
 

### 2016-02-23 tmm.tex
Make the figures appear in order
Prepare for final submission
Final single column

@@
 %
-%\documentclass[journal,draftclsnofoot,onecolumn]{IEEEtran}
-\documentclass[journal]{IEEEtran}
+\documentclass[journal,draftclsnofoot,onecolumn]{IEEEtran}
+%\documentclass[journal]{IEEEtran}
 %
@@
 \author{Shengbin~Meng, Jun~Sun, {\em Member, IEEE}, Yizhou~Duan and Zongming~Guo, {\em Member, IEEE} % <-this % stops a space
-\thanks{Manuscript received July 15, 2015; revised December 3, 2015 and January 12, 2016.
+\thanks{Manuscript received July 15, 2015; revised December 3, 2015 and January 12, 2016; accepted February 21, 2016.
 This work was supported by  National Key Technology R\&D Program of China under Grant 2015AA011605 and National Natural Science Foundation of China under contract No.
 61271020.}
+\thanks{Copyright (c) 2013 IEEE.
+Personal use of this material is permitted.
+However, permission to use this material for any other purposes must be obtained from the IEEE by sending a request to pubs-permissions@ieee.org.}
 \thanks{The authors are with the Institute of Computer Science and Technology, Peking University, Beijing%
@@
 Jun Sun and Zongming Guo are also with the Cooperative Medianet Innovation Center, Shanghai, 200240, China.
-Jun Sun is the corresponding author.}}
+Jun Sun is the corresponding author.}
+}
 
@@
 \centering
-\includegraphics[width = 0.9\linewidth]{GOP-Structure.png}
+\includegraphics[width = 0.8\linewidth]{GOP-Structure.png}
 \caption{Group of pictures (GOP) in SVC \label{fig:GOP_Structure}}
@@
 \centering
-\includegraphics[width = 0.9\linewidth]{ModelVerification.png}
+\includegraphics[width = 0.8\linewidth]{ModelVerification.png}
 \caption{Comparison of the actual and the estimated distortion for sequence {\em Foreman} \label{fig:model_verification}}
@@
 \subfloat[City]{
-\includegraphics[width=0.42\textwidth]{City.jpg}
+\includegraphics[width=0.40\textwidth]{City.jpg}
 \label{fig:City}}
 \subfloat[Foreman]{
-\includegraphics[width=0.42\textwidth]{Foreman.jpg}
+\includegraphics[width=0.40\textwidth]{Foreman.jpg}
 \label{fig:Foreman}}
@@
 \subfloat[Harbour]{
-\includegraphics[width=0.42\textwidth]{Harbour.jpg}
+\includegraphics[width=0.40\textwidth]{Harbour.jpg}
 \label{fig:Harbour}}
 \subfloat[Soccer]{
-\includegraphics[width=0.42\textwidth]{Soccer.jpg}
+\includegraphics[width=0.40\textwidth]{Soccer.jpg}
 \label{fig:Soccer}}
@@
 
-Since STP and LTP have their own limitations, we implement the complete PID-based quality control algorithm, which can both reduce the quality variance and improve the average quality level.
-From the results shown in Fig.
-\ref{fig:performance-two}, we can conclude that when integrated with the integral part and the derivative part, the effect of the proportional part is not as aggressive as that in STP.
-An obvious proof can be found in Fig.
-\ref{fig:variance-two}, which clearly shows that the proposed PID quality control algorithm achieves a lower quality variance compared to the PDF algorithm.
-Table \ref{tab:improvement} lists the statistical experimental results for these four quality control algorithms, in which the PID-based control algorithm has shown its advantage over the others, especially in reducing the quality fluctuation.
-It can be seen that, compared to PDF, the PID-based quality control algorithm improves 8.6\% in video quality with a 24.8\% reduction in quality fluctuation.
-The video quality fluctuation of the four control algorithms, when the bandwidth fluctuates around 800 kbps, is shown in Fig.
-\ref{fig:fluctuation}, from which we can observe a more stable video quality in the proposed PID quality control algorithm.
-
 \begin{figure*}[t]
@@
 \subfloat[Average quality level of different control algorithms]{
-\includegraphics[width=0.42\textwidth]{Quality-all.png}
+\includegraphics[width=0.40\textwidth]{Quality-all.png}
 \label{fig:quality-all}}
 \subfloat[Quality level variance of different control algorithms]{
-\includegraphics[width=0.42\textwidth]{Variance-all.png}
+\includegraphics[width=0.40\textwidth]{Variance-all.png}
 \label{fig:variance-all}}
@@
 \subfloat[Average quality level of the PID and PDF control algorithms]{
-\includegraphics[width=0.42\textwidth]{Quality-two.png}
+\includegraphics[width=0.40\textwidth]{Quality-two.png}
 \label{fig:quality-two}}
 \subfloat[Quality level variance of the PID and PDF control algorithms]{
-\includegraphics[width=0.42\textwidth]{Variance-two.png}
+\includegraphics[width=0.40\textwidth]{Variance-two.png}
 \label{fig:variance-two}}
@@
 
+Since STP and LTP have their own limitations, we implement the complete PID-based quality control algorithm, which can both reduce the quality variance and improve the average quality level.
+From the results shown in Fig.
+\ref{fig:performance-two}, we can conclude that when integrated with the integral part and the derivative part, the effect of the proportional part is not as aggressive as that in STP.
+An obvious proof can be found in Fig.
+\ref{fig:variance-two}, which clearly shows that the proposed PID quality control algorithm achieves a lower quality variance compared to the PDF algorithm.
+Table \ref{tab:improvement} lists the statistical experimental results for these four quality control algorithms, in which the PID-based control algorithm has shown its advantage over the others, especially in reducing the quality fluctuation.
+It can be seen that, compared to PDF, the PID-based quality control algorithm improves 8.6\% in video quality with a 24.8\% reduction in quality fluctuation.
+The video quality fluctuation of the four control algorithms, when the bandwidth fluctuates around 800 kbps, is shown in Fig.
+\ref{fig:fluctuation}, from which we can observe a more stable video quality in the proposed PID quality control algorithm.
+
 \begin{figure}
 \centering
-\includegraphics[width = 0.9\linewidth]{Fluctuation.png}
+\includegraphics[width = 0.8\linewidth]{Fluctuation.png}
 \caption{Video quality fluctuation with time \label{fig:fluctuation}}

### 2016-03-22 tmm.tex
Revert "Final single column"
This reverts commit 2e8eebe0417dc7e6d06c5b277e405902af328261.
Final double column
Correct a bibitem
Proof

@@
 %
-\documentclass[journal,draftclsnofoot,onecolumn]{IEEEtran}
-%\documentclass[journal]{IEEEtran}
+%\documentclass[journal,draftclsnofoot,onecolumn]{IEEEtran}
+\documentclass[journal]{IEEEtran}
 %
@@
 61271020.}
-\thanks{Copyright (c) 2013 IEEE.
+\thanks{Copyright (c) 2016 IEEE.
 Personal use of this material is permitted.
@@
 The state-of-the-art solutions for avoiding playback pause in the client media player mainly focus on how to select and schedule the video packets.
-In \cite{Gao06}, K.
-Gao et al.
+In \cite{Gao06}, Gao et al.
 proposed a priority-based scheduling strategy, which guarantees that packets of higher importance will be transmitted earlier.
@@
 \end{equation}
-where $i$ refers to an enhancement packet in the set $I_1$, $c_i$ is a vector containing coefficients within the enhancement packet $i$, ${\rm\bf T_i}$ is the transform matrix depending on the QP value of $i$ and ${\rm\bf T}_i \cdot c_i$ gives the residual values decoded from $i$.
+where $i$ refers to an enhancement packet in the set $I_1$, $c_i$ is a vector containing coefficients within the enhancement packet $i$, ${\rm\bf T}_i$ is the transform matrix depending on the QP value of $i$ and ${\rm\bf T}_i \cdot c_i$ gives the residual values decoded from $i$.
 
@@
 \bibitem{Schierl10}
-Y.
-Schierl, R.
-Sanchez, C.
-Globisch, Hellge, and T.
+T.
+Schierl, Y.S.
+De La Fuente, R.
+Globisch, C.
+Hellge and T.
 Wiegand, ``Priority-based media delivery using SVC with RTP and HTTP streaming'', {\em Multimedia Tools And Applications}, vol.
